### 2016-09-23 cbm-rbd-paper.tex
actually add the tex file

\documentclass[authoryear]{elsarticle}

% ------------ packages -------------

\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{graphicx}
\usepackage[english]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{booktabs}
\usepackage{tikz}

\usepackage{url}
\usepackage[bookmarks]{hyperref}

%\usetikzlibrary{shapes.misc,fit}
\usetikzlibrary{%
   arrows,%
   calc,%
   fit,%
   patterns,%
   plotmarks,%
   shapes.geometric,%
   shapes.misc,%
   shapes.symbols,%
   shapes.arrows,%
   shapes.callouts,%
   shapes.multipart,%
   shapes.gates.logic.US,%
   shapes.gates.logic.IEC,%
   er,%
   automata,%
   backgrounds,%
   chains,%
   topaths,%
   trees,%
   petri,%
   mindmap,%
   matrix,%
   calendar,%
   folding,%
   fadings,%
   through,%
   patterns,%
   positioning,%
   scopes,%
   decorations.fractals,%
   decorations.shapes,%
   decorations.text,%
   decorations.pathmorphing,%
   decorations.pathreplacing,%
   decorations.footprints,%
   decorations.markings,%
   shadows}

%\usepackage{hyperref}
%\usepackage[bookmarks]{hyperref}
%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}

% ------------ custom defs -------------

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}
\newcommand{\posrealszero}{\reals_{\ge 0}}
\newcommand{\naturals}{\mathbb{N}}

\newcommand{\dd}{\,\mathrm{d}}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{{\bm#1}}

\newcommand{\uz}{^{(0)}} % upper zero
\newcommand{\un}{^{(n)}} % upper n
\newcommand{\ui}{^{(i)}} % upper i

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ol}[1]{\overline{#1}}

\newcommand{\Rsys}{R_\text{sys}}
\newcommand{\lRsys}{\ul{R}_\text{sys}}
\newcommand{\uRsys}{\ol{R}_\text{sys}}

\newcommand{\Fsys}{F_\text{sys}}
\newcommand{\lFsys}{\ul{F}_\text{sys}}
\newcommand{\uFsys}{\ol{F}_\text{sys}}

\def\Rsys{R_\text{sys}}
\def\Tsys{T_\text{sys}}

\newcommand{\E}{\operatorname{E}}
\newcommand{\V}{\operatorname{Var}}
\newcommand{\wei}{\operatorname{Wei}} % Weibull Distribution
\newcommand{\ig}{\operatorname{IG}}   % Inverse Gamma Distribution

\newcommand{\El}{\ul{\operatorname{E}}}
\newcommand{\Eu}{\ol{\operatorname{E}}}

\def\yz{y\uz}
\def\yn{y\un}
%\def\yi{y\ui}
\newcommand{\yfun}[1]{y^{({#1})}}
\newcommand{\yfunl}[1]{\ul{y}^{({#1})}}
\newcommand{\yfunu}[1]{\ol{y}^{({#1})}}

\def\ykz{y\uz_k}
\def\ykn{y\un_k}

\def\yzl{\ul{y}\uz}
\def\yzu{\ol{y}\uz}
\def\ynl{\ul{y}\un}
\def\ynu{\ol{y}\un}
\def\yil{\ul{y}\ui}
\def\yiu{\ol{y}\ui}

\def\ykzl{\ul{y}\uz_k}
\def\ykzu{\ol{y}\uz_k}
\def\yknl{\ul{y}\un_k}
\def\yknu{\ol{y}\un_k}

\newcommand{\ykzfun}[1]{y\uz_{#1}}
\newcommand{\ykzlfun}[1]{\ul{y}\uz_{#1}}
\newcommand{\ykzufun}[1]{\ol{y}\uz_{#1}}

\def\nz{n\uz}
\def\nn{n\un}
%\def\ni{n\ui}
\newcommand{\nfun}[1]{n^{({#1})}}
\newcommand{\nfunl}[1]{\ul{n}^{({#1})}}
\newcommand{\nfunu}[1]{\ol{n}^{({#1})}}

\def\nkz{n\uz_k}
\def\nkn{n\un_k}
\newcommand{\nkzfun}[1]{n\uz_{#1}}
\newcommand{\nkzlfun}[1]{\ul{n}\uz_{#1}}
\newcommand{\nkzufun}[1]{\ol{n}\uz_{#1}}

\def\nzl{\ul{n}\uz}
\def\nzu{\ol{n}\uz}
\def\nnl{\ul{n}\un}
\def\nnu{\ol{n}\un}
\def\nil{\ul{n}\ui}
\def\niu{\ol{n}\ui}

\def\nkzl{\ul{n}\uz_k}
\def\nkzu{\ol{n}\uz_k}
\def\nknl{\ul{n}\un_k}
\def\nknu{\ol{n}\un_k}

\def\taut{\tau(\vec{t})}
\def\ttau{\tilde{\tau}}
\def\ttaut{\ttau(\vec{t})}

\def\MZ{\mathcal{M}\uz}
\def\MN{\mathcal{M}\un}

\def\MkZ{\mathcal{M}\uz_k}
\def\MkN{\mathcal{M}\un_k}

\def\PkZ{\Pi\uz_k}
\def\PkN{\Pi\un_k}
\newcommand{\PZi}[1]{\Pi\uz_{#1}}

\def\tnow{t_\text{now}}
\def\tpnow{t^+_\text{now}}

% ------------ options -------------

\allowdisplaybreaks

\journal{RESS}

\begin{document}

% ------------ frontmatter -------------

\begin{frontmatter}
\title{Condition-Based Maintenance for Systems based on Bayesian Component Models***}

\author[tue]{Gero Walter}
\ead{g.m.walter@tue.nl}
\author[tue]{Simme Douwe Flapper}
\ead{s.d.p.flapper@tue.nl}

\address[tue]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, Netherlands}

\begin{abstract}
CBM when no (continuous) degradation signal for system available, but status of components observable (works yes/no)

use method from asce-asme paper:
gives delay time distribution, base maintenance decision directly on that
(via threshold for reliability?)

Bayesian approach allows
component models to include expert info, test data (if available), and status of components in the running system
(write down explicit formula for test data including censored observations)

main message: can do cbm without degradation signal,
useful for redundant systems,
method reflects aleatory and epistemic uncertainty in all information sources
\end{abstract}

\begin{keyword}
condition-based maintenance \sep system reliability \sep delay time model \sep survival signature \sep imprecise probability \sep p-box
\end{keyword}
\end{frontmatter}

% ------------ manuscript -------------

\section{Introduction}
\label{intro}

CBM usually with directly or indirectly observable continuous measurable condition / degradation signal,
delay time (time till failure) via distance of current signal level to fixed known failure threshold
%but in practice threshold often not known

here we propose a different approach to CBM: if no degradation signal for system available,
use system layout (reliability block diagram) and information on components' status:
need only to observe when a component fails,
and expert information about expected component failure times.

i.e., model not for a degradation signal of the system, but for component lifetimes:
we use the well-known Weibull model for component lifetimes.
To keep the model simple, we assume known shape parameter,
and that components fail independently.
these simplifying assumptions might not hold in practice,
then model can serve as approximation.

The Bayesian approach to the Weibull model allows to integrate, for each component type,
three sources of information: expert knowledge, data from component tests,
and status of components in the monitored system, i.e., current system condition.

Furthermore, our method appropriately reflects epistemic uncertainty,
by using parametric p-boxes, an imprecise probability model, for the component models.

epistemic vs. aleatoric uncertainty: big topic in reliability and risk

***NASA Langley UQ challenge, illustration that uniform distribution does not express ignorance (Edoardo Patelli)***

The proposed system delay time model adequately reflects uncertainty in the delay time distribution
according to the current system status,
in particular making more cautious predictions when failure behaviour in the monitored system
seems to deviate from what is expected from expert knowledge and test data.

\section*{Acknowledgements}

CAMPI

%\bibliographystyle{elsarticle-num}
%\bibliography{refs}

\end{document}

### 2016-09-27 cbm-rbd-paper.tex
Wang and Jia discussion

@@
 
-i.e., model not for a degradation signal of the system, but for component lifetimes:
+i.e., parametric model not for a degradation signal of the system or delay time, but for component lifetimes:
 we use the well-known Weibull model for component lifetimes.
@@
 
-***NASA Langley UQ challenge, illustration that uniform distribution does not express ignorance (Edoardo Patelli)***
+***refer to Terje Aven, NASA Langley UQ challenge, illustration that uniform distribution does not express ignorance (Edoardo Patelli)***
 
@@
 seems to deviate from what is expected from expert knowledge and test data.
+
+***to add timing of next inspection into the model we would need to add interval-censored data
+(failure has happened between last and current inspection)
+
+***3-param Weibull for repaired/exchanged components? Means `just' to shift time?
+(introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as `unshifted' component type)
+
+***Wang \& Jia 2007 give a model that uses Bayesian updating,
+but the actual model is different:
+
+They have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
+model for delay time (time between defect and failure) is Weibull $h \sim \wei(\alpha,\beta)$,
+and each of $\lambda, \alpha, \beta$ has a Gamma prior distribution.
+The expected overall cost rate is then used to find a cost-optimal inspection interval.
+For this they assume that failures are immediately repaired,
+and defects found in an inspection are then repaired.
+Is this really CBM?
+
+They use prior predictive distributions for certain statistics (number of defects, number of failures, \ldots between $0$ and $T$)
+to obtain prior values for the Gamma hyperparameters,
+by solving prior predictive equations -- but give no detail on how they actually do this.
+
+In the end they actually do not advocate to calculate the posterior expected cost rate (15),
+but rather plug in posterior estimates for $\lambda, \alpha, \beta$,
+so neglecting uncertainty in estimation.
+%They also do not indicate how sensitive
+
+We do not assume a parametric distribution for delay time,
+it rather arises as a consequence of the system layout and component failure distributions.
+
+Expert input in our model is, for each component type,
+Weibull shape parameter, range of expected failure time (translated to scale parameter),
+and range of expert info weight (how sure about mean failure time guess).
+By using ranges we do a systematic sensitivity analysis.
+
+Our model gives the lower and upper delay time distribution at $\tnow$,
+so takes current system condition into account.
+We need additional criteria to indicate repair now yes/no.
+(Could indicate which failed component(s) to repair best.)
 

### 2016-09-29 cbm-rbd-paper.tex
adding refs file

@@
 
-***to add timing of next inspection into the model we would need to add interval-censored data
-(failure has happened between last and current inspection)
+Expert input in our model is, for each component type,
+Weibull shape parameter, range of expected failure time (translated to scale parameter),
+and range of expert info weight (how sure about mean failure time guess).
+By using ranges we do a systematic sensitivity analysis.
 
-***3-param Weibull for repaired/exchanged components? Means `just' to shift time?
-(introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as `unshifted' component type)
+Our model gives the lower and upper delay time distribution at $\tnow$,
+so takes current system condition into account.
 
-***Wang \& Jia 2007 give a model that uses Bayesian updating,
-but the actual model is different:
+We need additional criteria to indicate repair now yes/no.
+(Could indicate which failed component(s) to repair best.)
 
-They have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
+\subsection{Literature***}
+
+example for Bayesian method in maintenance planning: \cite{2007:wang-jia}
+
+***Wang \& Jia (2007) propose a model that uses Bayesian updating,
+but the model aims to identify an optimal inspection interval.
+This is CBM via inspections, not CBM via continuous monitoring as we aim to do.
+
+Wang \& Jia (2007) have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
 model for delay time (time between defect and failure) is Weibull $h \sim \wei(\alpha,\beta)$,
@@
 For this they assume that failures are immediately repaired,
-and defects found in an inspection are then repaired.
-Is this really CBM?
+and defects found in an inspection are repaired during inspection.
 
@@
 
-We do not assume a parametric distribution for delay time,
-it rather arises as a consequence of the system layout and component failure distributions.
+(We do not assume a parametric distribution for delay time,
+it rather arises as a consequence of the system layout and component failure distributions.)
 
-Expert input in our model is, for each component type,
-Weibull shape parameter, range of expected failure time (translated to scale parameter),
-and range of expert info weight (how sure about mean failure time guess).
-By using ranges we do a systematic sensitivity analysis.
+\section{Outlook}
 
-Our model gives the lower and upper delay time distribution at $\tnow$,
-so takes current system condition into account.
-We need additional criteria to indicate repair now yes/no.
-(Could indicate which failed component(s) to repair best.)
+*** to add timing of next inspection into the model we would need to add interval-censored data
+(failure has happened between last and current inspection)
+
+*** if repaired/exchanged components are present in system,
+the one needs to use actual ages (and not time since system startup) in parameter update,
+introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as unreplaced component type
 
@@
 
-%\bibliographystyle{elsarticle-num}
-%\bibliography{refs}
+\bibliographystyle{elsarticle-harv}
+\bibliography{refs}
 

### 2016-10-04 cbm-rbd-paper.tex
ideas for paper structure

@@
 
+\section{***summary of ASCE-ASME paper}
+
+sets of priors on component survival,
+survival signature,
+test data inclusion,
+noninformatiove censoring,
+set of system reliability curves as output,
+wider set in case of prior-data conflict
+
+\section{***extensions to ASCE-ASME paper}
+
+repaired components: separate type in survival signature,
+but same hyperparameter learning.
+
+\section{***from (set of) survival curves to maintenance decision}
+
+infinite-horizon cost rate (discounted as well?)
+like in age-based policy:
+this indicates in how much time from now one should repair the system
+
+\begin{align*}
+g(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}
+\end{align*}
+
+and $\tau^* = \arg\min g(\tau)$ is the cost-optimal repair time from now
+
+sets of $\Rsys(t)$: need to determine sets of $g(\tau)$.
+for each $\tau$, fix $\Rsys(\tau) \in [\lRsys(\tau), \uRsys(\tau)]$ and optimize $I(\tau) = \int_0^\tau \Rsys(t) \dd t$:
+$\ol{I}(\tau)$ by $\uRsys(t)$, $\ul{I}(\tau)$ by $\lRsys(t)$ until level of $\Rsys(\tau)$.
+
+from sets of $g(\tau)$ to (set of) $\tau^*$:
+worst case, best case, interval (how?)
+
 \section{Outlook}

### 2016-10-05 cbm-rbd-paper.tex
second ref, some musings

--- 2016-09-29 cbm-rbd-paper.tex
@@
 Our model gives the lower and upper delay time distribution at $\tnow$,
-so takes current system condition into account.
+taking current system condition into account.
 
@@
 
-example for Bayesian method in maintenance planning: \cite{2007:wang-jia}
+Example for Bayesian method in maintenance planning: \cite{2007:wang-jia}
 
@@
 
+\begin{scriptsize}
 Wang \& Jia (2007) have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
@@
 so neglecting uncertainty in estimation.
-%They also do not indicate how sensitive
-
 (We do not assume a parametric distribution for delay time,
 it rather arises as a consequence of the system layout and component failure distributions.)
+
+\end{scriptsize}
+
+Example for Bayesian method in CBM with continuous monitoring: \cite{2011:elwany-et-al}
+(exponential degradation model, whose parameters $\theta'$ and $\beta$ each have a prior
+which is updated using the degradation signal history,
+and use total expected infinite-horizon discounted cost to determine the maintenance policy)
+
+\section{***summary of ASCE-ASME paper method}
+
+sets of priors on component survival,
+survival signature,
+test data inclusion,
+noninformatiove censoring,
+set of system reliability curves as output,
+wider set in case of prior-data conflict
+
+\section{***extensions to ASCE-ASME paper}
+
+repaired components: separate type in survival signature,
+but same hyperparameter learning (using actual age).
+
+\section{***from (set of) survival curves to maintenance decision}
+
+infinite-horizon cost rate $g(\tau)$ (discounted as well?)
+like in age-based policy:
+this indicates in how much time from now ($\tnow$) it is economical to repair the system
+\begin{align*}
+g(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}
+\end{align*}
+and $\tau^* = \arg\min g(\tau) - \tnow$ is the cost-optimal repair time from now
+($\Rsys(\cdot)$ is always in terms of time since system startup)
+
+Sets of $\Rsys(t)$: need to determine sets of $g(\tau)$.
+for each $\tau$, fix $\Rsys(\tau) \in [\lRsys(\tau), \uRsys(\tau)]$ and optimize $I(\tau) = \int_0^\tau \Rsys(t) \dd t$:
+\begin{itemize}
+\item nonpar.: $\ol{I}(\tau)$ by $\uRsys(t)$, $\ul{I}(\tau)$ by $\lRsys(t)$ until level of $\Rsys(\tau)$.
+\item par.: optimize over $\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right], \ldots, \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]$\\
+(is $g(\tau)$ indeed monotone in $\ykzfun{1}, \ldots \ykzfun{K}$?)
+\end{itemize}
+
+From sets of $g(\tau)$ to (set of) $\tau^*$:
+worst case, best case, interval (how?)
+
+Or, alternatively, simple 95\% policy? repair time from now such that system failure probability is below 5\%
+
+\section{Case study / numerical example}
+
+what system layout? something that demonstrates the power of the method (complex layout) or something simple?
+
+complex: e.g., bridge system where each of the four elements is a two out of three, and the bridge element is a two-parallel.
 
@@
 
+\section*{Bibliography}
+
 \bibliographystyle{elsarticle-harv}

### 2016-10-05 cbm-rbd-paper.tex
many things

--- 2016-09-29 cbm-rbd-paper.tex
@@
 
+\newcommand{\Tsys}{T_\text{sys}}
+
 \newcommand{\Rsys}{R_\text{sys}}
@@
 
-\def\Rsys{R_\text{sys}}
-\def\Tsys{T_\text{sys}}
+\newcommand{\lgt}{\ul{g}}
+\newcommand{\ugt}{\ol{g}}
 
@@
 \begin{frontmatter}
-\title{Condition-Based Maintenance for Systems based on Bayesian Component Models***}
+\title{Condition-Based Maintenance for Systems based on Bayesian P-Box Component Models***}
 
@@
 use method from asce-asme paper:
-gives delay time distribution, base maintenance decision directly on that
-(via threshold for reliability?)
+gives RUL in form of a p-box (set of distributions), base maintenance decision directly on that
+(via upper expected cost rate)
 
@@
 component models to include expert info, test data (if available), and status of components in the running system
-(write down explicit formula for test data including censored observations)
 
-main message: can do cbm without degradation signal,
-useful for redundant systems,
+main message: can do CBM for systems without degradation signal,
+especially useful for redundant systems,
 method reflects aleatory and epistemic uncertainty in all information sources
@@
 \begin{keyword}
-condition-based maintenance \sep system reliability \sep delay time model \sep survival signature \sep imprecise probability \sep p-box
+condition-based maintenance \sep system reliability \sep remaining useful life \sep survival signature \sep imprecise probability \sep p-box
 \end{keyword}
@@
 
-CBM usually with directly or indirectly observable continuous measurable condition / degradation signal,
-delay time (time till failure) via distance of current signal level to fixed known failure threshold
+CBM usually with directly or indirectly observable continuously measurable condition / degradation signal,
+estimated time till failure (RUL) via distance of current signal level to fixed known failure threshold.
+Inspection-based CBM via delay time model, modeling the time between detectable degradation and failure,
+again time till failure via distance of current degradation level to fixed known failure threshold,
+In both cases, maintenance decision via control limit / threshold for the signal.
 %but in practice threshold often not known
 
-here we propose a different approach to CBM: if no degradation signal for system available,
+Here we propose a different approach to CBM: if no degradation signal for system available,
 use system layout (reliability block diagram) and information on components' status:
@@
 
-i.e., parametric model not for a degradation signal of the system or delay time, but for component lifetimes:
+We use a parametric model not for a degradation signal of the system or for the delay time, but for component lifetimes:
 we use the well-known Weibull model for component lifetimes.
@@
 and that components fail independently.
-these simplifying assumptions might not hold in practice,
-then model can serve as approximation.
+These simplifying assumptions might not hold in practice,
+then the model can serve as a first approximation.
 
@@
 
-epistemic vs. aleatoric uncertainty: big topic in reliability and risk
+***epistemic vs. aleatoric uncertainty: big topic in reliability and risk
 
@@
 
-The proposed system delay time model adequately reflects uncertainty in the delay time distribution
+The proposed system RUL model adequately reflects uncertainty in the RUL distribution
 according to the current system status,
 in particular making more cautious predictions when failure behaviour in the monitored system
-seems to deviate from what is expected from expert knowledge and test data.
+seems to deviate from what is expected from expert knowledge and previous (test) data.
 
@@
 
-Our model gives the lower and upper delay time distribution at $\tnow$,
-so takes current system condition into account.
+Our model gives lower and upper bounds for the distribution of time till system failure,
+taking current (at time $\tnow$) system condition into account.
 
-We need additional criteria to indicate repair now yes/no.
-(Could indicate which failed component(s) to repair best.)
+Based on this, the additional criteria of expected cost rate is used to indicate repair now yes/no.
+(Could also indicate which failed component(s) to repair best.)
 
@@
 
-example for Bayesian method in maintenance planning: \cite{2007:wang-jia}
+Example for Bayesian method in CBM via inspections: \cite{2007:wang-jia}
+propose a model that uses Bayesian updating,
+but the model aims to identify an optimal inspection interval.
+%This is CBM via inspections, not CBM via continuous monitoring as we aim to do.
 
-***Wang \& Jia (2007) propose a model that uses Bayesian updating,
-but the model aims to identify an optimal inspection interval.
-This is CBM via inspections, not CBM via continuous monitoring as we aim to do.
-
+\begin{scriptsize}
 Wang \& Jia (2007) have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
@@
 so neglecting uncertainty in estimation.
-%They also do not indicate how sensitive
-
 (We do not assume a parametric distribution for delay time,
@@
 
+\end{scriptsize}
+
+Example for Bayesian method in CBM with continuous monitoring: \cite{2011:elwany-et-al}
+(exponential degradation model, whose parameters $\theta'$ and $\beta$ each have a prior
+which is updated using the degradation signal history,
+and use total expected infinite-horizon discounted cost to determine the maintenance policy)
+
+Example for Bayesian method in prediction of system remaining useful life: \cite{2012:sun-et-al}
+(constructs health index for a system based on sensor measurements,
+health status prediction is updated sequentially,
+leads to RUL distribution like our method,
+but no link from RUL to maintenance decision)
+
+\cite{2011:kim-et-al} develop a periodic monitoring CBM policy
+where a maintenance decision is triggered when
+a Bayesian control chart (a sequentially updated health indicator) %posterior probability that system is in a 'warning' state
+exceeds a control limit (threshold) that is determined
+by minimizing the expected average cost per time unit.
+(We use the same cost criterion, but base the maintenance decision directly on our exact RUL estimation.)
+
+***typical recent example for Bayesian network models in maintenance -- could also cover system reliabilty terrain***
+maybe Jones et al (RESS 95:3, 2010) ``The use of Bayesian network modelling for maintenance planning in a manufacturing industry'',
+or Bouaziz et al (2013) ``Towards Bayesian network methodology for predicting equipment health factor of complex semiconductor systems''
+
+\begin{scriptsize}
+Bayesian networks (BNs) are a very general method to jointly model multiple dependent random variables in a Bayesian way. 
+This needs assessments of conditional independece relations, and conditional probability models for each variable,
+the latter often in form of conditional probability tables (discrete variables).
+A Bayesian network models probabilistic relations between variables,
+unlike a reliability block diagram, which gives a deterministic relation
+between the status of components and the system state.
+
+One could model a system as a BN (each component is a variable),
+but that would add a lot of complications.
+Most algorithms for BNs assume discrete distributions,
+and do not scale well to large networks (many tasks are NP-hard).
+
+The above papers seem to use a BN to model a degradation signal or (system) health index (have to check again to be sure).
+Our approach is different, as we get an exact formulation for the system RUL directly.
+
+\end{scriptsize}
+
+\section{***summary of ASCE-ASME paper method}
+
+sets of priors on component survival,
+survival signature,
+test data inclusion
+(write down explicit formula for test data including censored observations),
+noninformatiove censoring,
+set of system reliability curves as output,
+wider set in case of prior-data conflict
+
+\section{***extensions to ASCE-ASME paper method}
+\label{sec:extensions}
+
+when repaired/replaced components are present in system,
+then one needs to use actual ages (and not time since system startup) in parameter update,
+introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as unreplaced component type
+
+repaired/replaced components require the creation of a separate type in the survival signature decomposition
+and thus the calculation of separate posterior predictive probabilities
+$P(C^k_t = l_k \mid \nkz,\ykz,\text{test data},\text{monitoring data})$,
+which use, however, the same hyperparameter learning (using actual component ages) as the `parent type'.
+
+output is a set of current system reliability curves
+taking into account the current system state,
+including the current ages of system components, 
+and the lifetime histories of all component types,
+including test data and expert assessments.
+The set of current, updated system reliability curves gives a RUL estimate
+in the form of a p-box, thus reflecting both aleatoric and epistemic uncertainty in the estimate.
+
+\section{***from (set of) reliability curves to maintenance decision}
+
+\subsection{***unit cost rate}
+
+To find the optimal moment for maintenance based on the current set of system reliability curves,
+we minimize the expected average cost per time unit,
+or unit cost rate, $g(\tau)$. (could be discounted as well, out of scope here.)
+%like in age-based policy
+This is similar to the approach by \cite{2011:kim-et-al},
+where we optimize directly the moment of maintenance $\tau$
+instead of a control limit for a control chart, or a threshold for a degradation signal.
+An advantage of our approach is that
+it indicates, for any current time $\tnow$, at which point in the future it is economical to repair the system,
+thus allowing for set-up time for maintenance work.
+
+Due to our extensions from Section~\ref{sec:extensions},
+maintenance work can consist of replacing (or returning to an as-good-as-new state) some or all failed or non-failed components,
+as arbitrary component ages can be taken into account.
+(However, computation times decrease when all components of the same type are replaced at the same time,
+as then the duplication of component types for the survival signature decomposition is not necessary.)
+
+Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
+Then the unit cost rate is, according to renewal theory, given by
+\begin{align}
+g(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}\,,
+\end{align}
+and $\tau^* = \arg\min g(\tau) - \tnow$ is the cost-optimal repair time from now
+($\Rsys(\cdot)$ is always in terms of time since system startup)
+
+\subsection{***bounds for unit cost rate}
+
+Bounds for $\Rsys(t)$ lead to bounds for $g(\tau)$.
+%For each $\tau$, fix $\Rsys(\tau) \in [\lRsys(\tau), \uRsys(\tau)]$ and optimize $I(\tau) = \int_0^\tau \Rsys(t) \dd t$
+%nonparametrically: $\ol{I}(\tau)$ by $\uRsys(t)$, $\ul{I}(\tau)$ by $\lRsys(t)$ until level of $\Rsys(\tau)$.
+Can get bounds $\lgt(\tau)$ and $\ugt(\tau)$ in the same way as bounds $\lRsys(t)$ and $\uRsys(t)$ in ASCE-ASME paper:
+need to optimize only over
+$\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right], \ldots, \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]$.
+
+This works because, like $\Rsys(t)$, also $g(\tau)$ is monotone in $\ykzfun{1}, \ldots \ykzfun{K}$:
+$\Rsys(\tau)$ is monotone in $\ykzfun{1}, \ldots \ykzfun{K}$ (ASCE-ASME paper),
+and $g(\tau)$ is monotonely decreasing in $\Rsys(\tau)$:
+
+First look at $I(\tau) := \int_0^\tau \Rsys(t) \dd t$.
+A lower bound for $I(\tau)$ is $\tau \Rsys(\tau)$ (obtained when $\Rsys(t)$ drops to $\Rsys(\tau)$ immediately after $t=0$),
+and an upper bound for $I(\tau)$ is $\tau$ (obtained when $\Rsys(t)$ remains at $1$ until immediately prior to $t = \tau$).
+Therefore, for each $\tau$ and $\Rsys(\tau)$ there exists a constant $R^* \in [\Rsys(\tau), 1]$
+such that $I(\tau) = \tau R^*$.
+Note that $R^*$ increases when $\Rsys(\tau)$ increases.
+
+Setting $\Rsys(\tau) =: R$ and $g(\tau) =: g$ to simplify notation, we get
+\begin{align*}
+g &= \frac{c_p R + c_u (1-R)}{\tau R + \tau R^*}
+   = \frac{(c_p - c_u) R + c_u}{\tau R + \tau R^*}\,.
+\end{align*}
+As $(c_p -c_u) < 0$, the enumerator of $g$ is monotonely decreasing in $R$.
+The denominator of $g$ is monotonely increasing in $R$, since $R^*$ must increase when $R$ increases.
+In total, $g$ is thus monotonely decreasing in $R$.
+
+***formulate above as theorem?
+
+\subsection{***from bounds for $g(\tau)$ to (set of) $\tau^*$:}
+
+%worst case, best case, interval (how?)
+\begin{itemize}
+\item worst case (minimax strategy): minimizing $\ugt(\tau)$ leads to $\tau^*_u$.
+\item interval dominance: for each $\tau$, we get a $g(\tau)$ interval $[\lgt(\tau), \ugt(\tau)]$.
+Throw out all $\tau$'s for which $\lgt(\tau) \ge \ugt(\tau^*_u)$.
+This will leave us with the set of $\tau$'s that are not dominated by $\tau^*_u$.
+(The set will be quite wide probably.)
+\item parametric / maximality (?): collect all $\tau$'s for which there is a prior parameter combination such that $\tau$ minimizes $g(\tau)$.
+(Need to do grid search over $\nkz$'s, or keep optimal pars when calculating $\lgt(\tau)$.)
+\end{itemize}
+
+\subsection{***simple 95\% policy}
+
+Or, alternatively to all the above, simple 95\% policy?
+Repair time from now such that lower system reliability is at least 95\%, i.e., upper system failure probability is at most 5\%.
+
+\section{Case study / numerical example}
+
+which system layout? something that demonstrates the power of the method (complex layout) or something simple?
+
+complex: e.g., bridge system where each of the four elements is a two out of three, and the bridge element is a two-parallel.
+
+or the simplified brake system from ASCE-ASME paper?
+
 \section{Outlook}
 
-*** to add timing of next inspection into the model we would need to add interval-censored data
-(failure has happened between last and current inspection)
-
-*** if repaired/exchanged components are present in system,
-the one needs to use actual ages (and not time since system startup) in parameter update,
-introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as unreplaced component type
+*** to use the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
+we would need to add interval-censored data (failure has happened between last and current inspection)
 
@@
 
+\section*{Bibliography}
+
 \bibliographystyle{elsarticle-harv}
+
 \bibliography{refs}

### 2016-10-06 cbm-rbd-paper.tex
RUL papers

@@
 CBM usually with directly or indirectly observable continuously measurable condition / degradation signal,
-estimated time till failure (RUL) via distance of current signal level to fixed known failure threshold.
+estimated time till failure (RUL) \citep{2014:rul-review, 2011:rul-review-statistical}
+via distance of current signal level to fixed known failure threshold.
 Inspection-based CBM via delay time model, modeling the time between detectable degradation and failure,
 again time till failure via distance of current degradation level to fixed known failure threshold,
-In both cases, maintenance decision via control limit / threshold for the signal.
+In both cases, maintenance decision via control limit / threshold for the signal, RUL not explicitely calculated.
 %but in practice threshold often not known
@@
 Furthermore, our method appropriately reflects epistemic uncertainty,
-by using parametric p-boxes, an imprecise probability model, for the component models.
+by using sets of conjugate priors \citep{diss} for the component models.
+The resulting sets of component posteriors are equivalent to parametric p-boxes,
+an imprecise probability model popular in risk and reliability engineering.
 
-***epistemic vs. aleatoric uncertainty: big topic in reliability and risk
+These parametric posteriors are then used to calculate the exact distribution of system RUL,
+we therefore accomplish the same as \cite{2013:si-et-al} for their situation.
+
+***figure of process: set of component priors $\to$ set of component posteriors $\to$ system RUL $\to$ $g(\tau)$ $\to$ $\tau^*$
+
+***single $\tau^*$ vs set of $\tau^*$: decision support
+
+***discuss \cite{2015:sankararaman}, epistemic vs. aleatoric uncertainty: big topic in reliability and risk
 
 ***refer to Terje Aven, NASA Langley UQ challenge, illustration that uniform distribution does not express ignorance (Edoardo Patelli)***
+
+***we go beyond what \cite{2015:sankararaman} recommends
 
@@
 which is updated using the degradation signal history,
-and use total expected infinite-horizon discounted cost to determine the maintenance policy)
+and use total expected infinite-horizon discounted cost to determine the maintenance policy,
+RUL not explicitely calculated)
 
@@
 but no link from RUL to maintenance decision)
+
+\cite{2013:si-et-al} do CBM with continuous monitoring taking into account the whole degradation path history.
+The authors provide exact expressions for the RUL distribution, which is updated in a Bayesian framework.
+The RUL distribution is used to construct a replacement decision model using the unit cost rate
+(eq. 35, citation Wang and Zhang 2005)\\
+***this is most similar to what we do: exact RUL distribution $\to$ maintenance decision,
+but we have component status instead of degradation signal as basis for RUL,
+and we model epistemic uncertainties!\\
+***check again to be sure, whot do they say about selection of prior parameters?***
 

### 2016-10-06 figure1.R
R files from asce-asme paper

@@ -1,0 +1,48 @@
+# --------------------------------------------------------------------------- #
+# ASCE-ASME paper - code for Fig 1
+# --------------------------------------------------------------------------- #
+
+source("weibull-sys-functions.R")
+source("plotdefs.R")
+
+# example for Fig 1: assume mean ft = 9
+beta <- 2
+y0 <- failuretolambda(9, beta)
+n0 <- 2
+t1 <- 1
+t2 <- 2
+
+n2 <- n0 + 2
+y2 <- (n0*y0 + t1^beta + t2^beta)/n2
+y2
+
+eft2 <- lambdatofailure(y2, beta)
+eft2
+
+invgammavar <- function(n0, y0)
+  y0^2/(1-1/n0)
+invgammasd <- function(n0, y0)
+  sqrt(y0^2/(1-1/n0))
+
+invgammavar(n2, y2)
+invgammasd(n2, y2)
+invgammasd(n0, y0)
+
+failuretolambda(7)
+(2*failuretolambda(7) + 6^2 + 7^2)/4
+
+# the plot
+xseq <- seq(0.1, 200, length.out = 300)
+fig1df <- data.frame(x = rep(xseq, 2),
+                     y = c(cpinvgamma(xseq, n0, y0), cpinvgamma(xseq, n2, y2)),
+                     p = factor(rep(c("Prior", "Posterior"), each = length(xseq)),
+                                levels = c("Prior", "Posterior")))
+fig1 <- ggplot(fig1df, aes(x=x)) + geom_line(aes(y=y, group=p, colour=p)) + ylim(0, 1) + 
+  theme_bw() + ijarcol + rightlegend + xlab(expression(lambda)) + ylab(expression(F(lambda)))
+#setEPS()
+#postscript("fig1.eps",width=5,height=3)
+pdf("fig1.pdf",width=6,height=3)
+fig1
+dev.off()
+
+#

### 2016-10-06 figure2.R

@@ -1,0 +1,113 @@
+# --------------------------------------------------------------------------- #
+# ASCE-ASME paper - code for Fig 2
+# --------------------------------------------------------------------------- #
+
+source("weibull-sys-functions.R")
+source("plotdefs.R")
+
+forfig2 <- list(n0 = c(2,5), y0 = c(failuretolambda(9,2), failuretolambda(11,2)), beta = 2)
+data2 <- c(1,2)
+data3 <- c(10,11)
+lvec <- seq(0.1, 300, length.out = 300) # lambda vec
+
+weidf <- function(prior, data, tvec){
+  n0 <- prior$n0
+  y0 <- prior$y0
+  beta <- prior$beta
+  n <- length(data)
+  tau <- sum(data^beta)
+  # prior set
+  prlower <- sapply(tvec, FUN = function(t){
+    optimize(f = cpigfornoptim, y = y0[2], t = t,
+             lower = n0[1], upper = n0[2], maximum = FALSE)$objective
+  })
+  prupper <- sapply(tvec, FUN = function(t){
+    optimize(f = cpigfornoptim, y = y0[1], t = t,
+             lower = n0[1], upper = n0[2], maximum = TRUE)$objective
+  })
+  # posterior set
+  polower <- sapply(tvec, FUN = function(t){
+    optimize(f = function(n0f, y0f, t){ # here n0 and y0 are fixed values
+      nn <- n0f + n
+      yn <- (n0f*y0f + tau)/nn
+      cpinvgamma(t, nn, yn)
+    }, y0f = y0[2], t = t,
+             lower = n0[1], upper = n0[2], maximum = FALSE)$objective
+  })
+  poupper <- sapply(tvec, FUN = function(t){
+    optimize(f = function(n0f, y0f, t){ # here n0 and y0 are fixed values
+      nn <- n0f + n
+      yn <- (n0f*y0f + tau)/nn
+      cpinvgamma(t, nn, yn)
+    }, y0f = y0[1], t = t,
+    lower = n0[1], upper = n0[2], maximum = TRUE)$objective
+  })  
+  data.frame(l = rep(tvec, 2), Fll = c(prlower, polower), Flu = c(prupper, poupper), 
+             Item = factor(rep(c("Prior", "Posterior"), each = length(tvec)),
[…]

### 2016-10-06 figures3f.R

@@ -1,0 +1,286 @@
+# --------------------------------------------------------------------------- #
+# ASCE-ASME paper - code for example figs
+# --------------------------------------------------------------------------- #
+
+source("weibull-sys-functions.R")
+source("plotdefs.R")
+
+# full system for prior
+br <- graph.formula(s -- M -- C1:C2:C3:C4, P1:P2:P3:P4 -- t,
+                    C1 -- P1, C2 -- P2, C3 -- P3, C4 -- P4, s -- H -- P3:P4)
+br <- setCompTypes(br, list("M"=c("M"), "H"=c("H"), "C"=c("C1", "C2", "C3", "C4"), "P"=c("P1", "P2", "P3", "P4")))
+brsysign <- computeSystemSurvivalSignature(br)
+
+# reduced system for posterior: we assume that C2, C3, P2 and P3 have failed
+brpos <- graph.formula(s -- M -- C1:C4, P1:P4 -- t,
+                       C1 -- P1, C4 -- P4, s -- H -- P4)
+brpos <- setCompTypes(brpos, list("M"=c("M"), "H"=c("H"), "C"=c("C1", "C4"), "P"=c("P1", "P4")))
+brpossysign <- computeSystemSurvivalSignature(brpos)
+
+# prior param sets
+brCpr <- LuckModel(n0 = c(1,5),  y0 = c(failuretolambda(8,2),   failuretolambda(10,2)))
+brHpr <- LuckModel(n0 = c(1,10), y0 = c(failuretolambda(2,1.2), failuretolambda(20,1.2)))
+brMpr <- LuckModel(n0 = c(2,5),  y0 = c(failuretolambda(5,2.5), failuretolambda(8,2.5)))
+brPpr <- LuckModel(n0 = c(1,10), y0 = c(failuretolambda(3,1.5), failuretolambda(4,1.5)))
+brpr <- list(brCpr, brHpr, brMpr, brPpr)
+brprnk <- c(4, 1, 1, 4)
+brbeta <- c(2, 1.2, 2.5, 1.5)
+brfts0 <- list(NULL, NULL, NULL, NULL)
+brprtvec <- seq(0, 20, length.out=101)
+
+# prior system reliability function at tnow = 0
+brprio <- sysrelPbox(luckobjlist = brpr, survsign = brsysign, nk = brprnk, beta = brbeta,
+                     fts = brfts0, tnow = 0, tvec = brprtvec, prior = TRUE)
+
[…]

### 2016-10-06 isipta2015posterexamples.R

@@ -1,0 +1,69 @@
+###############################################################################
+# the three poster examples
+###############################################################################
+posterprior1 <- LuckModel(n0 = c(2,10), y0 = c(failuretolambda(9,2), failuretolambda(11,2)))
+posterprior2 <- LuckModel(n0 = c(8,16), y0 = c(failuretolambda(4,2), failuretolambda(5,2)))
+posterprior3 <- LuckModel(n0 = c(1,5), y0 = c(failuretolambda(9,2), failuretolambda(11,2)))
+posterprior <- list(posterprior1, posterprior2, posterprior3)
+
+# prior system reliability at time 0
+posterfts0 <- list(NULL, NULL, NULL)
+# full system signature (for prior system reliability)
+postersys <- graph.formula(s -- 1:2 -- 3:4:5 -- t)
+V(postersys)$compType <- NA # This just creates the attribute compType
+V(postersys)$compType[match(c("1","3"), V(postersys)$name)] <- "Type 1"
+V(postersys)$compType[match(c("2","4"), V(postersys)$name)] <- "Type 2"
+V(postersys)$compType[match(c("5"), V(postersys)$name)] <- "Type 3"
+V(postersys)$compType[match(c("s","t"), V(postersys)$name)] <- NA
+postersyssign <- computeSystemSurvivalSignature(postersys)
+
+postertvec0 <- seq(0, 20, by=0.1)
+postercorners0 <- fourKcornersSysrel(luckobjlist = posterprior, survsign = postersyssign, beta = rep(2,3),
+                                     fts = posterfts0, tnow = 0, tvec = postertvec0, nk = c(2,2,1), prior = TRUE)
+posterpbox0 <- sysrelPbox(luckobjlist = posterprior, survsign = postersyssign, nk = c(2,2,1),
+                          beta = rep(2,3), fts = posterfts0, tnow = 0, tvec = postertvec0, prior = TRUE)
+#pdf("poster0.pdf", width=9, height=4)
+plotSysrelPbox(res = posterpbox0, polygonFillCol = rgb(255,154,0, max =255))
+fourKcornersSysrelPlot(tvec = postertvec0, rframe = postercorners0$lower, add = TRUE)
+fourKcornersSysrelPlot(tvec = postertvec0, rframe = postercorners0$upper, add = TRUE)
+#dev.off()
+
[…]

### 2016-10-06 plotdefs.R

@@ -1,0 +1,12 @@
+# --------------------------------------------------------------------------- #
+# ASCE-ASME paper - plot definitions
+# --------------------------------------------------------------------------- #
+
+bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
+rightlegend <- theme(legend.title = element_blank())
+nolegend <- guides(linetype="none", fill="none", group="none", colour="none")
+ijarcols <- c("#b2df8a", "#1f78b4")
+ijarcol <- scale_colour_manual(values = ijarcols)
+ijarfill <- scale_fill_manual(values = ijarcols)
+
+#

### 2016-10-06 priorpredictive.R

@@ -1,0 +1,51 @@
+# --------------------------------------------------------------------------- #
+# ASCE-ASME paper - prior predictive for t
+# --------------------------------------------------------------------------- #
+
+tvec <- seq(0, 10, length.out = 101)
+
+pr1 <- prpr(tvec, 2, failuretolambda(5,2), 2)
+pr2 <- prpr(tvec, 10, failuretolambda(5,2), 2)
+pr3 <- prpr(tvec, 2, failuretolambda(2,2), 2)
+#qplot(tvec, pr1, geom = "line")
+
+plot(tvec, pr1, type = "l")
+lines(tvec, pr2, col=2)
+lines(tvec, pr3, col=3)
+
+tvec <- seq(0, 10, length.out = 501)
+pr1n0 <- 1
+pr1y0 <- failuretolambda(5,2)
+fts1 <- rep(5, 5)
+pr1nn <- nn(pr1n0, fts1)
+pr1yn <- yn(2, failuretolambda(5,2), fts1, 2)
+pr1d <- prpr(tvec, pr1n0, pr1y0, 2)
+pr1r <- prprR(tvec, pr1n0, pr1y0, 2)
+pr1dp <- prpr(tvec, pr1nn, pr1yn, 2)
+pr1rp <- prprR(tvec, pr1nn, pr1yn, 2)
+plot(tvec, pr1r, type = "l", ylim=c(0,1), xlab="t", ylab="R(t)") # prior
+lines(tvec, pr1rp, col=2) # posterior
+
+# hazard
+plot(tvec, pr1d/pr1r, type = "l", xlab="t", ylab="h(t)", ylim=c(0,1)) # prior
+lines(tvec, pr1dp/pr1rp, col = 2) # posterior
+
+
+# prior predictive not so useful...
+
+# sysrel() and sysrelPbox work with one-component systems for prior and posterior
+# but without observed failure time, makes no sense with failure time due to t >= tnow >= fts
+ss1 <- oneCompSurvSign("C1")
+test1 <- sysrel(n0y0 = list(c(2, failuretolambda(5,2))), survsign = ss1, beta = 2, fts = list(NULL), tnow = 0,
+                t = 0, table = FALSE, nk = c(1), prior = TRUE)
+test1 <- sysrel(n0y0 = list(c(2, failuretolambda(5,2))), survsign = ss1, beta = 2, fts = list(NULL), tnow = 0,
[…]

### 2016-10-06 weibull-sys-functions.R

@@ -1,0 +1,417 @@
+###############################################################################
+#       Functions to calculate and plot sets of reliability curves            #
+#       for systems consisting of Weibull components with fixed shape         #
+###############################################################################
+
+# provides dinvgamma(x, shape, scale) where shape = alpha and scale = beta
+library(actuar)
+library(luck)
+library(ReliabilityTheory)
+library(ggplot2)
+library(reshape2)
+
+# translate lambda parameter of weibull to expected failure time
+# lambda - scale parameter of weibull
+# beta   - shape parameter of weibull
+lambdatofailure <- function(lambda, beta = 2){
+  lambda^(1/beta) * gamma(1 + 1/beta)
+}
+
+# translate failure time to lambda parameter of weibull
+# ft   - expected failure time
+# beta - shape parameter of weibull
+failuretolambda <- function(ft, beta = 2){
+  (ft/gamma(1 + 1/beta))^beta
+}
+
+# inverse gamma pdf and cdf with canonical parameters n0 and y0
+cdinvgamma <- function(x, n0, y0, ...)
+  dinvgamma(x, shape = n0+1, scale = n0*y0, ...)
+
+cpinvgamma <- function(x, n0, y0, ...)
+  pinvgamma(x, shape = n0+1, scale = n0*y0, ...)
+
+cpigforoptim <- function(ny, t, ...)
+  cpinvgamma(t, ny[1], ny[2], ...)
+
+cpigfornoptim <- function(n, y, t, ...)
+  cpinvgamma(t, n, y, ...)
+
+# function to calculate P(C_t = l | n^(0), y^(0), data),
+# the posterior predictive probability that l components function at time t
+# in the system observed until t_now (notion "of type k" dropped here)
+# this implements (20)
+# n0y0    pair c(n0,y0) of prior parameters
+# t       time t for which to calculate P(C_t), t > t_now
+# l       number of functioning components, \in {0, 1, ..., n-e}
+# n       number of components in the system
+# tnow    time until the system is observed
+# fts     vector of length e giving the observed failure times,
+#         or NULL if no failures observed
+# beta    fixed weibull shape parameter
+# prior   whether the prior predictive should be calculated,
[…]

### 2016-10-18 cbm-rbd-paper.tex
included one-cycle cost rate

@@
 
+\newcommand{\fsys}{f_\text{sys}}
 \newcommand{\Fsys}{F_\text{sys}}
@@
 
-Based on this, the additional criteria of expected cost rate is used to indicate repair now yes/no.
+Based on this, the additional criteria of unit cost rate is used to indicate the optimal time for repair.
 (Could also indicate which failed component(s) to repair best.)
+
+An advantage of our approach is that
+it indicates, for any current time $\tnow$, at which point in the future it is economical to repair the system,
+thus allowing for set-up time for maintenance work.
+
+***all expressed in time, but could also be in usage (number of cycles, etc).
 
@@
 
-\cite{2013:si-et-al} do CBM with continuous monitoring taking into account the whole degradation path history.
-The authors provide exact expressions for the RUL distribution, which is updated in a Bayesian framework.
-The RUL distribution is used to construct a replacement decision model using the unit cost rate
-(eq. 35, citation Wang and Zhang 2005)\\
+\cite{2013:si-et-al} do CBM with continuous monitoring for a single component,
+taking into account the whole degradation path history.
+The authors provide exact expressions for the RUL distribution, which is updated in an empirical Bayesian framework using conjugate priors.
+The RUL distribution is used to construct a replacement decision model using the unit cost rate via renewal reward
+(eq. 35)\\
 ***this is most similar to what we do: exact RUL distribution $\to$ maintenance decision,
@@
 and we model epistemic uncertainties!\\
-***check again to be sure, whot do they say about selection of prior parameters?***
 
@@
 
-\subsection{***unit cost rate}
-
 To find the optimal moment for maintenance based on the current set of system reliability curves,
 we minimize the expected average cost per time unit,
-or unit cost rate, $g(\tau)$. (could be discounted as well, out of scope here.)
-%like in age-based policy
-This is similar to the approach by \cite{2011:kim-et-al},
-where we optimize directly the moment of maintenance $\tau$
-instead of a control limit for a control chart, or a threshold for a degradation signal.
-An advantage of our approach is that
-it indicates, for any current time $\tnow$, at which point in the future it is economical to repair the system,
-thus allowing for set-up time for maintenance work.
+or unit cost rate, $g(\tau)$ %, where $\tau$ is the moment when preventive maintenance is exectued.
+(could be discounted as well, out of scope here.)
+
+In the literature, commonly two ways to calculate the unit cost rate are considered,
+a renewal reward theory based long-term unit cost rate $g_r(\tau)$,
+and the one-cycle cost rate $g_1(\tau)$ \citep{1996:mazzuchi-soyer}.
+We will discuss both approaches here with their advantages and disadvanatges.
+
+Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
+
+\subsection{***unit cost rate via renewal reward}
+
+The renewal reward theory based approach considers the unit cost rate as a long-term average,
+where the proposed policy is used over a large number of replacement cycles,
+and cycles can be seen as stochastic copies of each other.
+Under this assumption, the unit cost rate is, according to renewal theory,
+given as the expected cycle cost $ECC(\tau)$ divided by the expected cycle length $ECL(\tau)$:
+\begin{align}
+g_r(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}\,,
+\end{align}
+and $\tau_r^* = \arg\min g_r(\tau) - \tnow$ is the cost-optimal repair time from now
+(since $\Rsys(\cdot)$ is always in terms of time since system startup)
+
+***most often used in literature \citep{2013:si-et-al}, \citep{2011:kim-et-al}
+
+***stochastic copies assumption implies that the system is in the same state at the start of each cycle,
+so $c_p$ needs to include the costs of replacing all components
+to bring the system into the same state as at startup time.
+
+\subsection{***one-cycle unit cost rate}
+
+The one-cycle unit cost rate approach considers only the costs with respect to the current cycle.
+Conditional on the (random) system failure time $\Tsys$, the unit cost rate is 
+\begin{align*}
+g_1(\tau \mid \Tsys) &=
+\begin{cases}
+c_p / \tau  & \text{if } \Tsys \ge \tau \\
+c_u / \Tsys & \text{if } \Tsys < \tau
+\end{cases}
+\end{align*}
+
+Taking the expectation over $\Tsys$ leads to the unit cost rate being
+\begin{align*}
+g_1(\tau) &= \E[g_1(\tau \mid \Tsys)] = \frac{c_p}{\tau} \Rsys(\tau) + c_u \int_0^\tau \frac{1}{t} \fsys(t) \dd t
+\end{align*}
+***here, $\Rsys(\cdot)$ shifted such that $\tnow = 0$.
 
@@
 as then the duplication of component types for the survival signature decomposition is not necessary.)
-
-Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
-Then the unit cost rate is, according to renewal theory, given by
-\begin{align}
-g(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}\,,
-\end{align}
-and $\tau^* = \arg\min g(\tau) - \tnow$ is the cost-optimal repair time from now
-($\Rsys(\cdot)$ is always in terms of time since system startup)
 

### 2016-10-19 cbm-rbd-paper.tex
split paper (no sets of priors): title, abstract and intro

@@
 \begin{frontmatter}
-\title{Condition-Based Maintenance for Systems based on Bayesian P-Box Component Models***}
+\title{Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability}
 
@@
 \begin{abstract}
-CBM when no (continuous) degradation signal for system available, but status of components observable (works yes/no)
+We propose a new way of developing a condition-based maintenance policy for complex systems,
+based not on a one-dimensional continuous degradation signal,
+but on the status of all components within a system.
 
-use method from asce-asme paper:
-gives RUL in form of a p-box (set of distributions), base maintenance decision directly on that
-(via upper expected cost rate)
+By means of the survival signature,
+a generalization of the system signature allowing for multiple component types,
+we obtain a predictive distribution for system survival time
+(also known as RUL, remaining useful life)
+based on which of the system's components currently function or not,
+and the current age of the functioning components.
 
-Bayesian approach allows
-component models to include expert info, test data (if available), and status of components in the running system
+Component time to failure is modeled by a Weibull distribution with fixed shape parameter.
+The scale parameter is iteratively updated in a Bayesian fashion
+using the current (censored and non-censored) component lifetimes.
+Each component type has a separate model that may also include test data.
 
-main message: can do CBM for systems without degradation signal,
-especially useful for redundant systems,
-method reflects aleatory and epistemic uncertainty in all information sources
+The cost-optimal moment of repair for the system is obtained by minimizing the one-cycle unit cost rate.
+The unit cost rate is recalculated at fixed time points,
+leading to a dynamic policy since the aging of components and possible failures will change the cost-optimal moment of repair.
 \end{abstract}
@@
 \begin{keyword}
-condition-based maintenance \sep system reliability \sep remaining useful life \sep survival signature \sep imprecise probability \sep p-box
-\end{keyword}
+condition-based maintenance \sep system reliability \sep remaining useful life \sep survival signature \sep one-cycle unit cost rate\end{keyword}
 \end{frontmatter}
@@
 
-CBM usually with directly or indirectly observable continuously measurable condition / degradation signal,
-estimated time till failure (RUL) \citep{2014:rul-review, 2011:rul-review-statistical}
-via distance of current signal level to fixed known failure threshold.
-Inspection-based CBM via delay time model, modeling the time between detectable degradation and failure,
-again time till failure via distance of current degradation level to fixed known failure threshold,
-In both cases, maintenance decision via control limit / threshold for the signal, RUL not explicitely calculated.
+***main message:
+can do CBM for systems without degradation signal,
+especially useful for redundant systems,
+dynamic policy using one-cycle unit cost rate (exact, unlike renewal theorem based!),
+using iterative Bayesian update of component models,
+thus taking all information into account (history and current status)
+
+***Bayesian approach allows component models to include expert info, test data (if available),
+and information that can be gained from the behaviour of components in the running system
+in the form of censored and non-censored component lifetimes
+
+***we argue that our approach is CBM because it takes current system state into account
+and adjusts the moment of maintenance accordingly.
+
+\subsection*{---------------------}
+***general discussion on CBM as usual
+
+***Condition-based maintenance (CBM) has received considerable attention in the literature.
+The central idea is to maintain technical systems or components at just the right time,
+that is, before they fail,
+but not too early, in order to keep reliability high and operating costs low.
+%most fully use the component's or system's lifetime and to save on maintenance work
+
+***trade-off between risk of failure during operation
+(can lead to costly downtime: idle workforce, missed production, penalties, loss of reputation)
+and costs of premature maintenance
+(wasting potential component / system lifetime, downtime cost, cost of maintenance work)
+
+***so CBM must be based on some information about the state or health of the component / system.
+Two ways: continuous monitoring CBM and inspection-based CBM.
+
+***Continuous monitoring CBM policies are usually derived
+using a directly observable continuously measurable condition / degradation signal,
+or constructs such a signal or health status using indirect measurements.
+Estimated time till failure (RUL) \citep{2014:rul-review, 2011:rul-review-statistical}
+via distance of current signal level to a fixed known failure threshold.
+
+***Inspection-based CBM via delay time model, modeling the time between detectable degradation and failure,
+again time till failure via distance of current degradation level to fixed known failure threshold.
+
+***In both cases, maintenance decision via control limit / threshold for the signal
+(RUL not explicitely calculated)
+by minimizing the expected unit cost rate,
+which is often approximated using the renewal reward theorem.
 %but in practice threshold often not known
 
-Here we propose a different approach to CBM: if no degradation signal for system available,
-use system layout (reliability block diagram) and information on components' status:
-need only to observe when a component fails,
-and expert information about expected component failure times.
+\subsection*{---------------------}
 
-We use a parametric model not for a degradation signal of the system or for the delay time, but for component lifetimes:
-we use the well-known Weibull model for component lifetimes.
-To keep the model simple, we assume known shape parameter,
+Here we propose a different approach to CBM
+for the case when no degradation signal for the system is available,
+but system components can be identified and their functioning status
+(working or not working) can be monitored.
+In this situation, one can use the system's layout in reliability terms
+(i.e., its reliability block diagram) and information on components' status
+to directly calculate the RUL distribution,
+and base the maintenance policy on this distribution.
+(In fact, our approach can be seen as CBM based on a multivariate degradation signal,
+where each component sends a binary signal, and the reliability block diagram is used
+for sensor fusion.)
+
+Our approach can also be seen as a generalization of policies for $k$ out of $N$ systems to arbitrary system layouts.
+Furthermore, our approach allows for multiple types of components in the system,
+with each component type having its own failure behaviour.
+
+%We use a parametric model not for a degradation signal of the system or for the delay time, but for component lifetimes:
+For each component type, we use the well-known Weibull distribution to model component lifetimes.
+To keep the model simple and to demonstrate its feasability, we assume the shape parameter for each component type to be known,
+focusing on learning of the scale parameter,
 and that components fail independently.
-These simplifying assumptions might not hold in practice,
+These simplifying assumptions will often not hold in practice,
 then the model can serve as a first approximation.
+Generally, we see our contribution as opening up an entirely new way to derive CBM policies,
+and thus consider the model in this paper more as a proof of concept,
+where extension to more realistic models must happen in a second step.
+As an example, it is possible to extend the model to learn also the shape parameter along the lines of
+\cite{1969:soland},
+but this is not included here as it would complicate presentation.
+%need only to observe when a component fails,
+%and expert information about expected component failure times.
 
-The Bayesian approach to the Weibull model allows to integrate, for each component type,
+The Bayesian approach to the Weibull model \citep[see, e.g.,][]{1996:mazzuchi-soyer} allows to integrate, for each component type,
 three sources of information: expert knowledge, data from component tests,
-and status of components in the monitored system, i.e., current system condition.
+and the status of components in the monitored system. %, i.e., current system condition.
+These information sources are integrated into a single component model
+using the iterative nature of Bayesian updating,
+leading to a so-called posterior predictive distribution for the number of components surviving at any time in the future.
 
-Furthermore, our method appropriately reflects epistemic uncertainty,
-by using sets of conjugate priors \citep{diss} for the component models.
-The resulting sets of component posteriors are equivalent to parametric p-boxes,
-an imprecise probability model popular in risk and reliability engineering.
+These predictive distributions are then used to calculate the exact distribution of system RUL
+using the survival signature \citep{2012:survsign}.
+(***we therefore accomplish the same as \cite{2013:si-et-al} for their situation.)
 
-These parametric posteriors are then used to calculate the exact distribution of system RUL,
-we therefore accomplish the same as \cite{2013:si-et-al} for their situation.
+By its Bayesian nature, the system RUL distribution adequately reflects the uncertainties in RUL estimation
+related to modeling and prediction \citep{2015:sankararaman},
+readily adapting to any changes in component behaviour.
+The use of conjugate priors means that we get explicit formulas for the RUL distribution,
+so no numerical integration or simulation techniques are necessary.
+This allows for a very frequent, or even real-time, update of the RUL distribution,
+taking into account the changed structure when components have failed
+and the information gain from updating the component reliability distributions.
 
-***figure of process: set of component priors $\to$ set of component posteriors $\to$ system RUL $\to$ $g(\tau)$ $\to$ $\tau^*$
+Based on the RUL distribution at any current time $\tnow$,
+the optimal moment of maintenance given all information available at $\tnow$
+is then determined by minimizing the expected one-cycle unit cost rate.
+The expected one-cycle unit cost rate, also known as one-cycle criterion
+\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen},
+makes the trade-off between preventive and corrective maintenance according to the current cycle only,
+unlike the usually employed renewal based criterion,
+which approximates the unit cost rate using a renewal argument \citep[p.~296]{1996:mazzuchi-soyer},
+but is not suited for situations where one may whish to change the strategy per cycle \citep{2006:coolen-schrijner-coolen}.
 
-***single $\tau^*$ vs set of $\tau^*$: decision support
+Since the RUL distribution changes with current time $\tnow$,
+the corresponding optimal moment of maintenance $\tau^*$ changes as well,
+leading to a dynamic adaptive maintenance policy,
+similar to a CBM policy based on a continuosly monitored degradation signal.
+However, unlike such threshold-based CBM policies,
+our approach allows to easily take into account the time needed to set up maintenance work (known as set-up time),
+since it gives the optimal moment of maintenance as a time beyond current time $\tnow$,
+and maintenance can be initiated as soon as $\tau^*$ approaches the set-up time.
 
-***discuss \cite{2015:sankararaman}, epistemic vs. aleatoric uncertainty: big topic in reliability and risk
+In this paper, we assume that at the moment of maintenance,
+all components in the system are replaced,
+so the cost parameters in the unit cost rate must be determined accordingly.
+One could instead consider other replacement schemes (e.g., replacing only the failed components),
+or indeed optimize the unit cost rate over all possible replacement schemes,
+since our method for RUL calculation can handle differently aged components. 
+However, optimizing over replacement schemes opens up a full research programme on its own,
+and for situations with high set-up costs,
+as is typical for CBM applications,
+the replace-all scheme is most likely the cost-optimal strategy.
 
-***refer to Terje Aven, NASA Langley UQ challenge, illustration that uniform distribution does not express ignorance (Edoardo Patelli)***
+***figure of process: component priors $\to$ component posteriors $\to$ system RUL $\to$ $g(\tau)$ $\to$ $\tau^*$
 
-***we go beyond what \cite{2015:sankararaman} recommends
+***Expert input in our model is, for each component type,
+Weibull shape parameter, expected failure time (translated to scale parameter),
+and expert info weight (how sure about mean failure time guess).
+Component test data (can include right-censored observations) is optional.
+Further input is system layout (reliability block diagram indicating which component belongs to which type)
+and the cost parameters $c_p$ and $c_u$.
 
-The proposed system RUL model adequately reflects uncertainty in the RUL distribution
-according to the current system status,
-in particular making more cautious predictions when failure behaviour in the monitored system
-seems to deviate from what is expected from expert knowledge and previous (test) data.
+***here all expressed in time, but could also be in usage (number of cycles, etc).
 
-Expert input in our model is, for each component type,
-Weibull shape parameter, range of expected failure time (translated to scale parameter),
-and range of expert info weight (how sure about mean failure time guess).
-By using ranges we do a systematic sensitivity analysis.
+***compare to $M^*$ out of $N$ policy:
+we are dynamic (would mean for a $M^*$ out of $N$ policy that $M^*$ decreases over time due to component aging),
+we learn about component lifetimes,
+and we allow for set-up time
 
-Our model gives lower and upper bounds for the distribution of time till system failure,
-taking current (at time $\tnow$) system condition into account.
-
-Based on this, the additional criteria of unit cost rate is used to indicate the optimal time for repair.
-(Could also indicate which failed component(s) to repair best.)
-
-An advantage of our approach is that
-it indicates, for any current time $\tnow$, at which point in the future it is economical to repair the system,
-thus allowing for set-up time for maintenance work.
-
-***all expressed in time, but could also be in usage (number of cycles, etc).
-
-\subsection{Literature***}
+\section{Literature***}
 
@@
 
+Frank Coolen for inspiring discussions
+
 \section*{Bibliography}

### 2016-10-19 setsofpriorspart.tex
split paper (no sets of priors): title, abstract and intro

--- 2016-10-06 cbm-rbd-paper.tex
@@
 
-\journal{RESS}
+\journal{***}
 
@@
 
-CBM usually with directly or indirectly observable continuously measurable condition / degradation signal,
-estimated time till failure (RUL) \citep{2014:rul-review, 2011:rul-review-statistical}
-via distance of current signal level to fixed known failure threshold.
-Inspection-based CBM via delay time model, modeling the time between detectable degradation and failure,
-again time till failure via distance of current degradation level to fixed known failure threshold,
-In both cases, maintenance decision via control limit / threshold for the signal, RUL not explicitely calculated.
-%but in practice threshold often not known
+main message:
+can do CBM for systems without degradation signal,
+especially useful for redundant systems,
+method reflects aleatory and epistemic uncertainty in all information sources
 
-Here we propose a different approach to CBM: if no degradation signal for system available,
-use system layout (reliability block diagram) and information on components' status:
-need only to observe when a component fails,
-and expert information about expected component failure times.
-
-We use a parametric model not for a degradation signal of the system or for the delay time, but for component lifetimes:
-we use the well-known Weibull model for component lifetimes.
-To keep the model simple, we assume known shape parameter,
-and that components fail independently.
-These simplifying assumptions might not hold in practice,
-then the model can serve as a first approximation.
-
-The Bayesian approach to the Weibull model allows to integrate, for each component type,
-three sources of information: expert knowledge, data from component tests,
-and status of components in the monitored system, i.e., current system condition.
+use method from asce-asme paper:
+gives RUL in form of a p-box (set of distributions), base maintenance decision directly on that
+(via upper expected cost rate?)
 
@@
 an imprecise probability model popular in risk and reliability engineering.
-
-These parametric posteriors are then used to calculate the exact distribution of system RUL,
-we therefore accomplish the same as \cite{2013:si-et-al} for their situation.
 
@@
 and range of expert info weight (how sure about mean failure time guess).
+Component test data (can include right-censored observations) is optional.
 By using ranges we do a systematic sensitivity analysis.
@@
 
-Based on this, the additional criteria of expected cost rate is used to indicate repair now yes/no.
-(Could also indicate which failed component(s) to repair best.)
-
-\subsection{Literature***}
-
-Example for Bayesian method in CBM via inspections: \cite{2007:wang-jia}
-propose a model that uses Bayesian updating,
-but the model aims to identify an optimal inspection interval.
-%This is CBM via inspections, not CBM via continuous monitoring as we aim to do.
-
-\begin{scriptsize}
-Wang \& Jia (2007) have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
-model for delay time (time between defect and failure) is Weibull $h \sim \wei(\alpha,\beta)$,
-and each of $\lambda, \alpha, \beta$ has a Gamma prior distribution.
-The expected overall cost rate is then used to find a cost-optimal inspection interval.
-For this they assume that failures are immediately repaired,
-and defects found in an inspection are repaired during inspection.
-
-They use prior predictive distributions for certain statistics (number of defects, number of failures, \ldots between $0$ and $T$)
-to obtain prior values for the Gamma hyperparameters,
-by solving prior predictive equations -- but give no detail on how they actually do this.
-
-In the end they actually do not advocate to calculate the posterior expected cost rate (15),
-but rather plug in posterior estimates for $\lambda, \alpha, \beta$,
-so neglecting uncertainty in estimation.
-(We do not assume a parametric distribution for delay time,
-it rather arises as a consequence of the system layout and component failure distributions.)
-
-\end{scriptsize}
-
-Example for Bayesian method in CBM with continuous monitoring: \cite{2011:elwany-et-al}
-(exponential degradation model, whose parameters $\theta'$ and $\beta$ each have a prior
-which is updated using the degradation signal history,
-and use total expected infinite-horizon discounted cost to determine the maintenance policy,
-RUL not explicitely calculated)
-
-Example for Bayesian method in prediction of system remaining useful life: \cite{2012:sun-et-al}
-(constructs health index for a system based on sensor measurements,
-health status prediction is updated sequentially,
-leads to RUL distribution like our method,
-but no link from RUL to maintenance decision)
-
-\cite{2013:si-et-al} do CBM with continuous monitoring taking into account the whole degradation path history.
-The authors provide exact expressions for the RUL distribution, which is updated in a Bayesian framework.
-The RUL distribution is used to construct a replacement decision model using the unit cost rate
-(eq. 35, citation Wang and Zhang 2005)\\
-***this is most similar to what we do: exact RUL distribution $\to$ maintenance decision,
-but we have component status instead of degradation signal as basis for RUL,
-and we model epistemic uncertainties!\\
-***check again to be sure, whot do they say about selection of prior parameters?***
-
-\cite{2011:kim-et-al} develop a periodic monitoring CBM policy
-where a maintenance decision is triggered when
-a Bayesian control chart (a sequentially updated health indicator) %posterior probability that system is in a 'warning' state
-exceeds a control limit (threshold) that is determined
-by minimizing the expected average cost per time unit.
-(We use the same cost criterion, but base the maintenance decision directly on our exact RUL estimation.)
-
-***typical recent example for Bayesian network models in maintenance -- could also cover system reliabilty terrain***
-maybe Jones et al (RESS 95:3, 2010) ``The use of Bayesian network modelling for maintenance planning in a manufacturing industry'',
-or Bouaziz et al (2013) ``Towards Bayesian network methodology for predicting equipment health factor of complex semiconductor systems''
-
-\begin{scriptsize}
-Bayesian networks (BNs) are a very general method to jointly model multiple dependent random variables in a Bayesian way. 
-This needs assessments of conditional independece relations, and conditional probability models for each variable,
-the latter often in form of conditional probability tables (discrete variables).
-A Bayesian network models probabilistic relations between variables,
-unlike a reliability block diagram, which gives a deterministic relation
-between the status of components and the system state.
-
-One could model a system as a BN (each component is a variable),
-but that would add a lot of complications.
-Most algorithms for BNs assume discrete distributions,
-and do not scale well to large networks (many tasks are NP-hard).
-
-The above papers seem to use a BN to model a degradation signal or (system) health index (have to check again to be sure).
-Our approach is different, as we get an exact formulation for the system RUL directly.
-
-\end{scriptsize}
-
-\section{***summary of ASCE-ASME paper method}
-
-sets of priors on component survival,
-survival signature,
-test data inclusion
-(write down explicit formula for test data including censored observations),
-noninformatiove censoring,
-set of system reliability curves as output,
-wider set in case of prior-data conflict
-
-\section{***extensions to ASCE-ASME paper method}
-\label{sec:extensions}
-
-when repaired/replaced components are present in system,
-then one needs to use actual ages (and not time since system startup) in parameter update,
-introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as unreplaced component type
-
-repaired/replaced components require the creation of a separate type in the survival signature decomposition
-and thus the calculation of separate posterior predictive probabilities
-$P(C^k_t = l_k \mid \nkz,\ykz,\text{test data},\text{monitoring data})$,
-which use, however, the same hyperparameter learning (using actual component ages) as the `parent type'.
-
-output is a set of current system reliability curves
-taking into account the current system state,
-including the current ages of system components, 
-and the lifetime histories of all component types,
-including test data and expert assessments.
-The set of current, updated system reliability curves gives a RUL estimate
-in the form of a p-box, thus reflecting both aleatoric and epistemic uncertainty in the estimate.
-
-\section{***from (set of) reliability curves to maintenance decision}
-
-\subsection{***unit cost rate}
-
-To find the optimal moment for maintenance based on the current set of system reliability curves,
-we minimize the expected average cost per time unit,
-or unit cost rate, $g(\tau)$. (could be discounted as well, out of scope here.)
-%like in age-based policy
-This is similar to the approach by \cite{2011:kim-et-al},
-where we optimize directly the moment of maintenance $\tau$
-instead of a control limit for a control chart, or a threshold for a degradation signal.
 An advantage of our approach is that
@@
 
-Due to our extensions from Section~\ref{sec:extensions},
-maintenance work can consist of replacing (or returning to an as-good-as-new state) some or all failed or non-failed components,
-as arbitrary component ages can be taken into account.
-(However, computation times decrease when all components of the same type are replaced at the same time,
-as then the duplication of component types for the survival signature decomposition is not necessary.)
-
-Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
-Then the unit cost rate is, according to renewal theory, given by
-\begin{align}
-g(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}\,,
-\end{align}
-and $\tau^* = \arg\min g(\tau) - \tnow$ is the cost-optimal repair time from now
-($\Rsys(\cdot)$ is always in terms of time since system startup)
-
-\subsection{***bounds for unit cost rate}
-
-Bounds for $\Rsys(t)$ lead to bounds for $g(\tau)$.
-%For each $\tau$, fix $\Rsys(\tau) \in [\lRsys(\tau), \uRsys(\tau)]$ and optimize $I(\tau) = \int_0^\tau \Rsys(t) \dd t$
-%nonparametrically: $\ol{I}(\tau)$ by $\uRsys(t)$, $\ul{I}(\tau)$ by $\lRsys(t)$ until level of $\Rsys(\tau)$.
-Can get bounds $\lgt(\tau)$ and $\ugt(\tau)$ in the same way as bounds $\lRsys(t)$ and $\uRsys(t)$ in ASCE-ASME paper:
-need to optimize only over
-$\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right], \ldots, \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]$.
-
-This works because, like $\Rsys(t)$, also $g(\tau)$ is monotone in $\ykzfun{1}, \ldots \ykzfun{K}$:
-$\Rsys(\tau)$ is monotone in $\ykzfun{1}, \ldots \ykzfun{K}$ (ASCE-ASME paper),
-and $g(\tau)$ is monotonely decreasing in $\Rsys(\tau)$:
-
-First look at $I(\tau) := \int_0^\tau \Rsys(t) \dd t$.
-A lower bound for $I(\tau)$ is $\tau \Rsys(\tau)$ (obtained when $\Rsys(t)$ drops to $\Rsys(\tau)$ immediately after $t=0$),
-and an upper bound for $I(\tau)$ is $\tau$ (obtained when $\Rsys(t)$ remains at $1$ until immediately prior to $t = \tau$).
-Therefore, for each $\tau$ and $\Rsys(\tau)$ there exists a constant $R^* \in [\Rsys(\tau), 1]$
-such that $I(\tau) = \tau R^*$.
-Note that $R^*$ increases when $\Rsys(\tau)$ increases.
-
-Setting $\Rsys(\tau) =: R$ and $g(\tau) =: g$ to simplify notation, we get
-\begin{align*}
-g &= \frac{c_p R + c_u (1-R)}{\tau R + \tau R^*}
-   = \frac{(c_p - c_u) R + c_u}{\tau R + \tau R^*}\,.
-\end{align*}
-As $(c_p -c_u) < 0$, the enumerator of $g$ is monotonely decreasing in $R$.
-The denominator of $g$ is monotonely increasing in $R$, since $R^*$ must increase when $R$ increases.
-In total, $g$ is thus monotonely decreasing in $R$.
-
-***formulate above as theorem?
-
-\subsection{***from bounds for $g(\tau)$ to (set of) $\tau^*$:}
-
-%worst case, best case, interval (how?)
-\begin{itemize}
-\item worst case (minimax strategy): minimizing $\ugt(\tau)$ leads to $\tau^*_u$.
-\item interval dominance: for each $\tau$, we get a $g(\tau)$ interval $[\lgt(\tau), \ugt(\tau)]$.
-Throw out all $\tau$'s for which $\lgt(\tau) \ge \ugt(\tau^*_u)$.
-This will leave us with the set of $\tau$'s that are not dominated by $\tau^*_u$.
-(The set will be quite wide probably.)
-\item parametric / maximality (?): collect all $\tau$'s for which there is a prior parameter combination such that $\tau$ minimizes $g(\tau)$.
-(Need to do grid search over $\nkz$'s, or keep optimal pars when calculating $\lgt(\tau)$.)
-\end{itemize}
-
-\subsection{***simple 95\% policy}
-
-Or, alternatively to all the above, simple 95\% policy?
-Repair time from now such that lower system reliability is at least 95\%, i.e., upper system failure probability is at most 5\%.
-
-\section{Case study / numerical example}
-
-which system layout? something that demonstrates the power of the method (complex layout) or something simple?
-
-complex: e.g., bridge system where each of the four elements is a two out of three, and the bridge element is a two-parallel.
-
-or the simplified brake system from ASCE-ASME paper?
-
-\section{Outlook}
-
-*** to use the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
-we would need to add interval-censored data (failure has happened between last and current inspection)
+***all expressed in time, but could also be in usage (number of cycles, etc).
 
@@
 CAMPI
+
+Frank Coolen for inspiring discussions
 

### 2016-10-19 cbm-rbd-paper.tex
split paper: rest of paper

@@
 
+***CBM via RUL, $M^*$ out of $N$ policies?
+
+***also generally Bayesian methods in maintenance optimization?
+
+***cite CBM review Olde Keizer, Flapper, Teunter, and other refs from it?
+
 Example for Bayesian method in CBM via inspections: \cite{2007:wang-jia}
@@
 
-\section{***summary of ASCE-ASME paper method}
+\section{***summary of ASCE-ASME paper method minus sets of priors}
 
-sets of priors on component survival,
-survival signature,
+***\cite{2016:walter-coolen}
+
+component model: weibull with fixed shape,
+inverse gamma prior on scale parameter,
+fix priors via expected lifetime and prior strength,
+
 test data inclusion
 (write down explicit formula for test data including censored observations),
-noninformatiove censoring,
-set of system reliability curves as output,
-wider set in case of prior-data conflict
+noninformatiove censoring
 
-\section{***extensions to ASCE-ASME paper method}
-\label{sec:extensions}
+RUL via survival signature,
+posterior predictive distributions,
+system reliability curve (RUL) as output,
 
-when repaired/replaced components are present in system,
-then one needs to use actual ages (and not time since system startup) in parameter update,
-introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as unreplaced component type
-
-repaired/replaced components require the creation of a separate type in the survival signature decomposition
-and thus the calculation of separate posterior predictive probabilities
-$P(C^k_t = l_k \mid \nkz,\ykz,\text{test data},\text{monitoring data})$,
-which use, however, the same hyperparameter learning (using actual component ages) as the `parent type'.
-
-output is a set of current system reliability curves
+output is the current system reliability curve
 taking into account the current system state,
@@
 including test data and expert assessments.
-The set of current, updated system reliability curves gives a RUL estimate
-in the form of a p-box, thus reflecting both aleatoric and epistemic uncertainty in the estimate.
 
-\section{***from (set of) reliability curves to maintenance decision}
+\section{***from reliability curve (RUL) to maintenance decision}
 
@@
 we minimize the expected average cost per time unit,
-or unit cost rate, $g(\tau)$ %, where $\tau$ is the moment when preventive maintenance is exectued.
+called the unit cost rate, $g(\tau)$,
+to find the cost-optimal moment of maintenance $\tau^*$
 (could be discounted as well, out of scope here.)
@@
 In the literature, commonly two ways to calculate the unit cost rate are considered,
-a renewal reward theory based long-term unit cost rate $g_r(\tau)$,
-and the one-cycle cost rate $g_1(\tau)$ \citep{1996:mazzuchi-soyer}.
-We will discuss both approaches here with their advantages and disadvanatges.
+a renewal theory based long-term unit cost rate,
+and the one-cycle cost rate 
+\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}.
+Although the renewal theory based unit cost rate is often used
+in CBM literature \citep{2013:si-et-al,2011:kim-et-al},
+%As we discussed in the Introduction,
+we use the one-cycle cost rate as it is the most appropriate for our situation.
+%since it considers only the costs with respect to the current cycle.
 
 Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
+As discussed in the Introduction,
+we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system.
+Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
+such that often, $c_p \ll c_u$.
 
-\subsection{***unit cost rate via renewal reward}
-
-The renewal reward theory based approach considers the unit cost rate as a long-term average,
-where the proposed policy is used over a large number of replacement cycles,
-and cycles can be seen as stochastic copies of each other.
-Under this assumption, the unit cost rate is, according to renewal theory,
-given as the expected cycle cost $ECC(\tau)$ divided by the expected cycle length $ECL(\tau)$:
-\begin{align}
-g_r(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}\,,
-\end{align}
-and $\tau_r^* = \arg\min g_r(\tau) - \tnow$ is the cost-optimal repair time from now
-(since $\Rsys(\cdot)$ is always in terms of time since system startup)
-
-***most often used in literature \citep{2013:si-et-al}, \citep{2011:kim-et-al}
-
-***stochastic copies assumption implies that the system is in the same state at the start of each cycle,
-so $c_p$ needs to include the costs of replacing all components
-to bring the system into the same state as at startup time.
-
-\subsection{***one-cycle unit cost rate}
-
-The one-cycle unit cost rate approach considers only the costs with respect to the current cycle.
 Conditional on the (random) system failure time $\Tsys$, the unit cost rate is 
 \begin{align*}
-g_1(\tau \mid \Tsys) &=
+g(\tau \mid \Tsys) &=
 \begin{cases}
@@
 
-Taking the expectation over $\Tsys$ leads to the unit cost rate being
-\begin{align*}
-g_1(\tau) &= \E[g_1(\tau \mid \Tsys)] = \frac{c_p}{\tau} \Rsys(\tau) + c_u \int_0^\tau \frac{1}{t} \fsys(t) \dd t
-\end{align*}
+Taking the expectation over $\Tsys$ leads to the expected unit cost rate being
+\begin{align}
+g(\tau) &= \E[g(\tau \mid \Tsys)] = \frac{c_p}{\tau} \Rsys(\tau) + c_u \int_0^\tau \frac{1}{t} \fsys(t) \dd t
+\label{eq:gtau}
+\end{align}
 ***here, $\Rsys(\cdot)$ shifted such that $\tnow = 0$.
 
-Due to our extensions from Section~\ref{sec:extensions},
-maintenance work can consist of replacing (or returning to an as-good-as-new state) some or all failed or non-failed components,
-as arbitrary component ages can be taken into account.
-(However, computation times decrease when all components of the same type are replaced at the same time,
-as then the duplication of component types for the survival signature decomposition is not necessary.)
+We approximate the integral in \eqref{eq:gtau} numerically by a sum,
+where $\fsys(t)$ is calculated via differencen of $\Rsys(t)$ values on a dense grid.
+$g(\tau)$ is likewise evaluated on a dense grid,
+and $\tau^*_{\tnow} = \arg\min g(\tau)$ is determined as the minimum over the grid.
+The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
+$\tau^*$ depends on $\tnow$, and also on the history of the system.
 
-\subsection{***bounds for unit cost rate}
+At time $\tnow$, the corresponding $\tau^*_{\tnow}$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
+so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau^*_{\tnow}$.
 
-Bounds for $\Rsys(t)$ lead to bounds for $g(\tau)$.
-%For each $\tau$, fix $\Rsys(\tau) \in [\lRsys(\tau), \uRsys(\tau)]$ and optimize $I(\tau) = \int_0^\tau \Rsys(t) \dd t$
-%nonparametrically: $\ol{I}(\tau)$ by $\uRsys(t)$, $\ul{I}(\tau)$ by $\lRsys(t)$ until level of $\Rsys(\tau)$.
-Can get bounds $\lgt(\tau)$ and $\ugt(\tau)$ in the same way as bounds $\lRsys(t)$ and $\uRsys(t)$ in ASCE-ASME paper:
-need to optimize only over
-$\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right], \ldots, \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]$.
+****plot both $\tau^*_{\tnow}$ and $\tnow + \tau^*_{\tnow}$ over time for different failure histories
 
-This works because, like $\Rsys(t)$, also $g(\tau)$ is monotone in $\ykzfun{1}, \ldots \ykzfun{K}$:
-$\Rsys(\tau)$ is monotone in $\ykzfun{1}, \ldots \ykzfun{K}$ (ASCE-ASME paper),
-and $g(\tau)$ is monotonely decreasing in $\Rsys(\tau)$:
+\section{Comparison with $M^*$ out of $N$ policy}
 
-First look at $I(\tau) := \int_0^\tau \Rsys(t) \dd t$.
-A lower bound for $I(\tau)$ is $\tau \Rsys(\tau)$ (obtained when $\Rsys(t)$ drops to $\Rsys(\tau)$ immediately after $t=0$),
-and an upper bound for $I(\tau)$ is $\tau$ (obtained when $\Rsys(t)$ remains at $1$ until immediately prior to $t = \tau$).
-Therefore, for each $\tau$ and $\Rsys(\tau)$ there exists a constant $R^* \in [\Rsys(\tau), 1]$
-such that $I(\tau) = \tau R^*$.
-Note that $R^*$ increases when $\Rsys(\tau)$ increases.
+***
 
-Setting $\Rsys(\tau) =: R$ and $g(\tau) =: g$ to simplify notation, we get
-\begin{align*}
-g &= \frac{c_p R + c_u (1-R)}{\tau R + \tau R^*}
-   = \frac{(c_p - c_u) R + c_u}{\tau R + \tau R^*}\,.
-\end{align*}
-As $(c_p -c_u) < 0$, the enumerator of $g$ is monotonely decreasing in $R$.
-The denominator of $g$ is monotonely increasing in $R$, since $R^*$ must increase when $R$ increases.
-In total, $g$ is thus monotonely decreasing in $R$.
-
-***formulate above as theorem?
-
-\subsection{***from bounds for $g(\tau)$ to (set of) $\tau^*$:}
-
-%worst case, best case, interval (how?)
-\begin{itemize}
-\item worst case (minimax strategy): minimizing $\ugt(\tau)$ leads to $\tau^*_u$.
-\item interval dominance: for each $\tau$, we get a $g(\tau)$ interval $[\lgt(\tau), \ugt(\tau)]$.
-Throw out all $\tau$'s for which $\lgt(\tau) \ge \ugt(\tau^*_u)$.
-This will leave us with the set of $\tau$'s that are not dominated by $\tau^*_u$.
-(The set will be quite wide probably.)
-\item parametric / maximality (?): collect all $\tau$'s for which there is a prior parameter combination such that $\tau$ minimizes $g(\tau)$.
-(Need to do grid search over $\nkz$'s, or keep optimal pars when calculating $\lgt(\tau)$.)
-\end{itemize}
-
-\subsection{***simple 95\% policy}
-
-Or, alternatively to all the above, simple 95\% policy?
-Repair time from now such that lower system reliability is at least 95\%, i.e., upper system failure probability is at most 5\%.
-
-\section{Case study / numerical example}
+\section{Case study / numerical example for complex system layout}
 
@@
 \section{Outlook}
+
+*** study other replacement schemes, e.g., replacing only failed components:
+when repaired/replaced components are present in system,
+then one needs to use actual ages (and not time since system startup) in parameter update,
+introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as unreplaced component type.
+Repaired/replaced components require the creation of a separate type in the survival signature decomposition
+and thus the calculation of separate posterior predictive probabilities
+$P(C^k_t = l_k \mid \nkz,\ykz,\text{test data},\text{monitoring data})$,
+which use, however, the same hyperparameter learning (using actual component ages) as the `parent type'.
+
+*** move to sets of priors, set of RUL distributions like in \cite{2016:walter-coolen}.
+Leads to set of $g(\tau)$, finding (set of) $\tau^*$ is then non-trivial,
+needs decision criteria from IP literature like E-admissibility, maximality, or maximin.
 

### 2016-10-19 setsofpriorspart.tex
split paper: rest of paper

@@
 
+\section{***summary of ASCE-ASME paper method}
+
+sets of priors on component survival,
+survival signature,
+test data inclusion
+(write down explicit formula for test data including censored observations),
+noninformatiove censoring,
+set of system reliability curves as output,
+wider set in case of prior-data conflict
+
+\section{***extensions to ASCE-ASME paper method}
+\label{sec:extensions}
+
+output is a set of current system reliability curves
+taking into account the current system state,
+including the current ages of system components, 
+and the lifetime histories of all component types,
+including test data and expert assessments.
+The set of current, updated system reliability curves gives a RUL estimate
+in the form of a p-box, thus reflecting both aleatoric and epistemic uncertainty in the estimate.
+
+\section{***from (set of) reliability curves to maintenance decision}
+
+To find the optimal moment for maintenance based on the current set of system reliability curves,
+we minimize the expected average cost per time unit,
+or unit cost rate, $g(\tau)$ %, where $\tau$ is the moment when preventive maintenance is exectued.
+(could be discounted as well, out of scope here.)
+
+In the literature, commonly two ways to calculate the unit cost rate are considered,
+a renewal reward theory based long-term unit cost rate $g_r(\tau)$,
+and the one-cycle cost rate $g_1(\tau)$ \citep{1996:mazzuchi-soyer}.
+We will discuss both approaches here with their advantages and disadvanatges.
+
+Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
+
+\subsection{***unit cost rate via renewal reward}
+
+The renewal reward theory based approach considers the unit cost rate as a long-term average,
+where the proposed policy is used over a large number of replacement cycles,
+and cycles can be seen as stochastic copies of each other.
+Under this assumption, the unit cost rate is, according to renewal theory,
+given as the expected cycle cost $ECC(\tau)$ divided by the expected cycle length $ECL(\tau)$:
+\begin{align}
+g_r(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}\,,
+\end{align}
+and $\tau_r^* = \arg\min g_r(\tau) - \tnow$ is the cost-optimal repair time from now
+(since $\Rsys(\cdot)$ is always in terms of time since system startup)
+
+***most often used in literature \citep{2013:si-et-al}, \citep{2011:kim-et-al}
+
+***stochastic copies assumption implies that the system is in the same state at the start of each cycle,
+so $c_p$ needs to include the costs of replacing all components
+to bring the system into the same state as at startup time.
+
+\subsection{***one-cycle unit cost rate}
+
+The one-cycle unit cost rate approach considers only the costs with respect to the current cycle.
+Conditional on the (random) system failure time $\Tsys$, the unit cost rate is 
+\begin{align*}
+g_1(\tau \mid \Tsys) &=
+\begin{cases}
+c_p / \tau  & \text{if } \Tsys \ge \tau \\
+c_u / \Tsys & \text{if } \Tsys < \tau
+\end{cases}
+\end{align*}
+
+Taking the expectation over $\Tsys$ leads to the unit cost rate being
+\begin{align*}
+g_1(\tau) &= \E[g_1(\tau \mid \Tsys)] = \frac{c_p}{\tau} \Rsys(\tau) + c_u \int_0^\tau \frac{1}{t} \fsys(t) \dd t
+\end{align*}
+***here, $\Rsys(\cdot)$ shifted such that $\tnow = 0$.
+
+Due to our extensions from Section~\ref{sec:extensions},
+maintenance work can consist of replacing (or returning to an as-good-as-new state) some or all failed or non-failed components,
+as arbitrary component ages can be taken into account.
+(However, computation times decrease when all components of the same type are replaced at the same time,
+as then the duplication of component types for the survival signature decomposition is not necessary.)
+
+\subsection{***bounds for unit cost rate}
+
+Bounds for $\Rsys(t)$ lead to bounds for $g(\tau)$.
+%For each $\tau$, fix $\Rsys(\tau) \in [\lRsys(\tau), \uRsys(\tau)]$ and optimize $I(\tau) = \int_0^\tau \Rsys(t) \dd t$
+%nonparametrically: $\ol{I}(\tau)$ by $\uRsys(t)$, $\ul{I}(\tau)$ by $\lRsys(t)$ until level of $\Rsys(\tau)$.
+Can get bounds $\lgt(\tau)$ and $\ugt(\tau)$ in the same way as bounds $\lRsys(t)$ and $\uRsys(t)$ in ASCE-ASME paper:
+need to optimize only over
+$\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right], \ldots, \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]$.
+
+This works because, like $\Rsys(t)$, also $g(\tau)$ is monotone in $\ykzfun{1}, \ldots \ykzfun{K}$:
+$\Rsys(\tau)$ is monotone in $\ykzfun{1}, \ldots \ykzfun{K}$ (ASCE-ASME paper),
+and $g(\tau)$ is monotonely decreasing in $\Rsys(\tau)$:
+
+First look at $I(\tau) := \int_0^\tau \Rsys(t) \dd t$.
+A lower bound for $I(\tau)$ is $\tau \Rsys(\tau)$ (obtained when $\Rsys(t)$ drops to $\Rsys(\tau)$ immediately after $t=0$),
+and an upper bound for $I(\tau)$ is $\tau$ (obtained when $\Rsys(t)$ remains at $1$ until immediately prior to $t = \tau$).
+Therefore, for each $\tau$ and $\Rsys(\tau)$ there exists a constant $R^* \in [\Rsys(\tau), 1]$
+such that $I(\tau) = \tau R^*$.
+Note that $R^*$ increases when $\Rsys(\tau)$ increases.
+
+Setting $\Rsys(\tau) =: R$ and $g(\tau) =: g$ to simplify notation, we get
+\begin{align*}
+g &= \frac{c_p R + c_u (1-R)}{\tau R + \tau R^*}
+   = \frac{(c_p - c_u) R + c_u}{\tau R + \tau R^*}\,.
+\end{align*}
+As $(c_p -c_u) < 0$, the enumerator of $g$ is monotonely decreasing in $R$.
+The denominator of $g$ is monotonely increasing in $R$, since $R^*$ must increase when $R$ increases.
+In total, $g$ is thus monotonely decreasing in $R$.
+
+***formulate above as theorem?
+
+\subsection{***from bounds for $g(\tau)$ to (set of) $\tau^*$:}
+
+%worst case, best case, interval (how?)
+\begin{itemize}
+\item worst case (minimax strategy): minimizing $\ugt(\tau)$ leads to $\tau^*_u$.
+\item interval dominance: for each $\tau$, we get a $g(\tau)$ interval $[\lgt(\tau), \ugt(\tau)]$.
+Throw out all $\tau$'s for which $\lgt(\tau) \ge \ugt(\tau^*_u)$.
+This will leave us with the set of $\tau$'s that are not dominated by $\tau^*_u$.
+(The set will be quite wide probably.)
+\item parametric / maximality (?): collect all $\tau$'s for which there is a prior parameter combination such that $\tau$ minimizes $g(\tau)$.
+(Need to do grid search over $\nkz$'s, or keep optimal pars when calculating $\lgt(\tau)$.)
+\end{itemize}
+
+\subsection{***simple 95\% policy}
+
+Or, alternatively to all the above, simple 95\% policy?
+Repair time from now such that lower system reliability is at least 95\%, i.e., upper system failure probability is at most 5\%.
+
 \section*{Acknowledgements}

### 2016-10-20 cbm-rbd-paper.tex
Weibull component model and update with cens, two points by Simme Douwe

@@
 \def\ttaut{\ttau(\vec{t})}
+\def\tautk{\tau(\vec{t}_k)}
 
@@
 
+***operation: recalculate $\tau^*$ at fixed dense grid of time points (quasi-continuous),
+this makes sense even if nothing happens because the fact that components in the system still function
+gives information on component distributions;
+alternatively, do the recalculation every time when a component fails (failures contain the most information)
+
+***model allows also to switch to corrective policy when $g(\tau)$ monotonely decreasing (then $\tau \to \infty$)
+
 ***Expert input in our model is, for each component type,
@@
 
-***\cite{2016:walter-coolen}
+We consider a system with components of $k=1,\ldots,K$ different types;
+for each type $k$, there are $n_k$ exchangeable components in the system.
+
+***example reliability block diagram
 
@@
 including test data and expert assessments.
+
+***RUL model description below follows closely \cite{2016:walter-coolen},
+which describes the same RUL model.
+However, \cite{2016:walter-coolen} does not consider maintenance policies,
+and focuses on a generalization of the RUL model using sets of priors for the component models
+(effectively parametric P-boxes),
+allowing for vague and partial prior specifications,
+and sensitivity to prior-data conflict.
+
+\subsection{Bayesian update of Weibull component models}
+\label{sec:weibull}
+
+Here we describe the model for the component lifetimes,
+together with the Bayesian update procedure which allows to include
+expert knowledge, component tests, and information from the currently monitored components in the system.
+
+For each type $k$ component, we assume that the lifetime $T_{k,i}$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
+is Weibull distributed with fixed shape parameter $\beta_k > 0$,
+in short $T_{k,i} \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
+with density and cdf
+\begin{align}
+\label{eq:weibulldens}
+f(t_{k,i} \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_{k,i})^{\beta_k-1} e^{-\frac{(t_{k,i})^{\beta_k}}{\lambda_k}}\,, \\
+\label{eq:weibullcdf}
+F(t_{k,i} \mid \lambda_k) &= 1 - e^{-\frac{(t_{k,i})^{\beta_k}}{\lambda_k}} = P(T_{k,i} \leq t_{k,i} \mid \lambda_k)\,,
+\end{align}
+where $\lambda_k > 0$ and $t > 0$.
+
+The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
+or decreasing ($\beta_k < 1$) over time.
+For $\beta_k=1$, one obtains the Exponential distribution with constant hazard rate as a special case.
+To keep things simple, we assume $\beta_k$ to be known.
+(We plan to extend the model to learn also $\beta_k$ in a later step,
+using, e.g., the discretized approach by \cite{1969:soland}.)
+The scale parameter $\lambda_k$ can be interpreted through the relation
+\begin{align}
+\E[T_{k,i} \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
+\label{eq:lambdainterpret}
+\end{align}
+We will use this equation to convert expected lifetimes to $\lambda_k$ and vice versa.
+
+With a Bayesian approach, one can express expert knowledge about the reliability of the components
+by assigning a so-called prior distribution,
+a distribution over the unknown parameter $\lambda_k$.
+This prior distribution $f(\lambda_k)$ is then updated 
+to the so-called posterior distribution $f(\lambda_k \mid \vec{t})$,
+the distribution over $\lambda_k$ given the data $\vec{t}$,
+via Bayes' rule
+\begin{align*}
+f(\lambda_k \mid \vec{t}) &\propto f(\vec{t}\mid\lambda_k) f(\lambda_k)\,.
+\end{align*}
+The posterior $f(\lambda_k \mid \vec{t})$ subsumes the information
+from both expert knowledge and data,
+and forms the basis for all inferences, like, e.g., predictions.
+
+For the prior over $\lambda_k$,
+a convenient choice is to use the inverse Gamma distribution,
+which is commonly parametrized in terms of the parameters $a_k > 0$ and $b_k > 0$,
+\begin{align}
+f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}\,,
+\label{eq:ig-def}
+\end{align}
+in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
+Here, we have added the prior parameters $a_k$ and $b_k$ in notation
+to indicate that the prior over $\lambda$ depends on their values.
+
+The inverse Gamma is convenient because it is a conjugate prior,
+i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
+the prior parameters only need to be updated to obtain the posterior parameters,
+so no numerical integation or simulation techniques are necessary.
+Furthermore, this conjugacy holds also when right-censored observations are used for updating,
+as indicated below.
+
+In place of the usual parametrization in terms of $a_k$ and $b_k$,
+we use the parameters $\nkz > 1$ and $\ykz > 0$
+because they have a simple interpretation.
+They are defined as
+\begin{align}
+\nkz &= a_k - 1 & &\text{ and}
+&
+\ykz &= b_k / \nkz,
+\label{eq:abtony}
+\end{align}
+where $\ykz$ can be interpreted as the prior guess for the scale parameter $\lambda_k$,
+as $\E[\lambda_k\mid\nkz,\ykz] = \ykz$.
+Using \eqref{eq:lambdainterpret},
+we can thus translate an expert's statement of expected component lifetime into a corresponding value for $\ykz$.
+$\nkz$ can be seen as a prior strength or pseudocount,
+this will become clear in the discussion of the update step below.
+
+The parametrization in terms of $\nkz$ and $\ykz$ also clarifies the nature of the combination
+of prior information and data through Bayes' rule.
+In the conjugate setting,
+applying Bayes' rule simply means that the prior parameters $\nkz$ and $\ykz$
+are updated to posterior parameters, which we denote by $\nkn$ and $\ykn$, respectively.
+Assume we observe $n_k = e_k + c_k$ component lifetimes,
+where $e_k$ is the number of actual failure events,
+and $c_k$ is the number of right-censored observations.
+We denote the failure times by $t_{k,1}, \ldots, t_{k,e_k}$,
+and the censoring times by $t^+_{k,1}, \ldots, t^+_{k,c_k}$,
+and collect them in an observation vector $\vec{t}_k = (t_{k,1}, \ldots, t_{k,e_k}, t^+_{k,1}, \ldots, t^+_{k,c_k})$.
+Then, the updated, posterior parameters are
+\begin{align}
+\nkn &= \nkz + e_k\,, 
+&
+\ykn &=  \frac{\nkz \ykz + \tautk}{\nkz + e_k}\,,
+\label{eq:ig-update}
+\end{align}
+where $\tautk = \sum_{i=1}^{e_k} (t_{k,i})^\beta + \sum_{i=1}^{c_k} (t^+_{k,i})^\beta$.
+
+From the simple update rule \eqref{eq:ig-update}, we see that
+$\ykn$ is a weighted average of the prior parameter $\ykz$ and the maximum likelihood (ML) estimator $\tautk/e_k$,
+with weights proportional to $\nkz$ and $e_k$, respectively.
+$\nkz$ can thus be interpreted as a prior strength or pseudocount,
+indicating how much our prior guess should weigh against the $e_k$ observed failure events.
+Furthermore, $\V[\lambda\mid\nkz,\ykz] = (\ykz)^2 / (1 - 1/\nkz)$;
+for fixed $\ykz$, a higher $\nkz$ indicates thus 
+that more probability mass is concentrated around $\ykz$.
+
+Using \eqref{eq:abtony} and \eqref{eq:ig-update}, the posterior distribution over $\lambda_k$ is
+\begin{align}
+\lambda_k \mid \nkz, \ykz, \vec{t}_k \sim \ig(\nkz + e_k + 1, \nkz \ykz + \tautk)\,.
+\label{eq:ig-update-alpha}
+\end{align}
+%where we have added the prior parameters $\nkz$ and $\ykz$ in notation
+%to emphasize that the posterior is a synthesis of prior information and data.
+As this posterior \eqref{eq:ig-update-alpha} can be defined in terms of
+the updated, posterior parameters $\nkn$ and $\ykn$,
+we may also write
+\begin{align*}
+f(\lambda_k \mid \nkz, \ykz, \vec{t}_k) &= f(\lambda_k \mid \nkn, \ykn)\,.
+\end{align*}
+The iterative nature of Bayesian inference means that we can take the updated,
+posterior parameters as new prior parameters and update them again using new data.
+Indeed, we will use this property to use the extra information about components
+that accumulates during operation of the system:
+At any time $\tnow > 0$,
+all non-failed components correspond to a right censored observation $\tpnow$;
+any failed components instead contribute a fully observed, non-censored lifetime,
+and both types of observations can be used in the update step \eqref{eq:ig-update}.
+To keep notation simple,
+we will below denote the parameters of the inverse Gamma distribution by $\nkz$ and $\ykz$,
+regardless of them expressing expert information alone,
+or stemming from the combination of expert information and test data.
+
+\section{Reliability functions for complex systems using the survival signature}
+\label{sec:sysrel}
+
+The goal is to find, for a given monitored system, the system reliability curve $\Rsys(t)$ at current time $\tnow$,
+and we will now show how the system reliability function can be efficiently obtained using the survival signature.
+This system reliability gives us the RUL distribution on which we base our adaptive maintenance policy.
+
+We consider systems of arbitrary reliability block diagram layout,
+consisting of components of $K$ different types,
+and there are $n_k$ components of type $k$ in the system.
+This system is observed until time $\tnow$,
+leading to censored observation of lifetimes of components within the system.
+
+\section{Posterior predictive***}
+
+For this, we need the posterior predictive distribution
+of the number of components that function at times $t > \tnow$,
+which we will derive .
 

### 2016-10-20 cbm-rbd-paper.tex
start surv sign part

@@
 The goal is to find, for a given monitored system, the system reliability curve $\Rsys(t)$ at current time $\tnow$,
-and we will now show how the system reliability function can be efficiently obtained using the survival signature.
+and we will now show how the system reliability function, given component models, can be efficiently calculated using the survival signature.
 This system reliability gives us the RUL distribution on which we base our adaptive maintenance policy.
@@
 consisting of components of $K$ different types,
-and there are $n_k$ components of type $k$ in the system.
+where there are $n_k$ components of type $k$ in the system,
+and the total number of components in the system is $\sum_{k=1}^K n_k = n$.
 This system is observed until time $\tnow$,
-leading to censored observation of lifetimes of components within the system.
+leading to censored observation of certain component lifetimes within the system.
+
+In a system with $n$ components, the state of the components can be expressed by the state vector
+$\vec{x} = (x_1,x_2,\ldots,x_n) \in \{0,1\}^n$,
+with $x_i=1$ if the $i$th component functions and $x_i=0$ if not.
+The structure function $\phi : \{0,1\}^n \rightarrow \{0,1\}$, defined for all possible $\vec{x}$,
+takes  the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$ \cite{BP75}.
+Most real-life systems are coherent,
+which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
+so system functioning cannot be improved by worse performance of one or more of its components.
+Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.
+
+The survival signature \cite{2012:survsign} is a summary of the structure function
+for systems with $K$ groups of exchangeable components.
+Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,n_k$ for $k=1,\ldots,K$,
+it is defined as the probability for the event that the system functions
+given that precisely $l_k$ of its $n_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
+Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$,
+such that $\Rsys(t) = P(\Tsys > t)$ can be calculated using the law of total probability,
+\begin{align}
+P(\Tsys > t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
+                                                                                  P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
+             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
+             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
+\label{eq:sysrel-survsign}
+\end{align}
+where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$,
+and the last equality holds as we assume that components of different types are independent.
+Note that for coherent systems,
+the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
 

### 2016-10-21 cbm-rbd-paper.tex
post pred start

@@
 we use the parameters $\nkz > 1$ and $\ykz > 0$
+(the upper index ${}\uz$ is used to indicate that these are prior parameters)
 because they have a simple interpretation.
@@
 where $\tautk = \sum_{i=1}^{e_k} (t_{k,i})^\beta + \sum_{i=1}^{c_k} (t^+_{k,i})^\beta$.
+The upper index ${}\un$ indicates that these are posterior parameters resulting from an update with $n_k$ observations,
+where we leave out the index $k$ for $n_k$ in the upper index to increase legibility.
 
@@
 and the last equality holds as we assume that components of different types are independent.
-Note that for coherent systems,
-the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
+Note that for coherent systems, the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
 
-\section{Posterior predictive***}
+***An example for the survival signature for the system in Figure *** is given in Table ****.
 
-For this, we need the posterior predictive distribution
-of the number of components that function at times $t > \tnow$,
-which we will derive .
+\section{Component posterior predictive distributions***}
+\label{sec:postpred}
+
+To calculate the current system reliability curve,
+we thus need the probabilities $P(C^k_t = l_k)$,
+which give the number of components that function at times $t > \tnow$.
+In our Bayesian framework, these probabilities are given
+by a so-called predictive distribution that can be derived from the distribution over $\lambda$.
+This distribution needs to account for expert knowledge and test data;
+following our comment at the end of Section~\ref{sec:weibull},
+we assume here that ***change notation to $n_k^{(\text{test})}$ and $n_k^{(\text{now})}$???
+
+but also for the information gained from the current run of the system:
+both failure times of components (if any)
+and the right-censoring time $\tnow$ for each non-failed component in the system
+can be used to update $\nkz$ and $\ykz$.
+
+In analogue to the notation from Section~\ref{sec:weibull},
+let $n_k = e_k^{\tnow} + c_k^{\tnow}$ be the number of type $k$ components in the monitored system,
+where $e_k^{\tnow}$ is the number of components that have failed by $\tnow$,
+and $c_k^{\tnow}$ is the number of components that have not failed by $\tnow$.
+We can thus collect these observations, as of $\tnow$, in a vector
+$\vec{t}_k^{\tnow} = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
+containing $n_c$ right-censored obsevations $\tpnow$.
+
+Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
+must be used when calculating the posterior predictive distribution.
 

### 2016-10-21 cbm-rbd-paper.tex
change posterior parameters notation

@@
 \def\nknu{\ol{n}\un_k}
+
+\def\yknow{y_k^{(\tnow)}}
+\def\nknow{n_k^{(\tnow)}}
 
@@
 
-\section{***summary of ASCE-ASME paper method minus sets of priors}
+\section{***Adaptive system RUL / RLD based on Weibull component models}
 
@@
 test data inclusion
-(write down explicit formula for test data including censored observations),
-noninformatiove censoring
+with noninformatiove right-censoring
 
-RUL via survival signature,
+RUL/RLD via survival signature,
 posterior predictive distributions,
-system reliability curve (RUL) as output,
+system reliability distribution (RUL/RLD) as output,
 
@@
 ***RUL model description below follows closely \cite{2016:walter-coolen},
-which describes the same RUL model.
+which describes the same RUL/RLD model.
 However, \cite{2016:walter-coolen} does not consider maintenance policies,
-and focuses on a generalization of the RUL model using sets of priors for the component models
-(effectively parametric P-boxes),
+and focuses instead on a generalization of the RUL/RLD model using sets of priors for the component models
+(which can be seen as parametric P-boxes),
 allowing for vague and partial prior specifications,
-and sensitivity to prior-data conflict.
+and sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.
 
@@
 and both types of observations can be used in the update step \eqref{eq:ig-update}.
-To keep notation simple,
-we will below denote the parameters of the inverse Gamma distribution by $\nkz$ and $\ykz$,
-regardless of them expressing expert information alone,
-or stemming from the combination of expert information and test data.
+Before we write this out formally in Section~\ref{sec:postpred},
+we will first present how system reliability functions can be derived based on component models.
+%To keep notation simple,
+%we will below denote the parameters of the inverse Gamma distribution by $\nkz$ and $\ykz$,
+%regardless of them expressing expert information alone,
+%or stemming from the combination of expert information and test data.
 
-\section{Reliability functions for complex systems using the survival signature}
+\subsection{Reliability functions for complex systems using the survival signature}
 \label{sec:sysrel}
 
-The goal is to find, for a given monitored system, the system reliability curve $\Rsys(t)$ at current time $\tnow$,
-and we will now show how the system reliability function, given component models, can be efficiently calculated using the survival signature.
-This system reliability gives us the RUL distribution on which we base our adaptive maintenance policy.
+Here we describe how system reliability functions, given fixed component models,
+can be efficiently calculated using the survival signature.
+We will show in Section~***
+how this method can be used to find the system reliability function $\Rsys(t)$ at current time $\tnow$ for a monitored system,
+giving us the RUL/RLD distribution on which we base our adaptive maintenance policy.
 
@@
 and the total number of components in the system is $\sum_{k=1}^K n_k = n$.
-This system is observed until time $\tnow$,
-leading to censored observation of certain component lifetimes within the system.
+An example is given in Figure~***.
+Note that this system cannot be described as a nesting of series and parallel subsystems.
+%This system is observed until time $\tnow$,
+%leading to censored observation of certain component lifetimes within the system.
 
@@
 
-\section{Component posterior predictive distributions***}
+\subsection{Component posterior predictive distributions}
 \label{sec:postpred}
@@
 which give the number of components that function at times $t > \tnow$.
-In our Bayesian framework, these probabilities are given
-by a so-called predictive distribution that can be derived from the distribution over $\lambda$.
-This distribution needs to account for expert knowledge and test data;
-following our comment at the end of Section~\ref{sec:weibull},
-we assume here that ***change notation to $n_k^{(\text{test})}$ and $n_k^{(\text{now})}$???
+In the Bayesian framework, these probabilities are given
+by a so-called posterior predictive distribution that can be derived from the posterior over $\lambda$.
 
-but also for the information gained from the current run of the system:
-both failure times of components (if any)
-and the right-censoring time $\tnow$ for each non-failed component in the system
-can be used to update $\nkz$ and $\ykz$.
+Denote by $\nkn$ and $\ykn$ the parameters obtained
+by updating the prior parameters $\nkz$ and $\ykz$ using test data.
+The corresponding distribution $f(\lambda_l \mid \nkn, \ykn)$
+thus accounts for both expert knowledge and test data.
+However, following our comments at the end of Section~\ref{sec:weibull},
+the component models can be further updated
+using information gained from the current run of the system until $\tnow$:
+Any failure times of failed components,
+and the right-censoring time $\tpnow$ for each non-failed component
+can be used to update $\nkn$ and $\ykn$.
+We denote the resulting parameter values by $\nknow$ and $\yknow$.
+(It is of course possible to update $\nkz$ and $\ykz$ directly to $\nknow$ and $\yknow$ if no test data is available.)
+%Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
+%must be used when calculating the posterior predictive distribution.
 
@@
 $\vec{t}_k^{\tnow} = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
-containing $n_c$ right-censored obsevations $\tpnow$.
+containing $c_k^{\tnow}$ right-censored observations $\tpnow$.
 
-Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
-must be used when calculating the posterior predictive distribution.
-
-\section{***from reliability curve (RUL) to maintenance decision}
+\section{Dynamic maintenance policy based on the current system reliability function (RUL/RLD)}
 

### 2016-10-22 cbm-rbd-paper.tex
change notation again

@@
 
+\newcommand{\nk}{n_k}
+\newcommand{\nkp}{n_k'}
+\newcommand{\yk}{y_k}
+\newcommand{\ykp}{y_k'}
+
 \def\taut{\tau(\vec{t})}
@@
 \def\tpnow{t^+_\text{now}}
+
+\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
+\def\Phinow{\Phi^{(t_\text{now})}}
 
@@
 We consider a system with components of $k=1,\ldots,K$ different types;
-for each type $k$, there are $n_k$ exchangeable components in the system.
+for each type $k$, there are $N_k$ exchangeable components in the system.
 
@@
 
-For each type $k$ component, we assume that the lifetime $T_{k,i}$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
+For each type $k$ component, we assume that the lifetime $T_{k,i}$ ($i=1,\ldots,N_k$, $k = 1, \ldots, K$)
 is Weibull distributed with fixed shape parameter $\beta_k > 0$,
@@
 In place of the usual parametrization in terms of $a_k$ and $b_k$,
-we use the parameters $\nkz > 1$ and $\ykz > 0$
-(the upper index ${}\uz$ is used to indicate that these are prior parameters)
-because they have a simple interpretation.
+we use the parameters $\nk > 1$ and $\yk > 0$
+%(the upper index ${}\uz$ is used to indicate that these are prior parameters)
+because they are more simple to interpret.
 They are defined as
 \begin{align}
-\nkz &= a_k - 1 & &\text{ and}
+\nk &= a_k - 1 & &\text{ and}
 &
-\ykz &= b_k / \nkz,
+\yk &= b_k / \nk,
 \label{eq:abtony}
 \end{align}
-where $\ykz$ can be interpreted as the prior guess for the scale parameter $\lambda_k$,
-as $\E[\lambda_k\mid\nkz,\ykz] = \ykz$.
+where $\yk$ can be interpreted as the prior guess for the scale parameter $\lambda_k$,
+as $\E[\lambda_k\mid\nk,\yk] = \yk$.
 Using \eqref{eq:lambdainterpret},
-we can thus translate an expert's statement of expected component lifetime into a corresponding value for $\ykz$.
-$\nkz$ can be seen as a prior strength or pseudocount,
+we can thus translate an expert's statement of expected component lifetime into a corresponding value for $\yk$.
+$\nk$ can be seen as a prior strength or pseudocount,
 this will become clear in the discussion of the update step below.
 
-The parametrization in terms of $\nkz$ and $\ykz$ also clarifies the nature of the combination
+The parametrization in terms of $\nk$ and $\yk$ also clarifies the nature of the combination
 of prior information and data through Bayes' rule.
 In the conjugate setting,
-applying Bayes' rule simply means that the prior parameters $\nkz$ and $\ykz$
-are updated to posterior parameters, which we denote by $\nkn$ and $\ykn$, respectively.
-Assume we observe $n_k = e_k + c_k$ component lifetimes,
+applying Bayes' rule simply means that the prior parameters $\nk$ and $\yk$
+are updated to posterior parameters, which we denote by $\nkp$ and $\ykp$, respectively.
+Assume we observe $N_k = e_k + c_k$ component lifetimes,
 where $e_k$ is the number of actual failure events,
@@
 \begin{align}
-\nkn &= \nkz + e_k\,, 
+\nkp &= \nk + e_k\,, 
 &
-\ykn &=  \frac{\nkz \ykz + \tautk}{\nkz + e_k}\,,
+\ykp &=  \frac{\nk \yk + \tautk}{\nk + e_k}\,,
 \label{eq:ig-update}
@@
 where $\tautk = \sum_{i=1}^{e_k} (t_{k,i})^\beta + \sum_{i=1}^{c_k} (t^+_{k,i})^\beta$.
-The upper index ${}\un$ indicates that these are posterior parameters resulting from an update with $n_k$ observations,
-where we leave out the index $k$ for $n_k$ in the upper index to increase legibility.
+%The upper index ${}\un$ indicates that these are posterior parameters resulting from an update with $n_k$ observations,
+%where we leave out the index $k$ for $n_k$ in the upper index to increase legibility.
 
 From the simple update rule \eqref{eq:ig-update}, we see that
-$\ykn$ is a weighted average of the prior parameter $\ykz$ and the maximum likelihood (ML) estimator $\tautk/e_k$,
-with weights proportional to $\nkz$ and $e_k$, respectively.
-$\nkz$ can thus be interpreted as a prior strength or pseudocount,
+$\ykp$ is a weighted average of the prior parameter $\yk$ and the maximum likelihood (ML) estimator $\tautk/e_k$,
+with weights proportional to $\nk$ and $e_k$, respectively.
+$\nk$ can thus be interpreted as a prior strength or pseudocount,
 indicating how much our prior guess should weigh against the $e_k$ observed failure events.
-Furthermore, $\V[\lambda\mid\nkz,\ykz] = (\ykz)^2 / (1 - 1/\nkz)$;
-for fixed $\ykz$, a higher $\nkz$ indicates thus 
-that more probability mass is concentrated around $\ykz$.
+Furthermore, $\V[\lambda\mid\nk,\yk] = (\yk)^2 / (1 - 1/\nk)$;
+for fixed $\yk$, a higher $\nk$ indicates thus 
+that more probability mass is concentrated around $\yk$.
 
@@
 \begin{align}
-\lambda_k \mid \nkz, \ykz, \vec{t}_k \sim \ig(\nkz + e_k + 1, \nkz \ykz + \tautk)\,.
+\lambda_k \mid \nk, \yk, \vec{t}_k \sim \ig(\nk + e_k + 1, \nk \yk + \tautk)\,.
 \label{eq:ig-update-alpha}
@@
 As this posterior \eqref{eq:ig-update-alpha} can be defined in terms of
-the updated, posterior parameters $\nkn$ and $\ykn$,
+the updated, posterior parameters $\nkp$ and $\ykp$,
 we may also write
 \begin{align*}
-f(\lambda_k \mid \nkz, \ykz, \vec{t}_k) &= f(\lambda_k \mid \nkn, \ykn)\,.
+f(\lambda_k \mid \nk, \yk, \vec{t}_k) &= f(\lambda_k \mid \nkp, \ykp)\,.
 \end{align*}
@@
 We will show in Section~***
-how this method can be used to find the system reliability function $\Rsys(t)$ at current time $\tnow$ for a monitored system,
+how this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
 giving us the RUL/RLD distribution on which we base our adaptive maintenance policy.
@@
 consisting of components of $K$ different types,
-where there are $n_k$ components of type $k$ in the system,
-and the total number of components in the system is $\sum_{k=1}^K n_k = n$.
-An example is given in Figure~***.
+where there are $N_k$ components of type $k$ in the system,
+and the total number of components in the system is $\sum_{k=1}^K N_k = N$.
+An example system reliability block diagram is given in Figure~***.
 Note that this system cannot be described as a nesting of series and parallel subsystems.
@@
 
-In a system with $n$ components, the state of the components can be expressed by the state vector
-$\vec{x} = (x_1,x_2,\ldots,x_n) \in \{0,1\}^n$,
+In a system with $N$ components, the state of the components can be expressed by the state vector
+$\vec{x} = (x_1,x_2,\ldots,x_N) \in \{0,1\}^N$,
 with $x_i=1$ if the $i$th component functions and $x_i=0$ if not.
-The structure function $\phi : \{0,1\}^n \rightarrow \{0,1\}$, defined for all possible $\vec{x}$,
-takes  the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$ \cite{BP75}.
+The structure function $\phi : \{0,1\}^N \rightarrow \{0,1\}$, defined for all possible $\vec{x}$,
+takes the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$ \citep{BP75}.
 Most real-life systems are coherent,
@@
 
-The survival signature \cite{2012:survsign} is a summary of the structure function
+The survival signature \citep{2012:survsign} is a summary of the structure function
 for systems with $K$ groups of exchangeable components.
-Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,n_k$ for $k=1,\ldots,K$,
+Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,N_k$ for $k=1,\ldots,K$,
 it is defined as the probability for the event that the system functions
-given that precisely $l_k$ of its $n_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
+given that precisely $l_k$ of its $N_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
 Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$,
@@
 \begin{align}
-P(\Tsys > t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
+P(\Tsys > t) &= \sum_{l_1=0}^{N_1} \cdots \sum_{l_K=0}^{N_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                                                   P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
-             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
-             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
+             &= \sum_{l_1=0}^{N_1} \cdots \sum_{l_K=0}^{N_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
+             &= \sum_{l_1=0}^{N_1} \cdots \sum_{l_K=0}^{N_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
 \label{eq:sysrel-survsign}
@@
 
-\subsection{Component posterior predictive distributions}
+\subsection{Component posterior predictive distributions at $\tnow$}
 \label{sec:postpred}
 
-To calculate the current system reliability curve,
-we thus need the probabilities $P(C^k_t = l_k)$,
-which give the number of components that function at times $t > \tnow$.
+To calculate the current system reliability function $\Rsysnow(t)$,
+we thus need, for each $k=1,\ldots, K$, the probabilities $P(C^k_t = l_k)$
+for the number of type $k$ components that function at times $t > \tnow$.
 In the Bayesian framework, these probabilities are given
@@
 
-Denote by $\nkn$ and $\ykn$ the parameters obtained
-by updating the prior parameters $\nkz$ and $\ykz$ using test data.
-The corresponding distribution $f(\lambda_l \mid \nkn, \ykn)$
-thus accounts for both expert knowledge and test data.
-However, following our comments at the end of Section~\ref{sec:weibull},
+Denote by $\nkz$ and $\ykz$ the parameters reflecting the knowledge base at system start-up time $t=0$.
+These could have been obtained by updating prior parameters $\nk$ and $\yk$ (reflecting expert knowledge)
+to $\nkp$ and $\ykp$ using test data,
+or could be taken directly equal to $\nk$ and $\yk$ if no test data is available.
+In both cases, the distribution $f(\lambda_l \mid \nkz, \ykz)$
+thus accounts for all knowledge on component type $k$ that is available at system start-up.
+
+Following our comments at the end of Section~\ref{sec:weibull},
 the component models can be further updated
@@
 and the right-censoring time $\tpnow$ for each non-failed component
-can be used to update $\nkn$ and $\ykn$.
+can be used to update $\nkz$ and $\ykz$.
 We denote the resulting parameter values by $\nknow$ and $\yknow$.
-(It is of course possible to update $\nkz$ and $\ykz$ directly to $\nknow$ and $\yknow$ if no test data is available.)
+%(It is of course possible to update $\nkz$ and $\ykz$ directly to $\nknow$ and $\yknow$ if no test data is available.)
 %Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
@@
 In analogue to the notation from Section~\ref{sec:weibull},
-let $n_k = e_k^{\tnow} + c_k^{\tnow}$ be the number of type $k$ components in the monitored system,
+let $N_k = e_k^{\tnow} + c_k^{\tnow}$ be the number of type $k$ components in the monitored system,
 where $e_k^{\tnow}$ is the number of components that have failed by $\tnow$,
@@
 containing $c_k^{\tnow}$ right-censored observations $\tpnow$.
+
+$\Phinow$
 

### 2016-10-22 cbm-rbd-paper.tex
system reliability calculation part done, small changes in policy part

@@
 \newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
-\def\Phinow{\Phi^{(t_\text{now})}}
+\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
+\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
+\def\eknow{e_k^{(\tnow)}}
+\def\cknow{c_k^{(\tnow)}}
+\def\vectknow{\vec{t}_k^{(\tnow)}}
+\def\Phinow{\Phi^{(\tnow)}}
+\newcommand{\gnow}{g^{(\tnow)}}
 
@@
 and the right-censoring time $\tpnow$ for each non-failed component
-can be used to update $\nkz$ and $\ykz$.
+can be used to update $\nkz$ and $\ykz$ according to \eqref{eq:ig-update}.
 We denote the resulting parameter values by $\nknow$ and $\yknow$.
@@
 In analogue to the notation from Section~\ref{sec:weibull},
-let $N_k = e_k^{\tnow} + c_k^{\tnow}$ be the number of type $k$ components in the monitored system,
-where $e_k^{\tnow}$ is the number of components that have failed by $\tnow$,
-and $c_k^{\tnow}$ is the number of components that have not failed by $\tnow$.
+let $N_k = \eknow + \cknow$ be the number of type $k$ components in the monitored system,
+where $\eknow$ is the number of components that have failed by $\tnow$,
+and $\cknow$ is the number of components that have not failed by $\tnow$.
 We can thus collect these observations, as of $\tnow$, in a vector
-$\vec{t}_k^{\tnow} = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
-containing $c_k^{\tnow}$ right-censored observations $\tpnow$.
+$\vectknow = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
+containing $\cknow$ right-censored observations $\tpnow$.
+%
+The resulting posterior predictive distribution for any $t > \tnow$ is obtained as
+\begin{align}
+\lefteqn{%
+P(C^k_t = l_k\mid\nkz,\ykz, \vectknow) }\hspace*{5.75ex} \nonumber\\  %
+ &= { \cknow \choose l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{3.5ex}
+                               \big[P(T^k \leq t \mid T^k > \tnow, \lambda_k)\big]^{\cknow - l_k}
+    f(\lambda_k\mid\nkz,\ykz,\vectknow) \dd \lambda_k\,,
+\label{eq:postpredtnow}
+\end{align}
+where $T^k$ is the Weibull distributed lifetime of a component of type $k$.
+Now, by the Weibull assumption \eqref{eq:weibullcdf}, one has
+\begin{align}
+P(T^k \leq t \mid T^k > \tnow, \lambda_k)
+ &= \frac{P(\tnow < T^k \leq t \mid\lambda_k)}{P(T^k > \tnow \mid \lambda_k)} \nonumber\\
+ &= \frac{F(t\mid\lambda_k) - F(\tnow\mid\lambda_k)}{1-F(\tnow\mid\lambda_k)} 
+% = \frac{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}} - e^{-\frac{t^{\beta_k}}{\lambda_k}}}{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}}}
+  = 1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\,.
+\label{eq:weibullcondprob}
+\end{align}
+Substituting \eqref{eq:weibullcondprob} and the posterior \eqref{eq:ig-update-alpha} using $\vectknow$,
+written in terms of the updated parameters $\nknow$ and $\yknow$,
+into \eqref{eq:postpredtnow}, we get
+\begin{align}
+\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)}\hspace*{5.75ex} \nonumber\\
+ &= { \cknow \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
+                               \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{\cknow - l_k}
+    \times \nonumber\\ & \hspace*{14.5ex}
+    \frac{\big(\nknow\yknow\big)^{\nknow + 1}}{\Gamma(\nknow + 1)}
+    \lambda_k^{-(\nknow + 1) - 1} e^{-\frac{\nknow\yknow}{\lambda_k}} \dd \lambda_k \nonumber\\
+ &= { \cknow \choose l_k} \sum_{j=0}^{\cknow - l_k} (-1)^j { \cknow - l_k \choose j}
+    \frac{\big(\nknow\yknow\big)^{\nknow + 1}}{\Gamma(\nknow + 1)} 
+    \times \nonumber\\ & \hspace*{1ex}
+    \int \lambda_k^{-(\nknow + 1) - 1}
+    \exp\Big\{-\frac{(l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}) + \nknow\yknow}{\lambda_k}\Big\} \dd \lambda_k\,.
+\end{align}
+The terms remaining under the integral form the core of an inverse gamma distribution \eqref{eq:ig-def}
+with parameters $\nknow + 1$ and $\nknow\yknow + (l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}))$,
+allowing to solve the integral using the corresponding normalization constant.
+We thus have, for $l_k \in \{0,1,\ldots,\cknow\}$,
+\begin{align}
+\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)} \nonumber\\
+ &= { \cknow \choose l_k} \sum_{j=0}^{\cknow - l_k} (-1)^j { \cknow - l_k \choose j}
+    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
+ &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!}   
+    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
+ &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!} \times \nonumber\\ & \hspace*{10ex}  
+    \left(\frac{\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow       (\tnow)^{\beta_k} }%
+               {\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + (\cknow - l_k - j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
+    \nkz + \eknow + 1}.
+\label{eq:postpred-priorparams}
+\end{align}
+%These posterior predictive probabilities can also be expressed as a cumulative probability mass function (cmf)
+%\begin{align}
+%F(l_k \mid \nkz,\ykz,\vectknow) = P(C^k_t \leq l_k \mid \nkz,\ykz,\vectknow) 
+% = \sum_{j=0}^{l_k} P(C^k_t = j \mid \nkz,\ykz,\vectknow)\,.
+%\end{align}
 
-$\Phinow$
+\subsection{System reliability function at $\tnow$}
+
+Now that we can calulate the component posterior predictive distributions at $\tnow$,
+we can use the method from Section~\ref{sec:sysrel}
+to determine the system reliability distribution $\Rsysnow(t)$,
+giving us the probability that the system functions at times $t > \tnow$,
+taking into account all information available at $\tnow$:
+\begin{align}
+\Rsysnow(t) &:= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
+                \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
+\label{eq:sysrel-tnow}
+\end{align}
+Note that if one or several components have failed by $\tnow$,
+the system layout changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$,
+so we denote the updated survival signature by $\Phinow(l_1,\ldots,l_K)$.
+
+Next, we will describe how an adaptive maintenance policy based on \eqref{eq:sysrel-tnow}
+can be obtained.
 
@@
 
-To find the optimal moment for maintenance based on the current set of system reliability curves,
+To find the optimal moment for maintenance based on the current system reliability function $\Rsysnow(t)$,
 we minimize the expected average cost per time unit,
 called the unit cost rate, $g(\tau)$,
-to find the cost-optimal moment of maintenance $\tau^*$
+to find the cost-optimal moment of maintenance $\tau_*$
 (could be discounted as well, out of scope here.)
 
-In the literature, commonly two ways to calculate the unit cost rate are considered,
-a renewal theory based long-term unit cost rate,
-and the one-cycle cost rate 
-\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}.
-Although the renewal theory based unit cost rate is often used
-in CBM literature \citep{2013:si-et-al,2011:kim-et-al},
+We use the expected one-cycle cost rate 
+\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}
+to calculate the unit cost rate.
+Although a different, renewal theory based way to calculate the unit cost rate is often used
+in CBM literature \citep[e.g.,][]{2013:si-et-al,2011:kim-et-al},
 %As we discussed in the Introduction,
-we use the one-cycle cost rate as it is the most appropriate for our situation.
+we use the one-cycle cost rate as it is the most appropriate for our situation,
+where $\tau_*$ changes with every cycle, and indeed changes with $\tnow$.
 %since it considers only the costs with respect to the current cycle.
 
+\subsection{Expected unit cycle cost rate}
+
 Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
+Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
+such that often, $c_p \ll c_u$,
+and these are exactly the situations where CBM is most effective (***cite working paper on relative benefit).
+
 As discussed in the Introduction,
 we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system.
-Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
-such that often, $c_p \ll c_u$.
+That means that every time a new cycle starts, the system is the same state with all components (as-good-as) new.
+Replacement schemes that do not replace all components need to take into account the different ages of components in the system
+at the start of a new cycle.
+While this is in principle possible in our approach,
+notation explodes to account for that***
 
-Conditional on the (random) system failure time $\Tsys$, the unit cost rate is 
+Let $\Tsysnow$ be the random variable corresponding to $\Rsysnow(t)$,
+giving the (random) system failure time for times $t > \tnow$,
+conditioned on all information available at $\tnow$,
+and $\fsysnow(t)$ be the corresponding density.
+Conditional on $\Tsysnow$, the unit cost rate is 
 \begin{align*}
-g(\tau \mid \Tsys) &=
+g(\tau \mid \Tsysnow) &=
 \begin{cases}
-c_p / \tau  & \text{if } \Tsys \ge \tau \\
-c_u / \Tsys & \text{if } \Tsys < \tau
+c_p / \tau  & \text{if } \Tsysnow \ge \tau \\
+c_u / \Tsys & \text{if } \Tsysnow < \tau
 \end{cases}
 \end{align*}
-
-Taking the expectation over $\Tsys$ leads to the expected unit cost rate being
+Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
 \begin{align}
-g(\tau) &= \E[g(\tau \mid \Tsys)] = \frac{c_p}{\tau} \Rsys(\tau) + c_u \int_0^\tau \frac{1}{t} \fsys(t) \dd t
+\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
 \label{eq:gtau}
 \end{align}
-***here, $\Rsys(\cdot)$ shifted such that $\tnow = 0$.
+***$\fsysnow(t)$ needs to fulfill certain conditions for the integral to exist / to be finite.
+
+$\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient (****)
+
+***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.
+
+***if $\gnow(\tau)$ monotonely decreasing, corrective maintenance is optimal: policy switch!
+
+\subsection{Numerical optimization of the expected unit cycle cost rate}
+
+*** not possible / *** to minimize $\gnow(\tau)$ analytically.
 
 We approximate the integral in \eqref{eq:gtau} numerically by a sum,
-where $\fsys(t)$ is calculated via differencen of $\Rsys(t)$ values on a dense grid.
-$g(\tau)$ is likewise evaluated on a dense grid,
-and $\tau^*_{\tnow} = \arg\min g(\tau)$ is determined as the minimum over the grid.
-The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
-$\tau^*$ depends on $\tnow$, and also on the history of the system.
+where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on a dense grid.
+$\gnow(\tau)$ is likewise evaluated on a dense grid,
+and $\tau_*^{(\tnow)} = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
+%The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
+%$\tau^*$ depends on $\tnow$, and also on the history of the system.
 
-At time $\tnow$, the corresponding $\tau^*_{\tnow}$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
-so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau^*_{\tnow}$.
+***calculations in \textsf{R} can be vectorized and are thus fast.
 
-****plot both $\tau^*_{\tnow}$ and $\tnow + \tau^*_{\tnow}$ over time for different failure histories
+At time $\tnow$, the corresponding $\tau_*^{\tnow}$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
+so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau_*^{\tnow}$.
+
+***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy
+
+****plot both $\tau_*^{\tnow}$ and $\tnow + \tau_*^{\tnow}$ over time for different failure histories
+
+\subsection{Operational procedure}
+
+*** could update $\tau_*$ every time a component fails,
+but (near) real-time update of $\tau_*$ possible and useful as non-failed components still contribute to knowledge base via right-censored observation $\tpnow$.
 

### 2016-10-24 cbm-rbd-paper.tex
RBD figure, surv sign table

@@
 
-We consider a system with components of $k=1,\ldots,K$ different types;
-for each type $k$, there are $N_k$ exchangeable components in the system.
-
-***example reliability block diagram
-
-component model: weibull with fixed shape,
+***component model: weibull with fixed shape,
 inverse gamma prior on scale parameter,
 fix priors via expected lifetime and prior strength,
-
 test data inclusion
@@
 
-RUL/RLD via survival signature,
+***RUL/RLD via survival signature,
 posterior predictive distributions,
@@
 
-output is the current system reliability curve
+***output is $\Rsysnow(t)$, the current (at time $\tnow$) system reliability function
+(residual life distribution, RLD)
 taking into account the current system state,
@@
 and the lifetime histories of all component types,
-including test data and expert assessments.
+including test data (if available) and expert assessments.
 
-***RUL model description below follows closely \cite{2016:walter-coolen},
-which describes the same RUL/RLD model.
-However, \cite{2016:walter-coolen} does not consider maintenance policies,
-and focuses instead on a generalization of the RUL/RLD model using sets of priors for the component models
+We can analyze systems of arbitrary layout, consisting of components of $k=1,\ldots,K$ different types,
+where for each type $k$, there are $N_k$ exchangeable components in the system.
+As an example, Figure~\ref{fig:bridge-layout} depicts the reliability block diagram of a bridge type system
+with three component types $A$, $B$, $C$, where $N_A=4$, $N_B=1$, and $N_C=1$.
+
+***Model description in this Section follows closely \cite{2016:walter-coolen},
+who present the same RUL/RLD model.
+However, \cite{2016:walter-coolen} do not consider maintenance policies,
+and focus instead on a generalization of the RUL/RLD model using sets of priors for the component models
 (which can be seen as parametric P-boxes),
@@
 and sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
+ hv path/.style={very thick, to path={-| (\tikztotarget)}},
+ vh path/.style={very thick, to path={|- (\tikztotarget)}}]
+%\begin{scope}[scale=0.75]
+\node[type1] (T1-2) at ( 1.4, 1) {$A_1$};
+\node[type1] (T1-3) at ( 1.4,-1) {$A_2$};
+\node[type1] (T1-5) at ( 4.2, 1) {$A_3$};
+\node[type1] (T1-6) at ( 4.2,-1) {$A_4$};
+\node[type2] (T2)   at ( 2.8, 0) {$B_1$};
+\node[type3] (T3)   at ( 5.6, 0) {$C_1$};
+\coordinate (start) at (0  ,0);
+\coordinate (end)   at (6.3,0);
+\coordinate (bista) at (0.7,0);
+\coordinate (biend) at (4.9,0);
+\path (bista)     edge[hv path] (start)
+                  edge[vh path] (T1-2.west)
+                  edge[vh path] (T1-3.west)
+      (T1-2.east) edge[hv path] (T2.north)
+      (T1-3.east) edge[hv path] (T2.south)
+      (T2.north)  edge[vh path] (T1-5.west)
+      (T2.south)  edge[vh path] (T1-6.west)
+      (biend)     edge[vh path] (T1-5.east)
+                  edge[vh path] (T1-6.east)
+                  edge[hv path] (T3.west)
+      (T3.east)   edge[hv path] (end);
+%\end{scope}
+\end{tikzpicture}
+\caption{Reliability block diagram for a `bridge' type system with three component types $A$, $B$, $C$.
+Note that this system layout cannot be expressed as a nesting of series and parallel layouts.
+The corresponding survival signature $\Phi(l_A,l_B,l_C)$ is given in Table~\ref{tab:bridge-survsign}.}
+\label{fig:bridge-layout}
+\end{figure}
 
@@
 
+\begin{table}
+\centering
+\begin{tabular}{ccclccccl}
+  \toprule
+$l_A$ & $l_B$ & $l_C$ & $\Phi$ & \quad & $l_A$ & $l_B$ & $l_C$ & $\Phi$\\ 
+  \midrule
+0 & 0 & 1 & 0    & & 0 & 1 & 1 & 0 \\ 
+1 & 0 & 1 & 0    & & 1 & 1 & 1 & 0 \\ 
+2 & 0 & 1 & 0.33 & & 2 & 1 & 1 & 0.67 \\ 
+3 & 0 & 1 & 1    & & 3 & 1 & 1 & 1 \\ 
+4 & 0 & 1 & 1    & & 4 & 1 & 1 & 1 \\ 
+   \bottomrule
+\end{tabular}
+\caption{Survival signature $\Phi(l_A,l_B,l_C)$ for the bridge system from Figure~\ref{fig:bridge-layout},
+omitting all rows with $l_C=0$, since $\Phi(l_A,l_B,0)=0$ for all $l_A$ and $l_B$.}
+\label{tab:bridge-survsign}
+\end{table}
+
 \subsection{Reliability functions for complex systems using the survival signature}
@@
 can be efficiently calculated using the survival signature.
-We will show in Section~***
+We will show in Section~\ref{sec:sysreltnow}
 how this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
@@
 and the total number of components in the system is $\sum_{k=1}^K N_k = N$.
-An example system reliability block diagram is given in Figure~***.
+An example system reliability block diagram is given in Figure~\ref{fig:bridge-layout}.
 Note that this system cannot be described as a nesting of series and parallel subsystems.
@@
 
-***An example for the survival signature for the system in Figure *** is given in Table ****.
+As an example, the survival signature for the system in Figure~\ref{fig:bridge-layout} is given in Table~\ref{tab:bridge-survsign}.
 
@@
 \subsection{System reliability function at $\tnow$}
+\label{sec:sysreltnow}
 

### 2016-10-24 cbm-rbd-paper.tex
RBD figure, surv sign table

@@
 
-\section{***Adaptive system RUL / RLD based on Weibull component models}
+\section{Adaptive system residual life distribution based on Weibull component models}
 
@@
 we thus need, for each $k=1,\ldots, K$, the probabilities $P(C^k_t = l_k)$
-for the number of type $k$ components that function at times $t > \tnow$.
+for the number of type $k$ components that function at times $t > \tnow$,
+taking into account all information available at $\tnow$.
 In the Bayesian framework, these probabilities are given
@@
 where $T^k$ is the Weibull distributed lifetime of a component of type $k$.
+Note that through the condition $T^k > \tnow$, we also take into account
+that the components in the system age $\tnow$.
 Now, by the Weibull assumption \eqref{eq:weibullcdf}, one has

### 2016-10-24 cbm-rbd-paper.tex
coputaton complexity comments for Rsysnow

@@
 Note that through the condition $T^k > \tnow$, we also take into account
-that the components in the system age $\tnow$.
+that the components in the system have the age $\tnow$.
 Now, by the Weibull assumption \eqref{eq:weibullcdf}, one has
@@
 
-Next, we will describe how an adaptive maintenance policy based on \eqref{eq:sysrel-tnow}
-can be obtained.
+For each prediction time $t$,
+\eqref{eq:sysrel-tnow} is a sum over over $\prod_{k=1}^K (\cknow + 1)$ terms;
+however, some of these terms correspond to $\Phinow(l_1,\ldots,l_K) = 0$,
+which can thus be disregarded.
+For each of the remaining terms,
+we must calculate the product $\prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)$.
+For all products, the constituting factors can be taken from the same table
+enumerating $P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)$ for all $l_k \in \{0, 1, \cknow\}$, $k=1\ldots,K$,
+so \eqref{eq:postpred-priorparams} needs to be invoked 
+only $\sum_{k=1}^K (\cknow + 1)$ times.
+
+We will evaluate \eqref{eq:sysrel-tnow} on a dense grid of prediction times $t > \tnow$,
+thus discretely approximating the RLD.
+As the evaluation of \eqref{eq:sysrel-tnow} for each $t$ does not involve any complex numeric calculations or Monte Carlo sampling,
+the grid of prediction values can be very fine.
+
+Next, we will describe how an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
+such a fine discrete approximation of the RLD can be obtained.
 

### 2016-10-24 cbm-rbd-paper.tex
policy section start

@@
 \newcommand{\gnow}{g^{(\tnow)}}
+\newcommand{\tausnow}{\tau_*^{(\tnow)}}
+\newcommand{\tsetup}{\tau_{\text{setup}}}
 
@@
 
-\section{Dynamic maintenance policy based on the current system reliability function (RUL/RLD)}
-
-To find the optimal moment for maintenance based on the current system reliability function $\Rsysnow(t)$,
-we minimize the expected average cost per time unit,
-called the unit cost rate, $g(\tau)$,
-to find the cost-optimal moment of maintenance $\tau_*$
-(could be discounted as well, out of scope here.)
+\section{Dynamic/Adaptive maintenance policy based on the current system residual life distribution}
+\label{sec:policy}
+
+We can now derive the adaptive / dynamic maintenance policy
+that resembles a CBM policy.
+However, instead of a determining a threshold for a degradation signal like in usual CBM policies,
+we determine, for each present time $\tnow$,
+the adaptive and dynamic timespan $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
+Close to system startup, $\tausnow$ will be large;
+but as components in the system age and some indeed fail over time,
+$\tausnow$ will typically decrease,
+and whenever $\tausnow$ decreases below $\tsetup$, the timespan needed to set up maintenance work
+(often referred to as setup time),
+a preventive maintenance action is initiated.
+
+The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
+using the expected unit cost rate for the current operational cycle, see Section~\ref{sec:costrate} below.
+Each operational cycle starts with the system being in an (as good as) new state,
+i.e., all components in the system are new and have not aged.
+A cycle ends when the system is either maintained preventively at $\tnow + \tausnow$ (on an absolute time scale),
+or the system fails, which triggers a corrective maintenance action.
+We assume that either maintenance action takes negligible time,
+and that either action results in an (as good as) new system state by replacing all components,
+such that the system begins a new cycle begins under identical conditions.
+
+***info from finished cycle is added to component knowledge base,
+thus included in $\nkz$ and $\ykz$ for the following cycle.
+
+Therefore, at each present time $\tnow$
+(at a frequency small enough to be negligible on the system lifetime scale),
+the current residual life distribution $\Rsysnow(t)$ is recalculated,
+and the corresponding $\tausnow$ determined.
+
+***as $\Rsysnow(t)$ on discrete grid until horizon, optimize $\tausnow$ over same discrete grid.
+if $\gnow(\tau)$ always decreasing, corrective maintenance strategy! so we can switch maintenance policy!
+
+%To find the optimal moment for maintenance based on the current system reliability function $\Rsysnow(t)$,
+%we minimize the expected average cost per time unit,
+%called the unit cost rate, $g(\tau)$,
+%leading to the cost-optimal moment of maintenance $\tau_*$.
+%(could be discounted as well, out of scope here.)
+
+\subsection{Expected unit cycle cost rate}
+\label{sec:costrate}
 
@@
 we use the one-cycle cost rate as it is the most appropriate for our situation,
-where $\tau_*$ changes with every cycle, and indeed changes with $\tnow$.
+where $\tau_*$ changes with every cycle, and indeed changes with $\tnow$ within each cycle.
 %since it considers only the costs with respect to the current cycle.
 
-\subsection{Expected unit cycle cost rate}
-
-Let $c_p$ be the cost of planned / preventive maintenance, and $c_u$ the cost of unplanned / breakdown maintenance, where $c_p < c_u$.
+Let $c_p$ be the cost of planned (preventive) maintenance, and $c_u$ the cost of unplanned (breakdown) maintenance, where $c_p < c_u$.
 Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
 such that often, $c_p \ll c_u$,
-and these are exactly the situations where CBM is most effective (***cite working paper on relative benefit).
+and these are exactly the situations where CBM is most effective
+(***cite de Jonge and Teunter working paper on relative benefit).
 
@@
 
+***$\tsetup$ could vary over time, e.g., longer on weekends or outside office hours,
+
 \section*{Acknowledgements}

### 2016-10-24 cbm-rbd-paper.tex
work on policy section intro

@@
 that resembles a CBM policy.
-However, instead of a determining a threshold for a degradation signal like in usual CBM policies,
+However, instead of determining a threshold for a degradation signal like in usual CBM policies,
 we determine, for each present time $\tnow$,
@@
 but as components in the system age and some indeed fail over time,
-$\tausnow$ will typically decrease,
-and whenever $\tausnow$ decreases below $\tsetup$, the timespan needed to set up maintenance work
-(often referred to as setup time),
+$\tausnow$ will typically decrease.
+Let $\tsetup$ be the timespan needed to set up maintenance work,
+often referred to simply as setup time.
+As soon as $\tausnow$ decreases below $\tsetup$,
 a preventive maintenance action is initiated.
@@
 The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
-using the expected unit cost rate for the current operational cycle, see Section~\ref{sec:costrate} below.
+by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle, see Section~\ref{sec:costrate} below.
+
 Each operational cycle starts with the system being in an (as good as) new state,
 i.e., all components in the system are new and have not aged.
-A cycle ends when the system is either maintained preventively at $\tnow + \tausnow$ (on an absolute time scale),
+A cycle ends when the system is either maintained preventively at time $\tnow + \tausnow$ (on an absolute time scale),
 or the system fails, which triggers a corrective maintenance action.
-We assume that either maintenance action takes negligible time,
+The calculation of $\tausnow$ thus resembles the calculation
+of the maintenance interval in an age based policy.
+However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
+our policy is adaptive and dynamic like a CBM policy.
+
+It is possible that $\gnow(\tau)$ is monotonely decreasing, corrective maintenance strategy! so we can switch maintenance policy!
+
+During a cycle,
+$\tausnow$ is recalculated at a frequency small enough to be negligible on the system lifetime scale.
+This is possible because we use a fast discrete approximation of the unit cost rate function.
+
+***as $\Rsysnow(t)$ on discrete grid until some horizon, optimize $\tausnow$ over same discrete grid.
+
+*** could update $\tausnow$ every time a component fails,
+but (near) real-time update of $\tau_*$ possible and useful,
+as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
+
+At the end of each cycle,
+the component information gained during the completed cycle is added to the component knowledge base
+by updating the parameters $\nk$ and $\yk$ accordingly,
+%using failure and censoring times as of the end of the cycle.
+such that $\nkz$ and $\ykz$ for the following cycle account for the lifetimes and censoring observed during the previous cycle.
+We assume that both planned and unplanned maintenance action takes negligible time,
 and that either action results in an (as good as) new system state by replacing all components,
-such that the system begins a new cycle begins under identical conditions.
-
-***info from finished cycle is added to component knowledge base,
-thus included in $\nkz$ and $\ykz$ for the following cycle.
-
-Therefore, at each present time $\tnow$
-(at a frequency small enough to be negligible on the system lifetime scale),
-the current residual life distribution $\Rsysnow(t)$ is recalculated,
-and the corresponding $\tausnow$ determined.
-
-***as $\Rsysnow(t)$ on discrete grid until horizon, optimize $\tausnow$ over same discrete grid.
-if $\gnow(\tau)$ always decreasing, corrective maintenance strategy! so we can switch maintenance policy!
+such that the system begins a new cycle always under the same condition.
 
@@
 \label{sec:costrate}
+
+To determine the optimal time to maintenance $\tausnow$,
 
@@
 \end{align}
-***$\fsysnow(t)$ needs to fulfill certain conditions for the integral to exist / to be finite.
-
-$\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient (****)
+
+***$\fsysnow(t)$ needs to fulfill certain conditions for the integral to exist / to be finite because of $1/t$.
+we have no problem because of discrete approximation of $\Rsysnow(t)$ resp. $\fsysnow(t)$.
+($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
 
@@
 ****plot both $\tau_*^{\tnow}$ and $\tnow + \tau_*^{\tnow}$ over time for different failure histories
-
-\subsection{Operational procedure}
-
-*** could update $\tau_*$ every time a component fails,
-but (near) real-time update of $\tau_*$ possible and useful as non-failed components still contribute to knowledge base via right-censored observation $\tpnow$.
 

### 2016-10-24 cbm-rbd-paper.tex
work on 4.1 and 4.2

@@
 a preventive maintenance action is initiated.
+%and executed at time $\tnow + \tausnow$.
 
@@
 by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle, see Section~\ref{sec:costrate} below.
-
 Each operational cycle starts with the system being in an (as good as) new state,
 i.e., all components in the system are new and have not aged.
-A cycle ends when the system is either maintained preventively at time $\tnow + \tausnow$ (on an absolute time scale),
+A cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
 or the system fails, which triggers a corrective maintenance action.
-The calculation of $\tausnow$ thus resembles the calculation
-of the maintenance interval in an age based policy.
-However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
+The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
+of the maintenance interval in an age based policy;
+however, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
 our policy is adaptive and dynamic like a CBM policy.
 
-It is possible that $\gnow(\tau)$ is monotonely decreasing, corrective maintenance strategy! so we can switch maintenance policy!
+It is also possible that $\gnow(\tau)$ is monotonely decreasing.
+In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
+This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
+but also capable of indicating when corrective maintenance is the better option.
+%i.e., capable of choosing the maintenance policy.
 
@@
 $\tausnow$ is recalculated at a frequency small enough to be negligible on the system lifetime scale.
-This is possible because we use a fast discrete approximation of the unit cost rate function.
-
-***as $\Rsysnow(t)$ on discrete grid until some horizon, optimize $\tausnow$ over same discrete grid.
-
-*** could update $\tausnow$ every time a component fails,
-but (near) real-time update of $\tau_*$ possible and useful,
-as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
+This is feasible because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
+and determine $\tausnow$ with a simple grid search.
+Updating $\tausnow$ frequently is useful because,
+even in absence of failures of system components,
+all components age, and also non-failure adds information to the component models.
+Both factors influence $\Rsysnow(t)$ and thus $\tausnow$.
+%An alternative would be to update $\tausnow$ only when a component fails,
+%but as a (near) real-time update of $\taausnow$ is possible and useful,
+%as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
 
@@
 To determine the optimal time to maintenance $\tausnow$,
-
-We use the expected one-cycle cost rate 
+we use the expected one-cycle cost rate 
 \citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}
-to calculate the unit cost rate.
+as the unit cost rate.
 Although a different, renewal theory based way to calculate the unit cost rate is often used
@@
 we use the one-cycle cost rate as it is the most appropriate for our situation,
-where $\tau_*$ changes with every cycle, and indeed changes with $\tnow$ within each cycle.
+where $\tausnow$ changes with every cycle, and indeed changes with $\tnow$ within each cycle.
 %since it considers only the costs with respect to the current cycle.
@@
 
-As discussed in the Introduction,
+As discussed in the Introduction and above,
 we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system.
-That means that every time a new cycle starts, the system is the same state with all components (as-good-as) new.
+That means that every time a new cycle starts, the system is in the same state with all components (as-good-as) new.
 Replacement schemes that do not replace all components need to take into account the different ages of components in the system
@@
 While this is in principle possible in our approach,
-notation explodes to account for that***
+exploring such selective replacement schemes is out of scope for this paper
+and worthy for a seperate contribution.
 
@@
 
-***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.
-
-***if $\gnow(\tau)$ monotonely decreasing, corrective maintenance is optimal: policy switch!
+%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.
 
@@
 
-*** not possible / *** to minimize $\gnow(\tau)$ analytically.
+%*** not possible / *** to minimize $\gnow(\tau)$ analytically.
+***we calculate $\Rsysnow(t)$ on discrete grid until some horizon, optimize $\tausnow$ over same discrete grid.
 
@@
 
-At time $\tnow$, the corresponding $\tau_*^{\tnow}$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
-so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau_*^{\tnow}$.
-
-***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy
+***if min $\gnow(\tau)$ at horizon, corrective maintenance is optimal: policy switch!
+%***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy
+
+%At time $\tnow$, the corresponding $\tausnow$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
+%so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau_*^{\tnow}$.
 
@@
 
-***
+***???
 
@@
 
-which system layout? something that demonstrates the power of the method (complex layout) or something simple?
-
-complex: e.g., bridge system where each of the four elements is a two out of three, and the bridge element is a two-parallel.
-
-or the simplified brake system from ASCE-ASME paper?
+use simple system layout, example history of compnents failing
+
+use the simplified brake system from ASCE-ASME paper?
 
@@
 then one needs to use actual ages (and not time since system startup) in parameter update,
-introduces new component type for $\Rsys(t)$ calculation but with same posterior parameters as unreplaced component type.
+introduces new component type for $\Rsysnow(t)$ calculation but with same posterior parameters as unreplaced component type.
 Repaired/replaced components require the creation of a separate type in the survival signature decomposition
 and thus the calculation of separate posterior predictive probabilities
-$P(C^k_t = l_k \mid \nkz,\ykz,\text{test data},\text{monitoring data})$,
+$P(C^k_t = l_k \mid \nkz,\ykz,\vectknow)$,
 which use, however, the same hyperparameter learning (using actual component ages) as the `parent type'.

### 2016-10-25 cbm-rbd-paper.tex
minor tweaks

@@
 we obtain a predictive distribution for system survival time
-(also known as RUL, remaining useful life)
+%(also known as RUL, remaining useful life)
+(known as residual life distribution, RLD)
 based on which of the system's components currently function or not,
@@
 (i.e., its reliability block diagram) and information on components' status
-to directly calculate the RUL distribution,
+to directly calculate the residual life distribution (RLD),
 and base the maintenance policy on this distribution.
@@
 
-These predictive distributions are then used to calculate the exact distribution of system RUL
+These predictive distributions are then used to calculate the exact distribution of system residual life
 using the survival signature \citep{2012:survsign}.
@@
 
-By its Bayesian nature, the system RUL distribution adequately reflects the uncertainties in RUL estimation
+By its Bayesian nature, the system residual life distribution adequately reflects the uncertainties %in RUL estimation
 related to modeling and prediction \citep{2015:sankararaman},
 readily adapting to any changes in component behaviour.
-The use of conjugate priors means that we get explicit formulas for the RUL distribution,
+The use of conjugate priors means that we get explicit formulas for the RLD,
 so no numerical integration or simulation techniques are necessary.
-This allows for a very frequent, or even real-time, update of the RUL distribution,
+This allows for a very frequent, or even real-time, update of the RLD,
 taking into account the changed structure when components have failed
@@
 
-Based on the RUL distribution at any current time $\tnow$,
+Based on the RLD at any current time $\tnow$,
 the optimal moment of maintenance given all information available at $\tnow$
@@
 
-Since the RUL distribution changes with current time $\tnow$,
-the corresponding optimal moment of maintenance $\tau^*$ changes as well,
+Since the RLD changes with current time $\tnow$,
+the corresponding optimal moment of maintenance $\tausnow$ changes as well,
 leading to a dynamic adaptive maintenance policy,
@@
 since it gives the optimal moment of maintenance as a time beyond current time $\tnow$,
-and maintenance can be initiated as soon as $\tau^*$ approaches the set-up time.
+and maintenance can be initiated as soon as $\tausnow$ equals the set-up time.
 
@@
 or indeed optimize the unit cost rate over all possible replacement schemes,
-since our method for RUL calculation can handle differently aged components. 
+since our method for RLD calculation can handle differently aged components. 
 However, optimizing over replacement schemes opens up a full research programme on its own,
@@
 
-***figure of process: component priors $\to$ component posteriors $\to$ system RUL $\to$ $g(\tau)$ $\to$ $\tau^*$
-
-***operation: recalculate $\tau^*$ at fixed dense grid of time points (quasi-continuous),
-this makes sense even if nothing happens because the fact that components in the system still function
+***figure of process: component priors $\to$ component posteriors $\to$ system RLD $\to$ $\gnow(\tau)$ $\to$ $\tausnow$
+
+***operation: recalculate $\tausnow$ at fixed dense grid of time points (quasi-continuous),
+this makes sense even when no failures happen because the fact that components in the system still function
 gives information on component distributions;
@@
 
-***model allows also to switch to corrective policy when $g(\tau)$ monotonely decreasing (then $\tau \to \infty$)
+***model allows also to switch to corrective policy when $\gnow(\tau)$ monotonely decreasing (then $\tausnow \to \infty$)
 
@@
 
-***CBM via RUL, $M^*$ out of $N$ policies?
+***CBM via RUL/RLD, $M^*$ out of $N$ policies?
 
@@
 that resembles a CBM policy.
-However, instead of determining a threshold for a degradation signal like in usual CBM policies,
+However, instead of determining a threshold for a degradation signal like in usual CBM approaches,
 we determine, for each present time $\tnow$,
@@
 all components age, and also non-failure adds information to the component models.
-Both factors influence $\Rsysnow(t)$ and thus $\tausnow$.
+Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$.
 %An alternative would be to update $\tausnow$ only when a component fails,
@@
 such that $\nkz$ and $\ykz$ for the following cycle account for the lifetimes and censoring observed during the previous cycle.
-We assume that both planned and unplanned maintenance action takes negligible time,
-and that either action results in an (as good as) new system state by replacing all components,
+%We assume that both planned and unplanned maintenance action takes negligible time,
+We assume that both a planned and unplanned maintenance action results in an (as good as) new system state by replacing all components,
 such that the system begins a new cycle always under the same condition.
+As we use a one-cycle criterion, the time these maintenance actions take does not matter for the determination of $\tausnow$.
+Downtimes are instead accounted for via the costs parameters,
+as described next.
 
@@
 Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
-such that often, $c_p \ll c_u$,
-and these are exactly the situations where CBM is most effective
+such that often, $c_p \ll c_u$.
+CBM is known to be most effective when the difference between $c_p$ and $c_u$ is large
 (***cite de Jonge and Teunter working paper on relative benefit).
@@
 
-use simple system layout, example history of compnents failing
+use simple system layout, example history of components failing
 
@@
 
-*** move to sets of priors, set of RUL distributions like in \cite{2016:walter-coolen}.
-Leads to set of $g(\tau)$, finding (set of) $\tau^*$ is then non-trivial,
-needs decision criteria from IP literature like E-admissibility, maximality, or maximin.
+*** move to sets of priors, set of residual life distributions like in \cite{2016:walter-coolen}.
+Leads to set of $\gnow(\tau)$, finding (set of) $\tausnow$ is then non-trivial,
+needs decision criteria from imprecise probability literature like E-admissibility, maximality, or maximin
+\citep[see, e.g., \S 9***][]{itip}.
 
@@
 
-***$\tsetup$ could vary over time, e.g., longer on weekends or outside office hours,
+***$\tsetup$ could vary over time, e.g., longer on weekends or outside office hours
 

### 2016-10-25 weibull-sys-functions.R
bug in postpredC

@@ -1,11 +1,9 @@
 ###############################################################################
-#       Functions to calculate and plot sets of reliability curves            #
+#       Functions to calculate and plot system reliability functions          #
 #       for systems consisting of Weibull components with fixed shape         #
 ###############################################################################
 
-# provides dinvgamma(x, shape, scale) where shape = alpha and scale = beta
-library(actuar)
-library(luck)
+library(actuar) # provides dinvgamma(x, shape, scale) where shape = alpha and scale = beta
 library(ReliabilityTheory)
 library(ggplot2)
 library(reshape2)
@@ -40,36 +38,35 @@ cpigfornoptim <- function(n, y, t, ...)
 # function to calculate P(C_t = l | n^(0), y^(0), data),
 # the posterior predictive probability that l components function at time t
 # in the system observed until t_now (notion "of type k" dropped here)
-# this implements (20)
-# n0y0    pair c(n0,y0) of prior parameters
+# n0y0    pair c(n0,y0) of prior parameters (start of cycle values)
 # t       time t for which to calculate P(C_t), t > t_now
-# l       number of functioning components, \in {0, 1, ..., n-e}
+# l       number of functioning components, \in {0, 1, ..., c = n-e}
 # n       number of components in the system
 # tnow    time until the system is observed
 # fts     vector of length e giving the observed failure times,
 #         or NULL if no failures observed
 # beta    fixed weibull shape parameter
 # prior   whether the prior predictive should be calculated,
-#         when FALSE, fts is ignored 
+#         when TRUE, fts is ignored 
 postpredC <- function(n0y0, beta, n, fts, tnow, t, l, prior = FALSE){
   if (t < tnow)
     stop("t must be larger than tnow")
   if(!prior){
     e <- length(fts)
     if (n < e)
-      stop("there can be at most n failure times!")
+      stop("too many elements in fts, there can be at most n failure times!")
   } else {
     e <- 0
   }
   if (l > n-e)
-    stop("l can be at most n-e")
+    stop("l can be at most c=n-e")
   nn <- n0y0[1] + e
   if(!prior)
-    nnyn <- n0y0[1]*n0y0[2] + (n-e)*tnow + sum(fts^beta)
[…]

### 2016-10-25 weibull-sys-functions.R
potential edits for sysrel function

@@ -58,14 +58,14 @@ postpredC <- function(n0y0, beta, n, fts, tnow, t, l, prior = FALSE){
   } else {
     e <- 0
   }
-  if (l > n-e)
+  if (l > n-e) # any(l > n-e?)
     stop("l can be at most c=n-e")
   nn <- n0y0[1] + e
   if(!prior)
     nnyn <- n0y0[1]*n0y0[2] + (n-e)*(tnow^beta) + sum(fts^beta)
   else
     nnyn <- n0y0[1]*n0y0[2]
-  j <- seq(0, n-e-l)
+  j <- seq(0, n-e-l) # !!!
   choose(n-e, l) * sum( (-1)^j * choose(n-e-l, j) * (nnyn/(nnyn + (l+j)*(t^beta - tnow^beta)))^(nn + 1) )
 }
 
@@ -120,49 +120,51 @@ fourCornersCcmf <- function(luckobj, beta, n, fts, tnow, t, prior = FALSE){
   cat("br", paste(round(br,4), collapse = " "), "\n")
 }
 
-# calculates the system reliability / survival
-# this implements (13) (last equation in Sec 4.2 using the posterior predictive from 4.3)
+# calculates the system reliability for fixed future time t > tnow
+# order of length K vectors must be the same as in survsign table (!!!)
 #
 # n0y0     list of K prior parameter pairs c(n0,y0)
 # survsign data frame with the survival signature as output by computeSystemSurvivalSignature()
+#          this must be signature for the reduced system if components have failed!
 # beta     vector of K fixed weibull shape parameters
 # fts      list of K vectors giving the observed failure times for the compents of type 1,...,K;
 #          the list element should be NULL if no failure has been observed for type k
 # tnow     time until the system is observed
 # t        time t for which to calculate P(T_sys > t), t > t_now
 # table    if table of posterior predictive probabilities should be given along with the reliability
-# nk       vector of length K giving the number of components of each type,
+# Nk       vector of length K giving the number of components of each type,
 #          this is needed only when reduced survival signature is used
-# prior    whether the prior system relibability should be calculated
-sysrel <- function(n0y0, survsign, beta, fts, tnow, t, table = FALSE, nk = NULL, prior = FALSE){
[…]

### 2016-10-25 weibull-sys-functions.R
more ideas for sysrel function

@@ -58,7 +58,7 @@ postpredC <- function(n0y0, beta, n, fts, tnow, t, l, prior = FALSE){
   } else {
     e <- 0
   }
-  if (l > n-e) # any(l > n-e?)
+  if (l > n-e)
     stop("l can be at most c=n-e")
   nn <- n0y0[1] + e
   if(!prior)
@@ -122,10 +122,12 @@ fourCornersCcmf <- function(luckobj, beta, n, fts, tnow, t, prior = FALSE){
 
 # calculates the system reliability for fixed future time t > tnow
 # order of length K vectors must be the same as in survsign table (!!!)
+# (what happens when a component type is no longer in the reduced graph?)
 #
 # n0y0     list of K prior parameter pairs c(n0,y0)
 # survsign data frame with the survival signature as output by computeSystemSurvivalSignature()
 #          this must be signature for the reduced system if components have failed!
+#          -> use induced_subgraph()
 # beta     vector of K fixed weibull shape parameters
 # fts      list of K vectors giving the observed failure times for the compents of type 1,...,K;
 #          the list element should be NULL if no failure has been observed for type k
@@ -133,7 +135,7 @@ fourCornersCcmf <- function(luckobj, beta, n, fts, tnow, t, prior = FALSE){
 # t        time t for which to calculate P(T_sys > t), t > t_now
 # table    if table of posterior predictive probabilities should be given along with the reliability
 # Nk       vector of length K giving the number of components of each type,
-#          this is needed only when reduced survival signature is used
+#          this is needed only when reduced survival signature is used (???)
 # prior    whether the prior system relibability should be calculated (no updating with things observed until tnow)
 sysrel <- function(n0y0, survsign, beta, fts, tnow, t, table = FALSE, Nk = NULL, prior = FALSE){
   K <- length(fts)
@@ -158,7 +160,7 @@ sysrel <- function(n0y0, survsign, beta, fts, tnow, t, table = FALSE, Nk = NULL,
     tmpname <- paste("PCt", names(survsign2)[k], sep="")
     ncols <- length(survsign2)
     names(survsign2) <- c(names(survsign2)[-ncols], tmpname)
-    # better vectorize inner for loop and append vector to survsign, postpredC needs to allow vectorial l
+    # better vectorize inner for loop and append vector to survsign
     for (i in 1:dim(survsign2)[1]){
[…]

### 2016-10-27 cbm-rbd-paper.tex
survsign first and in separate section, brakesys instead of bridgesys

@@
 
+\section{Reliability functions for complex systems using the survival signature}
+\label{sec:sysrel}
+
+Here we describe how the system reliability function, given fixed component models and the system layout,
+can be efficiently calculated using the survival signature.
+We will show in Section~\ref{sec:sysreltnow}
+how this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
+giving us the residual life distribution on which we base our adaptive maintenance policy.
+
+We can analyze systems of arbitrary reliability block diagram layout,
+consisting of components of $K$ different types,
+where there are $N_k$ exchangeable components of type $k$ in the system,
+and the total number of components in the system is $\sum_{k=1}^K N_k = N$.
+
+As a running example, we consider a simplified automotive braking system
+consisting of four component types $M$, $H$, $C$ and $P$,
+with reliability block diagram as depicted in Figure~\ref{fig:brakesys-layout}.
+The master brake cylinder ($M$) activates all four wheel brake cylinders ($C_1$ -- $C_4$),
+which in turn actuate a braking pad assembly each ($P_1$ -- $P_4$).
+The hand brake mechanism ($H$) directly actuates the brake pad assemblies $P_3$ and $P_4$;
+the vehicle brakes when at least one brake pad assembly is actuated.
+Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
+%This system is observed until time $\tnow$,
+%leading to censored observation of certain component lifetimes within the system.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+[typeM/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
+ typeC/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
+ typeP/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
+ typeH/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
+ type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ cross/.style={cross out,draw=red,very thick,minimum width=9mm, minimum height=7mm},
+ hv path/.style={thick, to path={-| (\tikztotarget)}},
+ vh path/.style={thick, to path={|- (\tikztotarget)}}]
+\begin{scope}[xscale=1.5, yscale=1.2]
+\node[typeM] (M)    at ( 0  , 0  ) {$M$};
+\node[typeC] (C1)   at ( 1  , 1.5) {$C_1$};
+\node[typeC] (C2)   at ( 1  , 0.5) {$C_2$};
+%\node[cross]        at ( 1  , 0.5) {};
+\node[typeC] (C3)   at ( 1  ,-0.5) {$C_3$};
+%\node[cross]        at ( 1  ,-0.5) {};
+\node[typeC] (C4)   at ( 1  ,-1.5) {$C_4$};
+\node[typeP] (P1)   at ( 2  , 1.5) {$P_1$};
+\node[typeP] (P2)   at ( 2  , 0.5) {$P_2$};
+%\node[cross]        at ( 2  , 0.5) {};
+\node[typeP] (P3)   at ( 2  ,-0.5) {$P_3$};
+%\node[cross]        at ( 2  ,-0.5) {};
+\node[typeP] (P4)   at ( 2  ,-1.5) {$P_4$};
+\node[typeH] (H)    at ( 0  ,-1  ) {$H$};
+\coordinate (start)  at (-0.7, 0);
+\coordinate (startC) at ( 0.5, 0);
+\coordinate (startH) at (-0.4, 0);
+\coordinate (Hhop1)  at ( 0.4,-1);
+\coordinate (Hhop2)  at ( 0.6,-1);
+\coordinate (endP)   at ( 2.5, 0);
+\coordinate (end)    at ( 2.8, 0);
+\path (start)     edge[hv path] (M.west)
+      (M.east)    edge[hv path] (startC)
+      (startC)    edge[vh path] (C1.west)
+                  edge[vh path] (C2.west)
+                  edge[vh path] (C3.west)
+                  edge[vh path] (C4.west)
+      (C1.east)   edge[hv path] (P1.west)
+      (C2.east)   edge[hv path] (P2.west)
+      (C3.east)   edge[hv path] (P3.west)
+      (C4.east)   edge[hv path] (P4.west)
+      (endP)      edge[vh path] (P1.east)
+                  edge[vh path] (P2.east)
+                  edge[vh path] (P3.east)
+                  edge[vh path] (P4.east)
+                  edge[hv path] (end)
+      (startH)    edge[vh path] (H.west)
+      (H.east)    edge[hv path] (Hhop1)
+      (Hhop1)     edge[thick,out=90,in=90] (Hhop2)
+      (Hhop2)     edge[hv path] (P3.south)
+                  edge[hv path] (P4.north);
+\end{scope}
+\end{tikzpicture}
+\caption{Reliability block diagram for a simplified automotive brake system
+with four component types $M$, $H$, $C$ and $P$.
+Note that this system layout cannot be expressed as a nesting of series and parallel layouts.
+The corresponding survival signature $\Phi(l_M,l_H,l_C,l_P)$ is given in Table~\ref{tab:brakesys-survsign}.}
+\label{fig:brakesys-layout}
+\end{figure}
+
+In a system with $N$ components, the state of the components can be expressed by the state vector
+$\vec{x} = (x_1,x_2,\ldots,x_N) \in \{0,1\}^N$,
+with $x_i=1$ if the $i$th component functions and $x_i=0$ if not.
+The structure function $\phi : \{0,1\}^N \rightarrow \{0,1\}$, defined for all possible $\vec{x}$,
+takes the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$ \citep{BP75}.
+Most real-life systems are coherent,
+which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
+so system functioning cannot be improved by worse performance of one or more of its components.
+Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.
+
+The survival signature \citep{2012:survsign} is a summary of the structure function
+for systems with $K$ groups of exchangeable components.
+Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,N_k$ for $k=1,\ldots,K$,
+it is defined as the probability for the event that the system functions
+given that precisely $l_k$ of its $N_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
+Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$,
+such that $\Rsys(t) = P(\Tsys > t)$ can be calculated using the law of total probability,
+\begin{align}
+P(\Tsys > t) &= \sum_{l_1=0}^{N_1} \cdots \sum_{l_K=0}^{N_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
+                                                                                  P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
+             &= \sum_{l_1=0}^{N_1} \cdots \sum_{l_K=0}^{N_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
+             &= \sum_{l_1=0}^{N_1} \cdots \sum_{l_K=0}^{N_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
+\label{eq:sysrel-survsign}
+\end{align}
+where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$,
+and the last equality holds as we assume that components of different types are independent.
+Note that for coherent systems, the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
+
+Continuing our example,
+the survival signature for the system in Figure~\ref{fig:brakesys-layout} is given in Table~\ref{tab:brakesys-survsign},
+omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$.
+(The full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.)
+
+\begin{table}
+\centering
+\begin{tabular}{cccclcccccl}
+  \toprule
+M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
+  \midrule
+1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
+1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
+1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
+0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
+0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
+0 & 1 & 1 & 1 & 0.62 & & 1 & 1 & 1 & 1 & 0.62 \\ 
+0 & 1 & 1 & 2 & 0.92 & & 1 & 1 & 1 & 2 & 0.92 \\ 
+0 & 1 & 2 & 1 & 0.75 & & 1 & 1 & 2 & 1 & 0.75 \\ 
+0 & 1 & 2 & 2 & 0.97 & & 1 & 1 & 2 & 2 & 0.97 \\ 
+0 & 1 & 3 & 1 & 0.88 & & 1 & 1 & 3 & 1 & 0.88 \\ 
+   \bottomrule
+\end{tabular}
+\caption{Survival signature $\Phi(l_M, l_H, l_C, l_P)$
+for the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout},
+omitting the rows for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$.}
+\label{tab:brakesys-survsign}
+\end{table}
+
 \section{Adaptive system residual life distribution based on Weibull component models}
@@
 with noninformatiove right-censoring
-
-***RUL/RLD via survival signature,
-posterior predictive distributions,
-system reliability distribution (RUL/RLD) as output,
 
@@
 including test data (if available) and expert assessments.
-
-We can analyze systems of arbitrary layout, consisting of components of $k=1,\ldots,K$ different types,
-where for each type $k$, there are $N_k$ exchangeable components in the system.
-As an example, Figure~\ref{fig:bridge-layout} depicts the reliability block diagram of a bridge type system
-with three component types $A$, $B$, $C$, where $N_A=4$, $N_B=1$, and $N_C=1$.
 
@@
 and sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.
-
-\begin{figure}
-\centering
-\begin{tikzpicture}
-[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
- type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
- type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
- cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
- hv path/.style={very thick, to path={-| (\tikztotarget)}},
- vh path/.style={very thick, to path={|- (\tikztotarget)}}]
-%\begin{scope}[scale=0.75]
-\node[type1] (T1-2) at ( 1.4, 1) {$A_1$};
-\node[type1] (T1-3) at ( 1.4,-1) {$A_2$};
-\node[type1] (T1-5) at ( 4.2, 1) {$A_3$};
-\node[type1] (T1-6) at ( 4.2,-1) {$A_4$};
-\node[type2] (T2)   at ( 2.8, 0) {$B_1$};
-\node[type3] (T3)   at ( 5.6, 0) {$C_1$};
-\coordinate (start) at (0  ,0);
-\coordinate (end)   at (6.3,0);
-\coordinate (bista) at (0.7,0);
-\coordinate (biend) at (4.9,0);
-\path (bista)     edge[hv path] (start)
-                  edge[vh path] (T1-2.west)
-                  edge[vh path] (T1-3.west)
-      (T1-2.east) edge[hv path] (T2.north)
-      (T1-3.east) edge[hv path] (T2.south)
-      (T2.north)  edge[vh path] (T1-5.west)
-      (T2.south)  edge[vh path] (T1-6.west)
-      (biend)     edge[vh path] (T1-5.east)
-                  edge[vh path] (T1-6.east)
-                  edge[hv path] (T3.west)
-      (T3.east)   edge[hv path] (end);
-%\end{scope}
-\end{tikzpicture}
-\caption{Reliability block diagram for a `bridge' type system with three component types $A$, $B$, $C$.
-Note that this system layout cannot be expressed as a nesting of series and parallel layouts.
-The corresponding survival signature $\Phi(l_A,l_B,l_C)$ is given in Table~\ref{tab:bridge-survsign}.}
-\label{fig:bridge-layout}
-\end{figure}
 
@@
 
-\begin{table}
-\centering
-\begin{tabular}{ccclccccl}
-  \toprule
-$l_A$ & $l_B$ & $l_C$ & $\Phi$ & \quad & $l_A$ & $l_B$ & $l_C$ & $\Phi$\\ 
-  \midrule
-0 & 0 & 1 & 0    & & 0 & 1 & 1 & 0 \\ 
-1 & 0 & 1 & 0    & & 1 & 1 & 1 & 0 \\ 
-2 & 0 & 1 & 0.33 & & 2 & 1 & 1 & 0.67 \\ 
-3 & 0 & 1 & 1    & & 3 & 1 & 1 & 1 \\ 
-4 & 0 & 1 & 1    & & 4 & 1 & 1 & 1 \\ 
-   \bottomrule
-\end{tabular}
-\caption{Survival signature $\Phi(l_A,l_B,l_C)$ for the bridge system from Figure~\ref{fig:bridge-layout},
-omitting all rows with $l_C=0$, since $\Phi(l_A,l_B,0)=0$ for all $l_A$ and $l_B$.}
-\label{tab:bridge-survsign}
-\end{table}
-
-\subsection{Reliability functions for complex systems using the survival signature}
-\label{sec:sysrel}
-
-Here we describe how system reliability functions, given fixed component models,
-can be efficiently calculated using the survival signature.
-We will show in Section~\ref{sec:sysreltnow}
-how this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
-giving us the RUL/RLD distribution on which we base our adaptive maintenance policy.
-
-We consider systems of arbitrary reliability block diagram layout,
-consisting of components of $K$ different types,
-where there are $N_k$ components of type $k$ in the system,
-and the total number of components in the system is $\sum_{k=1}^K N_k = N$.
-An example system reliability block diagram is given in Figure~\ref{fig:bridge-layout}.
-Note that this system cannot be described as a nesting of series and parallel subsystems.
-%This system is observed until time $\tnow$,
-%leading to censored observation of certain component lifetimes within the system.
-
-In a system with $N$ components, the state of the components can be expressed by the state vector
-$\vec{x} = (x_1,x_2,\ldots,x_N) \in \{0,1\}^N$,
-with $x_i=1$ if the $i$th component functions and $x_i=0$ if not.
-The structure function $\phi : \{0,1\}^N \rightarrow \{0,1\}$, defined for all possible $\vec{x}$,
-takes the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$ \citep{BP75}.
-Most real-life systems are coherent,
-which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
-so system functioning cannot be improved by worse performance of one or more of its components.
-Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.
-
-The survival signature \citep{2012:survsign} is a summary of the structure function
-for systems with $K$ groups of exchangeable components.
-Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,N_k$ for $k=1,\ldots,K$,
-it is defined as the probability for the event that the system functions
-given that precisely $l_k$ of its $N_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
-Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$,
-such that $\Rsys(t) = P(\Tsys > t)$ can be calculated using the law of total probability,
-\begin{align}
-P(\Tsys > t) &= \sum_{l_1=0}^{N_1} \cdots \sum_{l_K=0}^{N_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
-                                                                                  P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
-             &= \sum_{l_1=0}^{N_1} \cdots \sum_{l_K=0}^{N_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
-             &= \sum_{l_1=0}^{N_1} \cdots \sum_{l_K=0}^{N_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
-\label{eq:sysrel-survsign}
-\end{align}
-where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$,
-and the last equality holds as we assume that components of different types are independent.
-Note that for coherent systems, the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
-
-As an example, the survival signature for the system in Figure~\ref{fig:bridge-layout} is given in Table~\ref{tab:bridge-survsign}.
-
 \subsection{Component posterior predictive distributions at $\tnow$}

### 2016-10-27 cbm-rbd-paper.tex
work on sec 4

@@
 
-Here we describe how the system reliability function, given fixed component models and the system layout,
+Here we describe how the system reliability function, given the system layout and arbitrary component models,
 can be efficiently calculated using the survival signature.
-We will show in Section~\ref{sec:sysreltnow}
-how this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
+We will show in Section~\ref{sec:adaptive-sysrel-weibull} how, for a certain choice of component model,
+this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
 giving us the residual life distribution on which we base our adaptive maintenance policy.
@@
 the survival signature for the system in Figure~\ref{fig:brakesys-layout} is given in Table~\ref{tab:brakesys-survsign},
-omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$.
-(The full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.)
+omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$,
+since the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.
 
@@
 \section{Adaptive system residual life distribution based on Weibull component models}
-
-***component model: weibull with fixed shape,
-inverse gamma prior on scale parameter,
-fix priors via expected lifetime and prior strength,
-test data inclusion
-with noninformatiove right-censoring
-
-***output is $\Rsysnow(t)$, the current (at time $\tnow$) system reliability function
-(residual life distribution, RLD)
-taking into account the current system state,
-including the current ages of system components, 
-and the lifetime histories of all component types,
-including test data (if available) and expert assessments.
-
-***Model description in this Section follows closely \cite{2016:walter-coolen},
-who present the same RUL/RLD model.
-However, \cite{2016:walter-coolen} do not consider maintenance policies,
-and focus instead on a generalization of the RUL/RLD model using sets of priors for the component models
-(which can be seen as parametric P-boxes),
-allowing for vague and partial prior specifications,
-and sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.
+\label{sec:adaptive-sysrel-weibull}
+
+In this section, we describe how the system reliability function $\Rsysnow(t)$ at current time $\tnow$ 
+can be calculated for a specific choice of component model.
+Section~\ref{sec:policy} will then show how an adaptive maintenance policy
+can be derived for a monitored system based on such a current system residual life distribution.
+
+We consider the well-known Weibull model for component lifetimes,
+which is used in a wide variety of reliability studies ***more motivation Weibull***. 
+To keep things simple, we assume that the shape parameter of the Weibull distribution is known,
+and that only the scale parameter needs to be estimated.
+By using a Bayesian approach, described in Section~\ref{sec:weibull},
+our component model allows to include both expert assessments and test data (if available),
+and furthermore can account for component lifetime information from the current run of the system up to $\tnow$.
+%***component model: weibull with fixed shape,
+%inverse gamma prior on scale parameter,
+%fix priors via expected lifetime and prior strength,
+%test data inclusion
+%with noninformatiove right-censoring
+%
+Section~\ref{sec:postpred} then derives the posterior predictive distribution
+for the Weibull component model as needed for the current system reliability calculation.
+Section~\ref{sec:sysreltnow} then adapts the method from Section~\ref{sec:sysrel} for the adaptive setting,
+resulting in a formula for $\Rsysnow(t)$.
+%***output is $\Rsysnow(t)$, the current (at time $\tnow$) system reliability function
+%(residual life distribution, RLD)
+%taking into account the current system state,
+%including the current ages of system components, 
+%and the lifetime histories of all component types,
+%including test data (if available) and expert assessments.
+
+The model description in this Section follows closely \cite{2016:walter-coolen},
+who presented the same residual life distribution model.
+However, \cite{2016:walter-coolen} do not consider any maintenance policies,
+and focus instead on a generalization of the RLD model using sets of priors for the component models.
+These sets of priors can be seen as parametric P-boxes,
+a certain kind of imprecise probability model \citep[see, e.g.,][]{itip}.
+Such models allow for vague and partial prior specifications,
+and provide sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.
 
@@
 
-Here we describe the model for the component lifetimes,
+Here we describe the Weibull model for the component lifetimes,
 together with the Bayesian update procedure which allows to include
@@
 and both types of observations can be used in the update step \eqref{eq:ig-update}.
-Before we write this out formally in Section~\ref{sec:postpred},
-we will first present how system reliability functions can be derived based on component models.
+%Before we write this out formally in Section~\ref{sec:postpred},
+%we will first present how system reliability functions can be derived based on component models.
+
 %To keep notation simple,
@@
 To calculate the current system reliability function $\Rsysnow(t)$,
-we thus need, for each $k=1,\ldots, K$, the probabilities $P(C^k_t = l_k)$
+we need, for each $k=1,\ldots, K$, the probabilities $P(C^k_t = l_k)$
 for the number of type $k$ components that function at times $t > \tnow$,
@@
 Any failure times of failed components,
-and the right-censoring time $\tpnow$ for each non-failed component
+and the right-censoring time $\tpnow$ for each non-failed component,
 can be used to update $\nkz$ and $\ykz$ according to \eqref{eq:ig-update}.

### 2016-10-28 cbm-rbd-paper.tex
work on section 5

@@
 \newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
+\newcommand{\tsysnow}{t^{(t_\text{now})}_\text{sys}}
 \newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
@@
 \begin{align}
-\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)} \nonumber\\
- &= { \cknow \choose l_k} \sum_{j=0}^{\cknow - l_k} (-1)^j { \cknow - l_k \choose j}
-    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
- &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!}   
-    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
- &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!} \times \nonumber\\ & \hspace*{10ex}  
-    \left(\frac{\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow       (\tnow)^{\beta_k} }%
-               {\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + (\cknow - l_k - j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
-    \nkz + \eknow + 1}.
 \label{eq:postpred-priorparams}
-\end{align}
+\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)}\hspace*{5ex} \nonumber\\
+ &= { \cknow \choose l_k} \sum_{j=0}^{\cknow - l_k} (-1)^j { \cknow - l_k \choose j} \times \nonumber\\ & \hspace*{10ex}
+    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \,, \\
+ & \quad\text{where } \nknow\yknow = \nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow (\tnow)^{\beta_k} \nonumber\\
+ & \quad\text{and }  \nknow = \nkz + \eknow \,. \nonumber
+% &= { \cknow \choose l_k} \sum_{j=0}^{\cknow - l_k} (-1)^j { \cknow - l_k \choose j} \times \nonumber\\ & \hspace*{1ex}
+%    \left(\frac{\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow (\tnow)^{\beta_k} }%
+%               {\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow (\tnow)^{\beta_k} +%
+%                (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big) }\right)^{\nkz + \eknow + 1}.
+% &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!}   
+%    \left(\frac{\nknow\yknow}{\nknow\yknow + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nknow + 1} \nonumber\\
+% &= \sum_{j=0}^{\cknow - l_k} (-1)^j \frac{\cknow !}{l_k! j! (\cknow - l_k - j)!} \times \nonumber\\ & \hspace*{10ex}  
+%    \left(\frac{\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow       (\tnow)^{\beta_k} }%
+%               {\nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + (\cknow - l_k - j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
+%    \nkz + \eknow + 1}.
+\end{align}
+%where $\nknow\yknow = \nkz\ykz + \sum_{i=1}^{\eknow} (t_{k,i})^{\beta_k} + \cknow (\tnow)^{\beta_k}$
+%and $\nknow = \nkz + \eknow + 1$.
 %These posterior predictive probabilities can also be expressed as a cumulative probability mass function (cmf)
@@
 \begin{align}
-\Rsysnow(t) &:= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
+\Rsysnow(t) &= \sum_{l_1=0}^{c_1^{(\tnow)}} \cdots \sum_{l_K=0}^{c_K^{(\tnow)}} \Phinow(l_1,\ldots,l_K)
                \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)\,.
@@
 
-We can now derive the adaptive / dynamic maintenance policy
+We can now derive the adaptive and dynamic maintenance policy
 that resembles a CBM policy.
@@
 a preventive maintenance action is initiated.
+This operational procedure is described in more detail in Section~\ref{sec:operationalprocedure}.
 %and executed at time $\tnow + \tausnow$.
@@
 The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
-by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle, see Section~\ref{sec:costrate} below.
-Each operational cycle starts with the system being in an (as good as) new state,
-i.e., all components in the system are new and have not aged.
+by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle.
+(An operational cycle begins with system start-up,
+and ends when either a failure of the system occors, or a preventive maintenance is carried out.)
+This criterion, as described in Section~\ref{sec:costrate} below in detail,
+only assumes that $\Rsysnow(t)$ can be calculated,
+and thus is not tied to our choice of component model.
+One could also consider other optimality criteria to determine $\tausnow$.
+When safety is paramount one could, e.g., determine $\tausnow$ such that
+the probability of system failure is at most at some very low pre-determined level.
+
+Section~\ref{sec:optim} then focuses on our choice of component model and the resulting form for $\Rsysnow(t)$,
+and shows how $\tausnow$ is determined in this situation.
+Numerical examples for different failure histories are given in Section~ref{sec:examples}.
+
+\subsection{Operational Procedure}
+\label{sec:operationalprocedure}
+
+Each operational cycle starts with system startup.
+At this point in time, the system being is in an (as good as) new state,
+i.e., all components in the system are (as good as) new and have not aged.
 A cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
 or the system fails, which triggers a corrective maintenance action.
-The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
-of the maintenance interval in an age based policy;
-however, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
-our policy is adaptive and dynamic like a CBM policy.
-
-It is also possible that $\gnow(\tau)$ is monotonely decreasing.
-In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
-This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
-but also capable of indicating when corrective maintenance is the better option.
-%i.e., capable of choosing the maintenance policy.
 
@@
 
+The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
+of the maintenance interval in an age based policy;
+however, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
+our policy is adaptive and dynamic like a CBM policy. 
+Like in an age-based policy, the derived $\gnow(\tau)$ can also be monotonely decreasing.
+In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
+This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
+but also capable of indicating when corrective maintenance is the better option.
+%i.e., capable of choosing the maintenance policy.
+
+A preventive maintenance action is triggered as soon as $\tausnow$ falls below $\tsetup$,
+the time needed to set up maintenance work.
+The system continues to run until maintenance work begins,
+and the cycle ends when maintenance work is completed.
+When the system fails, instead a corrective maintenance action is triggered,
+and the system is down also during the wait until maintenance work begins.
+This additional downtime must be reflected in the cost parameter $c_u$ (see Section~\ref{sec:costrate} below).
+Again, the cycle ends when maintenance work is completed.
+
 At the end of each cycle,
@@
 %using failure and censoring times as of the end of the cycle.
-such that $\nkz$ and $\ykz$ for the following cycle account for the lifetimes and censoring observed during the previous cycle.
+such that $\nkz$ and $\ykz$ for the following cycle account for the (censored) lifetimes observed during the previous cycle.
 %We assume that both planned and unplanned maintenance action takes negligible time,
@@
 such that the system begins a new cycle always under the same condition.
-As we use a one-cycle criterion, the time these maintenance actions take does not matter for the determination of $\tausnow$.
-Downtimes are instead accounted for via the costs parameters,
+Replacement schemes that do not replace all components need to take into account the different ages of components in the system
+at the start of a new cycle.
+While this is in principle possible in our approach,
+exploring such selective replacement schemes is out of scope for this paper,
+since optimizing over replacement schemes is, in our view, a higly interesting topic on its own,
+which we will comment on in the Outlook (Section~\ref{sec:outlook}).
+
+As we use a one-cycle criterion, the time both planned and unplanned maintenance actions require
+does not matter directly for the determination of $\tausnow$.
+Downtimes are instead accounted for indirectly via the costs parameters,
 as described next.
@@
 (***cite de Jonge and Teunter working paper on relative benefit).
-
-As discussed in the Introduction and above,
+%
+As discussed above,
 we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system.
 That means that every time a new cycle starts, the system is in the same state with all components (as-good-as) new.
-Replacement schemes that do not replace all components need to take into account the different ages of components in the system
-at the start of a new cycle.
-While this is in principle possible in our approach,
-exploring such selective replacement schemes is out of scope for this paper
-and worthy for a seperate contribution.
 
@@
 and $\fsysnow(t)$ be the corresponding density.
-Conditional on $\Tsysnow$, the unit cost rate is 
+Conditional on the realization of $\Tsysnow$, the unit cost rate is 
 \begin{align*}
-g(\tau \mid \Tsysnow) &=
+g(\tau \mid \Tsysnow = \tsysnow) &=
 \begin{cases}
-c_p / \tau  & \text{if } \Tsysnow \ge \tau \\
-c_u / \Tsys & \text{if } \Tsysnow < \tau
+c_p / \tau  & \text{if } \tsysnow \ge \tau \\
+c_u / \Tsys & \text{if } \tsysnow < \tau
 \end{cases}
@@
 \end{align}
-
-***$\fsysnow(t)$ needs to fulfill certain conditions for the integral to exist / to be finite because of $1/t$.
-we have no problem because of discrete approximation of $\Rsysnow(t)$ resp. $\fsysnow(t)$.
-($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
-
+Note that for the integral to exist in \eqref{eq:gtau},
+$\E[\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
+This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
+For our approach, however, this condition is not relevant,
+as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively.
+We will describe next how this approximation is used in \eqref{eq:gtau}.
+%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
 %***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.
@@
 \subsection{Numerical optimization of the expected unit cycle cost rate}
+\label{sec:optim}
 
@@
 
-****plot both $\tau_*^{\tnow}$ and $\tnow + \tau_*^{\tnow}$ over time for different failure histories
-
-\section{Comparison with $M^*$ out of $N$ policy}
-
-***???
-
-\section{Case study / numerical example for complex system layout}
-
-use simple system layout, example history of components failing
-
-use the simplified brake system from ASCE-ASME paper?
+\section{***numerical examples for complex system layout}
+\label{sec:examples}
+
+***use simplified brake system from ASCE-ASME paper, example history of components failing
+
+***plot both $\tau_*^{\tnow}$ and $\tnow + \tau_*^{\tnow}$ over time for different failure histories
+
+***larger simulation study?
 
 \section{Outlook}
+\label{sec:outlook}
 

### 2016-10-28 cbm-rbd-paper.tex
typo in 5.2., some clarification in 5.3

@@
 Note that for the integral to exist in \eqref{eq:gtau},
-$\E[\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
+$\E[1/\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
 This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
@@
 as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively.
-We will describe next how this approximation is used in \eqref{eq:gtau}.
+We will describe next how we numerically evaluate \eqref{eq:gtau} and find $\tausnow$.
 %($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
@@
 %*** not possible / *** to minimize $\gnow(\tau)$ analytically.
-***we calculate $\Rsysnow(t)$ on discrete grid until some horizon, optimize $\tausnow$ over same discrete grid.
+***we calculate $\Rsysnow(t)$ on discrete grid from $\tnow$ until some horizon time $\tnow + t_h$.
+$t_h$ can be determined by practical considerations,
+but generally should reach into the tail of $\Rsysnow(t)$.
+We calculate $\gnow(\tau)$ on the same grid,
+and determine $\tausnow$ as the minimum over this grid.
 
@@
 $\gnow(\tau)$ is likewise evaluated on a dense grid,
-and $\tau_*^{(\tnow)} = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
+and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
 %The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
@@
 
-***if min $\gnow(\tau)$ at horizon, corrective maintenance is optimal: policy switch!
+***if min $\gnow(\tau)$ at $\tnow + t_h$, corrective maintenance is optimal: policy switch!
 %***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy
@@
 \label{sec:outlook}
+
+***$\tsetup$ could vary over time, e.g., longer on weekends or outside office hours
 
@@
 
-***$\tsetup$ could vary over time, e.g., longer on weekends or outside office hours
-
 \section*{Acknowledgements}

### 2016-10-28 cbm-rbd-paper.tex
typo in 5.2., some clarification in 5.3
minor thing

@@
 Next, we will describe how an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
-such a fine discrete approximation of the RLD can be obtained.
-
-\section{Dynamic/Adaptive maintenance policy based on the current system residual life distribution}
+a current residual life distribution,
+first in general, then for our implementation,
+where a fine discrete approximation of the RLD is obtained.
+
+\section{Dynamic and adaptive maintenance policy based on the current system residual life distribution}
 \label{sec:policy}
@@
 
+***comments about `nervousness' of $\tausnow$ here or in \ref{sec:operationalprocedure}?
+
 The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$

### 2016-10-28 cbm-rbd-paper.tex
other comments by SDF addressed

@@
 ***comments about `nervousness' of $\tausnow$ here or in \ref{sec:operationalprocedure}?
+common cause failures currently not in the model, but will seriously influence residual life distribution,
+see comments in Outlook (Section~\ref{sec:outlook})
 
@@
 \label{sec:operationalprocedure}
+
+***illustrative figure?
 
@@
 
+***common-cause failures will seriously reduce RLD in a way currently not covered by our model.
+This needs to be implemented on the level of component models,
+specifically $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ 
+(not a product anymore if common-case failures can affect several component times at once).
+Combine ideas from \cite{2015:coolen-coolen-maturi} and \cite{Troffaes2014a}.
+
 *** move to sets of priors, set of residual life distributions like in \cite{2016:walter-coolen}.

### 2016-11-02 cbm-rbd-paper.tex
gnow-history functions and plot

@@
 
+***example figures with very weak prior info, could look different for stronger expert information!
+
+***also example where remaining component type is (close to) exponential,
+such that corrective maintenance becomes optimal!
+
+\begin{figure}
+\includegraphics[width=\textwidth]{ghistfig1}
+\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
+for the system depicted in Figure~\ref{fig:brakesys-layout},
+assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
+and $c_u = 1$, $c_p = 0.2$.}
+\label{fig:ghistfig1}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{tauhistfig1}
+\caption{$\tausnow$, $t^* = \tnow + \tausnow$ and $\gnow(\tausnow)$ as functions of $\tnow$
+for the system depicted in Figure~\ref{fig:brakesys-layout},
+assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
+and $c_u = 1$, $c_p = 0.2$.
+$\tausnow$ first decreases slightly, then remains basically constant during failure-free periods,
+dropping at each component failure.
+If $\tsetup = 0.5$, the drop of $\tausnow$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
+at (absolute) time $8.5$. 
+As $\tausnow$ does not change dramatically, $t^*$,
+the cost-optimal moment of maintenance on the absolute timescale,
+steadily increases, with small drops corresponding to $\tausnow$,
+indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
+Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime,
+and not the overall cost rate.
+For the maintenance action triggered at $\tnow = 8$,
+the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
+and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
+\label{fig:tauhistfig1}
+\end{figure}
+
 \section{***numerical examples for complex system layout}

### 2016-11-02 cbm-sys.R

@@ -37,7 +37,7 @@ brtnow8 <- sysrelnowhor(br8sysign, brn0y0, brbeta, brfts8, tnow=8, hor=10)
 qplot(brtnow8$t, brtnow8$rel)
 
 # posterior, assuming C2, C3, P2, P3 and H have failed -> take out elements corresponding to H
-brfts8H <- list(c(6, 7), 7, NULL, c(3, 4))
+brfts8H <- list(c(6, 7), 8, NULL, c(3, 4))
 br8H <- induced_subgraph(br, vids=c("s", "M", "C1", "P1", "C4", "P4", "t"))
 br8Hsysign <- computeSystemSurvivalSignature(br8H)
 sysrelnow(br8Hsysign, brn0y0[-2], brbeta[-2], brfts8H[-2], tnow=8, t=8)
@@ -46,23 +46,89 @@ sysrelnowhor(br8Hsysign, brn0y0[-2], brbeta[-2], brfts8H[-2], tnow=8, hor=10, se
 brtnow8H <- sysrelnowhor(br8Hsysign, brn0y0[-2], brbeta[-2], brfts8[-2], tnow=8, hor=10)
 qplot(brtnow8H$t, brtnow8H$rel)
 
-# plot sysrelnow history
-
+# to plot sysrelnow history
 brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = NA, M = NA, P1 = NA, P2 = 3, P3 = 4, P4 = NA)
-brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = NA, M = 5, P1 = 4, P2 = 3, P3 = 4, P4 = NA)
+brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = 8,  M = NA, P1 = NA, P2 = 3, P3 = 4, P4 = NA)
 
-brhist1 <- sysrelnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0:8), hor=10)
+brhist1 <- sysrelnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0,8), hor=10)
+#brhist1 <- sysrelnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0:8), hor=10)
 brhist1$tnow <- as.factor(brhist1$tnow)
 histfig1 <- ggplot(brhist1, aes(x = t, y = rel)) + ylim(0, 1) +
[…]

### 2016-11-02 plotdefs.R

@@ -1,5 +1,5 @@
 # --------------------------------------------------------------------------- #
-# ASCE-ASME paper - plot definitions
+# cbm systems paper - plot definitions
 # --------------------------------------------------------------------------- #
 
 bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())

### 2016-11-02 weibull-sys-functions.R

@@ -183,6 +183,7 @@ sysrelnowhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen
   presentctypes[[1]] <- 1:K
   # now go through ftschron (first element already done) and calculate survsign and fts
   failedcomps <- numeric(0)
+  cat("calculating reduced survival signatures ...\n")
   for (i in 2:length(ftschron)){
     failedcomps <- c(failedcomps, names(ftschron[i]))
     reducedsys <- induced_subgraph(sys, vids=V(sys)[!(name %in% failedcomps)])
@@ -210,239 +211,113 @@ sysrelnowhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen
   return(res)
 }
 
-# now gtau and tau*
-  
-
-# calculates the system reliability function for the 2*2^K corner priors
-# (all combinations of K lower and upper n's, for both lower and upper y)
-# luckobjlist list of K of prior luckmodel objetcs
-# survsign    data frame with the survival signature as output by computeSystemSurvivalSignature()
-# beta        vector of K fixed weibull shape parameters
-# fts         list of K vectors giving the observed failure times for the compents of type 1,...,K;
-#             the list element should be NULL if no failure has been observed for type k, 
-# tnow        time until the system is observed
-# tvec        vector of timepoints for which to calculate P(T_sys > t), t > t_now
-# nk          vector of length K giving the number of components of each type,
-#             this is needed only when reduced survival signature is used
-# prior       whether the prior system relibability should be calculated
-fourKcornersSysrel <- function(luckobjlist, survsign, beta, fts, tnow, tvec, nk = NULL, prior = FALSE){
-  K <- length(luckobjlist)
-  ncomb <- 2^K
-  combs <- as.list(rep(NA,K))
-  for (k in 1:K)
-    combs[[k]] <- c(1,2)
-  # with all y0[1], jede spalte eine kombination, darunter dann tvec 
-  lowercorners <- t(expand.grid(combs)) # transposed!
-  NAmat <- matrix(NA, nrow = length(tvec), ncol = ncomb)
-  lowercorners <- rbind(lowercorners, NAmat)
-  uppercorners <- lowercorners
-  # all n0 combinations with lower y's
-  for (i in 1:ncomb){ # over columns!
-    comblist <- as.list(rep(NA, K))
[…]

### 2016-11-03 cbm-sys.R
failure times plot

@@ -125,6 +125,21 @@ pdf("tauhistfig1.pdf", width = 6, height = 3)
 tauhistfig1
 dev.off()
 
+# failure history plot
+# turn compfts into a data.frame, make this a function
+brftsdf <- t(as.data.frame(brcompfts))
+brftsdf <- data.frame(brftsdf, Components = names(brcompfts))
+names(brftsdf)[1] <- "t"
+brftsdf <- data.frame(brftsdf, cens = is.na(brftsdf$t), id = 1:length(brcompfts))
+brftsdf$t[is.na(brftsdf$t)] <- 8
+
+#qplot(data=brftsdf, x=id, ymin=rep(0,dim(brftsdf)[1]), y=t, ymax=t, label=t, vjust=-0.5,
+#      geom=c("pointrange", "text"), shape=factor(cens)) + coord_flip() + scale_x_reverse() +
+#  scale_shape_manual(values=c(19, 1), label=c("Yes", "No"), name="Failure")
+
+ggplot(brftsdf, aes(x= Components, y=t, ymin=rep(0,dim(brftsdf)[1]), ymax=t)) + geom_linerange() +
+  geom_pointrange(aes(shape=factor(cens)), size=1) + geom_text(aes(label=t, vjust = -1)) + coord_flip() +
+  scale_shape_manual(values=c(19, 1), label=c("Yes", "No"), name="Failure")
 
 
 

### 2016-11-03 cbm-sys.R
better grids for history figures, attempt to speed up sysrelnowhist

@@ -107,7 +107,8 @@ ghistfig1 <- ggplot(brghist1a, aes(x = t, y = value)) + coord_cartesian(ylim = c
   #geom_line(aes(colour = tnow)) + xlab(expression(t)) +
   ylab(expression(paste(g^(t[now]), (t), " and ", R[sys]^(t[now]), (t)))) +
   #theme(legend.position = 'bottom', legend.direction = 'horizontal') +
-  guides(colour=guide_legend(title=expression(t[now])), linetype=guide_legend(title=NULL))
+  guides(colour=guide_legend(title=expression(t[now])), linetype=guide_legend(title=NULL)) +
+  scale_x_continuous(breaks=seq(0, 18, by=2), minor_breaks=0:18)
   #facet_wrap(~variable, nrow=2, scales = "free_y") + guides(colour=guide_legend(title=expression(t[now])))
 pdf("ghistfig1.pdf", width = 6, height = 3)
 ghistfig1
@@ -120,7 +121,8 @@ dev.off()
 brtaus1fine <- taustarhist(br, brctypes, brcompfts, brn0y0, brbeta, seq(0,8,by=0.1), hor=4, seqlen=401)
 tauhistfig1 <- ggplot(melt(brtaus1fine, "tnow"), aes(x = tnow, y = value)) + xlab(expression(t[now])) +
   geom_line(aes(colour = variable, group = variable)) + ylab(element_blank()) +
-  geom_point(aes(colour = variable, group = variable), size = 0.5) + guides(colour = guide_legend(title=NULL))
+  geom_point(aes(colour = variable, group = variable), size = 0.5) + guides(colour = guide_legend(title=NULL)) +
+  scale_x_continuous(breaks=seq(0, 18, by=2), minor_breaks=0:18)
 pdf("tauhistfig1.pdf", width = 6, height = 3)
 tauhistfig1
 dev.off()

### 2016-11-03 weibull-sys-functions.R

@@ -196,7 +196,9 @@ sysrelnowhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen
   }
   #list(siglist=siglist, ftslist=ftslist, prctypes = presentctypes)
   # now get reliability curves for each tnow
-  res <- data.frame()
+  #res <- data.frame()
+  reslen <- length(tnowvec) * seqlen
+  res <- data.frame(tnow = rep(tnowvec, each = seqlen), t = rep(NA, reslen), rel = rep(NA, reslen))
   for (tnow in tnowvec){
     # index in siglist, ftslist, presentctypes for current (tnow) status
     tnowi <- max(which(ftschron <= tnow))
@@ -206,7 +208,8 @@ sysrelnowhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen
                           sysrelnowhor(survsign = siglist[[tnowi]], n0y0 = n0y0[prctps],
                                        beta = beta[prctps], fts = ftslist[[tnowi]][prctps],
                                        tnow = tnow, hor = hor, seqlen = seqlen, prior = prior))
-    res <- rbind(res, current)
+    #res <- rbind(res, current)
+    res[res$tnow == tnow,] <- current
   }
   return(res)
 }

### 2016-11-04 campi-plots.R
component plots for talk

@@ -1,0 +1,38 @@
+# --------------------------------------------------------------------------- #
+# cbm systems paper - plots for campi slotevent talk
+# --------------------------------------------------------------------------- #
+
+source("weibull-sys-functions.R")
+source("plotdefs.R")
+
+# component reliability plots
+sysA <- graph.formula(s -- A -- t)
+betaA <- 2
+compA <- list(survsign = computeSystemSurvivalSignature(setCompTypes(sysA, list("A" = "A"))),
+              n0y0 = list(A = c(1, failuretolambda(5, betaA))),
+              beta = betaA)
+compArel0 <-sysrelnowhor(compA$survsign, compA$n0y0, compA$beta, list(A = NULL), tnow = 0, hor = 10, seqlen=101)
+compArel5 <-sysrelnowhor(compA$survsign, compA$n0y0, compA$beta, list(A = 5), tnow = 5, hor = 10, seqlen=101)
+pdf("talk-campi/compArel0.pdf", width = minirelsize, height = minirelsize)
+ggplot(compArel0, aes(x = t, y = rel)) + geom_line() + minirel
+dev.off()
+pdf("talk-campi/compArel5.pdf", width = minirelsize, height = minirelsize)
+ggplot(compArel5, aes(x = t, y = rel)) + geom_line() + minirel
+dev.off()
+
+sysB <- graph.formula(s -- B -- t)
+betaB <- 1.2
+compB <- list(survsign = computeSystemSurvivalSignature(setCompTypes(sysB, list("B" = "B"))),
+              n0y0 = list(B = c(1, failuretolambda(8, betaB))),
+              beta = betaB)
+compBrel0 <-sysrelnowhor(compB$survsign, compB$n0y0, compB$beta, list(B = NULL), tnow = 0, hor = 10, seqlen=101)
+compBrel5 <-sysrelnowhor(compB$survsign, compB$n0y0, compB$beta, list(B = NULL), tnow = 5, hor = 10, seqlen=101)
+pdf("talk-campi/compBrel0.pdf", width = minirelsize, height = minirelsize)
+ggplot(compBrel0, aes(x = t, y = rel)) + geom_line() + minirel
+dev.off()
+pdf("talk-campi/compBrel5.pdf", width = minirelsize, height = minirelsize)
+ggplot(compBrel5, aes(x = t, y = rel)) + geom_line() + minirel
+dev.off()
+
+
+#

### 2016-11-04 plotdefs.R

@@ -5,8 +5,24 @@
 bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
 rightlegend <- theme(legend.title = element_blank())
 nolegend <- guides(linetype="none", fill="none", group="none", colour="none")
+
+minirel <- list(theme(axis.title = element_blank()),
+                coord_cartesian(ylim = c(0, 1)),
+                scale_x_continuous(breaks=c(0, 5, 10, 15)),
+                scale_y_continuous(breaks=c(0, 0.5, 1)))
+minirelsize <- 1.5
+
 ijarcols <- c("#b2df8a", "#1f78b4")
 ijarcol <- scale_colour_manual(values = ijarcols)
 ijarfill <- scale_fill_manual(values = ijarcols)
+
+tuered <- rgb(0.839,0.000,0.290)
+tueblue <- rgb(0.000,0.400,0.800)
+tueyellow <- rgb(1.000,0.867,0.000)
+
+tuegreen <- rgb(0.000,0.675,0.510)
+tuewarmred <- rgb(0.969,0.192,0.192)
+tueorange <- rgb(1.000,0.604,0.000)
+tuedarkblue <- rgb(0.063,0.063,0.451)
 
 #

### 2016-11-04 campi-plots.R
campi talk slide 2

@@ -23,7 +23,7 @@ dev.off()
 sysB <- graph.formula(s -- B -- t)
 betaB <- 1.2
 compB <- list(survsign = computeSystemSurvivalSignature(setCompTypes(sysB, list("B" = "B"))),
-              n0y0 = list(B = c(1, failuretolambda(8, betaB))),
+              n0y0 = list(B = c(5, failuretolambda(8, betaB))),
               beta = betaB)
 compBrel0 <-sysrelnowhor(compB$survsign, compB$n0y0, compB$beta, list(B = NULL), tnow = 0, hor = 10, seqlen=101)
 compBrel5 <-sysrelnowhor(compB$survsign, compB$n0y0, compB$beta, list(B = NULL), tnow = 5, hor = 10, seqlen=101)
@@ -33,6 +33,55 @@ dev.off()
 pdf("talk-campi/compBrel5.pdf", width = minirelsize, height = minirelsize)
 ggplot(compBrel5, aes(x = t, y = rel)) + geom_line() + minirel
 dev.off()
+
+
+# AB system reliability plots
+sysAB <- graph.formula(s -- A1:A2:B -- t)
+sysABtypes <- list("A"=c("A1", "A2"), "B"=c("B"))
+sysAB <- setCompTypes(sysAB, sysABtypes)
+sysABsign <- computeSystemSurvivalSignature(sysAB)
+sysABfts <- list(A1 = NULL, A2 = 5, B = NULL)
+sysABn0y0 <- list(A = compA$n0y0$A, B = compB$n0y0$B)
+sysABrelhist05 <- sysrelnowhist(sysAB, sysABtypes, sysABfts, sysABn0y0, c(betaA, betaB), c(0,5), hor=15)
+pdf("talk-campi/sysABrel0.pdf", width = 1.5*minirelsize, height = minirelsize)
+ggplot(subset(sysABrelhist05, tnow == 0), aes(x = t, y = rel)) + geom_line() + minirel
+dev.off()
+pdf("talk-campi/sysABrel5.pdf", width = 1.5*minirelsize, height = minirelsize)
+ggplot(subset(sysABrelhist05, tnow == 5), aes(x = t, y = rel)) + geom_line() + minirel
+dev.off()
+
+sysABghist <- gnowhist(sysAB, sysABtypes, sysABfts, sysABn0y0, c(betaA, betaB), seq(0, 10, by=2.5), hor = 15, seqlen = 301)
+sysABghist$tnow <- as.factor(sysABghist$tnow)
+
[…]

### 2016-11-04 cbm-sys.R

@@ -47,7 +47,7 @@ brtnow8H <- sysrelnowhor(br8Hsysign, brn0y0[-2], brbeta[-2], brfts8[-2], tnow=8,
 qplot(brtnow8H$t, brtnow8H$rel)
 
 # to plot sysrelnow history
-brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = NA, M = NA, P1 = NA, P2 = 3, P3 = 4, P4 = NA)
+#brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = NA, M = NA, P1 = NA, P2 = 3, P3 = 4, P4 = NA)
 brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = 8,  M = NA, P1 = NA, P2 = 3, P3 = 4, P4 = NA)
 
 brhist1 <- sysrelnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0,8), hor=10)

### 2016-11-04 plotdefs.R

@@ -8,7 +8,7 @@ nolegend <- guides(linetype="none", fill="none", group="none", colour="none")
 
 minirel <- list(theme(axis.title = element_blank()),
                 coord_cartesian(ylim = c(0, 1)),
-                scale_x_continuous(breaks=c(0, 5, 10, 15)),
+                scale_x_continuous(breaks=c(0, 5, 10, 15, 20)),
                 scale_y_continuous(breaks=c(0, 0.5, 1)))
 minirelsize <- 1.5
 

### 2016-11-05 campi-plots.R
campi-slides uncovering piecewise with corresponding plots

@@ -44,37 +44,52 @@ sysABfts <- list(A1 = NULL, A2 = 5, B = NULL)
 sysABn0y0 <- list(A = compA$n0y0$A, B = compB$n0y0$B)
 sysABrelhist05 <- sysrelnowhist(sysAB, sysABtypes, sysABfts, sysABn0y0, c(betaA, betaB), c(0,5), hor=15)
 pdf("talk-campi/sysABrel0.pdf", width = 1.5*minirelsize, height = minirelsize)
-ggplot(subset(sysABrelhist05, tnow == 0), aes(x = t, y = rel)) + geom_line() + minirel
+ggplot(subset(sysABrelhist05, tnow == 0), aes(x = t, y = rel)) + geom_line(size = 0.8) + minirel
 dev.off()
 pdf("talk-campi/sysABrel5.pdf", width = 1.5*minirelsize, height = minirelsize)
-ggplot(subset(sysABrelhist05, tnow == 5), aes(x = t, y = rel)) + geom_line() + minirel
+ggplot(subset(sysABrelhist05, tnow == 5), aes(x = t, y = rel)) + geom_line(size = 0.8) + minirel
 dev.off()
 
-sysABghist <- gnowhist(sysAB, sysABtypes, sysABfts, sysABn0y0, c(betaA, betaB), seq(0, 10, by=2.5), hor = 15, seqlen = 301)
-sysABghist$tnow <- as.factor(sysABghist$tnow)
+sysABtnowseq <- seq(0, 10, by=2.5)
+sysABghist <- gnowhist(sysAB, sysABtypes, sysABfts, sysABn0y0, c(betaA, betaB), sysABtnowseq, hor = 15, seqlen = 301)
+sysABghist$tnow <- factor(sysABghist$tnow, levels = sysABtnowseq)
+sysABtauhist <- taustarhist(sysAB, sysABtypes, sysABfts, sysABn0y0, c(betaA, betaB), sysABtnowseq, hor = 5, seqlen = 501)
+sysABtauhist$tnowf <- factor(sysABtauhist$tnow, levels = sysABtnowseq)
 
-pdf("talk-campi/sysABrelhist5.pdf", width = 5.3, height = 1.6)
-ggplot(sysABghist, aes(x = t, y = rel)) + coord_cartesian(xlim = c(0,25), ylim = c(0,1)) + xlab(expression(t)) +
-  geom_line(aes(group = tnow, colour = tnow)) + #ylab(expression(paste(R[sys]^(t[now]), (t),))) +
[…]

### 2016-11-10 cbm-rbd-paper.tex
tsetup -> tprep, no update figure, gnowhist figure with more dense grid

--- 2016-10-28 cbm-rbd-paper.tex
@@
 \newcommand{\tausnow}{\tau_*^{(\tnow)}}
-\newcommand{\tsetup}{\tau_{\text{setup}}}
+\newcommand{\tprep}{\tau_{\text{prep}}}
 
@@
 $\tausnow$ will typically decrease.
-Let $\tsetup$ be the timespan needed to set up maintenance work,
-often referred to simply as setup time.
-As soon as $\tausnow$ decreases below $\tsetup$,
+Let $\tprep$ be the timespan needed to prepare maintenance work.
+As soon as $\tausnow$ decreases below $\tprep$,
 a preventive maintenance action is initiated.
@@
 This criterion, as described in Section~\ref{sec:costrate} below in detail,
-only assumes that $\Rsysnow(t)$ can be calculated,
+only assumes that $\Rsysnow(t)$ is given,
 and thus is not tied to our choice of component model.
@@
 and shows how $\tausnow$ is determined in this situation.
-Numerical examples for different failure histories are given in Section~ref{sec:examples}.
+Numerical examples for different failure histories are given in Section~\ref{sec:examples}.
 
@@
 
-A preventive maintenance action is triggered as soon as $\tausnow$ falls below $\tsetup$,
-the time needed to set up maintenance work.
+A preventive maintenance action is triggered as soon as $\tausnow$ falls below $\tprep$,
+the time needed to prepare maintenance work.
 The system continues to run until maintenance work begins,
@@
 since optimizing over replacement schemes is, in our view, a higly interesting topic on its own,
-which we will comment on in the Outlook (Section~\ref{sec:outlook}).
+and we will comment on this in the Outlook (Section~\ref{sec:outlook}).
 
@@
 c_p / \tau  & \text{if } \tsysnow \ge \tau \\
-c_u / \Tsys & \text{if } \tsysnow < \tau
+c_u / \Tsys & \text{if } \tsysnow < \tau \,.
 \end{cases}
@@
 \begin{align}
-\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t
+\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t\,.
 \label{eq:gtau}
@@
 
+***example figures with very weak prior info, could look different for stronger expert information!
+
+***also example where remaining component type is (close to) exponential,
+such that corrective maintenance becomes optimal!
+
+\begin{figure}
+\includegraphics[width=\textwidth]{ghistfig1}
+\caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
+for the system depicted in Figure~\ref{fig:brakesys-layout},
+assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
+and $c_u = 1$, $c_p = 0.2$.}
+\label{fig:ghistfig1}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{tauhistfig2}
+\caption{$\tausnow$, $t^* = \tnow + \tausnow$ and $\gnow(\tausnow)$ as functions of $\tnow$
+for the system depicted in Figure~\ref{fig:brakesys-layout},
+assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
+and $c_u = 1$, $c_p = 0.2$.
+$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
+dropping at each component failure.
+If $\tprep = 0.5$, the drop of $\tausnow$ from $0.72$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
+at (absolute) time $8.5$.
+As $\tausnow$ does not change dramatically most of the time, $t^*$,
+the cost-optimal moment of maintenance on the absolute timescale (top right panel),
+steadily increases, with small drops corresponding to drops in $\tausnow$,
+indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
+Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
+differing from the overall cost rate (lower right panel).
+%For the maintenance action triggered at $\tnow = 8$,
+%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
+%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
+At time $8$, the overall expected cost rate for repair at time $8.38$ is $0.314$,
+up from $0.076$ for repair at time $8.62$, as cost-optimal at time $8$.}
+\label{fig:tauhistfig2}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{tauhistfig3}
+\caption{Illustration of the gains due to the parameter update.
+$\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
+same with $t^*$ (top right panel).
+The adaptive algorithm recongnizes the higher reliability of system components,
+leading to lower current (lower left panel) and total (lower right panels) unit cost rates.}
+\label{fig:tauhistfig3}
+\end{figure}
+
 \section{***numerical examples for complex system layout}
@@
 
-***$\tsetup$ could vary over time, e.g., longer on weekends or outside office hours
+***$\tprep$ could vary over time, e.g., longer on weekends or outside office hours
 

### 2016-11-10 cbm-sys.R

@@ -88,9 +88,17 @@ ggplot(melt(ocgnow0, id="tau"), aes(x=tau, y=value)) + geom_line(aes(colour = va
 ocgnow5 <- gnowhor(ocsysign, ocn0y0, ocbeta, list(M = NULL), tnow=5, hor=20, seqlen=201)
 ggplot(melt(ocgnow5, id="tau"), aes(x=tau, y=value)) + geom_line(aes(colour = variable))  + coord_cartesian(ylim=c(0,1))
 
+# failure history plot
+# turn compfts into a data.frame
+brfstdf <- compfts2df(brcompfts)
+# plot directly
+plotfts(brcompfts)
+#plotfts(brcompfts,10) 
+#plotfts(brcompfts,6) 
+
 # gnow & sysrelnow histories
-brghist1 <- gnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0,2,4,6,8), hor = 10, seqlen = 201)
-#brghist1 <- gnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0:8), hor=10)
+brghist1 <- gnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0,2,4,6,8), hor = 10, seqlen = 1001)
+#brghist2 <- gnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0,8), hor=4, seqlen = 401)
 brghist1$tnow <- as.factor(brghist1$tnow)
 ghistfig1 <- ggplot(brghist1, aes(x = t)) + coord_cartesian(ylim=c(0,1)) +
   geom_line(aes(group = tnow, colour = tnow, y = gnow), linetype = 1) + xlab(expression(t)) +
@@ -102,7 +110,7 @@ brghist1a <- brghist1
 names(brghist1a)[c(3,4)] <- c("Reliability", "Unit cost rate")
 brghist1a <- melt(brghist1a, c("tnow", "t"))
 brghist1a <- subset(brghist1a, !is.na(value))
-ghistfig1 <- ggplot(brghist1a, aes(x = t, y = value)) + coord_cartesian(ylim = c(0, 2.1)) +
+ghistfig1 <- ggplot(brghist1a, aes(x = t, y = value)) + coord_cartesian(ylim = c(0, 2.9)) +
   geom_line(aes(colour = tnow, linetype = variable)) + xlab(expression(t)) +
   #geom_line(aes(colour = tnow)) + xlab(expression(t)) +
[…]

### 2016-11-10 weibull-sys-functions.R

@@ -161,7 +161,7 @@ sysrelnowhor <- function(survsign, n0y0, beta, fts, tnow, hor, seqlen=101, prior
 # ctypes   list giving the types of components in the system, same format as
 #          used for setCompTypes(), but needs the same order as in survsign table (!!!)
 # compfts  list with elements named like the vertices in sys, giving the failure
-#          time of this component; can be NULL if component does not fail
+#          time of this component; can be NA if component does not fail
 # n0y0     list of K prior parameter pairs c(n0,y0)
 # beta     vector of K fixed weibull shape parameters
 # tnowvec  vector of times for which to evaluate sysrelnow
@@ -205,6 +205,7 @@ sysrelnowhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen
     prctps <- presentctypes[[tnowi]]
     cat("calculating sysrel for tnow =", tnow, "...\n")
     current <- data.frame(tnow = tnow,
+                          # add nn, ny
                           sysrelnowhor(survsign = siglist[[tnowi]], n0y0 = n0y0[prctps],
                                        beta = beta[prctps], fts = ftslist[[tnowi]][prctps],
                                        tnow = tnow, hor = hor, seqlen = seqlen, prior = prior))
@@ -213,6 +214,50 @@ sysrelnowhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen
   }
   return(res)
 }
+
+# transform failure history argument for sysrelnowhist() into data.frame for plotting the history
+# compfts  list with elements named like the vertices in sys, giving the failure
+#          time of this component; can be NA if component does not fail
+# maxtnow  censoring time for the non-failed components;
+#          equal to last failure time if not given.
+#          If set smaller than last failure time, maxtnow is the censoring time
+#          for all failure times after maxtnow
+compfts2df <- function(compfts, maxtnow = NA){
+  compftsdf <- t(as.data.frame(compfts))
+  compftsdf <- data.frame(compftsdf, Components = names(compfts))
+  names(compftsdf)[1] <- "t"
[…]

### 2016-11-11 cbm-sys.R
better plot with rel and gnow

@@ -100,11 +100,6 @@ plotfts(brcompfts)
 brghist1 <- gnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0,2,4,6,8), hor = 10, seqlen = 1001)
 #brghist2 <- gnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0,8), hor=4, seqlen = 401)
 brghist1$tnow <- as.factor(brghist1$tnow)
-ghistfig1 <- ggplot(brghist1, aes(x = t)) + coord_cartesian(ylim=c(0,1)) +
-  geom_line(aes(group = tnow, colour = tnow, y = gnow), linetype = 1) + xlab(expression(t)) +
-  geom_line(aes(group = tnow, colour = tnow, y = rel), linetype = 2)  + ylab(expression(paste(R[sys]^(t[now]), (t), " and ",
-                                                                                              g^(t[now]), (t))))
-ghistfig1 + guides(colour=guide_legend(title=expression(t[now])))
 
 brghist1a <- brghist1
 names(brghist1a)[c(3,4)] <- c("Reliability", "Unit cost rate")
@@ -112,14 +107,30 @@ brghist1a <- melt(brghist1a, c("tnow", "t"))
 brghist1a <- subset(brghist1a, !is.na(value))
 ghistfig1 <- ggplot(brghist1a, aes(x = t, y = value)) + coord_cartesian(ylim = c(0, 2.9)) +
   geom_line(aes(colour = tnow, linetype = variable)) + xlab(expression(t)) +
-  #geom_line(aes(colour = tnow)) + xlab(expression(t)) +
+  #geom_line(aes(colour = tnow)) + xlab(expression(t)) + facet_wrap(~variable, nrow=2, scales = "free_y") +
   ylab(expression(paste(g^(t[now]), (t), " and ", R[sys]^(t[now]), (t)))) +
   #theme(legend.position = 'bottom', legend.direction = 'horizontal') +
   guides(colour=guide_legend(title=expression(t[now])), linetype=guide_legend(title=NULL)) +
   scale_x_continuous(breaks=seq(0, 18, by=2), minor_breaks=0:18)
-  #facet_wrap(~variable, nrow=2, scales = "free_y") + guides(colour=guide_legend(title=expression(t[now])))
 pdf("ghistfig1.pdf", width = 6, height = 3)
 ghistfig1
[…]

### 2016-11-11 weibull-sys-functions.R

@@ -7,6 +7,7 @@ library(actuar) # provides dinvgamma(x, shape, scale) where shape = alpha and sc
 library(ReliabilityTheory)
 library(ggplot2)
 library(reshape2)
+library(gridExtra)
 
 # translate lambda parameter of weibull to expected failure time
 # lambda - scale parameter of weibull

### 2016-11-11 cbm-rbd-paper.tex
better plot with rel and gnow
figure caption update

@@
 \begin{figure}
-\includegraphics[width=\textwidth]{ghistfig1}
+\includegraphics[width=\textwidth]{ghistfig2}
 \caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
@@
 and $c_u = 1$, $c_p = 0.2$.}
-\label{fig:ghistfig1}
+\label{fig:ghistfig2}
 \end{figure}
@@
 \includegraphics[width=\textwidth]{tauhistfig2}
-\caption{$\tausnow$, $t^* = \tnow + \tausnow$ and $\gnow(\tausnow)$ as functions of $\tnow$
+\caption{$\tausnow$, $t^* = \tnow + \tausnow$, $\gnow(\tausnow)$, and the total cost rate **** as functions of $\tnow$
 for the system depicted in Figure~\ref{fig:brakesys-layout},
@@
 $\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
-dropping at each component failure.
+dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
 If $\tprep = 0.5$, the drop of $\tausnow$ from $0.72$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
 at (absolute) time $8.5$.
-As $\tausnow$ does not change dramatically most of the time, $t^*$,
+Since $\tausnow$ does not change dramatically most of the time, $t^*$,
 the cost-optimal moment of maintenance on the absolute timescale (top right panel),
@@
 At time $8$, the overall expected cost rate for repair at time $8.38$ is $0.314$,
-up from $0.076$ for repair at time $8.62$, as cost-optimal at time $8$.}
+up from $0.076$ for repair at time $8.62$, as cost-optimal at time $7.9$.}
 \label{fig:tauhistfig2}

### 2016-11-14 cbm-sys.R
one-cycle total cost rate

@@ -14,10 +14,12 @@ brsysign <- computeSystemSurvivalSignature(br)
 
 # tests # order is C H M P
 brbeta <- c(2, 1.2, 2.5, 1.5)
-brn0y0 <- list(C=c(1, failuretolambda(8, brbeta[1])),
-               H=c(1, failuretolambda(2, brbeta[2])),
-               M=c(2, failuretolambda(5, brbeta[3])),
-               P=c(1, failuretolambda(3, brbeta[4])))
+brmttf <- c(8, 2, 5, 3)
+brn0 <- c(1, 1, 2, 1)
+brn0y0 <- list(C=c(brn0[1], failuretolambda(brmttf[1], brbeta[1])),
+               H=c(brn0[2], failuretolambda(brmttf[2], brbeta[2])),
+               M=c(brn0[3], failuretolambda(brmttf[3], brbeta[3])),
+               P=c(brn0[4], failuretolambda(brmttf[4], brbeta[4])))
 # prior
 brfts0 <- list(C=NULL, H=NULL, M=NULL, P=NULL)
 sysrelnow(brsysign, brn0y0, brbeta, brfts0, tnow=0, t=1)
@@ -49,6 +51,13 @@ qplot(brtnow8H$t, brtnow8H$rel)
 # to plot sysrelnow history
 #brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = NA, M = NA, P1 = NA, P2 = 3, P3 = 4, P4 = NA)
 brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = 8,  M = NA, P1 = NA, P2 = 3, P3 = 4, P4 = NA)
+# failure history plot
+# turn compfts into a data.frame
+brfstdf <- compfts2df(brcompfts)
+# plot directly
+plotfts(brcompfts)
+#plotfts(brcompfts,10) 
+#plotfts(brcompfts,6) 
 
 brhist1 <- sysrelnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0,8), hor=10)
 #brhist1 <- sysrelnowhist(br, brctypes, brcompfts, brn0y0, brbeta, c(0:8), hor=10)
@@ -77,6 +86,7 @@ qplot(brgnow0$tau, brgnow0$gnow, geom="line") + coord_cartesian(ylim=c(0,1))
[…]

### 2016-11-14 weibull-sys-functions.R

@@ -342,13 +342,21 @@ taustarhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen =
                         cu = 1, cp = 0.2, onecycle = TRUE){
   res <- gnowhist(sys = sys, ctypes = ctypes, compfts = compfts, n0y0 = n0y0, beta = beta,
                   tnowvec = tnowvec, hor = hor, seqlen = seqlen, prior = prior, cu = cu, cp = cp, onecycle = onecycle)
-  res <- subset(res, !is.na(res$gnow))
-  cstars <- aggregate(gnow ~ tnow, res, min)$gnow
-  tstarsi <- aggregate(gnow ~ tnow, res, which.min)
+  res2 <- subset(res, !is.na(res$gnow))
+  cstars <- aggregate(gnow ~ tnow, res2, min)$gnow
+  tstarsi <- aggregate(gnow ~ tnow, res2, which.min)
   tstarsi <- tstarsi$gnow + (seqlen - 1) * (0:(length(tnowvec) - 1))
-  tstars <- res$t[tstarsi]
+  tstars <- res2$t[tstarsi]
   taustars <- tstars - tnowvec
-  ctotal <- (cstars * taustars) / tstars
+  cuint <- sapply(tnowvec, function(tnowi){
+    trel <- subset(res, res$tnow == tnowi)
+    f <- -diff(trel$rel)
+    tauvec <- trel$t[-1] # absolute timescale!
+    tau <- trel$t[which.min(trel$gnow)]
+    sum(f[tauvec <= tau] / tauvec[tauvec <= tau])
+  })
+  #cat("cuint =", cuint)
+  ctotal <- cp / tstars * res2$rel[tstarsi] + cu * cuint
   data.frame(tnow = tnowvec, taustar = taustars, tstar = tstars, cstar = cstars, ctotal = ctotal)
 }
 

### 2016-11-17 cbm-sim.R
nnynlist function, censtime in sim1cycle

@@ -29,15 +29,17 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
   signnow <- computeSystemSurvivalSignature(sysnow)
   wctnow <- 1:K       # which component types are now present in the system?
   ftsnow <- as.list(rep(list(NULL), K))
-  gotonext = TRUE     # indicator that loop should go on
-  failed = FALSE      # indicator whether the system has failed
-  repschedfor = Inf   # for which time is repair scheduled?
+  gotonext <- TRUE     # indicator that loop should go on
+  failed <- FALSE      # indicator whether the system has failed
+  repschedfor <- Inf   # for which time is repair scheduled?
+  censtime <- Inf
   res <- data.frame() # initialize results data frame
   while(gotonext){
     cat("tnow =", tnow,"\n")
     if (!failed){ # if not failed already in previous loop, check...
       if (all(signnow$Probability == 0)){ # system has failed now, schedule repair for tnow + tprep if not scheduled already
         failed <- TRUE
+        censtime <- tnow
         taustarnow <- NA
         if (repschedfor == Inf)
           repschedfor <- tnow + tprep
@@ -49,6 +51,7 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
           taustarnow <- gnowvec$tau[which.min(gnowvec$gnow)] - tnow
           if (taustarnow <= tprep){ # schedule repair for tnow + tprep if not scheduled already
             repschedfor <- tnow + tprep
+            censtime <- tnow + tprep
           } # else do nothing & go on to next loop (repschedfor is still Inf)
         } else { # repair already scheduled: do nothing
           taustarnow <- NA
@@ -63,7 +66,7 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
       gotonext <- FALSE
     }
     # write all current things in results data frame
-    resnow <- data.frame(tnow = tnow, failed = failed, taustar = taustarnow, repschedfor = repschedfor)
+    resnow <- data.frame(tnow = tnow, failed = failed, taustar = taustarnow, repschedfor = repschedfor, censtime = censtime)
     res <- rbind(res, resnow)
     # now prepare for next loop
     tnow <- tnow + tnowstep

### 2016-11-17 cbm-sys.R

@@ -277,7 +277,9 @@ dev.off()
 brcompftssim <- list(C1 = 10, C2 = 6, C3 = 7, C4 = 10, H = 8,  M = 12, P1 = 10, P2 = 3, P3 = 4, P4 = 10)
 
 brsim1 <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim, n0y0 = brn0y0, beta = brbeta,
-                    tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = FALSE)
+                    tnowstep = 1, hor = 4, tprep = 0.1, trepa = 0, seqlen = 401, prior = FALSE)
+brsim1pr <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim, n0y0 = brn0y0, beta = brbeta,
+                      tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = TRUE)
 
 
 

### 2016-11-17 weibull-sys-functions.R

@@ -368,6 +368,7 @@ taustarhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen =
 # can be used to include test data and to update after an operational cycle ends
 # fts   vector of observed failure times
 # cts   vector of censoring times
+# beta  Weibull shape parameter
 nn <- function(n0, fts)
   n0 + length(fts)
 yn <- function(n0, y0, fts, cts, beta)
@@ -375,8 +376,13 @@ yn <- function(n0, y0, fts, cts, beta)
 nnyn <- function(n0y0, fts, cts, beta)
   c(nn(n0y0[1], fts), yn(n0y0[1], n0y0[2], fts, cts, beta))
 # update n0y0 list: 
-#nnynlist <- function(n0y0list, beta){
-  
+nnynlist <- function(n0y0list, ftslist, ctslist, beta){
+  K <- length(n0y0list)
+  res <- as.list(1:K)
+  for (k in 1:K){
+    res[[k]] <- nnyn(n0y0list[[k]], ftslist[[k]], ctslist[[k]], beta[k])
+  }
+  res
 }
 
 

### 2016-11-17 cbm-rbd-paper.tex
one-cycle total cost rate
updating section 5, graphs for different failure histories in paper, sim1cycle now returns all interesting stuff

@@
 \newcommand{\tprep}{\tau_{\text{prep}}}
+\newcommand{\tstarnow}{t_*^{(\tnow)}}
+\newcommand{\cstarnow}{c_*^{(\tnow)}}
+\newcommand{\ctotalnow}{c_\text{total}^{(\tnow)}}
 
@@
 Each operational cycle starts with system startup.
-At this point in time, the system being is in an (as good as) new state,
+At this point in time, the system is in an (as good as) new state,
 i.e., all components in the system are (as good as) new and have not aged.
@@
 We assume that both a planned and unplanned maintenance action results in an (as good as) new system state by replacing all components,
-such that the system begins a new cycle always under the same condition.
-Replacement schemes that do not replace all components need to take into account the different ages of components in the system
+such that the system begins a new cycle always under the same conditions.
+Replacement schemes that do not replace all components would require to account for the different ages of components in the system
 at the start of a new cycle.
@@
 does not matter directly for the determination of $\tausnow$.
-Downtimes are instead accounted for indirectly via the costs parameters,
+Downtimes are instead accounted for indirectly via the costs parameters in the trade-off leading to $\tausnow$,
 as described next.
@@
 and $\fsysnow(t)$ be the corresponding density.
-Conditional on the realization of $\Tsysnow$, the unit cost rate is 
-\begin{align*}
+Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate is 
+\begin{align}
 g(\tau \mid \Tsysnow = \tsysnow) &=
 \begin{cases}
-c_p / \tau  & \text{if } \tsysnow \ge \tau \\
-c_u / \Tsys & \text{if } \tsysnow < \tau \,.
+c_p / \tau     & \text{if } \tsysnow \ge \tnow + \tau \\
+c_u / \tsysnow & \text{if } \tsysnow  <  \tnow + \tau \,.
 \end{cases}
-\end{align*}
-Taking the expectation over $\Tsysnow$ leads to the expected unit cost rate being
-\begin{align}
-\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(t) \dd t\,.
 \label{eq:gtau}
 \end{align}
-Note that for the integral to exist in \eqref{eq:gtau},
-$\E[1/\Tsysnow]$ must exist, which is a condition for $\fsysnow(t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
+Note that here, $\tau$ is a timespan starting from $\tnow$,
+and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
+In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
+where $0$ corresponds to the time of system start-up.
+Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
+\begin{align}
+\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
+\label{eq:gtnowtau}
+\end{align}
+again incorporating all that is known at time $\tnow$.
+
+Note that for the integral in \eqref{eq:gtnowtau} to exist, $\E[1/\Tsysnow \mid \Tsysnow > \tnow]$ must exist,
+which is a condition for $\fsysnow(\tnow + t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
 This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
 For our approach, however, this condition is not relevant,
-as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively.
-We will describe next how we numerically evaluate \eqref{eq:gtau} and find $\tausnow$.
+as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively
+(see Section~\ref{sec:optim} below).
+
+Minimizing $\gnow(\tau)$ leads to $\tausnow$,
+the optimal moment of maintenance on a prospective time scale.
+(Our procedure is illustrated for a number of current times $\tnow$ in Figure~\ref{fig:ghistfig2}.)
+The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
+thus is the lowest unit cost rate attainable for the remaining lifetime of the system,
+i.e., for what happens beyond current time $\tnow$.
+Also of interest is the total cost rate at $\tnow$, denoted by $\ctotalnow$.
+This gives the expected unit cost rate calculated over the full time since system start-up,
+under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
+$\ctotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
+However, when many (or few but critical) components fail, $\ctotalnow$ may increase,
+since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
+For a numerical example, these relations are depicted in Figure~\ref{fig:tauhistfig2}.
+
+We will describe next how we numerically evaluate \eqref{eq:gtnowtau} and find $\tausnow$
+for our choice of component model.
 %($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
@@
 $t_h$ can be determined by practical considerations,
-but generally should reach into the tail of $\Rsysnow(t)$.
+but generally should reach into the tail of $\Rsysnow(t)$
+such that one can be sure to find $\tausnow$.
 We calculate $\gnow(\tau)$ on the same grid,
@@
 
-We approximate the integral in \eqref{eq:gtau} numerically by a sum,
+We approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
 where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on a dense grid.
@@
 %so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau_*^{\tnow}$.
-
-***example figures with very weak prior info, could look different for stronger expert information!
-
-***also example where remaining component type is (close to) exponential,
-such that corrective maintenance becomes optimal!
 
@@
 \includegraphics[width=\textwidth]{tauhistfig2}
-\caption{$\tausnow$, $t^* = \tnow + \tausnow$, $\gnow(\tausnow)$, and the total cost rate **** as functions of $\tnow$
+\caption{$\tausnow$, $\tstarnow = \tnow + \tausnow$, $\cstarnow = \gnow(\tausnow)$,
+and the total unit cost rate $\ctotalnow$ as functions of $\tnow$
 for the system depicted in Figure~\ref{fig:brakesys-layout},
@@
 Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
-differing from the overall cost rate (lower right panel).
+differing from the overall cost rate $\ctotalnow$ (lower right panel).
 %For the maintenance action triggered at $\tnow = 8$,
@@
 %and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
-At time $8$, the overall expected cost rate for repair at time $8.38$ is $0.314$,
-up from $0.076$ for repair at time $8.62$, as cost-optimal at time $7.9$.}
+At time $8$, the overall expected cost rate for repair scheduled at time $8.38$ is $0.044$,
+up from $0.036$ for repair scheduled at time $8.62$, as cost-optimal at time $7.9$.}
 \label{fig:tauhistfig2}
@@
 \includegraphics[width=\textwidth]{tauhistfig3}
-\caption{Illustration of the gains due to the parameter update.
+\caption{Illustration of the gains due to the parameter update
+assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.
 $\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{tauhist2fig3}
+\caption{***early failures: $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$}
+\label{fig:tauhist2fig3}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{tauhist3fig3}
+\caption{***very late failures: $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$}
+\label{fig:tauhist3fig3}
+\end{figure}
+
 \section{***numerical examples for complex system layout}
@@
 
-***use simplified brake system from ASCE-ASME paper, example history of components failing
-
-***plot both $\tau_*^{\tnow}$ and $\tnow + \tau_*^{\tnow}$ over time for different failure histories
+***use simplified brake system from ASCE-ASME paper,
+different example histories (when do components fail?)
+
+***In current graphs,
+prior component model parameters are taken as in Table~\ref{tab:priorparams},
+and $c_u = 1$, $c_p = 0.2$. *** plot prior predictive distributions?***
+
+***example figures are with very weak prior info
+(see Table~\ref{tab:priorparams}: $\nkz = 1$ or $2$),
+things could look different for stronger expert information!
+
+***also example where remaining component type is (close to) exponential,
+such that corrective maintenance becomes optimal!
+
+\begin{table}
+\centering
+\begin{tabular}{crrrrrrr}
+  \toprule
+$k$ & $\beta_k$ & $\E[T_i^k]$ & $\ykz$ & $\nkz$ \\
+  \midrule
+M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
+H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
+C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
+P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
+  \bottomrule
+\end{tabular}
+\caption{Prior parameters for the four component types as used in the numeric examples.}
+\label{tab:priorparams}
+\end{table}
 

### 2016-11-17 cbm-sim.R

@@ -26,20 +26,18 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
   # initializing: initial arguments for gnowhor
   tnow <- 0
   sysnow <- sys
-  signnow <- computeSystemSurvivalSignature(sysnow)
+  signnow <- sign <- computeSystemSurvivalSignature(sysnow)
   wctnow <- 1:K       # which component types are now present in the system?
   ftsnow <- as.list(rep(list(NULL), K))
   gotonext <- TRUE     # indicator that loop should go on
   failed <- FALSE      # indicator whether the system has failed
   repschedfor <- Inf   # for which time is repair scheduled?
-  censtime <- Inf
   res <- data.frame() # initialize results data frame
   while(gotonext){
     cat("tnow =", tnow,"\n")
     if (!failed){ # if not failed already in previous loop, check...
       if (all(signnow$Probability == 0)){ # system has failed now, schedule repair for tnow + tprep if not scheduled already
         failed <- TRUE
-        censtime <- tnow
         taustarnow <- NA
         if (repschedfor == Inf)
           repschedfor <- tnow + tprep
@@ -51,7 +49,6 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
           taustarnow <- gnowvec$tau[which.min(gnowvec$gnow)] - tnow
           if (taustarnow <= tprep){ # schedule repair for tnow + tprep if not scheduled already
             repschedfor <- tnow + tprep
-            censtime <- tnow + tprep
           } # else do nothing & go on to next loop (repschedfor is still Inf)
         } else { # repair already scheduled: do nothing
           taustarnow <- NA
@@ -66,7 +63,7 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
       gotonext <- FALSE
     }
     # write all current things in results data frame
-    resnow <- data.frame(tnow = tnow, failed = failed, taustar = taustarnow, repschedfor = repschedfor, censtime = censtime)
+    resnow <- data.frame(tnow = tnow, failed = failed, taustar = taustarnow, repschedfor = repschedfor)
     res <- rbind(res, resnow)
     # now prepare for next loop
     tnow <- tnow + tnowstep
[…]

### 2016-11-17 cbm-sys.R

@@ -277,9 +277,14 @@ dev.off()
 brcompftssim <- list(C1 = 10, C2 = 6, C3 = 7, C4 = 10, H = 8,  M = 12, P1 = 10, P2 = 3, P3 = 4, P4 = 10)
 
 brsim1 <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim, n0y0 = brn0y0, beta = brbeta,
-                    tnowstep = 1, hor = 4, tprep = 0.1, trepa = 0, seqlen = 401, prior = FALSE)
+                    tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = FALSE)
 brsim1pr <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim, n0y0 = brn0y0, beta = brbeta,
                       tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = TRUE)
+
+# example where system fails at time 3.7
+brcompftssim0 <- list(C1 = 10, C2 = 6, C3 = 7, C4 = 10, H = 3.6,  M = 3.7, P1 = 10, P2 = 3, P3 = 4, P4 = 10)
+brsim0 <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim0, n0y0 = brn0y0, beta = brbeta,
+                    tnowstep = 0.25, hor = 4, tprep = 1, trepa = 0, seqlen = 401, prior = FALSE)
 
 
 

### 2016-11-17 weibull-sys-functions.R

@@ -92,7 +92,7 @@ sysrelnow <- function(survsign, n0y0, beta, fts, tnow, t, prior = FALSE, table =
   ck <- apply(survsign, 2, max)
   ck <- ck[-length(ck)]
   # e_k from fts (number of failed components per type)
-  ek <- unlist(lapply(fts, length))
+  ek <- sapply(fts, length)
   Nk <- ck + ek
   if(length(fts) != K | length(beta) != K | length(Nk) != K)
     stop("Check the length of arguments n0y0, beta, fts.\n

### 2016-11-17 cbm-sim.R
minor stuff for sim1cycle

@@ -19,8 +19,9 @@
 # cu       cost of unplanned (corrective) repair action
 # cp       cost of planned (preventive) repair action, cp < cu
 # onecycle whether to use the one-cycle criterion or the renewal-based one
+# timeround to how many digits to round the time points
 sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, trepa = 0,
-                      seqlen = 101, prior = FALSE, cu = 1, cp = 0.2, onecycle = TRUE){
+                      seqlen = 101, prior = FALSE, cu = 1, cp = 0.2, onecycle = TRUE, timeround = 5){
   K <- length(ctypes)
   ftschron <- sort(unlist(compfts)) # when something fails
   # initializing: initial arguments for gnowhor
@@ -29,12 +30,13 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
   signnow <- sign <- computeSystemSurvivalSignature(sysnow)
   wctnow <- 1:K       # which component types are now present in the system?
   ftsnow <- as.list(rep(list(NULL), K))
+  failedcompsnow <- numeric(0)
   gotonext <- TRUE     # indicator that loop should go on
   failed <- FALSE      # indicator whether the system has failed
   repschedfor <- Inf   # for which time is repair scheduled?
   res <- data.frame() # initialize results data frame
   while(gotonext){
-    cat("tnow =", tnow,"\n")
+    cat("tnow =", tnow, "failedcompsnow =", failedcompsnow, "\n")
     if (!failed){ # if not failed already in previous loop, check...
       if (all(signnow$Probability == 0)){ # system has failed now, schedule repair for tnow + tprep if not scheduled already
         failed <- TRUE
@@ -66,7 +68,7 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
     resnow <- data.frame(tnow = tnow, failed = failed, taustar = taustarnow, repschedfor = repschedfor)
     res <- rbind(res, resnow)
     # now prepare for next loop
-    tnow <- tnow + tnowstep
+    tnow <- round(tnow + tnowstep, timeround)
     # update stuff if system not failed (otherwise not needed except tnow update!)
     if (!failed){
       failedcompsnow <- ftschron[ftschron <= tnow]

### 2016-11-17 cbm-sys.R

@@ -274,14 +274,15 @@ dev.off()
 # -------------------------------------------------------------------------
 
 # simulate one operational cycle
+# new compfts with failure times for all components such that sim1cycle definitively terminates
 brcompftssim <- list(C1 = 10, C2 = 6, C3 = 7, C4 = 10, H = 8,  M = 12, P1 = 10, P2 = 3, P3 = 4, P4 = 10)
 
 brsim1 <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim, n0y0 = brn0y0, beta = brbeta,
-                    tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = FALSE)
+                    tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = FALSE)
 brsim1pr <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim, n0y0 = brn0y0, beta = brbeta,
-                      tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = TRUE)
+                      tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = TRUE)
 
-# example where system fails at time 3.7
+# quick sexample where system fails at time 3.7
 brcompftssim0 <- list(C1 = 10, C2 = 6, C3 = 7, C4 = 10, H = 3.6,  M = 3.7, P1 = 10, P2 = 3, P3 = 4, P4 = 10)
 brsim0 <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim0, n0y0 = brn0y0, beta = brbeta,
                     tnowstep = 0.25, hor = 4, tprep = 1, trepa = 0, seqlen = 401, prior = FALSE)

### 2016-11-18 cbm-rbd-paper.tex
work on sec 5, component prior predictive plot

@@
 \end{align}
-again incorporating all that is known at time $\tnow$.
+and $\tausnow = \arg\min \gnow(\tau)$.
+$\tausnow$, the optimal moment of maintenance as of $\tnow$,
+incorporates thus all that is known at current time $\tnow$.
+%The lower index $\tnow$ of $\tausnow$ emphasizes that
+%depends on $\tnow$, and also on the history of the system.
+Figure~\ref{fig:ghistfig2} illustrates this procedure for a number of current times $\tnow$.
 
@@
 the optimal moment of maintenance on a prospective time scale.
-(Our procedure is illustrated for a number of current times $\tnow$ in Figure~\ref{fig:ghistfig2}.)
 The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
-thus is the lowest unit cost rate attainable for the remaining lifetime of the system,
+thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
 i.e., for what happens beyond current time $\tnow$.
@@
 
-%*** not possible / *** to minimize $\gnow(\tau)$ analytically.
-***we calculate $\Rsysnow(t)$ on discrete grid from $\tnow$ until some horizon time $\tnow + t_h$.
-$t_h$ can be determined by practical considerations,
-but generally should reach into the tail of $\Rsysnow(t)$
-such that one can be sure to find $\tausnow$.
+Since $\Rsysnow(t)$ is not tractable analytically,
+we calculate $\Rsysnow(t)$ for values of $t$ on a dense grid spanning from $\tnow$ to some horizon time $\tnow + t_h$.
+(The choice of $h_t$ is discussed in more detail below.)
 We calculate $\gnow(\tau)$ on the same grid,
-and determine $\tausnow$ as the minimum over this grid.
-
-We approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
-where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on a dense grid.
-$\gnow(\tau)$ is likewise evaluated on a dense grid,
-and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
-%The lower index $\tnow$ of the optimal moment of maintenance serves to remind that
-%$\tau^*$ depends on $\tnow$, and also on the history of the system.
+and determine $\tausnow$ by minimizing over this grid.
+Here, we approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
+where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on the grid.
+%$\gnow(\tau)$ is likewise evaluated on a dense grid,
+%and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
+
+The horizon span $t_h$ can be determined by practical considerations,
+but generally should reach far enough into the tail of $\Rsysnow(t)$
+such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
+Note that from \eqref{eq:gtnowtau} it is clear that one needs only ****
 
@@
 \caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
-for the system depicted in Figure~\ref{fig:brakesys-layout},
+for the system depicted in Figure~\ref{fig:brakesys-layout}
+and prior component models as given in Table~\ref{tab:priorparams},
 assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
-and $c_u = 1$, $c_p = 0.2$.}
+and costs $c_u = 1$, $c_p = 0.2$.}
 \label{fig:ghistfig2}
+\end{figure}
+
+\section{***numerical examples for complex system layout}
+\label{sec:examples}
+
+***use simplified brake system from ASCE-ASME paper,
+different example histories (when do components fail?)
+
+***In current graphs,
+prior component model parameters are taken as in Table~\ref{tab:priorparams},
+and $c_u = 1$, $c_p = 0.2$. *** plot prior predictive distributions?***
+
+***example figures are with very weak prior info
+(see Table~\ref{tab:priorparams}: $\nkz = 1$ or $2$),
+things could look different for stronger expert information!
+
+***also example where remaining component type is (close to) exponential,
+such that corrective maintenance becomes optimal!
+
+\begin{table}
+\centering
+\begin{tabular}{crrrrrrr}
+  \toprule
+$k$ & $\beta_k$ & $\E[T_i^k]$ & $\ykz$ & $\nkz$ \\
+  \midrule
+M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
+H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
+C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
+P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
+  \bottomrule
+\end{tabular}
+\caption{Prior parameters for the four component types as used in subsequent numerical examples.
+The corresponding expected failure behaviour is visualized in Figure~\ref{fig:comppriorfig1}.}
+\label{tab:priorparams}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{comppriorfig1}
+\caption{Prior predictive reliability functions corresponding to the values from Table~\ref{tab:priorparams},
+%for the four component types of the system depicted in Figure~\ref{fig:brakesys-layout},
+showing the expected failure behaviour according to this choice of parameters.}
+\label{fig:comppriorfig1}
 \end{figure}
@@
 
-\section{***numerical examples for complex system layout}
-\label{sec:examples}
-
-***use simplified brake system from ASCE-ASME paper,
-different example histories (when do components fail?)
-
-***In current graphs,
-prior component model parameters are taken as in Table~\ref{tab:priorparams},
-and $c_u = 1$, $c_p = 0.2$. *** plot prior predictive distributions?***
-
-***example figures are with very weak prior info
-(see Table~\ref{tab:priorparams}: $\nkz = 1$ or $2$),
-things could look different for stronger expert information!
-
-***also example where remaining component type is (close to) exponential,
-such that corrective maintenance becomes optimal!
-
-\begin{table}
-\centering
-\begin{tabular}{crrrrrrr}
-  \toprule
-$k$ & $\beta_k$ & $\E[T_i^k]$ & $\ykz$ & $\nkz$ \\
-  \midrule
-M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
-H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
-C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
-P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
-  \bottomrule
-\end{tabular}
-\caption{Prior parameters for the four component types as used in the numeric examples.}
-\label{tab:priorparams}
-\end{table}
-
 ***larger simulation study?

### 2016-11-18 cbm-sys.R

@@ -20,7 +20,7 @@ brn0y0 <- list(C=c(brn0[1], failuretolambda(brmttf[1], brbeta[1])),
                H=c(brn0[2], failuretolambda(brmttf[2], brbeta[2])),
                M=c(brn0[3], failuretolambda(brmttf[3], brbeta[3])),
                P=c(brn0[4], failuretolambda(brmttf[4], brbeta[4])))
-# prior
+# system (prior) predictive at tnow = 0
 brfts0 <- list(C=NULL, H=NULL, M=NULL, P=NULL)
 sysrelnow(brsysign, brn0y0, brbeta, brfts0, tnow=0, t=1)
 sysrelnowvec(brsysign, brn0y0, brbeta, brfts0, tnow=0, tvec=1:20)
@@ -47,6 +47,41 @@ sysrelnowvec(br8Hsysign, brn0y0[-2], brbeta[-2], brfts8H[-2], tnow=8, tvec=8:20)
 sysrelnowhor(br8Hsysign, brn0y0[-2], brbeta[-2], brfts8H[-2], tnow=8, hor=10, seqlen=5)
 brtnow8H <- sysrelnowhor(br8Hsysign, brn0y0[-2], brbeta[-2], brfts8[-2], tnow=8, hor=10)
 qplot(brtnow8H$t, brtnow8H$rel)
+
+# component prior predictive reliability functions to visualize prior assumptions
+comphor <- 10; complen <- 201
+onecomp <- graph.formula(s -- 1 -- t)
+Ccomp <- setCompTypes(onecomp, list(C = "1"))
+Hcomp <- setCompTypes(onecomp, list(H = "1"))
+Mcomp <- setCompTypes(onecomp, list(M = "1"))
+Pcomp <- setCompTypes(onecomp, list(P = "1"))
+Crel <- sysrelnowhor(computeSystemSurvivalSignature(Ccomp), brn0y0[1], brbeta[1], brfts0[1],
+                     tnow = 0, hor = comphor, seqlen = complen)
+Hrel <- sysrelnowhor(computeSystemSurvivalSignature(Hcomp), brn0y0[2], brbeta[2], brfts0[2],
+                     tnow = 0, hor = comphor, seqlen = complen)
+Mrel <- sysrelnowhor(computeSystemSurvivalSignature(Mcomp), brn0y0[3], brbeta[3], brfts0[3],
+                     tnow = 0, hor = comphor, seqlen = complen)
[…]

### 2016-11-18 cbm-sim.R
multicycle simulation

@@ -36,7 +36,7 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
   repschedfor <- Inf   # for which time is repair scheduled?
   res <- data.frame() # initialize results data frame
   while(gotonext){
-    cat("tnow =", tnow, "failedcompsnow =", failedcompsnow, "\n")
+    cat("tnow =", tnow, ": ") #"failedcompsnow =", failedcompsnow, "\n")
     if (!failed){ # if not failed already in previous loop, check...
       if (all(signnow$Probability == 0)){ # system has failed now, schedule repair for tnow + tprep if not scheduled already
         failed <- TRUE
@@ -110,7 +110,6 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
   ck <- Nk - ek
   for (k in 1:K)
     censlist[[k]] <- rep(repschedfor, ck[k])
-  #print(ftslist); print(censlist)
   nnyn <- nnynlist(n0y0, ftslist, censlist, beta) # updated parameters at end of cycle
   # time the whole cycle took
   tend <- repschedfor + trepa
@@ -127,7 +126,45 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
 }  
 
 
-
+# function to simulate N operational cycles for one machine,
+# i.e. updated parameters from one cycle are used as prior parameters in next cycle
+# sys      system reliability block diagram at t = 0
+# ctypes   list giving the types of components in the system, same format as
+#          used for setCompTypes(), but needs the same order as in survsign table (!!!)
+# compfts  list with elements named like the vertices in sys, giving the N (simulated)
+#          failure times of this component -- assumed that no failure times == 0
+# n0y0     list of K prior parameter pairs c(n0,y0)
+# beta     vector of K fixed weibull shape parameters
+# tnowstep time interval after which current system reliability is re-evaluated
+# hor      how many time units from tnow into the future to calculate sysrelnow
+# tprep    preparation time to do preventive maintenance
+# trepa    time needed to repair the system
+# seqlen   at how many points to evaluate sysrelnow
+# cu       cost of unplanned (corrective) repair action
+# cp       cost of planned (preventive) repair action, cp < cu
[…]

### 2016-11-18 cbm-sys-old.R

@@ -1,0 +1,255 @@
+brprtvec <- seq(0, 20, length.out=101)
+
+# prior system reliability function at tnow = 0
+brprio <- sysrelPbox(luckobjlist = brpr, survsign = brsysign, nk = brprnk, beta = brbeta,
+                     fts = brfts0, tnow = 0, tvec = brprtvec, prior = TRUE)
+
+# component reliability functions via sysrelPbox, posterior does not work
+brMprrel <- sysrelPbox(luckobjlist = list(brpr[[1]]), survsign = oneCompSurvSign("M"), nk = 1,
+                       beta = brbeta[1], fts = list(NULL), tnow = 0, tvec = brprtvec, prior = TRUE)
+brHprrel <- sysrelPbox(luckobjlist = list(brpr[[2]]), survsign = oneCompSurvSign("H"), nk = 1,
+                       beta = brbeta[2], fts = list(NULL), tnow = 0, tvec = brprtvec, prior = TRUE)
+brCprrel <- sysrelPbox(luckobjlist = list(brpr[[3]]), survsign = oneCompSurvSign("C"), nk = 1,
+                       beta = brbeta[3], fts = list(NULL), tnow = 0, tvec = brprtvec, prior = TRUE)
+brPprrel <- sysrelPbox(luckobjlist = list(brpr[[4]]), survsign = oneCompSurvSign("P"), nk = 1,
+                       beta = brbeta[4], fts = list(NULL), tnow = 0, tvec = brprtvec, prior = TRUE)
+brprdf <- rbind(data.frame(brMprrel, Part = "M", Item = "Prior"), data.frame(brHprrel, Part = "H", Item = "Prior"),
+                data.frame(brCprrel, Part = "C", Item = "Prior"), data.frame(brPprrel, Part = "P", Item = "Prior"))
+brprdf$Item <- ordered(brprdf$Item, levels=c("Prior", "Posterior"))
+brprdf$Part <- ordered(brprdf$Part, levels=c("M", "H", "C", "P"))
+fig3 <- ggplot(brprdf, aes(x = tvec)) + theme_bw() + ijarcol + ijarfill + ylim(0, 1) +  
+  geom_ribbon(aes(ymin = lower, ymax = upper, group = Item, colour = Item, fill = Item), alpha = 0.5) +
+  geom_line(aes(y = lower, group = Item, colour = Item)) + 
[…]

### 2016-11-18 cbm-sys.R

@@ -80,8 +80,7 @@ pdf("comppriorfig2.pdf", width = 6, height = 4)
 comppriorfig2
 dev.off()
 
-
-
+# -------------------------------------------------------------------------------------------------
 
 # to plot sysrelnow history
 #brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = NA, M = NA, P1 = NA, P2 = 3, P3 = 4, P4 = NA)
@@ -322,269 +321,52 @@ brcompftssim0 <- list(C1 = 10, C2 = 6, C3 = 7, C4 = 10, H = 3.6,  M = 3.7, P1 = 
 brsim0 <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim0, n0y0 = brn0y0, beta = brbeta,
                     tnowstep = 0.25, hor = 4, tprep = 1, trepa = 0, seqlen = 401, prior = FALSE)
 
+# simulate several operational cycles
+brcompftssim2 <- list(C1 = c(10, 10), C2 = c(6, 6), C3 = c(7, 7), C4 = c(10, 10), H = c(8, 8),
+                      M = c(12, 12), P1 = c(10, 10), P2 = c(3, 3), P3 = c(4, 4), P4 = c(10, 10))
+brsim2pr <- simNcycle(sys = br, ctypes = brctypes, compfts = brcompftssim2, n0y0 = brn0y0, beta = brbeta,
+                      tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = TRUE)
+brsim2pr <- simNcycle(sys = br, ctypes = brctypes, compfts = brcompftssim2, n0y0 = brn0y0, beta = brbeta,
+                      tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = TRUE, cycleupdate = FALSE)
 
-
-
-
+# simulate Weibull failure times according to prior parameter choices (note different parametrization!)
+set.seed(1328)
+ncycles <- 5
+C1sim1 <- rweibull(ncycles, shape = brbeta[1], scale = (failuretolambda(brmttf[1], brbeta[1]))^(1/brbeta[1]))
+C2sim1 <- rweibull(ncycles, shape = brbeta[1], scale = (failuretolambda(brmttf[1], brbeta[1]))^(1/brbeta[1]))
[…]

### 2016-11-18 cbm-sim.R
two 5-cycle simulations

@@ -151,23 +151,43 @@ simNcycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
     stop("each element of compfts must contain the same number of failure times")
   compftsi <- lapply(compfts, function(x) x[1])
   n0y0i <- n0y0
-  res <- list()
+  res <- res2 <- nnyn <- list()
   for (i in 1:N){
     cat("Operational cycle", i, "\n")
     res[[i]] <- sim1cycle(sys = sys, ctypes = ctypes, compfts = compftsi, n0y0 = n0y0i, beta = beta,
                           tnowstep = tnowstep, hor = hor, tprep = tprep, trepa = trepa, seqlen = seqlen,
                           prior = prior, cu = cu, cp = cp, onecycle = onecycle, timeround = timeround)
+    res2 <- rbind(res2, data.frame(cycle = i, res[[i]]$res))
+    nnynlist <- list(nnyn, res[[i]]$nnyn)
     if (i < N){ # update stuff for next cycle
       compftsi <- lapply(compfts, function(x) x[i + 1])
       if (cycleupdate)
         n0y0i <- res[[i]]$nnyn
     }
   }
-  return(res) # or concatenate res dfs, list of nnnyn's, vector of tend, downtime, costrate?
+  res2$cycle <- as.factor(res2$cycle)
+  tendvec <- sapply(res, function(resi) resi$tend)
+  downtimevec <- sapply(res, function(resi) resi$downtime)
+  costratevec <- sapply(res, function(resi) resi$costrate)
+  return(list(res = res2, nnyn = nnynlist, tend = tendvec, downtime = downtimevec, costrate = costratevec))
 }
 
-
-
+# function to simulate Weibull failure times according to prior parameter choices (note different parametrization!)
+# ncycles  how many failure times to simulate for each component
+brWeibullData <- function(ncycles, beta, mttf){
+  C1sim1 <- rweibull(ncycles, shape = beta[1], scale = (failuretolambda(mttf[1], beta[1]))^(1/beta[1]))
+  C2sim1 <- rweibull(ncycles, shape = beta[1], scale = (failuretolambda(mttf[1], beta[1]))^(1/beta[1]))
[…]

### 2016-11-18 cbm-sys.R

@@ -329,43 +329,44 @@ brsim2pr <- simNcycle(sys = br, ctypes = brctypes, compfts = brcompftssim2, n0y0
 brsim2pr <- simNcycle(sys = br, ctypes = brctypes, compfts = brcompftssim2, n0y0 = brn0y0, beta = brbeta,
                       tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = TRUE, cycleupdate = FALSE)
 
+# -------------------------------------------------------------------------
+
 # simulate Weibull failure times according to prior parameter choices (note different parametrization!)
 set.seed(1328)
-ncycles <- 5
-C1sim1 <- rweibull(ncycles, shape = brbeta[1], scale = (failuretolambda(brmttf[1], brbeta[1]))^(1/brbeta[1]))
-C2sim1 <- rweibull(ncycles, shape = brbeta[1], scale = (failuretolambda(brmttf[1], brbeta[1]))^(1/brbeta[1]))
-C3sim1 <- rweibull(ncycles, shape = brbeta[1], scale = (failuretolambda(brmttf[1], brbeta[1]))^(1/brbeta[1]))
-C4sim1 <- rweibull(ncycles, shape = brbeta[1], scale = (failuretolambda(brmttf[1], brbeta[1]))^(1/brbeta[1]))
-Hsim1  <- rweibull(ncycles, shape = brbeta[2], scale = (failuretolambda(brmttf[2], brbeta[2]))^(1/brbeta[2]))
-Msim1  <- rweibull(ncycles, shape = brbeta[3], scale = (failuretolambda(brmttf[3], brbeta[3]))^(1/brbeta[3]))
-P1sim1 <- rweibull(ncycles, shape = brbeta[4], scale = (failuretolambda(brmttf[4], brbeta[4]))^(1/brbeta[4]))
-P2sim1 <- rweibull(ncycles, shape = brbeta[4], scale = (failuretolambda(brmttf[4], brbeta[4]))^(1/brbeta[4]))
-P3sim1 <- rweibull(ncycles, shape = brbeta[4], scale = (failuretolambda(brmttf[4], brbeta[4]))^(1/brbeta[4]))
-P4sim1 <- rweibull(ncycles, shape = brbeta[4], scale = (failuretolambda(brmttf[4], brbeta[4]))^(1/brbeta[4]))
-brcompftssim1 <- list(C1 = C1sim1, C2 = C2sim1, C3 = C3sim1, C4 = C4sim1, H = Hsim1,
[…]

### 2016-11-19 cbm-rbd-paper.tex
multicycle simulation
third simulation

@@
 since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
-For a numerical example, these relations are depicted in Figure~\ref{fig:tauhistfig2}.
+These relations are depicted in Figure~\ref{fig:tauhistfig2}. %for a numerical example,
 
@@
 such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
-Note that from \eqref{eq:gtnowtau} it is clear that one needs only ****
+Note that \eqref{eq:gtnowtau} indicates that values for $\Rsysnow(t)$ and $\fsysnow(t)$ 
+only for $t \leq \tau$ are needed to calculate $\gnow(\tau)$.
+
+We use \textsf{R} \citep{R} for our calculations,
+using the package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
+to calculate survival signatures.
+As the parameter update step is closed-form,
+$\tausnow$
 

### 2016-11-19 cbm-sys.R

@@ -335,10 +335,15 @@ brsim2pr <- simNcycle(sys = br, ctypes = brctypes, compfts = brcompftssim2, n0y0
 set.seed(1328)
 brcompftssim1 <- brWeibullData(5, brbeta, brmttf)
 brcompftssim2 <- brWeibullData(5, brbeta, brmttf)
+brcompftssim3 <- brWeibullData(5, brbeta, brmttf)
 brsimN51 <- simNcycle(sys = br, ctypes = brctypes, compfts = brcompftssim1, n0y0 = brn0y0, beta = brbeta,
                       tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401)
+brsimN51$downtime; brsimN51$tend; brsimN51$costrate
 # overall costrate
 weighted.mean(brsimN51$costrate, brsimN51$tend)
+# to compare: initial taustar is 1.27 with expected cost rate 0.2207986
+# for this data (no system failure before 1.27), we get cost rate 0.2/1.27 = 0.1574803
+# but with 5 replacements over time 5 * 1.27 = 6.35, while we get 15.5 lifetime
 brsimN51fig1 <- ggplot(brsimN51$res, aes(x = tnow, y = taustar)) + 
   geom_line(aes(colour = cycle, group = cycle)) + geom_point(aes(colour = cycle, group = cycle)) +
   xlab(expression(t[now])) + ylab(expression(paste(tau["*"]^(t[now]), (t[now])))) +
@@ -361,12 +366,23 @@ pdf("brsimN52fig1.pdf", width = 5, height = 3)
 brsimN52fig1
 dev.off()
 
+brsimN53 <- simNcycle(sys = br, ctypes = brctypes, compfts = brcompftssim3, n0y0 = brn0y0, beta = brbeta,
+                      tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401)
+brsimN53$downtime; brsimN53$tend; brsimN53$costrate
+weighted.mean(brsimN53$costrate, brsimN53$tend)
+brsimN53fig1 <- ggplot(brsimN53$res, aes(x = tnow, y = taustar)) + 
+  geom_line(aes(colour = cycle, group = cycle)) + geom_point(aes(colour = cycle, group = cycle)) +
+  xlab(expression(t[now])) + ylab(expression(paste(tau["*"]^(t[now]), (t[now])))) +
[…]

### 2016-11-21 cbm-sys.R
simultae 20 5-cycles

@@ -378,12 +378,27 @@ pdf("brsimN53fig1.pdf", width = 5, height = 3)
 brsimN53fig1
 dev.off()
 
-
-
-
 # -------------------------------------------------------------------------
 
+# simulate 20 5-cycle machines with priors as given
+set.seed(2211)
+brsim5cycle20data <- list()
+for (i in 1:20){
+  brsim5cycle20data[[i]] <- brWeibullData(5, brbeta, brmttf)
+}
+brsim5cycle20 <- list()
+for (i in 1:20){
+  brsim5cycle20[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = brsim5cycle20data[[i]], n0y0 = brn0y0,
+                                  beta = brbeta, tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401)
+}
 
+brsim5cycle20summary <- data.frame(id = 1:20,
+                                   downtime = sapply(brsim5cycle20, function(res) sum(res$downtime)),
+                                   meantend = sapply(brsim5cycle20, function(res) mean(res$tend)),
+                                   meancostrate = sapply(brsim5cycle20, function(res) weighted.mean(res$costrate, res$tend)))
 
+brsim5cycle20fig1 <- ggplot(melt(brsim5cycle20summary, "id"), aes(x = id, y = value)) + 
+  geom_line(aes(colour = variable, group = variable)) + geom_point(aes(colour = variable, group = variable))
+brsim5cycle20fig1
 
 #

### 2016-11-21 cbm-rbd-paper.tex
other prior parameters

@@
 %depends on $\tnow$, and also on the history of the system.
-Figure~\ref{fig:ghistfig2} illustrates this procedure for a number of current times $\tnow$.
+Figure~\ref{fig:ghist1fig2} illustrates this procedure for a number of current times $\tnow$.
 
@@
 since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
-These relations are depicted in Figure~\ref{fig:tauhistfig2}. %for a numerical example,
+These relations are depicted in Figure~\ref{fig:tauhist1fig2}. %for a numerical example,
 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{ghistfig2}
+\includegraphics[width=\textwidth]{ghist1fig2}
 \caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
@@
 and costs $c_u = 1$, $c_p = 0.2$.}
-\label{fig:ghistfig2}
+\label{fig:ghist1fig2}
 \end{figure}
@@
 ***example figures are with very weak prior info
-(see Table~\ref{tab:priorparams}: $\nkz = 1$ or $2$),
+(see Table~\ref{tab:priorparams}: $\nkz = 1$ for all $k$),
 things could look different for stronger expert information!
@@
   \midrule
-M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
-H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
-C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
-P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
+% test prior
+%M & $2.5$ & $5$\rule{1.5ex}{0ex} & $75.4$ & $2$\rule{1ex}{0ex} \\
+%H & $1.2$ & $2$\rule{1.5ex}{0ex} & $ 2.5$ & $1$\rule{1ex}{0ex} \\
+%C & $2  $ & $8$\rule{1.5ex}{0ex} & $81.5$ & $1$\rule{1ex}{0ex} \\
+%P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 6.1$ & $1$\rule{1ex}{0ex} \\
+% prior 1
+M & $2.5$ & $ 5$\rule{1.5ex}{0ex} & $244.1$ & $1$\rule{1ex}{0ex} \\
+H & $1  $ & $10$\rule{1.5ex}{0ex} & $ 10.0$ & $1$\rule{1ex}{0ex} \\
+C & $2  $ & $ 8$\rule{1.5ex}{0ex} & $ 11.5$ & $1$\rule{1ex}{0ex} \\
+P & $1.5$ & $ 5$\rule{1.5ex}{0ex} & $ 13.0$ & $1$\rule{1ex}{0ex} \\
   \bottomrule
@@
 \caption{Prior parameters for the four component types as used in subsequent numerical examples.
-The corresponding expected failure behaviour is visualized in Figure~\ref{fig:comppriorfig1}.}
+The corresponding expected failure behaviour is visualized in Figure~\ref{fig:compprior1fig1}.}
 \label{tab:priorparams}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{comppriorfig1}
+\includegraphics[width=0.8\textwidth]{compprior1fig1}
 \caption{Prior predictive reliability functions corresponding to the values from Table~\ref{tab:priorparams},
@@
 showing the expected failure behaviour according to this choice of parameters.}
-\label{fig:comppriorfig1}
+\label{fig:compprior1fig1}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{tauhistfig2}
+\includegraphics[width=\textwidth]{tauhist1fig2}
 \caption{$\tausnow$, $\tstarnow = \tnow + \tausnow$, $\cstarnow = \gnow(\tausnow)$,
@@
 and $c_u = 1$, $c_p = 0.2$.
-$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
+%$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
+$\tausnow$ (top left panel) first decreases, then starts to increase during failure-free periods,
 dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
-If $\tprep = 0.5$, the drop of $\tausnow$ from $0.72$ to $0.38$ at $\tnow = 8$ would trigger a maintenance action
-at (absolute) time $8.5$.
-Since $\tausnow$ does not change dramatically most of the time, $t^*$,
+If $\tprep = 1$, the drop of $\tausnow$ from $1.43$ to $0.91$ at $\tnow = 4$ would trigger a maintenance action
+at (absolute) time $5$.
+Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
 the cost-optimal moment of maintenance on the absolute timescale (top right panel),
@@
 %and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
-At time $8$, the overall expected cost rate for repair scheduled at time $8.38$ is $0.044$,
-up from $0.036$ for repair scheduled at time $8.62$, as cost-optimal at time $7.9$.}
-\label{fig:tauhistfig2}
+At time $4$, the overall expected cost rate for repair scheduled at time $4.91$ is $0.064$,
+up from $0.055$ for repair scheduled at time $5.33$, as cost-optimal at time $3.9$.}
+\label{fig:tauhist1fig2}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{tauhistfig3}
+\includegraphics[width=\textwidth]{tauhist1fig3}
 \caption{Illustration of the gains due to the parameter update
@@
 $\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
-same with $t^*$ (top right panel).
+same with $\tstarnow$ (top right panel).
 The adaptive algorithm recongnizes the higher reliability of system components,
 leading to lower current (lower left panel) and total (lower right panels) unit cost rates.}
-\label{fig:tauhistfig3}
+\label{fig:tauhist1fig3}
 \end{figure}
+
+%****************************
 
@@
 
-***larger simulation study?
+%*******************************
+
+larger simulation study?
 

### 2016-11-21 cbm-sys-other.R

@@ -1,0 +1,173 @@
+# --------------------------------------------------------------------------- #
+# CBM systems paper - code for example figs - other prior
+# --------------------------------------------------------------------------- #
+
+source("weibull-sys-functions.R")
+source("cbm-sim.R")
+source("plotdefs.R")
+
+# full system for prior
+br <- graph.formula(s -- M -- C1:C2:C3:C4, P1:P2:P3:P4 -- t,
+                    C1 -- P1, C2 -- P2, C3 -- P3, C4 -- P4, s -- H -- P3:P4)
+brctypes <- list("C"=c("C1", "C2", "C3", "C4"), "H"=c("H"), "M"=c("M"), "P"=c("P1", "P2", "P3", "P4"))
+br <- setCompTypes(br, brctypes)
+brsysign <- computeSystemSurvivalSignature(br)
+
+# order is C H M P
+br1beta <- c(2, 1, 2.5, 1.5)
+br1mttf <- c(3, 10, 8, 5)
+br1n0 <- c(1, 1, 1, 1) # weak prior
+br1n0y0 <- list(C=c(br1n0[1], failuretolambda(br1mttf[1], br1beta[1])),
+                H=c(br1n0[2], failuretolambda(br1mttf[2], br1beta[2])),
+                M=c(br1n0[3], failuretolambda(br1mttf[3], br1beta[3])),
+                P=c(br1n0[4], failuretolambda(br1mttf[4], br1beta[4])))
+brfts0 <- list(C=NULL, H=NULL, M=NULL, P=NULL)
+
+# component prior predictive reliability functions to visualize prior assumptions
+comphor <- 10; complen <- 201
+onecomp <- graph.formula(s -- 1 -- t)
+Ccomp <- setCompTypes(onecomp, list(C = "1"))
+Hcomp <- setCompTypes(onecomp, list(H = "1"))
+Mcomp <- setCompTypes(onecomp, list(M = "1"))
+Pcomp <- setCompTypes(onecomp, list(P = "1"))
+Crel1 <- sysrelnowhor(computeSystemSurvivalSignature(Ccomp), br1n0y0[1], br1beta[1], brfts0[1],
+                      tnow = 0, hor = comphor, seqlen = complen)
+Hrel1 <- sysrelnowhor(computeSystemSurvivalSignature(Hcomp), br1n0y0[2], br1beta[2], brfts0[2],
+                      tnow = 0, hor = comphor, seqlen = complen)
[…]

### 2016-11-21 cbm-sim.R
more in other prior

@@ -113,16 +113,18 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
   nnyn <- nnynlist(n0y0, ftslist, censlist, beta) # updated parameters at end of cycle
   # time the whole cycle took
   tend <- repschedfor + trepa
+  # time the system functioned
+  tfunc <- max(res$tnow[!(res$failed)])
   # downtime and unit cost rate
   if (failed){
     downtime <- repschedfor - min(res$tnow[res$failed]) # only in tnowstep resolution!
-    costrate <- cu / tend
+    costrate <- cu / tend # *** or / tfunc? or penalty cost for downtime?
   } else {
     downtime <- 0
-    costrate <- cp / tend
+    costrate <- cp / tend # *** or / tfunc? or penalty cost for downtime?
   }
   # return res and all
-  list(res = res, nnyn = nnyn, tend = tend, downtime = downtime, costrate = costrate)
+  list(res = res, nnyn = nnyn, tend = tend, tfunc = tfunc, downtime = downtime, costrate = costrate)
 }  
 
 
@@ -167,9 +169,20 @@ simNcycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, tr
   }
   res2$cycle <- as.factor(res2$cycle)
   tendvec <- sapply(res, function(resi) resi$tend)
+  tfuncvec <- sapply(res, function(resi) resi$tfunc)
   downtimevec <- sapply(res, function(resi) resi$downtime)
   costratevec <- sapply(res, function(resi) resi$costrate)
-  return(list(res = res2, nnyn = nnynlist, tend = tendvec, downtime = downtimevec, costrate = costratevec))
+  return(list(res = res2, nnyn = nnynlist, tend = tendvec, tfunc = tfuncvec, downtime = downtimevec, costrate = costratevec))
+}
+
+# function to calculate tend, tfunc, downtime, costrate for age-based policy from simNcycle object
+simNcycleAgebased <- function(simNcycleobj, tprep = 0.5, trepa = 0, cu = 1, cp = 0.2){
+  
+}
+
+# function to calculate tend, tfunc, downtime, costrate for corrective policy from simNcycle object
+simNcycleCorrective <- function(simNcycleobj, tprep = 0.5, trepa = 0, cu = 1, cp = 0.2){
+  
 }
 
 # function to simulate Weibull failure times according to prior parameter choices (note different parametrization!)

### 2016-11-21 cbm-sys-other.R

@@ -152,6 +152,18 @@ br1sim5cycle20data <- list()
 for (i in 1:20){
   br1sim5cycle20data[[i]] <- brWeibullData(5, br1beta, br1mttf)
 }
+
+br1simN51 <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data[[1]], n0y0 = br1n0y0, beta = br1beta,
+                      tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401)
+br1simN51$downtime; br1simN51$tend; br1simN51$tfunc; br1simN51$costrate
+br1simN51fig1 <- ggplot(br1simN51$res, aes(x = tnow, y = taustar)) + 
+  geom_line(aes(colour = cycle, group = cycle)) + geom_point(aes(colour = cycle, group = cycle)) +
+  xlab(expression(t[now])) + ylab(expression(paste(tau["*"]^(t[now]), (t[now])))) +
+  guides(colour = guide_legend(title="Cycle")) + scale_y_continuous(breaks=seq(0, 2, by=0.5), minor_breaks=seq(0, 2, by=0.25))
+pdf("br1simN51fig1.pdf", width = 5, height = 3)
+br1simN51fig1
+dev.off()
+
 br1sim5cycle20 <- list()
 for (i in 1:20){
   br1sim5cycle20[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data[[i]], n0y0 = br1n0y0,

### 2016-11-22 cbm-sim-prep.R
simplfied simulation

@@ -13,14 +13,15 @@
 # beta     vector of K fixed weibull shape parameters
 # tnowstep time interval after which current system reliability is re-evaluated
 # hor      how many time units from tnow into the future to calculate sysrelnow
-# thresh   threshold time below which to do preventive maintenance
+# tprep    preparation time to do preventive maintenance
+# trepa    time needed to repair the system
 # seqlen   at how many points to evaluate sysrelnow
 # cu       cost of unplanned (corrective) repair action
 # cp       cost of planned (preventive) repair action, cp < cu
 # onecycle whether to use the one-cycle criterion or the renewal-based one
 # timeround to how many digits to round the time points
-sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, thresh, seqlen = 101,
-                      prior = FALSE, cu = 1, cp = 0.2, onecycle = TRUE, timeround = 5){
+sim1cycleprep <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, tprep, trepa = 0,
+                          seqlen = 101, prior = FALSE, cu = 1, cp = 0.2, onecycle = TRUE, timeround = 5){
   K <- length(ctypes)
   ftschron <- sort(unlist(compfts)) # when something fails
   # initializing: initial arguments for gnowhor
@@ -32,40 +33,50 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, thresh, s
   failedcompsnow <- numeric(0)
   gotonext <- TRUE     # indicator that loop should go on
   failed <- FALSE      # indicator whether the system has failed
+  repschedfor <- Inf   # for which time is repair scheduled?
   res <- data.frame() # initialize results data frame
   while(gotonext){
-    cat("tnow =", tnow, ": ") #"failedcompsnow =", failedcompsnow, "\n")
-    if (all(signnow$Probability == 0)){ # system has failed now, repair with cost cu
-      failed <- TRUE
-      cost <- cu
+    cat("tnow =", tnow, ":") #"failedcompsnow =", failedcompsnow, "\n")
+    if (!failed){ # if not failed already in previous loop, check...
+      if (all(signnow$Probability == 0)){ # system has failed now, schedule repair for tnow + tprep if not scheduled already
+        failed <- TRUE
+        taustarnow <- NA
[…]

### 2016-11-22 cbm-sys-other.R

@@ -152,26 +152,27 @@ br1sim5cycle20data <- list()
 for (i in 1:20){
   br1sim5cycle20data[[i]] <- brWeibullData(5, br1beta, br1mttf)
 }
-
+# just one 5-cycle for the start and to illustrate
 br1simN51 <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data[[1]], n0y0 = br1n0y0, beta = br1beta,
-                      tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401)
-br1simN51$downtime; br1simN51$tend; br1simN51$tfunc; br1simN51$costrate
+                       tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401)
+br1simN51$tend; br1simN51$tfunc; br1simN51$costrate
 br1simN51fig1 <- ggplot(br1simN51$res, aes(x = tnow, y = taustar)) + 
   geom_line(aes(colour = cycle, group = cycle)) + geom_point(aes(colour = cycle, group = cycle)) +
   xlab(expression(t[now])) + ylab(expression(paste(tau["*"]^(t[now]), (t[now])))) +
   guides(colour = guide_legend(title="Cycle")) + scale_y_continuous(breaks=seq(0, 2, by=0.5), minor_breaks=seq(0, 2, by=0.25))
-pdf("br1simN51fig1.pdf", width = 5, height = 3)
+pdf("br1simN51fig1.pdf", width = 6, height = 4)
 br1simN51fig1
 dev.off()
 
 br1sim5cycle20 <- list()
 for (i in 1:20){
+  cat("Repetition", i, "\n")
   br1sim5cycle20[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data[[i]], n0y0 = br1n0y0,
-                                   beta = br1beta, tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401)
+                                   beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401)
 }
 
-br1sim5cycle20summary <- data.frame(id = 1:20,
-                                    downtime = sapply(br1sim5cycle20, function(res) sum(res$downtime)),
+br1sim5cycle20summary <- data.frame(id = 1:30,
+                                    meantfunc = sapply(br1sim5cycle20, function(res) mean(res$tfunc)),
[…]

### 2016-11-22 cbm-sys.R

@@ -312,22 +312,22 @@ dev.off()
 brcompftssim <- list(C1 = 10, C2 = 6, C3 = 7, C4 = 10, H = 8,  M = 12, P1 = 10, P2 = 3, P3 = 4, P4 = 10)
 
 brsim1 <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim, n0y0 = brn0y0, beta = brbeta,
-                    tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = FALSE)
+                    tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = FALSE)
 brsim1pr <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim, n0y0 = brn0y0, beta = brbeta,
-                      tnowstep = 0.1, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = TRUE)
+                      tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = TRUE)
 
 # quick sexample where system fails at time 3.7
 brcompftssim0 <- list(C1 = 10, C2 = 6, C3 = 7, C4 = 10, H = 3.6,  M = 3.7, P1 = 10, P2 = 3, P3 = 4, P4 = 10)
 brsim0 <- sim1cycle(sys = br, ctypes = brctypes, compfts = brcompftssim0, n0y0 = brn0y0, beta = brbeta,
-                    tnowstep = 0.25, hor = 4, tprep = 1, trepa = 0, seqlen = 401, prior = FALSE)
+                    tnowstep = 0.25, hor = 4, thresh = 1, seqlen = 401, prior = FALSE)
 
 # simulate several operational cycles
 brcompftssim2 <- list(C1 = c(10, 10), C2 = c(6, 6), C3 = c(7, 7), C4 = c(10, 10), H = c(8, 8),
                       M = c(12, 12), P1 = c(10, 10), P2 = c(3, 3), P3 = c(4, 4), P4 = c(10, 10))
 brsim2pr <- simNcycle(sys = br, ctypes = brctypes, compfts = brcompftssim2, n0y0 = brn0y0, beta = brbeta,
-                      tnowstep = 0.5, hor = 4, tprep = 0.5, trepa = 0, seqlen = 401, prior = TRUE)
[…]

### 2016-11-22 sim-study.R
split other prior into different files

@@ -1,0 +1,44 @@
+# --------------------------------------------------------------------------- #
+# CBM systems paper - code for example figs - simulation study
+# --------------------------------------------------------------------------- #
+
+source("cbm-sys-other.R")
+
+# sim 1: data fits to priors
+# -------------------
+
+# simulate 20 5-cycle machines with priors as given
+set.seed(2211)
+br1sim5cycle20data1 <- list()
+for (i in 1:20){
+  br1sim5cycle20data1[[i]] <- brWeibullData(5, br1beta, br1mttf)
+}
+# just one 5-cycle for the start and to illustrate
+br1simN51 <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[1]], n0y0 = br1n0y0, beta = br1beta,
+                       tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401)
+br1simN51$tend; br1simN51$tfunc; br1simN51$costrate
+br1simN51fig1 <- ggplot(br1simN51$res, aes(x = tnow, y = taustar)) + 
+  geom_line(aes(colour = cycle, group = cycle)) + geom_point(aes(colour = cycle, group = cycle)) +
+  xlab(expression(t[now])) + ylab(expression(paste(tau["*"]^(t[now]), (t[now])))) +
+  guides(colour = guide_legend(title="Cycle")) + scale_y_continuous(breaks=seq(0, 2, by=0.5), minor_breaks=seq(0, 2, by=0.25))
+pdf("br1simN51fig1.pdf", width = 6, height = 4)
+br1simN51fig1
+dev.off()
+
+br1sim1 <- list()
+for (i in 1:20){
+  cat("Repetition", i, "\n")
+  br1sim1[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[i]], n0y0 = br1n0y0,
+                            beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401)
+}
+
+br1sim1summary <- data.frame(id = 1:30,
+                             meantfunc = sapply(br1sim5cycle20, function(res) mean(res$tfunc)),
+                             meantend = sapply(br1sim5cycle20, function(res) mean(res$tend)),
+                             meancostrate = sapply(br1sim5cycle20, function(res) weighted.mean(res$costrate, res$tend)))
+
[…]

### 2016-11-22 sim-study.R
simulation study set-up

@@ -5,7 +5,7 @@
 source("cbm-sys-other.R")
 
 # sim 1: data fits to priors
-# -------------------
+# --------------------------
 
 # simulate 20 5-cycle machines with priors as given
 set.seed(2211)
@@ -25,20 +25,90 @@ pdf("br1simN51fig1.pdf", width = 6, height = 4)
 br1simN51fig1
 dev.off()
 
-br1sim1 <- list()
+br1sim1 <- list()     # our model
+br1sim1pr <- list()   # do not update params during cycle, but at end of cycle 
+br1sim1prpr <- list() # never update params
+
+simsummary <- function(simlist){
+  data.frame(id = 1:length(simlist),
+             nfails = sapply(simlist, function(res) sum(res$tfunc != res$tend)),
+             meantend = sapply(simlist, function(res) mean(res$tend)),
+             meancostrate = sapply(simlist, function(res) weighted.mean(res$costrate, res$tend)))
+}
+
 for (i in 1:20){
   cat("Repetition", i, "\n")
   br1sim1[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[i]], n0y0 = br1n0y0,
                             beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401)
 }
-
-br1sim1summary <- data.frame(id = 1:30,
-                             meantfunc = sapply(br1sim5cycle20, function(res) mean(res$tfunc)),
-                             meantend = sapply(br1sim5cycle20, function(res) mean(res$tend)),
-                             meancostrate = sapply(br1sim5cycle20, function(res) weighted.mean(res$costrate, res$tend)))
-
+br1sim1summary <- simsummary(br1sim1)
 br1sim1fig1 <- ggplot(melt(br1sim1summary, "id"), aes(x = id, y = value)) + 
   geom_line(aes(colour = variable, group = variable)) + geom_point(aes(colour = variable, group = variable))
 br1sim1fig1
 
+for (i in 1:20){
+  cat("Repetition", i, "\n")
+  br1sim1pr[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[i]], n0y0 = br1n0y0,
+                              beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = TRUE)
+}
[…]

### 2016-11-22 exempl-fail-hist.R
work on sections 5 and 6

@@ -20,15 +20,15 @@ names(br1ghist1a)[c(3,4)] <- c("Reliability", "Unit cost rate")
 br1ghist1a <- melt(br1ghist1a, c("tnow", "t"))
 br1ghist1a <- subset(br1ghist1a, !is.na(value))
 ghist1fig2r <- ggplot(subset(br1ghist1a, variable == "Reliability"), aes(x = t, y = value)) +
-  geom_line(aes(colour = tnow)) + coord_cartesian(xlim = c(0, 18), ylim = c(0, 1)) +
-  xlab(expression(t)) + ylab(expression(paste(R[sys]^(t[now]), (t)))) + guides(colour = 'none') + 
+  geom_line(aes(linetype = tnow)) + coord_cartesian(xlim = c(0, 18), ylim = c(0, 1)) +
+  xlab(expression(t)) + ylab(expression(paste(R[sys]^(t[now]), (t)))) + guides(linetype = 'none') + 
   scale_x_continuous(breaks = seq(0, 18, by = 2), minor_breaks = 0:18) +
   scale_y_continuous(breaks = seq(0, 1, by = 0.2), minor_breaks = seq(0, 1, by = 0.1)) +
   theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
 ghist1fig2g <- ggplot(subset(br1ghist1a, variable == "Unit cost rate"), aes(x = t, y = value)) +
-  geom_line(aes(colour = tnow)) + coord_cartesian(xlim = c(0, 18), ylim = c(0, 2.2)) +
+  geom_line(aes(linetype = tnow)) + coord_cartesian(xlim = c(0, 18), ylim = c(0, 2.2)) +
   xlab(expression(t)) + ylab(expression(paste(g[sys]^(t[now]), (t)))) +
-  guides(colour=guide_legend(title=expression(t[now]))) +
+  guides(linetype = guide_legend(title=expression(t[now]))) +
   theme(legend.position = 'bottom', legend.direction = 'horizontal') +
   scale_x_continuous(breaks = seq(0, 18, by = 2), minor_breaks = 0:18) +
   scale_y_continuous(breaks = seq(0, 3, by = 0.5), minor_breaks = seq(0, 3, by = 0.25))
@@ -39,10 +39,14 @@ dev.off()
[…]

### 2016-11-22 cbm-rbd-paper.tex
minor stuff

@@
 \newcommand{\tprep}{\tau_{\text{prep}}}
+\newcommand{\tthresh}{\tau_{\text{thresh}}}
 \newcommand{\tstarnow}{t_*^{(\tnow)}}
-\newcommand{\cstarnow}{c_*^{(\tnow)}}
-\newcommand{\ctotalnow}{c_\text{total}^{(\tnow)}}
+\newcommand{\gstarnow}{g_*^{(\tnow)}}
+\newcommand{\gtotalnow}{g_\text{total}^{(\tnow)}}
 
@@
 the vehicle brakes when at least one brake pad assembly is actuated.
+***This example was originally introduced in Ebeling (???).***
 Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
@@
 we determine, for each present time $\tnow$,
-the adaptive and dynamic timespan $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
+the adaptive and dynamic time span $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
 Close to system startup, $\tausnow$ will be large;
@@
 $\tausnow$ will typically decrease.
-Let $\tprep$ be the timespan needed to prepare maintenance work.
-As soon as $\tausnow$ decreases below $\tprep$,
-a preventive maintenance action is initiated.
+%Let $\tprep$ be the time span needed to prepare maintenance work.
+%Let $\tthresh$ be a threshold time span chosen for practical reasons.
+%used to decide when maintenance is initiated, i.e.,
+A preventive maintenance action is initiated
+as soon as $\tausnow$ decreases below $\tthresh$,
+a time span chosen to reflect operational practicalities.***
 This operational procedure is described in more detail in Section~\ref{sec:operationalprocedure}.
@@
 common cause failures currently not in the model, but will seriously influence residual life distribution,
-see comments in Outlook (Section~\ref{sec:outlook})
+see comments in Outlook (Section~\ref{sec:outlook})***
 
@@
 (An operational cycle begins with system start-up,
-and ends when either a failure of the system occors, or a preventive maintenance is carried out.)
+and ends when either preventive maintenance is carried out,
+or a failure of the system occurs, with subsequent corrective maintenance.)
 This criterion, as described in Section~\ref{sec:costrate} below in detail,
@@
 and shows how $\tausnow$ is determined in this situation.
-Numerical examples for different failure histories are given in Section~\ref{sec:examples}.
+Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
+and a small simulation study is discussed in Section~\ref{sec:sim}.
 
@@
 
-A preventive maintenance action is triggered as soon as $\tausnow$ falls below $\tprep$,
-the time needed to prepare maintenance work.
-The system continues to run until maintenance work begins,
-and the cycle ends when maintenance work is completed.
-When the system fails, instead a corrective maintenance action is triggered,
-and the system is down also during the wait until maintenance work begins.
-This additional downtime must be reflected in the cost parameter $c_u$ (see Section~\ref{sec:costrate} below).
-Again, the cycle ends when maintenance work is completed.
+A preventive maintenance action is triggered as soon as $\tausnow$ falls below $\tthresh$,
+indicating that the optimal moment of maintenance is so close to present time $\tnow$
+that a preventive maintenance action should be carried out, incurring cost $c_p$.
+When the system fails, instead a corrective maintenance action is triggered, incurring cost $c_u$.
+With both preventive and corrective maintenance the current cycle ends,
+and a new cycle starts with a system with all components (as good as) new.
+%choice of a failure threshold in usual CBM policies.
+%This failure threshold gives the level of the degradation signal where 
+%This additional downtime must be reflected in the cost parameter $c_u$ (see Section~\ref{sec:costrate} below).
+%Again, the cycle ends when maintenance work is completed.
 
@@
 %We assume that both planned and unplanned maintenance action takes negligible time,
-We assume that both a planned and unplanned maintenance action results in an (as good as) new system state by replacing all components,
+
+We assume that both preventive and corrective maintenance results in an (as good as) new system state by replacing all components,
 such that the system begins a new cycle always under the same conditions.
@@
 exploring such selective replacement schemes is out of scope for this paper,
-since optimizing over replacement schemes is, in our view, a higly interesting topic on its own,
-and we will comment on this in the Outlook (Section~\ref{sec:outlook}).
-
-As we use a one-cycle criterion, the time both planned and unplanned maintenance actions require
+since optimizing over replacement schemes is, in our view, a higly interesting topic on its own
+that would merit a separate study.
+We will comment on this topic in the Outlook (Section~\ref{sec:outlook}).
+
+As we use a one-cycle criterion, the time both preventive and corrective maintenance actions require
 does not matter directly for the determination of $\tausnow$.
-Downtimes are instead accounted for indirectly via the costs parameters in the trade-off leading to $\tausnow$,
-as described next.
+Longer downtime and other negative effects of corrective maintenance
+are instead accounted for through the costs parameters used in the trade-off leading to $\tausnow$,
+as described in more detail below.
 
@@
 
-Let $c_p$ be the cost of planned (preventive) maintenance, and $c_u$ the cost of unplanned (breakdown) maintenance, where $c_p < c_u$.
-Usually, set-up costs, work costs and downtime costs are much higher for unplanned / breakdown maintenance,
+Let $c_p$ be the cost of preventive maintenance, and $c_u$ the cost of corrective (unplanned, breakdown) maintenance, where $c_p < c_u$.
+Usually, set-up costs, work costs and downtime costs are much higher for corrective maintenance,
 such that often, $c_p \ll c_u$.
-CBM is known to be most effective when the difference between $c_p$ and $c_u$ is large
-(***cite de Jonge and Teunter working paper on relative benefit).
+CBM is known to be most effective when the ratio $c_p / c_u$ is small
+(***cite de Jonge and Teunter working paper on relative benefit of CBM).
 %
@@
 and $\fsysnow(t)$ be the corresponding density.
-Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate is 
+Conditional on the realization $\tsysnow > \tnow$ of $\Tsysnow$, the unit cost rate is 
 \begin{align}
@@
 c_p / \tau               & \text{if } \tsysnow \ge \tnow + \tau \\
-c_u / \tsysnow & \text{if } \tsysnow  <  \tnow + \tau \,.
+c_u / (\tsysnow - \tnow) & \text{if } \tsysnow  <  \tnow + \tau \,.
 \end{cases}
@@
 \end{align}
-Note that here, $\tau$ is a timespan starting from $\tnow$,
+Note that here, $\tau$ is a time span starting from $\tnow$,
 and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
@@
 \begin{align}
-\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] = \frac{c_p}{\tau} \Rsysnow(\tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
+\gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] \nonumber\\ 
+            &= \frac{c_p}{\tau} \Rsysnow(\tnow + \tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
 \label{eq:gtnowtau}
@@
 and $\tausnow = \arg\min \gnow(\tau)$.
-$\tausnow$, the optimal moment of maintenance as of $\tnow$,
+Thus $\tausnow$, the optimal moment of maintenance as of $\tnow$,
 incorporates thus all that is known at current time $\tnow$.
@@
 Figure~\ref{fig:ghist1fig2} illustrates this procedure for a number of current times $\tnow$.
-
-Note that for the integral in \eqref{eq:gtnowtau} to exist, $\E[1/\Tsysnow \mid \Tsysnow > \tnow]$ must exist,
-which is a condition for $\fsysnow(\tnow + t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
-This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
-For our approach, however, this condition is not relevant,
-as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively
-(see Section~\ref{sec:optim} below).
-
-Minimizing $\gnow(\tau)$ leads to $\tausnow$,
-the optimal moment of maintenance on a prospective time scale.
-The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
-thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
-i.e., for what happens beyond current time $\tnow$.
-Also of interest is the total cost rate at $\tnow$, denoted by $\ctotalnow$.
-This gives the expected unit cost rate calculated over the full time since system start-up,
-under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
-$\ctotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
-However, when many (or few but critical) components fail, $\ctotalnow$ may increase,
-since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
-These relations are depicted in Figure~\ref{fig:tauhist1fig2}. %for a numerical example,
-
-We will describe next how we numerically evaluate \eqref{eq:gtnowtau} and find $\tausnow$
-for our choice of component model.
-%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
-%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.
-
-\subsection{Numerical optimization of the expected unit cycle cost rate}
-\label{sec:optim}
-
-Since $\Rsysnow(t)$ is not tractable analytically,
-we calculate $\Rsysnow(t)$ for values of $t$ on a dense grid spanning from $\tnow$ to some horizon time $\tnow + t_h$.
-(The choice of $h_t$ is discussed in more detail below.)
-We calculate $\gnow(\tau)$ on the same grid,
-and determine $\tausnow$ by minimizing over this grid.
-Here, we approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
-where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$ values on the grid.
-%$\gnow(\tau)$ is likewise evaluated on a dense grid,
-%and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
-
-The horizon span $t_h$ can be determined by practical considerations,
-but generally should reach far enough into the tail of $\Rsysnow(t)$
-such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
-Note that \eqref{eq:gtnowtau} indicates that values for $\Rsysnow(t)$ and $\fsysnow(t)$ 
-only for $t \leq \tau$ are needed to calculate $\gnow(\tau)$.
-
-We use \textsf{R} \citep{R} for our calculations,
-using the package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
-to calculate survival signatures.
-As the parameter update step is closed-form,
-$\tausnow$
-
-***calculations in \textsf{R} can be vectorized and are thus fast.
-
-***if min $\gnow(\tau)$ at $\tnow + t_h$, corrective maintenance is optimal: policy switch!
-%***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy
-
-%At time $\tnow$, the corresponding $\tausnow$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
-%so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau_*^{\tnow}$.
 
@@
 
-\section{***numerical examples for complex system layout}
+Note that for the integral in \eqref{eq:gtnowtau} to exist,
+%$\E[1/\Tsysnow \mid \Tsysnow > \tnow]$ must exist,
+$\E[1/\Tsysnow]$ must exist,
+which is a condition for $\fsysnow(\tnow + t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
+This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
+For our approach, however, this condition is not relevant,
+as we use a discrete approximation of $\Rsysnow(t)$ and $\fsysnow(t)$, respectively
+(see Section~\ref{sec:optim} below).
+
+Minimizing $\gnow(\tau)$ leads to $\tausnow$,
+the optimal moment of maintenance on a prospective time scale.
+The minimal prospective unit cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
+thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
+i.e., for what happens beyond current time $\tnow$.
+%$\gstarnow$ increases over time since 
+Also of interest is the total cost rate at $\tnow$, denoted by $\gtotalnow$.
+This gives the expected unit cost rate calculated over the full time since system start-up,
+under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
+$\gtotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
+However, when many (or few but critical) components fail, $\gtotalnow$ may increase,
+since then, system failure becomes much more likely, leading to a higher $\gstarnow$.
+Figure~\ref{fig:tauhist1fig2} illustrates these relations in the scenario depicted in Figure~\ref{fig:ghist1fig2}.
+
+We will describe next how we numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
+for our choice of component model.
+%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
+%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{tauhist1fig2}
+\caption{$\tausnow$, $\tstarnow = \tnow + \tausnow$, $\gstarnow = \gnow(\tausnow)$,
+and the total unit cost rate $\gtotalnow$ as functions of $\tnow$
+for the system depicted in Figure~\ref{fig:brakesys-layout},
+assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
+and $c_u = 1$, $c_p = 0.2$.
+%$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
+$\tausnow$ (top left panel) first decreases, then starts to increase during failure-free periods,
+dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
+If $\tthresh = 1$, the drop of $\tausnow$ from $1.43$ to $0.91$ at $\tnow = 4$ would trigger a maintenance action
+at (absolute) time $5$.
+Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
+the cost-optimal moment of maintenance on the absolute timescale (top right panel),
+steadily increases, with small drops corresponding to drops in $\tausnow$,
+showing that as time progresses, accumulated information indicates that maintenance can be postponed.
+Note that $\gstarnow$ (lower left panel) is the momentary cost rate relating to the expected residual lifetime,
+differing from the overall cost rate $\gtotalnow$ (lower right panel).
+%For the maintenance action triggered at $\tnow = 8$,
+%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
+%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
+At $\tnow = 4$, the overall expected cost rate for repair scheduled at time $4.91$ is $0.064$,
+up from $0.055$ for repair scheduled at time $5.33$, as cost-optimal at time $\tnow = 3.9$.}
+\label{fig:tauhist1fig2}
+\end{figure}
+
+\subsection{Numerical optimization of the expected unit cycle cost rate}
+\label{sec:optim}
+
+For our choice of component model,
+the resulting $\Rsysnow(t)$ as of \eqref{eq:sysrel-tnow}
+is closed-form, but not tractable analytically.
+Therefore,
+we evaluate $\Rsysnow(t)$ on a dense grid of time points $t$
+covering the time span from $\tnow$ to some horizon time $\tnow + t_h$.
+(The choice of $h_t$ is discussed in more detail below.)
+We calculate $\gnow(\tau)$ on the same grid,
+and determine $\tausnow$ by minimizing over this grid.
+Here, we approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
+where evaluations of $\fsysnow(\tnow + t)$ are calculated via differences of $\Rsysnow(\tnow + t)$ evaluations.
+%$\gnow(\tau)$ is likewise evaluated on a dense grid,
+%and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
+
+The horizon time span $t_h$ can be determined by practical considerations,
+but generally should reach far enough into the tail of $\Rsysnow(t)$
+such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
+Note that according to \eqref{eq:gtnowtau},
+the calculation of $\gnow(\tau)$ requires
+evaluations of $\Rsysnow(t)$ and $\fsysnow(t)$ only for $t \leq \tau$.
+
+We have implememted our method in \textsf{R} \citep{R},
+using the package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
+to calculate survival signatures.
+As the parameter update step is closed-form,
+recalculation of $\tausnow$ is a matter of seconds,
+allowing for a near real-time update.
+
+%***calculations in \textsf{R} can be vectorized and are thus fast.
+%***if min $\gnow(\tau)$ at $\tnow + t_h$, corrective maintenance is optimal: policy switch!
+%***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy
+
+%At time $\tnow$, the corresponding $\tausnow$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
+%so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau_*^{\tnow}$.
+
+\section{Numerical examples for a complex system}
 \label{sec:examples}
 
-***use simplified brake system from ASCE-ASME paper,
-different example histories (when do components fail?)
-
-***In current graphs,
-prior component model parameters are taken as in Table~\ref{tab:priorparams},
-and $c_u = 1$, $c_p = 0.2$. *** plot prior predictive distributions?***
-
-***example figures are with very weak prior info
-(see Table~\ref{tab:priorparams}: $\nkz = 1$ for all $k$),
-things could look different for stronger expert information!
-
-***also example where remaining component type is (close to) exponential,
-such that corrective maintenance becomes optimal!
+As illustrative example for a system with complex layout,
+we use the simplified automotive brake system as introduced in Section~\ref{sec:sysrel},
+see Figure~\ref{fig:brakesys-layout}.
+In all subsequent examples of this section,
+prior component model parameters are taken as in Table~\ref{tab:priorparams}.
 
@@
 % prior 1
-M & $2.5$ & $ 5$\rule{1.5ex}{0ex} & $244.1$ & $1$\rule{1ex}{0ex} \\
+C & $2  $ & $ 3$\rule{1.5ex}{0ex} & $ 11.5$ & $1$\rule{1ex}{0ex} \\
 H & $1  $ & $10$\rule{1.5ex}{0ex} & $ 10.0$ & $1$\rule{1ex}{0ex} \\
-C & $2  $ & $ 8$\rule{1.5ex}{0ex} & $ 11.5$ & $1$\rule{1ex}{0ex} \\
+M & $2.5$ & $ 8$\rule{1.5ex}{0ex} & $244.1$ & $1$\rule{1ex}{0ex} \\
 P & $1.5$ & $ 5$\rule{1.5ex}{0ex} & $ 13.0$ & $1$\rule{1ex}{0ex} \\
@@
 \end{table}
+
+Note that the scale parameter for component type H is $1$,
+such that failure times for this component type are assumed to follow an Exponential distribution.
+In cases where only $H$ and one or both of $P_3$ and $P_4$ are functioning,
+the system reliability function will thus be close to exponential,
+making preventive maintenance unattractive.
+
+Note also that $\nkz = 1$ for all four component types,
+indicating very weak prior knowledge.
+Observed failure times thus have a strong influence on the updating of $\ykz$,
+such that component models are primarily data-driven.
+This offers the advantage of quick adaption
+for the case that an expert's assessment of the component MTTF turns out to be inadequate.
+%things could look different for stronger expert information!
+When $\nkz$ and $\ykz$ also include test data,
+then $\nkz$ will typically be larger,
+since the update of $n_k$ involves the number of observed failures
+(see Section~\ref{sec:weibull}).
+
+The expected component failure behaviour according to the parameter choices in Table~\ref{tab:priorparams}
+is visualized in Figure~\ref{fig:compprior1fig1},
+showing the prior predictive reliability function for a single component of each type.
+We see that, e.g., median prior expected failure times are
+$2.2$, $4.1$, $6.3$, and $3.1$ for type $C$, $H$, $M$, and $P$ components, respectively.
+While it is quite unlikely that any type $C$ component will survive past time $6$,
+we expect 25\% of type $H$ components to survive past time $10$.
 
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{tauhist1fig2}
-\caption{$\tausnow$, $\tstarnow = \tnow + \tausnow$, $\cstarnow = \gnow(\tausnow)$,
-and the total unit cost rate $\ctotalnow$ as functions of $\tnow$
-for the system depicted in Figure~\ref{fig:brakesys-layout},
-assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
-and $c_u = 1$, $c_p = 0.2$.
-%$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
-$\tausnow$ (top left panel) first decreases, then starts to increase during failure-free periods,
-dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
-If $\tprep = 1$, the drop of $\tausnow$ from $1.43$ to $0.91$ at $\tnow = 4$ would trigger a maintenance action
-at (absolute) time $5$.
-Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
-the cost-optimal moment of maintenance on the absolute timescale (top right panel),
-steadily increases, with small drops corresponding to drops in $\tausnow$,
-indicating that as time progresses, accumulated information indicates that maintenance can be postponed.
-Note that $\gnow(\tausnow)$ is the momentary cost rate relating to the expected residual lifetime (lower left panel),
-differing from the overall cost rate $\ctotalnow$ (lower right panel).
-%For the maintenance action triggered at $\tnow = 8$,
-%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
-%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
-At time $4$, the overall expected cost rate for repair scheduled at time $4.91$ is $0.064$,
-up from $0.055$ for repair scheduled at time $5.33$, as cost-optimal at time $3.9$.}
-\label{fig:tauhist1fig2}
-\end{figure}
+The cost parameters are chosen as $c_u = 1$, $c_p = 0.2$ in all examples,
+i.e., corrective maintenance is five times more costly than preventive maintenance.
+This makes it worthwile to aim for a preventive repair of the system,
+but corrective maintenance will not be avoided at all cost.
+Indeed, $c_u / c_p = 5$ means that risking corrective maintenance is worthwile
+if one can expect to utilize the system five times longer
+than under a predictive maintenance schedule.
+
+We illustrate our procedure*** under three different failure time histories.
+
+The first failure history was underlying the illustrations
+in Figures~\ref{fig:ghist1fig2} and \ref{fig:tauhist1fig2}.
+Here, we observe
+$P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$ and $H = 8$,
+and in following the system until $\tnow = 8$,
+all other failure times are right-censored.
+Failures observed for type $C$ are thus considerably later than expected,
+while for type $P$, the two observed failures are close to the assumed MTTF. 
+Both failure at time $8$ for $H$ and non-failure by time $8$ for $M$ are nothing unusual.
+In total, due to the late type $C$ failures, prior assumptions are somewhat pessimistic.
+This is reflected in Figure~\ref{fig:tauhist1fig2},
+where $\tausnow$ first decreases but then tends to increase
+during failure-free periods, adjusting prior expectations since none of the type $C$ components fail.
+
+***move text from caption to here?***
+
+The effect of the continuous parameter update is illustrated in Figure~\ref{fig:tauhist1fig3}.
+This compares the results for our approach (as seen already in Figure~\ref{fig:tauhist1fig2})
+with an approach that does not update the component parameters,
+while still accounting for the fact that components age, and that a failed component changes the system layout.
+***so dynamic but not adaptive?***
+Jumps in $\tausnow$
 
@@
 
+The second failure history contains the failure times
+
+different example histories (when do components fail?)
+
 %****************************
@@
 
-larger simulation study?
+\section{Small simulation study}
+\label{sec:sim}
+
+small simulation study
+
+i.e., the Weibull scale parameters chosen as $\ykz$ in Table~\ref{tab:priorparams}.
 
@@
 
-***$\tprep$ could vary over time, e.g., longer on weekends or outside office hours
+***$\tthresh$ could vary over time, e.g., longer on weekends or outside office hours
+
+***$\tprep$ instead of $\tthresh$: always too late when scheduling maintenance once $\tausnow < \tprep$.
+Problem common to all CBM policies? usually no preparation time assumed?
 

### 2016-11-23 cbm-rbd-paper.tex
procedure figure

@@
 
+\begin{figure}
+\centering
+\begin{tikzpicture}
+[node distance=10mm,
+ font=\footnotesize,
+ box/.style={draw, rectangle, thick, minimum height=6mm, minimum width=26mm, rounded corners=2mm},
+ pfeil/.style={-latex', very thick}]
+\node (startup) [box]                       {\parbox{20ex}{\centering system start-up\\ (all comp.\ new)}};
+\node (sysfail) [box, right=of startup]     {system failed?};
+\node (tauchck) [box, below=6mm of sysfail] {$\tausnow < \tthresh$?};
+\node (gotonxt) [box, below=6mm of tauchck] {\parbox{15ex}{\centering continue to\\ next $\tnow$}};
+\draw [thick, dashed, rounded corners=2mm] ($(gotonxt.south east) + (2mm,-1mm)$) rectangle ($(sysfail.north west) + (-5mm,1mm)$) node[above left=0mm and -14mm] {each $\tnow$};
+\node [above left=0mm and -8mm of startup] {$t=0$};
+\node (correct) [box, right=of sysfail, minimum width=18mm] {\parbox{14ex}{\centering corrective\\ maintenance\\ cost $c_u$}};
+\node (prevent) [box, right=of tauchck, minimum width=18mm] {\parbox{14ex}{\centering preventive\\ maintenance\\ cost $c_p$}};
+\node (update) [box, below right=10mm and -4mm of prevent, minimum width=10mm] {\parbox{12ex}{\centering update parameters}};
+\draw[pfeil] (startup) -- (sysfail);
+\draw[pfeil] (sysfail) -- (tauchck) node[midway, right] {no};
+\draw[pfeil] (tauchck) -- (gotonxt) node[midway, right] {no};
+\draw[very thick] (gotonxt.west) -- ++(-3mm,0mm) -- ($(sysfail.west) + (-3mm,0mm)$);
+\draw[pfeil] (sysfail) -- (correct) node[midway, above] {yes};
+\draw[pfeil] (tauchck) -- (prevent) node[midway, above] {yes};
+\draw[pfeil] (correct) -| (update);
+\draw[pfeil] (prevent) -| (update);
+\draw[pfeil] (update) -| (startup) node[midway, below right] {start new cycle};
+\end{tikzpicture}
+\caption{***operational procedure}
+\label{fig:procedure}
+\end{figure}
+
 \subsection{Operational Procedure}
@@
 
-The first failure history was underlying the illustrations
-in Figures~\ref{fig:ghist1fig2} and \ref{fig:tauhist1fig2}.
-Here, we observe
+In the first failure history, we observe
 $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$ and $H = 8$,
@@
 all other failure times are right-censored.
+This is failure history used for Figures~\ref{fig:ghist1fig2} and \ref{fig:tauhist1fig2}.
 Failures observed for type $C$ are thus considerably later than expected,

### 2016-11-23 cbm-rbd-paper.tex
procedure figure again

@@
 \node [above left=0mm and -8mm of startup] {$t=0$};
-\node (correct) [box, right=of sysfail, minimum width=18mm] {\parbox{14ex}{\centering corrective\\ maintenance\\ cost $c_u$}};
-\node (prevent) [box, right=of tauchck, minimum width=18mm] {\parbox{14ex}{\centering preventive\\ maintenance\\ cost $c_p$}};
+\node (correct) [box, right=of sysfail, minimum width=18mm] {\parbox{14ex}{\centering corrective\\ maintenance\\ (cost $c_u$)}};
+\node (prevent) [box, right=of tauchck, minimum width=18mm] {\parbox{14ex}{\centering preventive\\ maintenance\\ (cost $c_p$)}};
 \node (update) [box, below right=10mm and -4mm of prevent, minimum width=10mm] {\parbox{12ex}{\centering update parameters}};
@@
 \draw[pfeil] (tauchck) -- (gotonxt) node[midway, right] {no};
-\draw[very thick] (gotonxt.west) -- ++(-3mm,0mm) -- ($(sysfail.west) + (-3mm,0mm)$);
+\draw[very thick] (gotonxt.west) -| ($(sysfail.west) + (-3mm,0mm)$);
 \draw[pfeil] (sysfail) -- (correct) node[midway, above] {yes};
@@
 
-***illustrative figure?
+***illustrative figure~\ref{fig:procedure}
 

### 2016-11-23 sim-study.R
reorganize first sim

@@ -4,6 +4,17 @@
 
 source("cbm-sys-other.R")
 
+simsummary <- function(simlist){
+  data.frame(id = 1:length(simlist),
+             nfails = sapply(simlist, function(res) sum(res$tfunc != res$tend)),
+             meantend = sapply(simlist, function(res) mean(res$tend)),
+             meancostrate = sapply(simlist, function(res) weighted.mean(res$costrate, res$tend)))
+}
+
+simlabeller <- as_labeller(c(nfails = "Number of system failures",
+                             meantend = "Average cycle length",
+                             meancostrate = "Average unit cost rate"))
+
 # sim 1: data fits to priors
 # --------------------------
 
@@ -13,6 +24,7 @@ br1sim5cycle20data1 <- list()
 for (i in 1:20){
   br1sim5cycle20data1[[i]] <- brWeibullData(5, br1beta, br1mttf)
 }
+
 # just one 5-cycle for the start and to illustrate
 br1simN51 <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[1]], n0y0 = br1n0y0, beta = br1beta,
                        tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401)
@@ -29,49 +41,37 @@ br1sim1 <- list()     # our model
 br1sim1pr <- list()   # do not update params during cycle, but at end of cycle 
 br1sim1prpr <- list() # never update params
 
-simsummary <- function(simlist){
-  data.frame(id = 1:length(simlist),
-             nfails = sapply(simlist, function(res) sum(res$tfunc != res$tend)),
-             meantend = sapply(simlist, function(res) mean(res$tend)),
-             meancostrate = sapply(simlist, function(res) weighted.mean(res$costrate, res$tend)))
-}
-
 for (i in 1:20){
-  cat("Repetition", i, "\n")
+  cat("Repetition", i, ": full update\n")
   br1sim1[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[i]], n0y0 = br1n0y0,
                             beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401)
+  cat("Repetition", i, ": end of cycle update only\n")
[…]

### 2016-11-23 exempl-fail-hist.R
examples section mostly done

@@ -52,13 +52,18 @@ tauhist1fig2
 dev.off()
 br1taus1fine[40:41,]
 br1taus1finepr <- taustarhist(br, brctypes, brcompfts, br1n0y0, br1beta, seq(0,8,by=0.1), hor=4, seqlen=401, prior=T)
-br1taus1prpo <- rbind(data.frame(melt(br1taus1fine, "tnow"), variable2 = "update"),
-                      data.frame(melt(br1taus1finepr, "tnow"), variable2 = "no update"))
+names(br1taus1finepr)[2:5] <- c(taustar = expression(tau['*']^(t[now])),
+                                tstar = expression(t['*']^(t[now])),
+                                cstar = expression(g['*']^(t[now])),
+                                ctotal = expression(g[total]^(t[now])))
+br1taus1prpo <- rbind(data.frame(melt(br1taus1fine, "tnow"), variable2 = "Parameter update"),
+                      data.frame(melt(br1taus1finepr, "tnow"), variable2 = "No parameter update"))
 tauhist1fig3 <- ggplot(br1taus1prpo, aes(x = tnow, y = value)) + xlab(expression(t[now])) +
-  geom_line(aes(colour = variable2)) + ylab("") + guides(colour = guide_legend(title=NULL)) +
+  geom_line(aes(colour = variable2)) + guides(colour = guide_legend(title=NULL)) +
   geom_point(aes(colour = variable2), size = 0.15) +
-  facet_wrap(~ variable, nrow = 2, scales = "free_y")
-pdf("tauhist1fig3.pdf", width = 6, height = 4)
+  facet_wrap(~ variable, nrow = 2, scales = "free_y", labeller = label_parsed) +
+  theme(axis.title.y = element_blank()) + bottomlegend
+pdf("tauhist1fig3.pdf", width = 6, height = 4.5)
 tauhist1fig3
 dev.off()
 
@@ -68,33 +73,51 @@ dev.off()
 brcompfts2 <- list(C1 = NA, C2 = 1, C3 = 2, C4 = NA, H = 8,  M = NA, P1 = NA, P2 = 0.5, P3 = 1.5, P4 = NA)
 plotfts(brcompfts2, 2)
 br1taus2fine <- taustarhist(br, brctypes, brcompfts2, br1n0y0, br1beta, seq(0, 2, by=0.05), hor=4, seqlen=401)
+names(br1taus2fine)[2:5] <- c(taustar = expression(tau['*']^(t[now])),
+                              tstar = expression(t['*']^(t[now])),
[…]

### 2016-11-23 sim-study.R
simulation early failures

@@ -14,6 +14,12 @@ simsummary <- function(simlist){
 simlabeller <- as_labeller(c(nfails = "Number of system failures",
                              meantend = "Average cycle length",
                              meancostrate = "Average unit cost rate"))
+simlabeller2 <- as_labeller(c(nfails = "Number of system failures",
+                              meantend = "Average cycle length",
+                              meancostrate = "Average unit cost rate",
+                              "Full update" = "Full update",
+                              "Cycle end update" = "Cycle end update",
+                              "No update" = "No update"))
 
 # sim 1: data fits to priors
 # --------------------------
@@ -69,9 +75,9 @@ br1sim1fig3 <- ggplot(melt(br1sim1prprsummary, "id"), aes(x = id, y = value)) +
   geom_line(aes(colour = variable, group = variable)) + geom_point(aes(colour = variable, group = variable))
 br1sim1fig3
 
-br1sim1summaryall <- rbind(data.frame(sim = "full update", br1sim1summary),
-                           data.frame(sim = "cycle end update", br1sim1prsummary),
-                           data.frame(sim = "no update", br1sim1prprsummary))
+br1sim1summaryall <- rbind(data.frame(sim = "Full update", br1sim1summary),
+                           data.frame(sim = "Cycle end update", br1sim1prsummary),
+                           data.frame(sim = "No update", br1sim1prprsummary))
 
 br1sim1fig4 <- ggplot(melt(br1sim1summaryall, c("id", "sim")), aes(x = id, y = value)) +
   geom_line(aes(linetype = sim, group = sim)) + geom_point(aes(shape = sim, group = sim)) +
@@ -105,8 +111,43 @@ for (i in 1:20){
                                 beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = TRUE, cycleupdate = FALSE)
 }
 
+br1sim2summary <- simsummary(br1sim2)
+br1sim2prsummary <- simsummary(br1sim2pr)
+br1sim2prprsummary <- simsummary(br1sim2prpr)
 
-# sim 2: failures later than expected
+br1sim2fig1 <- ggplot(melt(br1sim2summary, "id"), aes(x = id, y = value)) + 
[…]

### 2016-11-23 cbm-rbd-paper.tex

@@
 the vehicle brakes when at least one brake pad assembly is actuated.
-***This example was originally introduced in Ebeling (???).***
 Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
+***This is a popular example to illustrate such kinds of systems,
+see, e.g., \cite[p.~***]{2010:ebeling}.***
 %This system is observed until time $\tnow$,
@@
 enumerating $P(C^k_t = l_k\mid\nkz,\ykz, \vectknow)$ for all $l_k \in \{0, 1, \cknow\}$, $k=1\ldots,K$,
-so \eqref{eq:postpred-priorparams} needs to be invoked 
+so \eqref{eq:postpred-priorparams} needs to be evaluated 
 only $\sum_{k=1}^K (\cknow + 1)$ times.
@@
 as soon as $\tausnow$ decreases below $\tthresh$,
-a time span chosen to reflect operational practicalities.***
-This operational procedure is described in more detail in Section~\ref{sec:operationalprocedure}.
-%and executed at time $\tnow + \tausnow$.
+a time span chosen to reflect operational practicalities.
+This operational procedure is described in more detail in Section~\ref{sec:operationalprocedure};
+a graphical overview is given in Figure~\ref{fig:procedure}.
 
@@
 \draw[pfeil] (prevent) -| (update);
-\draw[pfeil] (update) -| (startup) node[midway, below right] {start new cycle};
+\draw[pfeil, dotted] (update) -| (startup) node[midway, below right] {start new cycle};
 \end{tikzpicture}
-\caption{***operational procedure}
+\caption{Operational procedure under the proposed maintenance policy,
+showing a single operational cycle,
+including the loop back to system startup that starts a new cycle.}
 \label{fig:procedure}
@@
 
-\subsection{Operational Procedure}
+\subsection{Operational procedure}
 \label{sec:operationalprocedure}
-
-***illustrative figure~\ref{fig:procedure}
 
@@
 all components age, and also non-failure adds information to the component models.
-Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$.
+Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
+as is visible in the top left panel of Figure~\ref{fig:tauhist1fig2}.
 %An alternative would be to update $\tausnow$ only when a component fails,
-%but as a (near) real-time update of $\taausnow$ is possible and useful,
+%but as a (near) real-time update of $\tausnow$ is possible and useful,
 %as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
@@
 The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
-of the maintenance interval in an age based policy;
+of the maintenance interval in an age based policy by trading off the costs of preventive and corrective maintenance;
 however, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
 our policy is adaptive and dynamic like a CBM policy. 
-Like in an age-based policy, the derived $\gnow(\tau)$ can also be monotonely decreasing.
+As can happen for an age-based policy, the derived $\gnow(\tau)$ may also be monotonely decreasing.
 In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
@@
 indicating that the optimal moment of maintenance is so close to present time $\tnow$
-that a preventive maintenance action should be carried out, incurring cost $c_p$.
-When the system fails, instead a corrective maintenance action is triggered, incurring cost $c_u$.
-With both preventive and corrective maintenance the current cycle ends,
+that a preventive maintenance action should be carried out immediately, incurring cost $c_p$.
+When the system fails, instead a corrective maintenance action is carried out, incurring cost $c_u$.
+The current cycle ends when either preventive and corrective maintenance is carried out,
 and a new cycle starts with a system with all components (as good as) new.
@@
 %using failure and censoring times as of the end of the cycle.
-such that $\nkz$ and $\ykz$ for the following cycle account for the (censored) lifetimes observed during the previous cycle.
+such that $\nkz$ and $\ykz$ for the next cycle account for the (censored) lifetimes observed during the previous cycle.
 %We assume that both planned and unplanned maintenance action takes negligible time,
 
-We assume that both preventive and corrective maintenance results in an (as good as) new system state by replacing all components,
+The operational procedure is visualized in Figure~\ref{fig:procedure},
+displaying a single cycle,
+also including the loop back to system startup that starts a new cycle.
+
+We assume that both preventive and corrective maintenance result in an (as good as) new system state by replacing all components,
 such that the system begins a new cycle always under the same conditions.
@@
 since optimizing over replacement schemes is, in our view, a higly interesting topic on its own
-that would merit a separate study.
+that would merit a separate investigation.
 We will comment on this topic in the Outlook (Section~\ref{sec:outlook}).
@@
 As discussed above,
-we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system.
-That means that every time a new cycle starts, the system is in the same state with all components (as-good-as) new.
+we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system,
+such that every time a new cycle starts, the system is in the same state with all components (as good as) new.
 
@@
 and $\fsysnow(t)$ be the corresponding density.
+Note that due to the conditional nature of $\Rsysnow(t)$,
+which gives the probability that the system functions at time $t$ given that it functions at $\tnow$,
+also $\fsysnow(t)$ is a conditional density.
+In particular, we have $\fsysnow(t) = 0$ for all $t \le \tnow$.
+
 Conditional on the realization $\tsysnow > \tnow$ of $\Tsysnow$, the unit cost rate is 
@@
 Thus $\tausnow$, the optimal moment of maintenance as of $\tnow$,
-incorporates thus all that is known at current time $\tnow$.
+incorporates all that is known at current time $\tnow$.
 %The lower index $\tnow$ of $\tausnow$ emphasizes that
 %depends on $\tnow$, and also on the history of the system.
-Figure~\ref{fig:ghist1fig2} illustrates this procedure for a number of current times $\tnow$.
+Figure~\ref{fig:ghist1fig2} shows $\Rsysnow(t)$ and the corresponding $\gnow(\tau)$ for a number of current times $\tnow$
+in a numeric example which is described in more detail in Section~\ref{sec:examples}.
+%illustrates the derivation of $\tausnow$ .
 
@@
 %$\E[1/\Tsysnow \mid \Tsysnow > \tnow]$ must exist,
-$\E[1/\Tsysnow]$ must exist,
+$\E[1/(\Tsysnow - \tnow)]$ must exist,
 which is a condition for $\fsysnow(\tnow + t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
@@
 %$\gstarnow$ increases over time since 
-Also of interest is the total cost rate at $\tnow$, denoted by $\gtotalnow$.
+Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
 This gives the expected unit cost rate calculated over the full time since system start-up,
-under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
+under the assumption that maintenance is scheduled for $\tstarnow := \tnow + \tausnow$.
 $\gtotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
@@
 covering the time span from $\tnow$ to some horizon time $\tnow + t_h$.
-(The choice of $h_t$ is discussed in more detail below.)
+(The choice of $t_h$ is discussed in more detail below.)
 We calculate $\gnow(\tau)$ on the same grid,
@@
 the calculation of $\gnow(\tau)$ requires
-evaluations of $\Rsysnow(t)$ and $\fsysnow(t)$ only for $t \leq \tau$.
+evaluations of $\Rsysnow(\tnow + t)$ and $\fsysnow(\tnow + t)$ only for $t \leq \tau$.
 
@@
 $2.2$, $4.1$, $6.3$, and $3.1$ for type $C$, $H$, $M$, and $P$ components, respectively.
-While it is quite unlikely that any type $C$ component will survive past time $6$,
+While it is a priori quite unlikely that any type $C$ component will survive past time $6$,
 we expect 25\% of type $H$ components to survive past time $10$.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{compprior1fig1}
+\includegraphics[width=\textwidth]{compprior1fig1}
 \caption{Prior predictive reliability functions corresponding to the values from Table~\ref{tab:priorparams},
 %for the four component types of the system depicted in Figure~\ref{fig:brakesys-layout},
-showing the expected failure behaviour according to this choice of parameters.}
+showing the expected failure behaviour.
+Note that each of these is not a plain Weibull reliability function,
+but a weighted average over Weibull reliability functions according to the prior distribution over the scale parameter.}
 \label{fig:compprior1fig1}
@@
 
-We illustrate our procedure*** under three different failure time histories.
+Here, we illustrate our procedure under three different exemplary failure time histories.
+(A systematic simulation study is then presented in Section~\ref{sec:sim}.)
 
@@
 all other failure times are right-censored.
-This is failure history used for Figures~\ref{fig:ghist1fig2} and \ref{fig:tauhist1fig2}.
-Failures observed for type $C$ are thus considerably later than expected,
+This is the failure history already used for Figures~\ref{fig:ghist1fig2} and \ref{fig:tauhist1fig2}.
+Here, failures observed for type $C$ are thus considerably later than expected,
 while for type $P$, the two observed failures are close to the assumed MTTF. 
 Both failure at time $8$ for $H$ and non-failure by time $8$ for $M$ are nothing unusual.
-In total, due to the late type $C$ failures, prior assumptions are somewhat pessimistic.
+In total, due to the late type $C$ failures, prior assumptions turn out to be somewhat pessimistic.
 This is reflected in Figure~\ref{fig:tauhist1fig2},
-where $\tausnow$ first decreases but then tends to increase
-during failure-free periods, adjusting prior expectations since none of the type $C$ components fail.
-
-***move text from caption to here?***
-
-The effect of the continuous parameter update is illustrated in Figure~\ref{fig:tauhist1fig3}.
-This compares the results for our approach (as seen already in Figure~\ref{fig:tauhist1fig2})
-with an approach that does not update the component parameters,
-while still accounting for the fact that components age, and that a failed component changes the system layout.
-***so dynamic but not adaptive?***
-Jumps in $\tausnow$
+where $\tausnow$ first decreases but then tends to increase during failure-free periods,
+which is a consequence of adjusting prior expectations for type $C$ components
+due to their unexpected reliability.
+
+***move some text from figure~\ref{fig:tauhist1fig2} caption to here?***
 
@@
 \includegraphics[width=\textwidth]{tauhist1fig3}
-\caption{Illustration of the gains due to the parameter update
+\caption{Illustration of the gains due to the parameter update at each $\tnow$,
 assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.
@@
 same with $\tstarnow$ (top right panel).
-The adaptive algorithm recongnizes the higher reliability of system components,
-leading to lower current (lower left panel) and total (lower right panels) unit cost rates.}
+This is because the adaptive algorithm recognizes that system components are more reliable than expected,
+leading to lower current (lower left panel) and total (lower right panels) expected unit cost rates.}
 \label{fig:tauhist1fig3}
@@
 
-The second failure history contains the failure times
-
-different example histories (when do components fail?)
-
-%****************************
+The effect of this continuous parameter update is illustrated in Figure~\ref{fig:tauhist1fig3}.
+There, the results as seen already in Figure~\ref{fig:tauhist1fig2} are compared
+to the case when component parameters are not updated,
+while still accounting for the fact that components age,
+and that a failed component changes the system layout.
+%***so dynamic but not adaptive?***
+We see that $\tausnow$ is steadily decreasing in the no update case,
+with the jumps at component failure times being less pronounced than in the update case.
+Without the continuous update, residual system lifetime continues to be underestimated,
+and maintenance is scheduled too early,
+leading to lower prospective ($\gstarnow$) and total ($\gtotalnow$) expected unit cost rates.
+
+In a second failure history, we observe the failure times $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$,
+and follow the system until $\tnow = 2$ only.
+Here, components of type $C$ behave more or less as expected,
+while type $P$ components fail quite early.
+Overall, prior assumptions are reasonably in line with observed failure behaviour.
+%with a slight tendency to earlier failures.
+Consequently, the difference between the continuous update case and the no update case is small,
+as visualized in Figure~\ref{fig:tauhist2fig3}.
+$\tausnow$ values are slightly lower when component parameters are updated,
+reflecting the slightly too early failures of type $P$ components.
+Due to recommending maintenance to be carried out a bit earlier,
+prospective and total cost rate are slightly higher than in the no update case.
+However, these differences are minuscule in comparison to the gains offered by the continuous update
+in case of the first failure history
+(note the differing vertical and horizontal scales in Figures~\ref{fig:tauhist1fig3} and \ref{fig:tauhist2fig3}).
 
@@
 \includegraphics[width=\textwidth]{tauhist2fig3}
-\caption{***early failures: $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$}
+\caption{Effect of the continuous parameter update for the second failure history ($C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$),
+containing slightly early failures of type $P$ components.
+With observed failure behaviour more or less in line with expectations,
+the model with and without continuous update perform similarly,
+unlike in case of the first failure history as depicted in Figure~\ref{fig:tauhist1fig3},
+where updating gave considerable gains.}
 \label{fig:tauhist2fig3}
@@
 
+The third failure history contains very late failures for all component types
+by assuming $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$,
+and following the system until $\tnow = 14$.
+The late failure times for type $C$ components are especially surprising,
+with the prior predictive reliability being $0.01$ at time $10$
+(see top left panel of Figure~\ref{fig:compprior1fig1}).
+Here, the situation is more extreme than in the first failure history.
+Figure~\ref{fig:tauhist3fig3} shows that, after a first short dip,
+$\tausnow$ for the continuous update model steadily increases until the first observed failure at $\tnow = 8$.
+For the model without update, $\tausnow$ steadily decreases instead,
+ignoring any information on component behaviour to be gained during the current system run.
+Assuming $\tthresh = 0.5$, the method without parameter update would recommend to maintain the system preventively at $\tnow = 8.4$,
+with only $P_2$ having failed by then, and all other components up and running,
+corresponding to a considerable waste of component lifetime.
+
 \begin{figure}
 \includegraphics[width=\textwidth]{tauhist3fig3}
-\caption{***very late failures: $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$}
+\caption{Effect of the continuous parameter update for the third failure history,
+containing very late failures for all component types ($C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$).}
 \label{fig:tauhist3fig3}
@@
 
-%*******************************
-
 \section{Small simulation study}
@@
 
-i.e., the Weibull scale parameters chosen as $\ykz$ in Table~\ref{tab:priorparams}.
+Case 1: failure behaviour as expected,
+failure times simulated using Weibull scale parameters $\lambda_k = \ykz$ from Table~\ref{tab:priorparams}.
+
+Case 2: failures earlier than expected,
+failure times simulated using $\lambda_k = 0.5 \ykz$ from Table~\ref{tab:priorparams}.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{br1sim2fig5}
+\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
+where failure times are earlier than expected.}
+\label{fig:br1sim2fig5}
+\end{figure}
+
+Case 3: failures later than expected,
+failure times simulated using $\lambda_k = 2 \ykz$ from Table~\ref{tab:priorparams}.
+
+***do boxplot comparison of all
 

### 2016-11-23 exempl-fail-hist.R
colours for taushistfigs

@@ -60,9 +60,9 @@ br1taus1prpo <- rbind(data.frame(melt(br1taus1fine, "tnow"), variable2 = "Parame
                       data.frame(melt(br1taus1finepr, "tnow"), variable2 = "No parameter update"))
 tauhist1fig3 <- ggplot(br1taus1prpo, aes(x = tnow, y = value)) + xlab(expression(t[now])) +
   geom_line(aes(colour = variable2)) + guides(colour = guide_legend(title=NULL)) +
-  geom_point(aes(colour = variable2), size = 0.15) +
+  geom_point(aes(colour = variable2), size = 0.15) + #theme_bw() +
   facet_wrap(~ variable, nrow = 2, scales = "free_y", labeller = label_parsed) +
-  theme(axis.title.y = element_blank()) + bottomlegend
+  theme(axis.title.y = element_blank()) + bottomlegend + ijarcol
 pdf("tauhist1fig3.pdf", width = 6, height = 4.5)
 tauhist1fig3
 dev.off()
@@ -88,7 +88,7 @@ tauhist2fig3 <- ggplot(br1taus2prpo, aes(x = tnow, y = value)) + xlab(expression
   geom_line(aes(colour = variable2)) + guides(colour = guide_legend(title=NULL)) +
   geom_point(aes(colour = variable2), size = 0.15) +
   facet_wrap(~ variable, nrow = 2, scales = "free_y", labeller = label_parsed) +
-  theme(axis.title.y = element_blank()) + bottomlegend
+  theme(axis.title.y = element_blank()) + bottomlegend+ ijarcol
 pdf("tauhist2fig3.pdf", width = 6, height = 4.5)
 tauhist2fig3
 dev.off()
@@ -112,7 +112,7 @@ tauhist3fig3 <- ggplot(br1taus3prpo, aes(x = tnow, y = value)) + xlab(expression
   geom_line(aes(colour = variable2)) + geom_point(aes(colour = variable2), size = 0.15) +
   scale_x_continuous(breaks = seq(0, 14, by = 4), minor_breaks = seq(0, 14, by = 2)) +
   facet_wrap(~ variable, nrow = 2, scales = "free_y", labeller = label_parsed) +
-  theme(axis.title.y = element_blank()) + bottomlegend
+  theme(axis.title.y = element_blank()) + bottomlegend + ijarcol
 pdf("tauhist3fig3.pdf", width = 6, height = 4.5)
 tauhist3fig3
 dev.off()

### 2016-11-23 sim-study.R
full -> cont.

@@ -75,7 +75,7 @@ br1sim1fig3 <- ggplot(melt(br1sim1prprsummary, "id"), aes(x = id, y = value)) +
   geom_line(aes(colour = variable, group = variable)) + geom_point(aes(colour = variable, group = variable))
 br1sim1fig3
 
-br1sim1summaryall <- rbind(data.frame(sim = "Full update", br1sim1summary),
+br1sim1summaryall <- rbind(data.frame(sim = "Continuous update", br1sim1summary),
                            data.frame(sim = "Cycle end update", br1sim1prsummary),
                            data.frame(sim = "No update", br1sim1prprsummary))
 
@@ -127,7 +127,7 @@ br1sim2fig3 <- ggplot(melt(br1sim2prprsummary, "id"), aes(x = id, y = value)) +
   geom_line(aes(colour = variable, group = variable)) + geom_point(aes(colour = variable, group = variable))
 br1sim2fig3
 
-br1sim2summaryall <- rbind(data.frame(sim = "Full update", br1sim2summary),
+br1sim2summaryall <- rbind(data.frame(sim = "Continuous update", br1sim2summary),
                            data.frame(sim = "Cycle end update", br1sim2prsummary),
                            data.frame(sim = "No update", br1sim2prprsummary))
 

### 2016-11-24 cbm-sim.R
redone sim1

@@ -155,12 +155,12 @@ simNcycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, thresh, s
 }
 
 # function to calculate tend, tfunc, costrate for age-based policy from simNcycle object
-#simNcycleAgebased <- function(simNcycleobj, tprep = 0.5, trepa = 0, cu = 1, cp = 0.2){
+#simNcycleAgebased <- function(simNcycleobj, thresh, cu = 1, cp = 0.2){
 #  
 #}
 
-# function to calculate tend, tfunc, costrate for corrective policy from simNcycle object
-#simNcycleCorrective <- function(simNcycleobj, tprep = 0.5, trepa = 0, cu = 1, cp = 0.2){
+# function to calculate tend, tfunc, costrate for corrective policy 
+#simNcycleCorrective <- function(sys, ctypes, compfts, thresh, cu = 1, cp = 0.2){
 #  
 #}
 

### 2016-11-24 sim-study.R

@@ -17,7 +17,7 @@ simlabeller <- as_labeller(c(nfails = "Number of system failures",
 simlabeller2 <- as_labeller(c(nfails = "Number of system failures",
                               meantend = "Average cycle length",
                               meancostrate = "Average unit cost rate",
-                              "Full update" = "Full update",
+                              "Continuous update" = "Continuous update",
                               "Cycle end update" = "Cycle end update",
                               "No update" = "No update"))
 
@@ -84,6 +84,13 @@ br1sim1fig4 <- ggplot(melt(br1sim1summaryall, c("id", "sim")), aes(x = id, y = v
   facet_wrap(~ variable, nrow = 1, scales = "free_y", labeller = simlabeller)
 br1sim1fig4
 
+br1sim1fig5 <- ggplot(melt(br1sim1summaryall, c("id", "sim")), aes(x = id, y = value)) +
+  geom_line(aes(group = sim)) + geom_point(aes(group = sim)) +
+  facet_grid(variable ~ sim, scales = "free_y", labeller = simlabeller2) +
+  xlab("5-cycle repetition number") + theme(axis.title.y = element_blank())
+pdf("br1sim1fig5.pdf", width = 6, height = 6)
+br1sim1fig5
+dev.off()
 
 # sim 2: failures earlier than expected
 # -------------------------------------

### 2016-11-24 sim-study.R
third simulation

@@ -147,9 +147,10 @@ br1sim2fig4
 dev.off()
 
 br1sim2fig5 <- ggplot(melt(br1sim2summaryall, c("id", "sim")), aes(x = id, y = value)) +
-  geom_line(aes(group = sim)) + geom_point(aes(group = sim)) +
+  geom_line(aes(group = sim)) + geom_point(aes(group = sim)) + 
   facet_grid(variable ~ sim, scales = "free_y", labeller = simlabeller2) +
-  xlab("5-cycle repetition number") + theme(axis.title.y = element_blank())
+  xlab("5-cycle repetition number") + theme(axis.title.y = element_blank()) +
+  geom_hline(yintercept = median(value))
 pdf("br1sim2fig5.pdf", width = 6, height = 6)
 br1sim2fig5
 dev.off()
@@ -157,6 +158,40 @@ dev.off()
 # sim 3: failures later than expected
 # -----------------------------------
 
+# simulate 20 5-cycle machines
+set.seed(2411)
+br1sim5cycle20data3 <- list()
+for (i in 1:20){
+  br1sim5cycle20data3[[i]] <- brWeibullData(5, br1beta, 2*br1mttf)
+}
 
+br1sim3 <- list()     # our model
+br1sim3pr <- list()   # do not update params during cycle, but at end of cycle 
+br1sim3prpr <- list() # never update params
+
+for (i in 1:20){
+  cat("Repetition", i, ": full update\n")
+  br1sim3[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data3[[i]], n0y0 = br1n0y0,
+                            beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401)
+  cat("Repetition", i, ": end of cycle update only\n")
+  br1sim3pr[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data3[[i]], n0y0 = br1n0y0,
+                              beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = TRUE)
+  cat("Repetition", i, ": no update\n")
+  br1sim3prpr[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data3[[i]], n0y0 = br1n0y0,
[…]

### 2016-11-24 cbm-rbd-paper.tex
first sim figure

@@
 
-small simulation study
+We now present a small simulation study
 
@@
 failure times simulated using Weibull scale parameters $\lambda_k = \ykz$ from Table~\ref{tab:priorparams}.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{br1sim1fig5}
+\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
+where failure times are simulated according to prior parameters.}
+\label{fig:br1sim1fig5}
+\end{figure}
 
@@
 \caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
-where failure times are earlier than expected.}
+where failure times are simulated as being earlier than expected.}
 \label{fig:br1sim2fig5}

### 2016-11-25 exempl-fail-hist-2.R
use total cost rate as criterion?

@@ -1,0 +1,134 @@
+# --------------------------------------------------------------------------- #
+# CBM systems paper - code for example figs - 3 exemplary failure histories
+# using total unit cost rate now!
+# --------------------------------------------------------------------------- #
+
+source("cbm-sys-other.R")
+
+# exemplary failure history
+brcompfts <- list(C1 = NA, C2 = 6, C3 = 7, C4 = NA, H = 8,  M = NA, P1 = NA, P2 = 3, P3 = 4, P4 = NA)
+# failure history plot
+brfstdf <- compfts2df(brcompfts)
+plotfts(brcompfts)
+#plotfts(brcompfts,10) 
+#plotfts(brcompfts,6) 
+
+# gnow & sysrelnow histories
+br1ghist2 <- gnowhist(br, brctypes, brcompfts, br1n0y0, br1beta, c(0,2,4,6,8), hor = 10,
+                      seqlen = 1001, onecycle = FALSE)
+br1ghist2$tnow <- as.factor(br1ghist2$tnow)
+br1ghist2a <- br1ghist2
+names(br1ghist2a)[c(3,4)] <- c("Reliability", "Unit cost rate")
+br1ghist2a <- melt(br1ghist2a, c("tnow", "t"))
+br1ghist2a <- subset(br1ghist2a, !is.na(value))
+ghist1fig2rT <- ggplot(subset(br1ghist2a, variable == "Reliability"), aes(x = t, y = value)) +
+  geom_line(aes(linetype = tnow)) + coord_cartesian(xlim = c(0, 18), ylim = c(0, 1)) +
+  xlab(expression(t)) + ylab(expression(paste(R[sys]^(t[now]), (t)))) + guides(linetype = 'none') + 
+  scale_x_continuous(breaks = seq(0, 18, by = 2), minor_breaks = 0:18) +
+  scale_y_continuous(breaks = seq(0, 1, by = 0.2), minor_breaks = seq(0, 1, by = 0.1)) +
+  theme(axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank())
+ghist1fig2gT <- ggplot(subset(br1ghist2a, variable == "Unit cost rate"), aes(x = t, y = value)) +
+  geom_line(aes(linetype = tnow)) + coord_cartesian(xlim = c(0, 18), ylim = c(0, 0.5)) +
+  xlab(expression(t)) + ylab(expression(paste(g[sys]^(t[now]), (t)))) +
[…]

### 2016-11-25 exempl-fail-hist.R

@@ -36,6 +36,7 @@ pdf("ghist1fig2.pdf", width = 6, height = 4)
 grid.arrange(ghist1fig2r, ghist1fig2g, nrow = 2, heights = c(1, 1.5))
 dev.off()
 
+
 # -------------------------------------------------------------------------------------------------
 
 br1taus1fine <- taustarhist(br, brctypes, brcompfts, br1n0y0, br1beta, seq(0,8,by=0.1), hor=4, seqlen=401)
@@ -66,6 +67,7 @@ tauhist1fig3 <- ggplot(br1taus1prpo, aes(x = tnow, y = value)) + xlab(expression
 pdf("tauhist1fig3.pdf", width = 6, height = 4.5)
 tauhist1fig3
 dev.off()
+
 
 # -------------------------------------------------------------------------
 

### 2016-11-25 sim-study-2.R

@@ -1,0 +1,124 @@
+# --------------------------------------------------------------------------- #
+# CBM systems paper - code for example figs - simulation study
+# using total unit cost rate now!
+# choose lower thresh now???
+# --------------------------------------------------------------------------- #
+
+source("cbm-sys-other.R")
+
+simsummary <- function(simlist){
+  data.frame(id = 1:length(simlist),
+             nfails = sapply(simlist, function(res) sum(res$tfunc != res$tend)),
+             meantend = sapply(simlist, function(res) mean(res$tend)),
+             meancostrate = sapply(simlist, function(res) weighted.mean(res$costrate, res$tend)))
+}
+
+simsummary2 <- function(simlist){
+  nrep <- length(simlist)
+  ncyc <- length(simlist[[1]]$tend)
+  data.frame(repid = rep(1:nrep, each = ncyc),
+             cycid = rep(1:ncyc, nrep),
+             failed = sapply(simlist, function(res) res$tfunc != res$tend),
+             tend = sapply(simlist, function(res) res$tend),
+             costrate = sapply(simlist, function(res) res$costrate))
+}
+
+simlabeller <- as_labeller(c(nfails = "Number of system failures",
+                             meantend = "Average cycle length",
+                             meancostrate = "Average unit cost rate"))
+simlabeller2 <- as_labeller(c(nfails = "Number of system failures",
+                              meantend = "Average cycle length",
+                              meancostrate = "Average unit cost rate",
+                              "Continuous update" = "Continuous update",
+                              "Cycle end update" = "Cycle end update",
+                              "No update" = "No update"))
+
+
+# sim 2: failures earlier than expected
+# -------------------------------------
+
+# simulate 20 5-cycle machines
+set.seed(2211)
+br1sim5cycle20data2 <- list()
+for (i in 1:20){
+  br1sim5cycle20data2[[i]] <- brWeibullData(5, br1beta, 0.5*br1mttf)
+}
+
+br1sim2T <- list()     # our model
[…]

### 2016-11-25 sim-study.R

@@ -185,11 +185,14 @@ br1sim3summary <- simsummary(br1sim3)
 br1sim3prsummary <- simsummary(br1sim3pr)
 br1sim3prprsummary <- simsummary(br1sim3prpr)
 
+br1sim3summaryall <- rbind(data.frame(sim = "Continuous update", br1sim3summary),
+                           data.frame(sim = "Cycle end update", br1sim3prsummary),
+                           data.frame(sim = "No update", br1sim3prprsummary))
+
 br1sim3fig5 <- ggplot(melt(br1sim3summaryall, c("id", "sim")), aes(x = id, y = value)) +
   geom_line(aes(group = sim)) + geom_point(aes(group = sim)) + 
   facet_grid(variable ~ sim, scales = "free_y", labeller = simlabeller2) +
-  xlab("5-cycle repetition number") + theme(axis.title.y = element_blank()) +
-  geom_hline(yintercept = median(value))
+  xlab("5-cycle repetition number") + theme(axis.title.y = element_blank())
 pdf("br1sim3fig5.pdf", width = 6, height = 6)
 br1sim3fig5
 dev.off()

### 2016-11-25 weibull-sys-functions.R

@@ -267,15 +267,21 @@ plotfts <- function(compfts, maxtnow = NA, pointsize = 1, tlabelvjust = -1){
 # cu       cost of unplanned (corrective) repair action
 # cp       cost of planned (preventive) repair action, cp < cu
 # onecycle whether to use the one-cycle criterion or the renewal-based one
-gnow <- function(tau, rel, f, cu = 1, cp = 0.2, onecycle = TRUE){
+# tnow     one-cycle total cost criterion needs current tnow
+gnow <- function(tau, rel, f, cu = 1, cp = 0.2, onecycle = TRUE, tnow = 0){
   if (onecycle){
     gnow <- (cp / tau) * rel + cu * sapply(tau, function(ctau){
       sum(f[tau <= ctau] / tau[tau <= ctau])
     })
   } else {
-    gnow <- (cp * rel + cu * (1 - rel)) / ( tau * rel + sapply(tau, function(ctau){
-      sum(rel[tau <= ctau])
-    }))
+    # one-cycle total cost criterion 
+    gnow <- (cp / (tau + tnow)) * rel + cu * sapply(tau, function(ctau){
+      sum(f[tau <= ctau] / (tau[tau <= ctau] + tnow))
+    })
+    # renewal reward criterion
+    #gnow <- (cp * rel + cu * (1 - rel)) / ( tau * rel + sapply(tau, function(ctau){
+    #  sum(rel[tau <= ctau])
+    #}))
   }
   data.frame(tau = tau, rel = rel, gnow = gnow)  
 }
@@ -295,7 +301,7 @@ gnowhor <- function(survsign, n0y0, beta, fts, tnow, hor, seqlen=101, prior = FA
   f <- -diff(trel$rel)
   tau <- trel$t[-1] - tnow # shift to start directly after 0
   rel <- trel$rel[-1]
-  res <- gnow(tau = tau, rel = rel, f = f, cu = cu, cp = cp, onecycle = onecycle)
+  res <- gnow(tau = tau, rel = rel, f = f, cu = cu, cp = cp, onecycle = onecycle, tnow = tnow)
   res$tau <- tau + tnow
   return(res)
 }
@@ -331,7 +337,8 @@ gnowhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen = 10
     fi <- -diff(trel$rel)
     taui <- trel$t[-1] - tnowi # shift to start directly after 0
[…]

### 2016-11-26 cbm-sim.R
bug in simulation for case when cycle ends without a single component failure, sims with total cost rate

@@ -85,12 +85,15 @@ sim1cycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, thresh, s
   ftslist <- as.list(rep(list(NULL), K))
   ftsfinal <- ftschron[ftschron <= tnow]
   ftsindex <- sapply(ctypes, function(ctypesl) names(ftsfinal) %in% ctypesl)
-  if (length(ftsfinal) == 1)
-    ftsindex <- which(ftsindex)
-  else
-    ftsindex <- apply(ftsindex, 1, which)
-  for (k in 1:K)
-    ftslist[[k]] <- ftsfinal[ftsindex == k]
+  if (length(ftsfinal) >= 1){
+    if (length(ftsfinal) == 1){
+      ftsindex <- which(ftsindex)
+    } else {
+      ftsindex <- apply(ftsindex, 1, which)
+    }
+    for (k in 1:K)
+      ftslist[[k]] <- ftsfinal[ftsindex == k]
+  }
   # censoring time is last tnow, number of censored components from
   censlist <- as.list(rep(list(NULL), K))
   ek <- sapply(ftslist, length)

### 2016-11-26 sim-study-2.R

@@ -33,6 +33,32 @@ simlabeller2 <- as_labeller(c(nfails = "Number of system failures",
                               "Cycle end update" = "Cycle end update",
                               "No update" = "No update"))
 
+# sim 1: data fits to priors
+# --------------------------
+
+# simulate 20 5-cycle machines with priors as given
+set.seed(2211)
+br1sim5cycle20data1 <- list()
+for (i in 1:20){
+  br1sim5cycle20data1[[i]] <- brWeibullData(5, br1beta, br1mttf)
+}
+
+br1sim1T <- list()     # our model
+br1sim1prT <- list()   # do not update params during cycle, but at end of cycle 
+br1sim1prprT <- list() # never update params
+
+for (i in 1:20){
+  cat("Repetition", i, ": full update\n")
+  br1sim1T[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[i]], n0y0 = br1n0y0,
+                             beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, onecycle = FALSE)
+  cat("Repetition", i, ": end of cycle update only\n")
+  br1sim1prT[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[i]], n0y0 = br1n0y0,
+                               beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = TRUE, onecycle = FALSE)
+  cat("Repetition", i, ": no update\n")
+  br1sim1prprT[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[i]], n0y0 = br1n0y0,
+                                 beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = TRUE, cycleupdate = FALSE, onecycle = FALSE)
+}
+
 
 # sim 2: failures earlier than expected
 # -------------------------------------
@@ -120,5 +146,20 @@ for (i in 1:20){
                                  beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = TRUE, cycleupdate = FALSE, onecycle = FALSE)
 }
 
+br1sim3Tsummary <- simsummary(br1sim3T)
+br1sim3prTsummary <- simsummary(br1sim3prT)
[…]

### 2016-11-27 sim-study-2.R
sims with lower thresh

@@ -118,19 +118,82 @@ pdf("br1sim2fig5T.pdf", width = 6, height = 6)
 br1sim2fig5T
 dev.off()
 
+# figure with boxplot instead of means
 br1sim2Tsummary2 <- simsummary2(br1sim2T)
 br1sim2prTsummary2 <- simsummary2(br1sim2prT)
 br1sim2prprTsummary2 <- simsummary2(br1sim2prprT)
-
 br1sim2Tsummary2all <- rbind(data.frame(sim = "Continuous update", br1sim2Tsummary2),
                              data.frame(sim = "Cycle end update", br1sim2prTsummary2),
                              data.frame(sim = "No update", br1sim2prprTsummary2))
-
 br1sim2fig2Ta <- ggplot(melt(br1sim2Tsummary2all, c("repid", "cycid", "sim")), aes(x = repid, y = value)) + 
   stat_boxplot(aes(group = repid)) +
   #geom_point(aes(group = variable, colour = cycid)) +
   facet_grid(variable ~ sim, scales = "free_y")
 br1sim2fig2Ta
+
+# earlier failures with lower threshold
+
+# thresh = 0.1
+br1sim2Tt01 <- list()     # our model
+br1sim2prTt01 <- list()   # do not update params during cycle, but at end of cycle 
+br1sim2prprTt01 <- list() # never update params
+
+for (i in 1:20){
+  cat("Repetition", i, ": full update\n")
+  br1sim2Tt01[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data2[[i]], n0y0 = br1n0y0,
+                                beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.1, seqlen = 401, onecycle = FALSE)
+  cat("Repetition", i, ": end of cycle update only\n")
+  br1sim2prTt01[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data2[[i]], n0y0 = br1n0y0,
+                                  beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.1, seqlen = 401, prior = TRUE, onecycle = FALSE)
+  cat("Repetition", i, ": no update\n")
+  br1sim2prprTt01[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data2[[i]], n0y0 = br1n0y0,
[…]

### 2016-11-27 sim-study.R

@@ -247,7 +247,7 @@ dev.off()
 set.seed(2711)
 br1sim5cycle20data5 <- list()
 for (i in 1:20){
-  br1sim5cycle20data5[[i]] <- brWeibullData(5, br1beta, 5*br1mttf)
+  br1sim5cycle20data5[[i]] <- brWeibullData(5, br1beta, 3*br1mttf)
 }
 
 br1sim5 <- list()     # our model
@@ -257,13 +257,13 @@ br1sim5prpr <- list() # never update params
 for (i in 1:20){
   cat("Repetition", i, ": full update\n")
   br1sim5[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data5[[i]], n0y0 = br1n0y0,
-                            beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401)
+                            beta = br1beta, tnowstep = 0.1, hor = 8, thresh = 0.5, seqlen = 801)
   cat("Repetition", i, ": end of cycle update only\n")
   br1sim5pr[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data5[[i]], n0y0 = br1n0y0,
-                              beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = TRUE)
+                              beta = br1beta, tnowstep = 0.1, hor = 8, thresh = 0.5, seqlen = 801, prior = TRUE)
   cat("Repetition", i, ": no update\n")
   br1sim5prpr[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data5[[i]], n0y0 = br1n0y0,
-                                beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.5, seqlen = 401, prior = TRUE, cycleupdate = FALSE)
+                                beta = br1beta, tnowstep = 0.1, hor = 8, thresh = 0.5, seqlen = 801, prior = TRUE, cycleupdate = FALSE)
 }
 
 

### 2016-11-28 cbm-rbd-paper.tex
third sim fig
total cost rate sim figures in

@@
 Case 2: failures earlier than expected,
-failure times simulated using $\lambda_k = 0.5 \ykz$ from Table~\ref{tab:priorparams}.
+failure times simulated using
+$\lambda_k = 0.5 \ykz$ (Figure~\ref{fig:br1sim2fig5}) or
+$\lambda_k = 0.2 \ykz$ (Figure~\ref{fig:br1sim4fig5}).
 
@@
 \caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
-where failure times are simulated as being earlier than expected.}
+where failure times are simulated as being earlier ($0.5 \times$ MTTF) than expected.}
 \label{fig:br1sim2fig5}
@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{br1sim4fig5}
+\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
+where failure times are simulated as being much earlier ($0.2 \times$ MTTF) than expected.}
+\label{fig:br1sim4fig5}
+\end{figure}
+
 Case 3: failures later than expected,
@@
 
-***do boxplot comparison of all
+\begin{figure}
+\includegraphics[width=\textwidth]{br1sim3fig5}
+\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
+where failure times are simulated as being later ($2 \times$ MTTF) than expected.}
+\label{fig:br1sim3fig5}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{br1sim1fig5T}
+\includegraphics[width=0.5\textwidth]{br1sim2fig5T}
+\includegraphics[width=0.5\textwidth]{br1sim3fig5T}
+\includegraphics[width=0.5\textwidth]{br1sim4fig5T}
+\caption{***Simulation study with ***total costrate criterion***, $\tthresh = 0.5$.
+TL: $\lambda_k =     \ykz$,
+TR: $\lambda_k = 0.5 \ykz$,
+BL: $\lambda_k = 2   \ykz$,
+BR: $\lambda_k = 0.2 \ykz$}
+\label{fig:simtotalcostrate05}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt01}
+\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt02}
+\caption{***Simulation study with ***total costrate criterion***, $\tthresh = 0.1$ (left) and $\tthresh = 0.2$ (right).}
+\label{fig:simtotalcostrate0102}
+\end{figure}
 

### 2016-11-28 cbm-rbd-paper.tex
total cost rate sim figures in

@@
 
+\iffalse
 Case 1: failure behaviour as expected,
@@
 \label{fig:br1sim3fig5}
+\end{figure}
+\fi
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{br1sim1fig5}
+\includegraphics[width=0.5\textwidth]{br1sim2fig5}
+\includegraphics[width=0.5\textwidth]{br1sim3fig5}
+\includegraphics[width=0.5\textwidth]{br1sim4fig5}
+\caption{***Simulation study with ***prsopective costrate criterion***, $\tthresh = 0.5$.
+TL: $\lambda_k =     \ykz$,
+TR: $\lambda_k = 0.5 \ykz$,
+BL: $\lambda_k = 2   \ykz$,
+BR: $\lambda_k = 0.2 \ykz$}
+\label{fig:simprospcostrate05}
 \end{figure}

### 2016-11-28 cbm-rbd-paper.tex
one figure for sim prosp. costrate

@@
 \includegraphics[width=0.5\textwidth]{br1sim4fig5}
-\caption{***Simulation study with ***prsopective costrate criterion***, $\tthresh = 0.5$.
+\caption{***Simulation study with ***prospective costrate criterion***, $\tthresh = 0.5$.
 TL: $\lambda_k =     \ykz$,
@@
 \includegraphics[width=0.5\textwidth]{br1sim2fig5Tt02}
-\caption{***Simulation study with ***total costrate criterion***, $\tthresh = 0.1$ (left) and $\tthresh = 0.2$ (right).}
+\caption{***Simulation study with ***total costrate criterion***, early failures ($0.5 \times$ MTTF),
+$\tthresh = 0.1$ (left) and $\tthresh = 0.2$ (right).}
 \label{fig:simtotalcostrate0102}

### 2016-11-28 cbm-rbd-paper.tex
very early failures tauhist figure (section 6)

@@
 
-\section{Numerical examples for a complex system}
+\section{Further elaboration of the case study}
 \label{sec:examples}
@@
 Here, we illustrate our procedure under three different exemplary failure time histories.
-(A systematic simulation study is then presented in Section~\ref{sec:sim}.)
+(A more systematic simulation study is then presented in Section~\ref{sec:sim}.)
 
@@
 
-The third failure history contains very late failures for all component types
-by assuming $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$,
-and following the system until $\tnow = 14$.
-The late failure times for type $C$ components are especially surprising,
-with the prior predictive reliability being $0.01$ at time $10$
-(see top left panel of Figure~\ref{fig:compprior1fig1}).
-Here, the situation is more extreme than in the first failure history.
-Figure~\ref{fig:tauhist3fig3} shows that, after a first short dip,
-$\tausnow$ for the continuous update model steadily increases until the first observed failure at $\tnow = 8$.
-For the model without update, $\tausnow$ steadily decreases instead,
-ignoring any information on component behaviour to be gained during the current system run.
-Assuming $\tthresh = 0.5$, the method without parameter update would recommend to maintain the system preventively at $\tnow = 8.4$,
-with only $P_2$ having failed by then, and all other components up and running,
-corresponding to a considerable waste of component lifetime.
+%The third failure history contains very late failures for all component types
+%by assuming $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$,
+%and following the system until $\tnow = 14$.
+%The late failure times for type $C$ components are especially surprising,
+%with the prior predictive reliability being $0.01$ at time $10$
+%(see top left panel of Figure~\ref{fig:compprior1fig1}).
+%Here, the situation is more extreme than in the first failure history.
+%Figure~\ref{fig:tauhist3fig3} shows that, after a first short dip,
+%$\tausnow$ for the continuous update model steadily increases until the first observed failure at $\tnow = 8$.
+%For the model without update, $\tausnow$ steadily decreases instead,
+%ignoring any information on component behaviour to be gained during the current system run.
+%Assuming $\tthresh = 0.5$, the method without parameter update would recommend to maintain the system preventively at $\tnow = 8.4$,
+%with only $P_2$ having failed by then, and all other components up and running,
+%corresponding to a considerable waste of component lifetime.
+%
+%\begin{figure}
+%\includegraphics[width=\textwidth]{tauhist3fig3}
+%\caption{Effect of the continuous parameter update for the third failure history,
+%containing very late failures for all component types ($C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$).}
+%\label{fig:tauhist3fig3}
+%\end{figure}
+
+The third failure history contains very early failures
+with $C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$,
+and we follow the system until $\tnow = 0.5$.
+
+***without update consistently higher, adaptive algorithm takes surprisingly early failures into account,
+unlike in other scenarios, overall trend for $\tausnow$ constant because of heavy drops,
+costs are underestimated without update***
 
 \begin{figure}
-\includegraphics[width=\textwidth]{tauhist3fig3}
+\includegraphics[width=\textwidth]{tauhist4fig3}
 \caption{Effect of the continuous parameter update for the third failure history,
-containing very late failures for all component types ($C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$).}
-\label{fig:tauhist3fig3}
+containing very early failures ($C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$).}
+\label{fig:tauhist4fig3}
 \end{figure}

### 2016-11-28 sim-study.R
lower thresold for other totalcost sims, very late failure sim

@@ -257,15 +257,21 @@ br1sim5prpr <- list() # never update params
 for (i in 1:20){
   cat("Repetition", i, ": full update\n")
   br1sim5[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data5[[i]], n0y0 = br1n0y0,
-                            beta = br1beta, tnowstep = 0.1, hor = 8, thresh = 0.5, seqlen = 801)
-  cat("Repetition", i, ": end of cycle update only\n")
-  br1sim5pr[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data5[[i]], n0y0 = br1n0y0,
-                              beta = br1beta, tnowstep = 0.1, hor = 8, thresh = 0.5, seqlen = 801, prior = TRUE)
-  cat("Repetition", i, ": no update\n")
-  br1sim5prpr[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data5[[i]], n0y0 = br1n0y0,
-                                beta = br1beta, tnowstep = 0.1, hor = 8, thresh = 0.5, seqlen = 801, prior = TRUE, cycleupdate = FALSE)
+                            beta = br1beta, tnowstep = 0.2, hor = 6, thresh = 0.5, seqlen = 601)
+#  cat("Repetition", i, ": end of cycle update only\n")
+#  br1sim5pr[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data5[[i]], n0y0 = br1n0y0,
+#                              beta = br1beta, tnowstep = 0.2, hor = 6, thresh = 0.5, seqlen = 601, prior = TRUE)
+#  cat("Repetition", i, ": no update\n")
+#  br1sim5prpr[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data5[[i]], n0y0 = br1n0y0,
+#                                beta = br1beta, tnowstep = 0.2, hor = 6, thresh = 0.5, seqlen = 601, prior = TRUE, cycleupdate = FALSE)
 }
 
+br1sim5summary <- simsummary(br1sim5)
+#br1sim5prsummary <- simsummary(br1sim5pr)
+#br1sim5prprsummary <- simsummary(br1sim5prpr)
 
[…]

### 2016-11-28 cbm-rbd-paper.tex
changes after dicussion with SDF

@@
 
-\subsection{System reliability function at $\tnow$}
+\subsection{Conditional system reliability function at $\tnow$}
 \label{sec:sysreltnow}
@@
 \end{align}
+Since this is the system reliability distribution conditional on the system surviving until $\tnow$,
+we have that $\Rsysnow(\tnow) = 1$.
 Note that if one or several components have failed by $\tnow$,
@@
 c_p / \tau               & \text{if } \tsysnow \ge \tnow + \tau \\
-c_u / (\tsysnow - \tnow) & \text{if } \tsysnow  <  \tnow + \tau \,.
+c_u / (\tsysnow - \tnow) & \text{if } \tnow < \tsysnow  <  \tnow + \tau \,.
 \end{cases}
@@
 \gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] \nonumber\\ 
-            &= \frac{c_p}{\tau} \Rsysnow(\tnow + \tau) + c_u \int_0^\tau \frac{1}{t} \fsysnow(\tnow + t) \dd t\,,
+            &= \frac{c_p}{\tau} \Rsysnow(\tnow + \tau) + c_u \int_0^\tau \frac{1}{\theta} \fsysnow(\tnow + \theta) \dd \theta\,,
 \label{eq:gtnowtau}
@@
 $\E[1/(\Tsysnow - \tnow)]$ must exist,
-which is a condition for $\fsysnow(\tnow + t)$ for values of $t$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
+which is a condition for $\fsysnow(\tnow + \theta)$ for values of $\theta$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
 This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
@@
 Here, we approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
-where evaluations of $\fsysnow(\tnow + t)$ are calculated via differences of $\Rsysnow(\tnow + t)$ evaluations.
+where evaluations of $\fsysnow(t)$ are calculated via differences of $\Rsysnow(t)$ evaluations.
 %$\gnow(\tau)$ is likewise evaluated on a dense grid,
@@
 the calculation of $\gnow(\tau)$ requires
-evaluations of $\Rsysnow(\tnow + t)$ and $\fsysnow(\tnow + t)$ only for $t \leq \tau$.
+evaluations of $\Rsysnow(t)$ and $\fsysnow(t)$ only for $\tnow < t \le \tnow + \tau$.
 
@@
 As the parameter update step is closed-form,
-recalculation of $\tausnow$ is a matter of seconds,
+recalculation of $\tausnow$ is a matter of one or two seconds,
 allowing for a near real-time update.

### 2016-11-28 exempl-fail-hist.R

@@ -39,26 +39,39 @@ dev.off()
 
 # -------------------------------------------------------------------------------------------------
 
+# tauhist figures
+
 br1taus1fine <- taustarhist(br, brctypes, brcompfts, br1n0y0, br1beta, seq(0,8,by=0.1), hor=4, seqlen=401)
-names(br1taus1fine)[2:5] <- c(taustar = expression(tau['*']^(t[now])),
+names(br1taus1fine)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
                               tstar = expression(t['*']^(t[now])),
                               cstar = expression(g['*']^(t[now])),
-                              ctotal = expression(g[total]^(t[now])))
-tauhist1fig2 <- ggplot(melt(br1taus1fine, "tnow"), aes(x = tnow, y = value)) + xlab(expression(t[now])) +
+                              ctotal = expression(g[total]^(t[now])),
+                              relstar = expression(paste(R[sys]^(t[now]),(t['*']^(t[now])))))
+tauhist1fig2 <- ggplot(melt(br1taus1fine[-6], "tnow"), aes(x = tnow, y = value)) + xlab(expression(t[now])) +
   geom_line(aes(group = variable))  + geom_point(aes(group = variable), size = 0.15) +
   facet_wrap(~ variable, nrow = 2, scales = "free_y", labeller = label_parsed) +
   theme(axis.title.y = element_blank())
 pdf("tauhist1fig2.pdf", width = 6, height = 4)
 tauhist1fig2
 dev.off()
-br1taus1fine[40:41,]
+#br1taus1fine[40:41,]
+
+tauhist1fig2R <- ggplot(melt(br1taus1fine[-5], "tnow"), aes(x = tnow, y = value)) + xlab(expression(t[now])) +
+  geom_line(aes(group = variable))  + geom_point(aes(group = variable), size = 0.15) +
+  facet_wrap(~ variable, nrow = 2, scales = "free_y", labeller = label_parsed) +
+  theme(axis.title.y = element_blank())
+pdf("tauhist1fig2R.pdf", width = 6, height = 4)
+tauhist1fig2R
+dev.off()
+
 br1taus1finepr <- taustarhist(br, brctypes, brcompfts, br1n0y0, br1beta, seq(0,8,by=0.1), hor=4, seqlen=401, prior=T)
-names(br1taus1finepr)[2:5] <- c(taustar = expression(tau['*']^(t[now])),
[…]

### 2016-11-28 weibull-sys-functions.R

@@ -355,6 +355,7 @@ taustarhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen =
   tstarsi <- tstarsi$gnow + (seqlen - 1) * (0:(length(tnowvec) - 1))
   tstars <- res2$t[tstarsi]
   taustars <- tstars - tnowvec
+  relstars <- res2$rel[tstarsi]
   cuint <- sapply(tnowvec, function(tnowi){
     trel <- subset(res, res$tnow == tnowi)
     f <- -diff(trel$rel)
@@ -364,7 +365,7 @@ taustarhist <- function(sys, ctypes, compfts, n0y0, beta, tnowvec, hor, seqlen =
   })
   #cat("cuint =", cuint)
   ctotal <- cp / tstars * res2$rel[tstarsi] + cu * cuint
-  data.frame(tnow = tnowvec, taustar = taustars, tstar = tstars, cstar = cstars, ctotal = ctotal)
+  data.frame(tnow = tnowvec, taustar = taustars, tstar = tstars, cstar = cstars, ctotal = ctotal, relstar = relstars)
 }
 
 

### 2016-11-28 exempl-fail-hist-2.R
rstar also for total cost

@@ -43,11 +43,12 @@ dev.off()
 
 br1taus1fineT <- taustarhist(br, brctypes, brcompfts, br1n0y0, br1beta, seq(0,8,by=0.1),
                              hor=4, seqlen=401, onecycle = FALSE)
-names(br1taus1fineT)[2:5] <- c(taustar = expression(tau['*']^(t[now])),
+names(br1taus1fineT)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
                                tstar = expression(t['*']^(t[now])),
                                cstar = expression(g['*']^(t[now])),
-                               ctotal = expression(g[total]^(t[now])))
-tauhist1fig2T <- ggplot(melt(br1taus1fineT, "tnow"), aes(x = tnow, y = value)) + xlab(expression(t[now])) +
+                               ctotal = expression(g[total]^(t[now])),
+                               relstar = expression(paste(R[sys]^(t[now]),(t['*']^(t[now])))))
+tauhist1fig2T <- ggplot(melt(br1taus1fineT[-6], "tnow"), aes(x = tnow, y = value)) + xlab(expression(t[now])) +
   geom_line(aes(group = variable))  + geom_point(aes(group = variable), size = 0.15) +
   facet_wrap(~ variable, nrow = 2, scales = "free_y", labeller = label_parsed) +
   theme(axis.title.y = element_blank())
@@ -57,12 +58,13 @@ dev.off()
 #br1taus1fine[40:41,]
 br1taus1fineprT <- taustarhist(br, brctypes, brcompfts, br1n0y0, br1beta, seq(0,8,by=0.1),
                                hor=4, seqlen=401, prior = TRUE, onecycle = FALSE)
-names(br1taus1fineprT)[2:5] <- c(taustar = expression(tau['*']^(t[now])),
+names(br1taus1fineprT)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
                                  tstar = expression(t['*']^(t[now])),
                                  cstar = expression(g['*']^(t[now])),
-                                 ctotal = expression(g[total]^(t[now])))
-br1taus1prpoT <- rbind(data.frame(melt(br1taus1fineT, "tnow"), variable2 = "Parameter update"),
-                       data.frame(melt(br1taus1fineprT, "tnow"), variable2 = "No parameter update"))
[…]

### 2016-11-29 cbm-sim.R
corrective maintenance simulation

@@ -162,10 +162,82 @@ simNcycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, thresh, s
 #  
 #}
 
-# function to calculate tend, tfunc, costrate for corrective policy 
-#simNcycleCorrective <- function(sys, ctypes, compfts, thresh, cu = 1, cp = 0.2){
-#  
-#}
+# function to calculate tend, costrate for a single cycle using the corrective policy (cp is ignored)
+# sys      system reliability block diagram at t = 0
+# ctypes   list giving the types of components in the system, same format as
+#          used for setCompTypes(), but needs the same order as in survsign table (!!!)
+# compfts  list with elements named like the vertices in sys, giving the N (simulated)
+#          failure times of this component -- assumed that no failure times == 0
+# tnowstep time interval after which current system reliability is re-evaluated
+# cu       cost of unplanned (corrective) repair action
+# cp       cost of planned (preventive) repair action, cp < cu
+sim1cycleCorrective <- function(sys, ctypes, compfts, tnowstep, cu = 1, cp = 0.2){
+  K <- length(ctypes)
+  ftschron <- sort(unlist(compfts)) # when something happens
+  ftschroni <- 1
+  gotonext <- TRUE
+  res <- data.frame(tnow = 0, failed = FALSE) # initialize results data frame (assumed that initial system functions)
+  while(gotonext){
+    failedcompsnow <- ftschron[1:ftschroni]
+    tnow <- ceiling(ftschron[ftschroni] / tnowstep) * tnowstep
+    sysnow <- induced_subgraph(sys, vids=V(sys)[!(name %in% names(failedcompsnow))])
+    # catch error when sysnow now contains vertices s and t only (suddenly all components fail)
+    if(distances(sysnow, "s", "t") < Inf)
+      signnow <- computeSystemSurvivalSignature(sysnow)
+    else
+      signnow <- data.frame(Probability = 0)
+    # now check if system failed
+    if (all(signnow$Probability == 0)){ # system has failed now, repair with cost cu
+      failed <- TRUE
+      gotonext <- FALSE
+    } else { # system has not failed, go to next ftschron entry
+      failed <- FALSE
+      ftschroni <- ftschroni + 1
+    }
+    # write all current things in results data frame
+    resnow <- data.frame(tnow = tnow, failed = failed)
+    res <- rbind(res, resnow) 
+  }
+  names(tnow) <- NULL
[…]

### 2016-11-29 sim-study-AC.R

@@ -1,0 +1,110 @@
+# --------------------------------------------------------------------------- #
+# CBM systems paper - code for example figs - simulation study
+# age-based and corrective maintenance
+# --------------------------------------------------------------------------- #
+
+source("cbm-sys-other.R")
+
+simsummary <- function(simlist){
+  data.frame(id = 1:length(simlist),
+             nfails = sapply(simlist, function(res) sum(res$tfunc != res$tend)),
+             meantend = sapply(simlist, function(res) mean(res$tend)),
+             meancostrate = sapply(simlist, function(res) weighted.mean(res$costrate, res$tend)))
+}
+
+simsummary2 <- function(simlist){
+  nrep <- length(simlist)
+  ncyc <- length(simlist[[1]]$tend)
+  data.frame(repid = rep(1:nrep, each = ncyc),
+             cycid = rep(1:ncyc, nrep),
+             failed = as.vector(sapply(simlist, function(res) res$tfunc != res$tend)),
+             tend = as.vector(sapply(simlist, function(res) res$tend)),
+             costrate = as.vector(sapply(simlist, function(res) res$costrate)))
+}
+
+simlabeller <- as_labeller(c(nfails = "Number of system failures",
+                             meantend = "Average cycle length",
+                             meancostrate = "Average unit cost rate"))
+simlabeller2 <- as_labeller(c(nfails = "Number of system failures",
+                              meantend = "Average cycle length",
+                              meancostrate = "Average unit cost rate",
+                              "Continuous update" = "Continuous update",
+                              "Cycle end update" = "Cycle end update",
+                              "No update" = "No update"))
+
+# sim 1: data fits to priors
+# --------------------------
+
+# simulate 20 5-cycle machines with priors as given
+set.seed(2211)
+br1sim5cycle20data1 <- list()
+for (i in 1:20){
+  br1sim5cycle20data1[[i]] <- brWeibullData(5, br1beta, br1mttf)
+}
+
+br1sim1C <- list()   # corrective
[…]

### 2016-11-29 sim-study.R

@@ -43,6 +43,11 @@ pdf("br1simN51fig1.pdf", width = 6, height = 4)
 br1simN51fig1
 dev.off()
 
+# test sim corrective
+#testfts <- lapply(br1sim5cycle20data1[[1]], function(x) x[1])
+#br1simN51c <- sim1cycleCorrective(sys = br, ctypes = brctypes, compfts = testfts, tnowstep = 0.1)
+#br1simN51c <- simNcycleCorrective(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[1]], tnowstep = 0.1)
+
 br1sim1 <- list()     # our model
 br1sim1pr <- list()   # do not update params during cycle, but at end of cycle 
 br1sim1prpr <- list() # never update params

### 2016-11-29 cbm-rbd-paper.tex
switch to total cost rate & thresh = 0.1

@@
 \usepackage{tikz}
+\usepackage{sidecap}
 
@@
 
+*** change to total cost rate
+
 Conditional on the realization $\tsysnow > \tnow$ of $\Tsysnow$, the unit cost rate is 
@@
 where $0$ corresponds to the time of system start-up.
-Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being
+Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being***
 \begin{align}
@@
 %depends on $\tnow$, and also on the history of the system.
-Figure~\ref{fig:ghist1fig2} shows $\Rsysnow(t)$ and the corresponding $\gnow(\tau)$ for a number of current times $\tnow$
+Figure~\ref{fig:ghist1fig2T} shows $\Rsysnow(t)$ and the corresponding $\gnow(\tau)$ for a number of current times $\tnow$
 in a numeric example which is described in more detail in Section~\ref{sec:examples}.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{ghist1fig2}
+\includegraphics[width=\textwidth]{ghist1fig2T}
 \caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
@@
 and costs $c_u = 1$, $c_p = 0.2$.}
-\label{fig:ghist1fig2}
+\label{fig:ghist1fig2T}
 \end{figure}
@@
 the optimal moment of maintenance on a prospective time scale.
-The minimal prospective unit cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
+The minimal ***prospective unit cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
 thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
@@
 %$\gstarnow$ increases over time since 
-Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
+***Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
 This gives the expected unit cost rate calculated over the full time since system start-up,
@@
 since then, system failure becomes much more likely, leading to a higher $\gstarnow$.
-Figure~\ref{fig:tauhist1fig2} illustrates these relations in the scenario depicted in Figure~\ref{fig:ghist1fig2}.
+Figure~\ref{fig:tauhist1fig2} illustrates these relations in the scenario depicted in Figure~\ref{fig:ghist1fig2T}.
 
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{tauhist1fig2}
-\caption{$\tausnow$, $\tstarnow = \tnow + \tausnow$, $\gstarnow = \gnow(\tausnow)$,
-and the total unit cost rate $\gtotalnow$ as functions of $\tnow$
+\begin{SCfigure}
+\centering
+\includegraphics[width=0.5\textwidth]{tauhist1fig2T}
+\caption[t]{$\tausnow$, $\tstarnow = \tnow + \tausnow$ and $\gstarnow = \gnow(\tausnow)$
+%and the total unit cost rate $\gtotalnow$ as functions of $\tnow$
 for the system depicted in Figure~\ref{fig:brakesys-layout},
@@
 %$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
-$\tausnow$ (top left panel) first decreases, then starts to increase during failure-free periods,
+***$\tausnow$ (left panel) first decreases, then starts to increase during failure-free periods,
 dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
@@
 up from $0.055$ for repair scheduled at time $5.33$, as cost-optimal at time $\tnow = 3.9$.}
-\label{fig:tauhist1fig2}
-\end{figure}
+\label{fig:tauhist1fig2T}
+\end{SCfigure}
 
@@
 
-Here, we illustrate our procedure under three different exemplary failure time histories.
-(A more systematic simulation study is then presented in Section~\ref{sec:sim}.)
+Below, we illustrate our procedure under three different exemplary failure time histories;
+a more systematic simulation study is subsequently presented in Section~\ref{sec:sim}.
 
@@
 all other failure times are right-censored.
-This is the failure history already used for Figures~\ref{fig:ghist1fig2} and \ref{fig:tauhist1fig2}.
+This is the failure history already used for Figures~\ref{fig:ghist1fig2T} and \ref{fig:tauhist1fig2T}.
 Here, failures observed for type $C$ are thus considerably later than expected,
@@
 In total, due to the late type $C$ failures, prior assumptions turn out to be somewhat pessimistic.
-This is reflected in Figure~\ref{fig:tauhist1fig2},
+This is reflected in Figure~\ref{fig:tauhist1fig2T},
 where $\tausnow$ first decreases but then tends to increase during failure-free periods,
@@
 
-***move some text from figure~\ref{fig:tauhist1fig2} caption to here?***
+***move some text from figure~\ref{fig:tauhist1fig2T} caption to here?***
 
 \begin{figure}
-\includegraphics[width=\textwidth]{tauhist1fig3}
+\includegraphics[width=\textwidth]{tauhist1fig3T}
 \caption{Illustration of the gains due to the parameter update at each $\tnow$,
@@
 This is because the adaptive algorithm recognizes that system components are more reliable than expected,
-leading to lower current (lower left panel) and total (lower right panels) expected unit cost rates.}
-\label{fig:tauhist1fig3}
+***leading to lower current (lower left panel) and total (lower right panels) expected unit cost rates.}
+\label{fig:tauhist1fig3T}
 \end{figure}
 
-The effect of this continuous parameter update is illustrated in Figure~\ref{fig:tauhist1fig3}.
-There, the results as seen already in Figure~\ref{fig:tauhist1fig2} are compared
+The effect of this continuous parameter update is illustrated in Figure~\ref{fig:tauhist1fig3T}.
+There, the results as seen already in Figure~\ref{fig:tauhist1fig2T} are compared
 to the case when component parameters are not updated,
@@
 %***so dynamic but not adaptive?***
-We see that $\tausnow$ is steadily decreasing in the no update case,
+***We see that $\tausnow$ is steadily decreasing in the no update case,
 with the jumps at component failure times being less pronounced than in the update case.
@@
 Consequently, the difference between the continuous update case and the no update case is small,
-as visualized in Figure~\ref{fig:tauhist2fig3}.
-$\tausnow$ values are slightly lower when component parameters are updated,
+as visualized in Figure~\ref{fig:tauhist2fig3T}.
+***$\tausnow$ values are slightly lower when component parameters are updated,
 reflecting the slightly too early failures of type $P$ components.
@@
 in case of the first failure history
-(note the differing vertical and horizontal scales in Figures~\ref{fig:tauhist1fig3} and \ref{fig:tauhist2fig3}).
+(note the differing vertical and horizontal scales in Figures~\ref{fig:tauhist1fig3T} and \ref{fig:tauhist2fig3T}).
 
 \begin{figure}
-\includegraphics[width=\textwidth]{tauhist2fig3}
-\caption{Effect of the continuous parameter update for the second failure history ($C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$),
-containing slightly early failures of type $P$ components.
-With observed failure behaviour more or less in line with expectations,
+\includegraphics[width=\textwidth]{tauhist2fig3T}
+\caption{Effect of the continuous parameter update for the second failure history ($C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$)
+which is more or less in line with expectations.
+%containing slightly early failures of type $P$ components.
+***With observed failure behaviour more or less in line with expectations,
 the model with and without continuous update perform similarly,
-unlike in case of the first failure history as depicted in Figure~\ref{fig:tauhist1fig3},
+unlike in case of the first failure history as depicted in Figure~\ref{fig:tauhist1fig3T},
 where updating gave considerable gains.}
-\label{fig:tauhist2fig3}
+\label{fig:tauhist2fig3T}
 \end{figure}
@@
 
+***see Figure~\ref{fig:tauhist4fig3T}
+
 ***without update consistently higher, adaptive algorithm takes surprisingly early failures into account,
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{tauhist4fig3}
+\includegraphics[width=\textwidth]{tauhist4fig3T}
 \caption{Effect of the continuous parameter update for the third failure history,
-containing very early failures ($C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$).}
-\label{fig:tauhist4fig3}
+containing very early failures ($C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$).
+***more }
+\label{fig:tauhist4fig3T}
 \end{figure}
@@
 
-\iffalse
 Case 1: failure behaviour as expected,
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{br1sim1fig5}
+\includegraphics[width=\textwidth]{br1sim1fig5Tt01}
 \caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
 where failure times are simulated according to prior parameters.}
-\label{fig:br1sim1fig5}
+\label{fig:br1sim1fig5Tt01}
 \end{figure}
@@
 failure times simulated using
-$\lambda_k = 0.5 \ykz$ (Figure~\ref{fig:br1sim2fig5}) or
-$\lambda_k = 0.2 \ykz$ (Figure~\ref{fig:br1sim4fig5}).
+$\lambda_k = 0.5 \ykz$ (Figure~\ref{fig:br1sim2fig5Tt01})
 
 \begin{figure}
-\includegraphics[width=\textwidth]{br1sim2fig5}
+\includegraphics[width=\textwidth]{br1sim2fig5Tt01}
 \caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
 where failure times are simulated as being earlier ($0.5 \times$ MTTF) than expected.}
-\label{fig:br1sim2fig5}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{br1sim4fig5}
-\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
-where failure times are simulated as being much earlier ($0.2 \times$ MTTF) than expected.}
-\label{fig:br1sim4fig5}
+\label{fig:br1sim2fig5Tt01}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{br1sim3fig5}
+%\includegraphics[width=\textwidth]{br1sim3fig5Tt01}
 \caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
 where failure times are simulated as being later ($2 \times$ MTTF) than expected.}
-\label{fig:br1sim3fig5}
+\label{fig:br1sim3fig5Tt01}
 \end{figure}
-\fi
-
+
+% ------------- overview figures ----------------------------------
+\iffalse
 \begin{figure}
@@
 \end{figure}
+\fi
 

### 2016-11-29 exempl-fail-hist-2.R

@@ -48,11 +48,11 @@ names(br1taus1fineT)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
                                cstar = expression(g['*']^(t[now])),
                                ctotal = expression(g[total]^(t[now])),
                                relstar = expression(paste(R[sys]^(t[now]),(t['*']^(t[now])))))
-tauhist1fig2T <- ggplot(melt(br1taus1fineT[-6], "tnow"), aes(x = tnow, y = value)) + xlab(expression(t[now])) +
+tauhist1fig2T <- ggplot(melt(br1taus1fineT[-c(5,6)], "tnow"), aes(x = tnow, y = value)) + xlab(expression(t[now])) +
   geom_line(aes(group = variable))  + geom_point(aes(group = variable), size = 0.15) +
-  facet_wrap(~ variable, nrow = 2, scales = "free_y", labeller = label_parsed) +
+  facet_wrap(~ variable, nrow = 3, scales = "free_y", labeller = label_parsed) +
   theme(axis.title.y = element_blank())
-pdf("tauhist1fig2T.pdf", width = 6, height = 4)
+pdf("tauhist1fig2T.pdf", width = 3.5, height = 7)
 tauhist1fig2T
 dev.off()
 #br1taus1fine[40:41,]
@@ -63,14 +63,14 @@ names(br1taus1fineprT)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
                                  cstar = expression(g['*']^(t[now])),
                                  ctotal = expression(g[total]^(t[now])),
                                  relstar = expression(paste(R[sys]^(t[now]),(t['*']^(t[now])))))
-br1taus1prpoT <- rbind(data.frame(melt(br1taus1fineT[-6], "tnow"), variable2 = "Parameter update"),
-                       data.frame(melt(br1taus1fineprT[-6], "tnow"), variable2 = "No parameter update"))
+br1taus1prpoT <- rbind(data.frame(melt(br1taus1fineT[-c(5,6)], "tnow"), variable2 = "Parameter update"),
+                       data.frame(melt(br1taus1fineprT[-c(5,6)], "tnow"), variable2 = "No parameter update"))
 tauhist1fig3T <- ggplot(br1taus1prpoT, aes(x = tnow, y = value)) + xlab(expression(t[now])) +
[…]

### 2016-11-29 cbm-sim.R
age based 1 cycle

@@ -157,10 +157,109 @@ simNcycle <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, thresh, s
   return(list(res = res2, nnyn = nnynlist, tfunc = tfuncvec, tend = tendvec, costrate = costratevec))
 }
 
+# simulate one operational cycle with age-based maintenance policy
+# sys      system reliability block diagram at t = 0
+# ctypes   list giving the types of components in the system, same format as
+#          used for setCompTypes(), but needs the same order as in survsign table (!!!)
+# compfts  list with elements named like the vertices in sys, giving the (simulated)
+#          failure time of this component -- assumed that no failure times == 0
+# n0y0     list of K prior parameter pairs c(n0,y0)
+# beta     vector of K fixed weibull shape parameters
+# tnowstep time interval after which system functioning is re-evaluated
+# hor      how many time units from tnow into the future to calculate sysrelnow
+# seqlen   at how many points to evaluate sysrelnow
+# cu       cost of unplanned (corrective) repair action
+# cp       cost of planned (preventive) repair action, cp < cu
+# onecycle whether to use the one-cycle criterion or the renewal-based one
+sim1cycleAgebased <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, seqlen = 101,
+                              cu = 1, cp = 0.2, onecycle = TRUE){
+  K <- length(ctypes)
+  ftschron <- sort(unlist(compfts)) # when something fails
+  ftschroni <- 1
+  # get taustar: initial arguments for gnowhor
+  cat("Calculating maintenance interval ... ")
+  sign <- computeSystemSurvivalSignature(sys)
+  fts0 <- as.list(rep(list(NULL), K))
+  gvec <- gnowhor(sign, n0y0, beta, fts0, tnow = 0, hor = hor, seqlen = seqlen, cu = cu, cp = cp, onecycle = onecycle)
+  taustar <- gvec$tau[which.min(gvec$gnow)]
+  cat("taustar =", taustar, "\n")
+  # set up loop over component failure times: assumes that system is not failed initially (before first component failure)
+  gotonext <- TRUE
+  failed <- FALSE
+  res <- data.frame(tnow = 0, failed = FALSE) # initialize results data frame (assumed that initial system functions)
+  while(gotonext){
+    # when is the next component failure?
[…]

### 2016-11-29 sim-study.R

@@ -48,6 +48,12 @@ dev.off()
 #br1simN51c <- sim1cycleCorrective(sys = br, ctypes = brctypes, compfts = testfts, tnowstep = 0.1)
 #br1simN51c <- simNcycleCorrective(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[1]], tnowstep = 0.1)
 
+# test sim age-based
+testfts <- lapply(br1sim5cycle20data2[[1]], function(x) x[1])
+plotfts(testfts)
+br1simN51a <- sim1cycleAgebased(sys = br, ctypes = brctypes, compfts = testfts, n0y0 = br1n0y0, beta = br1beta,
+                                tnowstep = 0.1, hor = 4, seqlen = 401)
+
 br1sim1 <- list()     # our model
 br1sim1pr <- list()   # do not update params during cycle, but at end of cycle 
 br1sim1prpr <- list() # never update params

### 2016-11-29 weibull-sys-functions.R

@@ -251,10 +251,10 @@ compfts2df <- function(compfts, maxtnow = NA){
 #          equal to last failure time if not given.
 #          If set smaller than last failure time, maxtnow is the censoring time
 #          for all failure times after maxtnow
-plotfts <- function(compfts, maxtnow = NA, pointsize = 1, tlabelvjust = -1){
+plotfts <- function(compfts, maxtnow = NA, pointsize = 1, tlabelvjust = -1, labelround = 2){
   compftsdf <- compfts2df(compfts = compfts, maxtnow = maxtnow)
   ggplot(compftsdf, aes(x = Components, y = t, ymin = rep(0, dim(compftsdf)[1]), ymax = t)) + geom_linerange() +
-    geom_pointrange(aes(shape = factor(cens)), size = pointsize) + geom_text(aes(label = t, vjust = tlabelvjust)) + 
+    geom_pointrange(aes(shape = factor(cens)), size = pointsize) + geom_text(aes(label = round(t, labelround), vjust = tlabelvjust)) + 
     coord_flip() + scale_shape_manual(values = c(19, 1), label = c("Yes", "No"), name = "Failure")
 }
 

### 2016-11-29 cbm-sim.R
age based N cycles

@@ -255,10 +255,47 @@ sim1cycleAgebased <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, s
   list(res = res, nnyn = nnyn, tfunc = tfunc, tend = tnow, costrate = costrate)
 }  
 
-# function to calculate tend, tfunc, costrate for age-based policy from simNcycle object
-#simNcycleAgebased <- function(simNcycleobj, thresh, cu = 1, cp = 0.2){
-#  
-#}
+# simulate N operational cycles with age-based maintenance policy
+# i.e. updated parameters from one cycle are used as prior parameters in next cycle
+# sys      system reliability block diagram at t = 0
+# ctypes   list giving the types of components in the system, same format as
+#          used for setCompTypes(), but needs the same order as in survsign table (!!!)
+# compfts  list with elements named like the vertices in sys, giving the N (simulated)
+#          failure times of this component -- assumed that no failure times == 0
+# n0y0     list of K prior parameter pairs c(n0,y0)
+# beta     vector of K fixed weibull shape parameters
+# tnowstep time interval after which current system reliability is re-evaluated
+# hor      how many time units from tnow into the future to calculate sysrelnow
+# seqlen   at how many points to evaluate sysrelnow
+# cu       cost of unplanned (corrective) repair action
+# cp       cost of planned (preventive) repair action, cp < cu
+# onecycle whether to use the one-cycle criterion or the renewal-based one
+simNcycleAgebased <- function(sys, ctypes, compfts, n0y0, beta, tnowstep, hor, seqlen = 101, 
+                              cycleupdate = TRUE, cu = 1, cp = 0.2, onecycle = TRUE){
+  N <- length(compfts[[1]])
+  if (any(sapply(compfts, length) != N))
+    stop("each element of compfts must contain the same number of failure times")
+  compftsi <- lapply(compfts, function(x) x[1])
+  n0y0i <- n0y0
+  res <- res2 <- nnyn <- list()
+  for (i in 1:N){
+    cat("Operational cycle", i, "\n")
+    res[[i]] <- sim1cycleAgebased(sys = sys, ctypes = ctypes, compfts = compftsi, n0y0 = n0y0i, beta = beta,
+                                  tnowstep = tnowstep, hor = hor, seqlen = seqlen, cu = cu, cp = cp, onecycle = onecycle)
[…]

### 2016-11-29 sim-study.R

@@ -49,10 +49,12 @@ dev.off()
 #br1simN51c <- simNcycleCorrective(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data1[[1]], tnowstep = 0.1)
 
 # test sim age-based
-testfts <- lapply(br1sim5cycle20data2[[1]], function(x) x[1])
-plotfts(testfts)
-br1simN51a <- sim1cycleAgebased(sys = br, ctypes = brctypes, compfts = testfts, n0y0 = br1n0y0, beta = br1beta,
-                                tnowstep = 0.1, hor = 4, seqlen = 401)
+#testfts <- lapply(br1sim5cycle20data2[[1]], function(x) x[1])
+#plotfts(testfts)
+#br1simN51a <- sim1cycleAgebased(sys = br, ctypes = brctypes, compfts = testfts, n0y0 = br1n0y0, beta = br1beta,
+#                                tnowstep = 0.1, hor = 4, seqlen = 401)
+#br1simN51a <- simNcycleAgebased(sys = br, ctypes = brctypes, compfts = br1sim5cycle20data2[[1]], n0y0 = br1n0y0,
+#                                beta = br1beta, tnowstep = 0.1, hor = 4, seqlen = 401, cycleupdate = TRUE)
 
 br1sim1 <- list()     # our model
 br1sim1pr <- list()   # do not update params during cycle, but at end of cycle 

### 2016-11-29 sim-study-2.R
simulation figures all in one

@@ -1,7 +1,6 @@
 # --------------------------------------------------------------------------- #
 # CBM systems paper - code for example figs - simulation study
-# using total unit cost rate now!
-# choose lower thresh now???
+# using total unit cost rate & thresh = 0.1
 # --------------------------------------------------------------------------- #
 
 source("cbm-sys-other.R")
@@ -31,7 +30,20 @@ simlabeller2 <- as_labeller(c(nfails = "Number of system failures",
                               meancostrate = "Average unit cost rate",
                               "Continuous update" = "Continuous update",
                               "Cycle end update" = "Cycle end update",
-                              "No update" = "No update"))
+                              "No update" = "No update",
+                              "Age-based with update" = "Age-based with update",
+                              "Age-based without update" = "Age-based without update",
+                              "Corrective" = "Corrective"))
+
+simlabeller3 <- as_labeller(c(nfails = expression(n[failures]),
+                              meantend = expression(bar(t)[sys]),
+                              meancostrate = expression(bar(g)),
+                              "Continuous update" = "CBMcpu",
+                              "Cycle end update" = "CBMepu",
+                              "No update" = "CBMnpu",
+                              "Age-based with update" = "ABMepu",
+                              "Age-based without update" = "ABMnpu",
+                              "Corrective" = "CM"))
 
 # sim 1: data fits to priors
 # --------------------------
@@ -105,6 +117,54 @@ br1sim1fig5Tt01 <- ggplot(melt(br1sim1Tt01summaryall, c("id", "sim")), aes(x = i
   xlab("5-cycle repetition number") + theme(axis.title.y = element_blank())
 pdf("br1sim1fig5Tt01.pdf", width = 6, height = 6)
 br1sim1fig5Tt01
+dev.off()
+
+# corrective and age based
+
+br1sim1a <- list()   # age-based policy with parameter update
[…]

### 2016-11-29 cbm-rbd-paper.tex
simulation figures ready

@@
 \newcommand{\gtotalnow}{g_\text{total}^{(\tnow)}}
+\newcommand{\esys}{e_\text{sys}}
+\newcommand{\mrsys}{\bar{r}_\text{sys}}
 
@@
 Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
-as is visible in the top left panel of Figure~\ref{fig:tauhist1fig2}.
+as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T}.
 %An alternative would be to update $\tausnow$ only when a component fails,
@@
 
+$\esys$ is the number of system failures,
+$\mrsys$ is the mean realized system runtime (I called this 'cycle length' before),
+$\bar{g}$ is the mean realized unit cost rate.
+
+CBM = condition-based maintenance
+ABM = age-based maintenance
+CM = corrective maintenance
+cpu = continuous parameter update
+epu = end of cycle parameter update
+npu = no parameter update
+
 Case 1: failure behaviour as expected,
@@
 
+Obviously, CM has always 5 system failures in the 5 cycles, while CBM and ABM (mostly) avoid system failures.
+Mean system runtimes are longest for CM because it runs the system until failure, but this leads to the highest mean unit cost rates.
+CBM with continuous parameter update has the lowest mean unit cost rate since it has the longest system runtimes without failures.
+The age-based policy without parameter update always schedules maintenance for $\tau_*^{(0)} = 1.6$, and as the system does not fail before this time in any of the simulations, the system runtime is always 1.6 and the unit cost rate is $0.2 / 1.6 = 0.125$.
+
 \begin{figure}
-\includegraphics[width=\textwidth]{br1sim1fig5Tt01}
+\includegraphics[width=\textwidth]{br1sim1fig5Tt01ac}
 \caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{br1sim2fig5Tt01}
+\includegraphics[width=\textwidth]{br1sim2fig5Tt01ac}
 \caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
@@
 \begin{figure}
-%\includegraphics[width=\textwidth]{br1sim3fig5Tt01}
+\includegraphics[width=\textwidth]{br1sim3fig5Tt01ac}
 \caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,

### 2016-11-30 cbm-rbd-paper.tex
rework sections 3,4,5

@@
   \toprule
-M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
+$l_M$ & $l_H$ & $l_C$ & $l_P$ & $\Phi$ & \quad & $l_M$ & $l_H$ & $l_C$ & $l_P$ & $\Phi$\\ 
   \midrule
@@
 We consider the well-known Weibull model for component lifetimes,
-which is used in a wide variety of reliability studies ***more motivation Weibull***. 
+which is used in a wide variety of reliability studies \textbf{***more motivation Weibull***}. 
 To keep things simple, we assume that the shape parameter of the Weibull distribution is known,
@@
 
-The model description in this Section follows closely \cite{2016:walter-coolen},
+The model description below follows closely \cite{2016:walter-coolen},
 who presented the same residual life distribution model.
-However, \cite{2016:walter-coolen} do not consider any maintenance policies,
+However, \cite{2016:walter-coolen} did not consider any maintenance policies,
 and focus instead on a generalization of the RLD model using sets of priors for the component models.
@@
 together with the Bayesian update procedure which allows to include
-expert knowledge, component tests, and information from the currently monitored components in the system.
+expert knowledge, component tests, and information from the monitored components in the system.
 
@@
 %(the upper index ${}\uz$ is used to indicate that these are prior parameters)
-because they are more simple to interpret.
+because they are more easy to interpret.
 They are defined as
@@
 &
-\ykp &=  \frac{\nk \yk + \tautk}{\nk + e_k}\,,
+%\ykp &=  \frac{\nk \yk + \tautk}{\nk + e_k}\,,
+\ykp &=  \frac{\nk}{\nk + e_k}\, \yk + \frac{e_k}{\nk + e_k}\, \frac{\tautk}{e_k}\,,
 \label{eq:ig-update}
@@
 At any time $\tnow > 0$,
-all non-failed components correspond to a right censored observation $\tpnow$;
+all non-failed components contribute a right censored observation $\tpnow$;
 any failed components instead contribute a fully observed, non-censored lifetime,
@@
 We can thus collect these observations, as of $\tnow$, in a vector
-$\vectknow = (t_{k,1}, \ldots, t_{k,e_k}, \tpnow, \ldots, \tpnow)$,
+$\vectknow = (t_{k,1}, \ldots, t_{k,\eknow}, \tpnow, \ldots, \tpnow)$,
 containing $\cknow$ right-censored observations $\tpnow$.
@@
 \end{align}
-Substituting \eqref{eq:weibullcondprob} and the posterior \eqref{eq:ig-update-alpha} using $\vectknow$,
-written in terms of the updated parameters $\nknow$ and $\yknow$,
-into \eqref{eq:postpredtnow}, we get
+Consider the posterior \eqref{eq:ig-update-alpha} obtained using observations $\vectknow$,
+written in terms of the updated parameters $\nknow$ and $\yknow$.
+Substituting this posterior and \eqref{eq:weibullcondprob} into \eqref{eq:postpredtnow}, we get
 \begin{align}
@@
 we can use the method from Section~\ref{sec:sysrel}
-to determine the system reliability distribution $\Rsysnow(t)$,
+to determine the system residual life distribution (RLD) $\Rsysnow(t)$,
 giving us the probability that the system functions at times $t > \tnow$,
@@
 \end{align}
-Since this is the system reliability distribution conditional on the system surviving until $\tnow$,
-we have that $\Rsysnow(\tnow) = 1$.
+Since this is the distribution of system reliability conditional on the system surviving until $\tnow$,
+we have that $\Rsysnow(\tnow) = 1$ for any $\tnow$.
 Note that if one or several components have failed by $\tnow$,
 the system layout changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$,
-so we denote the updated survival signature by $\Phinow(l_1,\ldots,l_K)$.
+so we denote the current survival signature by $\Phinow(l_1,\ldots,l_K)$.
 
@@
 
-Next, we will describe how an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
+Next, we will describe an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
 a current residual life distribution,
@@
 that resembles a CBM policy.
-However, instead of determining a threshold for a degradation signal like in usual CBM approaches,
+Define the set of evaluation time points as $\{ \tnow : \tnow = m \delta, m \in \naturals_0\}$,
+%where $m = 0, 1, 2, \ldots$,
+%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
+with $\delta$ a sufficiently small time increment.
+Instead of determining a threshold for a degradation signal like in usual CBM approaches,
 we determine, for each present time $\tnow$,
@@
 A preventive maintenance action is initiated
-as soon as $\tausnow$ decreases below $\tthresh$,
-a time span chosen to reflect operational practicalities.
+as soon as $\tausnow$ decreases below $\delta$.
+%continuing to the the next evaluation point $\tnow$ would carry the risk 
+%a time span chosen to reflect operational practicalities.
 This operational procedure is described in more detail in Section~\ref{sec:operationalprocedure};
 a graphical overview is given in Figure~\ref{fig:procedure}.
-
-***comments about `nervousness' of $\tausnow$ here or in \ref{sec:operationalprocedure}?
-common cause failures currently not in the model, but will seriously influence residual life distribution,
-see comments in Outlook (Section~\ref{sec:outlook})***
 
@@
 or a failure of the system occurs, with subsequent corrective maintenance.)
-This criterion, as described in Section~\ref{sec:costrate} below in detail,
-only assumes that $\Rsysnow(t)$ is given,
+This criterion, as detailed in Section~\ref{sec:costrate} below,
+%only assumes that $\Rsysnow(t)$ is given,
+only assumes that a RLD is given,
 and thus is not tied to our choice of component model.
-One could also consider other optimality criteria to determine $\tausnow$.
-When safety is paramount one could, e.g., determine $\tausnow$ such that
+One could also consider alternative optimality criteria to determine $\tausnow$;
+when safety is paramount one could, e.g., determine $\tausnow$ such that
 the probability of system failure is at most at some very low pre-determined level.
@@
 Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
-and a small simulation study is discussed in Section~\ref{sec:sim}.
+and a small simulation study is presented in Section~\ref{sec:sim}.
 
@@
  font=\footnotesize,
- box/.style={draw, rectangle, thick, minimum height=6mm, minimum width=26mm, rounded corners=2mm},
+ box/.style={draw, rectangle, thick, minimum height=6mm, minimum width=28mm, rounded corners=2mm},
  pfeil/.style={-latex', very thick}]
@@
 \node (sysfail) [box, right=of startup]     {system failed?};
-\node (tauchck) [box, below=6mm of sysfail] {$\tausnow < \tthresh$?};
-\node (gotonxt) [box, below=6mm of tauchck] {\parbox{15ex}{\centering continue to\\ next $\tnow$}};
-\draw [thick, dashed, rounded corners=2mm] ($(gotonxt.south east) + (2mm,-1mm)$) rectangle ($(sysfail.north west) + (-5mm,1mm)$) node[above left=0mm and -14mm] {each $\tnow$};
+\node (tauchck) [box, below=6mm of sysfail] {$\tausnow < \delta$?};
+\node (gotonxt) [box, below=6mm of tauchck] {\parbox{17ex}{\centering continue to\\ $\tnow = (m+1)\delta$}};
+\draw [thick, dashed, rounded corners=2mm] ($(gotonxt.south east) + (2mm,-1mm)$) rectangle ($(sysfail.north west) + (-5mm,1mm)$) node[above left=0mm and -33mm] {each $\tnow = m \delta, m \in \naturals_0$};
 \node [above left=0mm and -8mm of startup] {$t=0$};
-\node (correct) [box, right=of sysfail, minimum width=18mm] {\parbox{14ex}{\centering corrective\\ maintenance\\ (cost $c_u$)}};
+\node (correct) [box, right=of sysfail, minimum width=18mm] {\parbox{14ex}{\centering corrective\\ maintenance\\ (cost $c_c$)}};
 \node (prevent) [box, right=of tauchck, minimum width=18mm] {\parbox{14ex}{\centering preventive\\ maintenance\\ (cost $c_p$)}};
@@
 During a cycle,
-$\tausnow$ is recalculated at a frequency small enough to be negligible on the system lifetime scale.
-This is feasible because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
-and determine $\tausnow$ with a simple grid search.
+$\tausnow$ is recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$,
+where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
+Frequent recalculation of $\tausnow$ is feasible
+when evaluation of the RLD is fast.
+Then, by evaluating the unit cost rate function $\gnow(\tau)$ on a discrete grid,
+$\tausnow$ can be approximated with a simple grid search.
+%because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
+%and determine $\tausnow$ with a simple grid search.
 Updating $\tausnow$ frequently is useful because,
@@
 Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
-as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T}.
+as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T},
+which gives a numerical example described in more detail in Section~\ref{sec:examples}.
 %An alternative would be to update $\tausnow$ only when a component fails,
@@
 
-A preventive maintenance action is triggered as soon as $\tausnow$ falls below $\tthresh$,
-indicating that the optimal moment of maintenance is so close to present time $\tnow$
-that a preventive maintenance action should be carried out immediately, incurring cost $c_p$.
-When the system fails, instead a corrective maintenance action is carried out, incurring cost $c_u$.
-The current cycle ends when either preventive and corrective maintenance is carried out,
+A preventive maintenance action is triggered at the smallest $m \in \naturals_0$
+such that $\tausnow < \delta$ for $\tnow = m \delta$.
+When $\tausnow$ falls below $\delta$,
+the optimal moment of maintenance is so close to present time $\tnow$
+that in continuing to the next $\tnow = (m+1)\delta$, one exceeds the optimal system failure risk
+as determined by the trade-off made by $\gnow(\cdot)$.
+This means that a preventive maintenance action should be carried out at $\tnow = m\delta$, which incurs cost $c_p$.
+When the system fails, instead a corrective maintenance action is carried out, incurring cost $c_c$.
+The current cycle ends when either preventive or corrective maintenance is carried out,
 and a new cycle starts with a system with all components (as good as) new.
@@
 exploring such selective replacement schemes is out of scope for this paper,
-since optimizing over replacement schemes is, in our view, a higly interesting topic on its own
-that would merit a separate investigation.
-We will comment on this topic in the Outlook (Section~\ref{sec:outlook}).
+since optimizing over replacement schemes is, in our view, a higly interesting topic
+that merits an investigation of its own,
+and we will comment on this in the Outlook (Section~\ref{sec:outlook}).
 
@@
 Longer downtime and other negative effects of corrective maintenance
-are instead accounted for through the costs parameters used in the trade-off leading to $\tausnow$,
-as described in more detail below.
+are instead accounted for through the costs parameters $c_p$ and $c_c$ used in the trade-off leading to $\tausnow$,
+as described next.
 
@@
 
-Let $c_p$ be the cost of preventive maintenance, and $c_u$ the cost of corrective (unplanned, breakdown) maintenance, where $c_p < c_u$.
+Let $c_p$ be the cost of preventive maintenance, and $c_c$ the cost of corrective (unplanned, breakdown) maintenance, where $c_p < c_c$.
 Usually, set-up costs, work costs and downtime costs are much higher for corrective maintenance,
-such that often, $c_p \ll c_u$.
-CBM is known to be most effective when the ratio $c_p / c_u$ is small
-(***cite de Jonge and Teunter working paper on relative benefit of CBM).
+such that often, $c_p \ll c_c$.
+CBM is known to be most effective when the ratio $c_p / c_c$ is small
+(\textbf{***cite de Jonge and Teunter working paper on relative benefit of CBM}).
 %
 As discussed above,
-we assume that both $c_p$ and $c_u$ include the cost of replacing all components in the system,
+we assume that both $c_p$ and $c_c$ include the cost of replacing all components in the system,
 such that every time a new cycle starts, the system is in the same state with all components (as good as) new.
@@
 which gives the probability that the system functions at time $t$ given that it functions at $\tnow$,
-also $\fsysnow(t)$ is a conditional density.
-In particular, we have $\fsysnow(t) = 0$ for all $t \le \tnow$.
-
-*** change to total cost rate
-
-Conditional on the realization $\tsysnow > \tnow$ of $\Tsysnow$, the unit cost rate is 
+also $\fsysnow(t)$ is a conditional density,
+with support $\{t \in \reals : t > \tnow \}$.
+%In particular, we have $\fsysnow(t) = 0$ for all $t \le \tnow$.
+
+Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate is 
 \begin{align}
@@
 \begin{cases}
-c_p / \tau               & \text{if } \tsysnow \ge \tnow + \tau \\
-c_u / (\tsysnow - \tnow) & \text{if } \tnow < \tsysnow  <  \tnow + \tau \,.
+%c_p / \tau               & \text{if } \tsysnow \ge \tnow + \tau \\
+%c_u / (\tsysnow - \tnow) & \text{if } \tnow < \tsysnow  <  \tnow + \tau \,.
+c_p / (\tnow + \tau) & \text{if } \hspace{7.4ex} \tsysnow \ge \tnow + \tau \\
+c_u /  \tsysnow      & \text{if }        \tnow < \tsysnow  <  \tnow + \tau \,.
 \end{cases}
@@
 where $0$ corresponds to the time of system start-up.
-Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate being***
+Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate
 \begin{align}
 \gnow(\tau) &= \E[g(\tau \mid \Tsysnow)] \nonumber\\ 
-            &= \frac{c_p}{\tau} \Rsysnow(\tnow + \tau) + c_u \int_0^\tau \frac{1}{\theta} \fsysnow(\tnow + \theta) \dd \theta\,,
+            &= \frac{c_p}{\tnow + \tau} \Rsysnow(\tnow + \tau)
+              + c_u \int_0^\tau \frac{1}{\tnow + \theta} \fsysnow(\tnow + \theta) \dd \theta\,.
 \label{eq:gtnowtau}
 \end{align}
-and $\tausnow = \arg\min \gnow(\tau)$.
-Thus $\tausnow$, the optimal moment of maintenance as of $\tnow$,
-incorporates all that is known at current time $\tnow$.
-%The lower index $\tnow$ of $\tausnow$ emphasizes that
-%depends on $\tnow$, and also on the history of the system.
+Thus $\gnow(\tau)$ gives the unit cost rate that we expect to incur over the complete operational cycle
+when, at time $\tnow$, we schedule preventive maintenance for time $\tnow + \tau$,
+so $\gnow(\tau)$ trades off the risk of system failure before $\tnow + \tau$
+with the gains we could reap when the system survives until $\tnow + \tau$.
 Figure~\ref{fig:ghist1fig2T} shows $\Rsysnow(t)$ and the corresponding $\gnow(\tau)$ for a number of current times $\tnow$
 in a numeric example which is described in more detail in Section~\ref{sec:examples}.
-%illustrates the derivation of $\tausnow$ .
 
@@
 
-Minimizing $\gnow(\tau)$ leads to $\tausnow$,
-the optimal moment of maintenance on a prospective time scale.
-The minimal ***prospective unit cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
-thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
-i.e., for what happens beyond current time $\tnow$.
+Finally, $\tausnow := \arg\min \gnow(\tau)$
+is the cost-optimal moment of maintenance as of $\tnow$,
+incorporating all that is known at current time $\tnow$.
+%The lower index $\tnow$ of $\tausnow$ emphasizes that
+%depends on $\tnow$, and also on the history of the system.
+%illustrates the derivation of $\tausnow$ .
+%Minimizing $\gnow(\tau)$ leads to $\tausnow$,
+%the optimal moment of maintenance on a prospective time scale.
+The minimal expected unit cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
+thus is, as of $\tnow$, the lowest unit cost rate for the current operational cycle
+that we can expected to attain.
+%attainable for the span of the remaining lifetime of the system,
+%i.e., for what happens beyond current time $\tnow$.
 %$\gstarnow$ increases over time since 
-***Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
-This gives the expected unit cost rate calculated over the full time since system start-up,
-under the assumption that maintenance is scheduled for $\tstarnow := \tnow + \tausnow$.
-$\gtotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
-However, when many (or few but critical) components fail, $\gtotalnow$ may increase,
-since then, system failure becomes much more likely, leading to a higher $\gstarnow$.
-Figure~\ref{fig:tauhist1fig2} illustrates these relations in the scenario depicted in Figure~\ref{fig:ghist1fig2T}.
-
-We will describe next how we numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
+%***Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
+%This gives the expected unit cost rate calculated over the full time since system start-up,
+%under the assumption that maintenance is scheduled for $\tstarnow := \tnow + \tausnow$.
+$\gstarnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time period.
+However, when many (or few but critical) components fail, $\gstarnow$ may increase,
+since then, system failure becomes much more likely, leading to a higher risk of incurring the corrective maintenance cost $c_c$.
+Figure~\ref{fig:tauhist1fig2T} illustrates these relations in the scenario depicted in Figure~\ref{fig:ghist1fig2T}.
+
+As can be seen there and in the numerical examples in Section~\ref{sec:examples} below,
+for continuous component lifetime distributions,
+$\tausnow$ is a smooth function of $\tnow$ during periods where no component fails,
+with discrete jumps at component failure times.
+The size of the jump depends on the relevance of the failed component for the current system reliability.
+Common cause failures, i.e., failures of several components at the same time due to a shared root cause,
+are currently not accounted for in our model, as we assume component failures to be mutually independent
+given the Weibull parameters.
+Common cause failures will seriously influence the RLD and thus $\tausnow$,
+and we will comment on possible extensions in the Outlook (Section~\ref{sec:outlook}).
+
+Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
 for our choice of component model.
@@
 %$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
-***$\tausnow$ (left panel) first decreases, then starts to increase during failure-free periods,
-dropping significantly at the failures of components $P_2$, $P_3$ and $H$ only.
-If $\tthresh = 1$, the drop of $\tausnow$ from $1.43$ to $0.91$ at $\tnow = 4$ would trigger a maintenance action
-at (absolute) time $5$.
+$\tausnow$ (top panel) decrease weakens and attains a near-constant speed from about $\tnow = 2$ during failure-free periods,
+with discrete drops at the failures of components $P_2$, $P_3$ and $H$ only.
+%With the failure of $H$ at time $\tnow = 8$,
+$\tausnow$ falls below $\delta = 0.1$ at time $\tnow = 6$,
+triggering preventive maintenance of the system.
+$\tausnow = 1.60$ at $\tnow = 0$, this corresponds to the optimal maintenance time
+in an age-based policy that takes the system as monolithic. 
 Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
-the cost-optimal moment of maintenance on the absolute timescale (top right panel),
+the cost-optimal moment of maintenance on the absolute timescale (center panel),
 steadily increases, with small drops corresponding to drops in $\tausnow$,
 showing that as time progresses, accumulated information indicates that maintenance can be postponed.
-Note that $\gstarnow$ (lower left panel) is the momentary cost rate relating to the expected residual lifetime,
-differing from the overall cost rate $\gtotalnow$ (lower right panel).
-%For the maintenance action triggered at $\tnow = 8$,
-%the overall cost rate is $c_p / 8.5 = 0.024$ if the system does not fail until time $8.5$,
-%and between $c_u / 8 = 0.125$ and $c_u / 8.5 = 0.118$ if the system fails.}
-At $\tnow = 4$, the overall expected cost rate for repair scheduled at time $4.91$ is $0.064$,
-up from $0.055$ for repair scheduled at time $5.33$, as cost-optimal at time $\tnow = 3.9$.}
+Consequently, $\gstarnow$ (bottom panel) is steadily decreasing,
+with small upward jumps at the failures of $P_2$ and $P_3$.
+%so the drops in $\tausnow$ do not entirely outweigh the higher likelihood of system failure
+%due to the failure of these components.
+%\textbf{***show $\Rsysnow(\tausnow)$???}
+At $\tnow = 6$, the expected unit cost rate is $0.033$,
+and so considerably lower than the expected cost rate of $0.2 / 1.6 = 0.125$
+for an age-based policy not accounting for component information.}
 \label{fig:tauhist1fig2T}
@@
 evaluations of $\Rsysnow(t)$ and $\fsysnow(t)$ only for $\tnow < t \le \tnow + \tau$.
+The choice of $t_h$ is thus not critical,
+in the sense that $\gnow(\tau)$ evaluations will be correct even if $t_h < \tausnow$.
 
@@
 
-***move some text from figure~\ref{fig:tauhist1fig2T} caption to here?***
+***move some text from figure~\ref{fig:tauhist1fig2T} caption to here or repeat?***
 
@@
 assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.
-$\tausnow$ (top left panel) is consistently lower for the non-adaptive algorithm,
-same with $\tstarnow$ (top right panel).
+$\tausnow$ (left panel) is consistently lower for the non-adaptive algorithm,
+same with $\tstarnow$ (center panel).
 This is because the adaptive algorithm recognizes that system components are more reliable than expected,
-***leading to lower current (lower left panel) and total (lower right panels) expected unit cost rates.}
+leading to lower expected unit cost rates $\gstarnow$ (right panel).
+$\tausnow$ for the non-adaptive algorithm drops below $\delta = 0.1$ at $\tnow = 4$,
+while maintenance is triggered for the adaptive algorithm at $\tnow = 6$.
+The parameter update thus allows to run the system for two more time units,
+corresponding to a unit cost rate of $0.2 / 6 = 0.033$ instead of $0.2 / 4 = 0.05$,
+a reduction of 33\%.}
 \label{fig:tauhist1fig3T}

### 2016-11-30 exempl-fail-hist-2.R

@@ -55,7 +55,7 @@ tauhist1fig2T <- ggplot(melt(br1taus1fineT[-c(5,6)], "tnow"), aes(x = tnow, y = 
 pdf("tauhist1fig2T.pdf", width = 3.5, height = 7)
 tauhist1fig2T
 dev.off()
-#br1taus1fine[40:41,]
+#br1taus1fineT[55:65,]
 br1taus1fineprT <- taustarhist(br, brctypes, brcompfts, br1n0y0, br1beta, seq(0,8,by=0.1),
                                hor=4, seqlen=401, prior = TRUE, onecycle = FALSE)
 names(br1taus1fineprT)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
@@ -73,6 +73,8 @@ tauhist1fig3T <- ggplot(br1taus1prpoT, aes(x = tnow, y = value)) + xlab(expressi
 pdf("tauhist1fig3T.pdf", width = 6, height = 2.75)
 tauhist1fig3T
 dev.off()
+
+#br1taus1fineprT[35:45,]
 
 br1taus1prpoTR <- rbind(data.frame(melt(br1taus1fineT[-5], "tnow"), variable2 = "Parameter update"),
                         data.frame(melt(br1taus1fineprT[-5], "tnow"), variable2 = "No parameter update"))

### 2016-11-30 cbm-rbd-paper.tex
subsections in sec 6, other stuff

@@
 are currently not accounted for in our model, as we assume component failures to be mutually independent
-given the Weibull parameters.
+given the component model parameters.
 Common cause failures will seriously influence the RLD and thus $\tausnow$,
@@
 
-\begin{SCfigure}
-\centering
-\includegraphics[width=0.5\textwidth]{tauhist1fig2T}
+\begin{figure}
+%\centering
+\includegraphics[width=\textwidth]{tauhist1fig2T}
 \caption[t]{$\tausnow$, $\tstarnow = \tnow + \tausnow$ and $\gstarnow = \gnow(\tausnow)$
@@
 \label{fig:tauhist1fig2T}
-\end{SCfigure}
+\end{figure}
 
@@
 
-As illustrative example for a system with complex layout,
-we use the simplified automotive brake system as introduced in Section~\ref{sec:sysrel},
+We now elucidate in more detail the case study used for the previous illustrative figures.
+We use the simplified automotive brake system as introduced in Section~\ref{sec:sysrel},
 see Figure~\ref{fig:brakesys-layout}.
-In all subsequent examples of this section,
-prior component model parameters are taken as in Table~\ref{tab:priorparams}.
+
+The cost parameters are chosen as $c_u = 1$, $c_p = 0.2$, % in all examples,
+i.e., corrective maintenance is five times more costly than preventive maintenance.
+This makes it worthwile to aim for a preventive repair of the system,
+but corrective maintenance will not be avoided at all cost.
+%Indeed, $c_u / c_p = 5$ means that risking corrective maintenance is worthwile
+%if one can expect to run the system five times longer
+%than the preventive maintenance interval.
+
+The choice of prior parameters for the four component models are discussed in Section~\ref{sec:ex-prior};
+then, our maintenance policy is illustrated under three different exemplary failure time histories,
+described in Sections~\ref{sec:ex-1}, \ref{sec:ex-2} and \ref{sec:ex-3}.
+A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.
 
@@
 
+\subsection{Prior component models}
+\label{sec:ex-prior}
+
+The prior component model parameters chosen for this case study
+are given in Table~\ref{tab:priorparams}.
 Note that the scale parameter for component type H is $1$,
@@
 
-The cost parameters are chosen as $c_u = 1$, $c_p = 0.2$ in all examples,
-i.e., corrective maintenance is five times more costly than preventive maintenance.
-This makes it worthwile to aim for a preventive repair of the system,
-but corrective maintenance will not be avoided at all cost.
-Indeed, $c_u / c_p = 5$ means that risking corrective maintenance is worthwile
-if one can expect to utilize the system five times longer
-than under a predictive maintenance schedule.
-
-Below, we illustrate our procedure under three different exemplary failure time histories;
-a more systematic simulation study is subsequently presented in Section~\ref{sec:sim}.
+\subsection{Failure history 1: failures later than expected}
+\label{sec:ex-1}
 
@@
 
+\subsection{Failure history 2: failure times as expected}
+\label{sec:ex-2}
+
 In a second failure history, we observe the failure times $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$,
-and follow the system until $\tnow = 2$ only.
+and follow the system until $\tnow = 2.5$ only.
 Here, components of type $C$ behave more or less as expected,
-while type $P$ components fail quite early.
+while type $P$ components fail slightly earlier than expected.
 Overall, prior assumptions are reasonably in line with observed failure behaviour.
@@
 as visualized in Figure~\ref{fig:tauhist2fig3T}.
-***$\tausnow$ values are slightly lower when component parameters are updated,
-reflecting the slightly too early failures of type $P$ components.
-Due to recommending maintenance to be carried out a bit earlier,
-prospective and total cost rate are slightly higher than in the no update case.
-However, these differences are minuscule in comparison to the gains offered by the continuous update
+***$\tausnow$ values for the model with parameter updates vary around those obtained without parameter updates,
+same for $\tstarnow$ and $\gstarnow$.
+Model with update suggests to mainatin a bit earlier,
+since $\tausnow$ drops below $\delta = 0.1$ at $\tnow = ***$,
+while this happens for the no update model at $\tnow = ***$.
+
+However, these differences are very small in comparison to the gains offered by the continuous update
 in case of the first failure history
@@
 \end{figure}
+
+\subsection{Failure history 3: failures earlier than expected}
+\label{sec:ex-3}
 
@@
 %\end{figure}
-
+%
 The third failure history contains very early failures
 with $C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$,
-and we follow the system until $\tnow = 0.5$.
+and we follow the system until $\tnow = 0.5$***0.75?.
 
@@
 ***without update consistently higher, adaptive algorithm takes surprisingly early failures into account,
-unlike in other scenarios, overall trend for $\tausnow$ constant because of heavy drops,
+unlike in other scenarios, overall trend for $\tstarnow$ constant because of heavy drops,
 costs are underestimated without update***
@@
 
-***$\tthresh$ could vary over time, e.g., longer on weekends or outside office hours
-
-***$\tprep$ instead of $\tthresh$: always too late when scheduling maintenance once $\tausnow < \tprep$.
-Problem common to all CBM policies? usually no preparation time assumed?
-
 *** study other replacement schemes, e.g., replacing only failed components:

### 2016-11-30 exempl-fail-hist-2.R

@@ -49,10 +49,10 @@ names(br1taus1fineT)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
                                ctotal = expression(g[total]^(t[now])),
                                relstar = expression(paste(R[sys]^(t[now]),(t['*']^(t[now])))))
 tauhist1fig2T <- ggplot(melt(br1taus1fineT[-c(5,6)], "tnow"), aes(x = tnow, y = value)) + xlab(expression(t[now])) +
-  geom_line(aes(group = variable))  + geom_point(aes(group = variable), size = 0.15) +
-  facet_wrap(~ variable, nrow = 3, scales = "free_y", labeller = label_parsed) +
+  geom_line(aes(group = variable), size = 0.25)  + geom_point(aes(group = variable), size = 0.15) +
+  facet_wrap(~ variable, ncol = 3, scales = "free_y", labeller = label_parsed) +
   theme(axis.title.y = element_blank())
-pdf("tauhist1fig2T.pdf", width = 3.5, height = 7)
+pdf("tauhist1fig2T.pdf", width = 6, height = 2)
 tauhist1fig2T
 dev.off()
 #br1taus1fineT[55:65,]
@@ -66,7 +66,7 @@ names(br1taus1fineprT)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
 br1taus1prpoT <- rbind(data.frame(melt(br1taus1fineT[-c(5,6)], "tnow"), variable2 = "Parameter update"),
                        data.frame(melt(br1taus1fineprT[-c(5,6)], "tnow"), variable2 = "No parameter update"))
 tauhist1fig3T <- ggplot(br1taus1prpoT, aes(x = tnow, y = value)) + xlab(expression(t[now])) +
-  geom_line(aes(colour = variable2)) + guides(colour = guide_legend(title=NULL)) +
+  geom_line(aes(colour = variable2), size = 0.25) + guides(colour = guide_legend(title=NULL)) +
   geom_point(aes(colour = variable2), size = 0.15) + #theme_bw() +
   facet_wrap(~ variable, ncol = 3, scales = "free_y", labeller = label_parsed) +
   theme(axis.title.y = element_blank()) + bottomlegend + ijarcol
@@ -92,30 +92,33 @@ dev.off()
 # earlier failures - are more or less like expected???
[…]

### 2016-11-30 cbm-rbd-paper.tex
SDF comments sec 3 and rework of taushist figures, sec 6

@@
 
-\section{Reliability functions for complex systems using the survival signature}
+\section{Reliability function for complex systems using the survival signature}
 \label{sec:sysrel}
 
-Here we describe how the system reliability function, given the system layout and arbitrary component models,
+Here we describe how the system reliability function, given the system reliability block diagram and arbitrary component models,
 can be efficiently calculated using the survival signature.
-We will show in Section~\ref{sec:adaptive-sysrel-weibull} how, for a certain choice of component model,
-this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
-giving us the residual life distribution on which we base our adaptive maintenance policy.
-
-We can analyze systems of arbitrary reliability block diagram layout,
+%We will show in Section~\ref{sec:adaptive-sysrel-weibull} how, for a certain choice of component model,
+%this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
+%giving us the residual life distribution on which we base our adaptive maintenance policy.
+
+We can analyze systems with an arbitrary reliability block diagram,
 consisting of components of $K$ different types,
@@
 Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
-***This is a popular example to illustrate such kinds of systems,
-see, e.g., \cite[p.~***]{2010:ebeling}.***
 %This system is observed until time $\tnow$,
@@
 \caption{Reliability block diagram for a simplified automotive brake system
-with four component types $M$, $H$, $C$ and $P$.
-Note that this system layout cannot be expressed as a nesting of series and parallel layouts.
-The corresponding survival signature $\Phi(l_M,l_H,l_C,l_P)$ is given in Table~\ref{tab:brakesys-survsign}.}
+with four component types $M$, $H$, $C$ and $P$.}
+%Note that this system layout cannot be expressed as a nesting of series and parallel layouts.
+%The corresponding survival signature $\Phi(l_M,l_H,l_C,l_P)$ is given in Table~\ref{tab:brakesys-survsign}.}
 \label{fig:brakesys-layout}
@@
 
-In a system with $N$ components, the state of the components can be expressed by the state vector
+In a system with $N$ components, the state of the system can be expressed by the state vector
 $\vec{x} = (x_1,x_2,\ldots,x_N) \in \{0,1\}^N$,
@@
 \end{align}
-where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$,
-and the last equality holds as we assume that components of different types are independent.
+where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$.
+The last equality holds as we assume that components fail independently.
 Note that for coherent systems, the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
@@
 omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$,
-since the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.
+because the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.
 
@@
 In a second failure history, we observe the failure times $C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$,
-and follow the system until $\tnow = 2.5$ only.
+and follow the system until $\tnow = 2.5$.
 Here, components of type $C$ behave more or less as expected,
@@
 same for $\tstarnow$ and $\gstarnow$.
-Model with update suggests to mainatin a bit earlier,
-since $\tausnow$ drops below $\delta = 0.1$ at $\tnow = ***$,
-while this happens for the no update model at $\tnow = ***$.
-
-However, these differences are very small in comparison to the gains offered by the continuous update
+With $\delta = 0.1$, the moment of maintenance is $2.6$ and $2.5$, respectively,
+this shows that for this failure history, where there is indeed no need to update,
+and $\tausnow$ behaviour is dominated by the update of the system reliability block diagram.
+Here, any differences due to the update are very small in comparison to the gains offered by the continuous update
 in case of the first failure history
@@
 The third failure history contains very early failures
-with $C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$,
-and we follow the system until $\tnow = 0.5$***0.75?.
+with $C_2 = 0.1$, $C_3 = 0.2$, $C_4 = 0.8$ $H = 1$, $P_2 = 0.3$, $P_3 = 0.4$,
+and we follow the system until $\tnow = 1$.
 
@@
 
-***without update consistently higher, adaptive algorithm takes surprisingly early failures into account,
-unlike in other scenarios, overall trend for $\tstarnow$ constant because of heavy drops,
-costs are underestimated without update***
+***without update $\tausnow$ consistently higher,
+adaptive algorithm takes surprisingly early failures into account.
+Unlike in the other two scenarios, the overall trend for $\tstarnow$ is a decrease,
+expected cycle costs are underestimated without update***
+
+Model with update consistently suggests to maintain earlier,
+but for both models, $\tausnow$ drops below $\delta = 0.1$ upon the failure of H at $\tnow = 1$.
+Like in failure history 2, the structural information plays an important part in the policy.
+This aspect will be confirmed in the small simulation study described next.
 
@@
 \caption{Effect of the continuous parameter update for the third failure history,
-containing very early failures ($C_2 = 0.2$, $C_3 = 0.3$, $H = 0.5$, $P_2 = 0.05$, $P_3 = 0.15$).
-***more }
+containing very early failures ($C_2 = 0.1$, $C_3 = 0.2$, $C_4 = 0.8$ $H = 1$, $P_2 = 0.3$, $P_3 = 0.4$).}
 \label{fig:tauhist4fig3T}
@@
 
-\section{Small simulation study}
+\section{A small simulation study}
 \label{sec:sim}

### 2016-11-30 exempl-fail-hist-2.R

@@ -92,14 +92,14 @@ dev.off()
 # earlier failures - are more or less like expected???
 brcompfts2 <- list(C1 = NA, C2 = 1, C3 = 2, C4 = NA, H = 8,  M = NA, P1 = NA, P2 = 0.5, P3 = 1.5, P4 = NA)
 plotfts(brcompfts2, 2)
-br1taus2fineT <- taustarhist(br, brctypes, brcompfts2, br1n0y0, br1beta, seq(0, 2.5, by=0.05),
+br1taus2fineT <- taustarhist(br, brctypes, brcompfts2, br1n0y0, br1beta, seq(0, 2.5, by=0.1),
                              hor=4, seqlen=401, onecycle = FALSE)
 names(br1taus2fineT)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
                                tstar = expression(t['*']^(t[now])),
                                cstar = expression(g['*']^(t[now])),
                                ctotal = expression(g[total]^(t[now])),
                                relstar = expression(paste(R[sys]^(t[now]),(t['*']^(t[now])))))
-br1taus2fineprT <- taustarhist(br, brctypes, brcompfts2, br1n0y0, br1beta, seq(0, 2.5, by=0.05),
+br1taus2fineprT <- taustarhist(br, brctypes, brcompfts2, br1n0y0, br1beta, seq(0, 2.5, by=0.1),
                                hor=4, seqlen=401, prior=T, onecycle = FALSE)
 names(br1taus2fineprT)[2:6] <- c(taustar = expression(tau['*']^(t[now])),
                                  tstar = expression(t['*']^(t[now])),
@@ -117,8 +117,11 @@ pdf("tauhist2fig3T.pdf", width = 6, height = 2.75)
 tauhist2fig3T
 dev.off()
 
-br1taus2fineT[35:41,]
-br1taus2fineprT[35:41,]
+br1taus2fineT[20:26,]
+br1taus2fineprT[20:26,]
+br1taus2fineTasdf <- taustarhist(br, brctypes, brcompfts2, br1n0y0, br1beta, seq(2.4, 2.8, by=0.1),
+                                 hor=4, seqlen=401, onecycle = FALSE)
+br1taus2fineTasdf
 
 br1taus2prpoTR <- rbind(data.frame(melt(br1taus2fineT[-5], "tnow"), variable2 = "Parameter update"),
[…]

### 2016-11-30 cbm-rbd-paper.tex
comments SDF sec 4

@@
 can be calculated for a specific choice of component model.
-Section~\ref{sec:policy} will then show how an adaptive maintenance policy
-can be derived for a monitored system based on such a current system residual life distribution.
+%Section~\ref{sec:policy} will then show how an adaptive maintenance policy
+%can be derived for a monitored system based on such a current system residual life distribution.
 
@@
 and that only the scale parameter needs to be estimated.
+The model could be extended to learn also the shape parameter in a later step,
+using, e.g., the discretized approach by \cite{1969:soland}.
+
 By using a Bayesian approach, described in Section~\ref{sec:weibull},
 our component model allows to include both expert assessments and test data (if available),
-and furthermore can account for component lifetime information from the current run of the system up to $\tnow$.
+and furthermore can account for component lifetime information from the current operational cycle up to $\tnow$.
 %***component model: weibull with fixed shape,
@@
 %
-Section~\ref{sec:postpred} then derives the posterior predictive distribution
+In Section~\ref{sec:postpred} we derive the posterior predictive distribution
 for the Weibull component model as needed for the current system reliability calculation.
-Section~\ref{sec:sysreltnow} then adapts the method from Section~\ref{sec:sysrel} for the adaptive setting,
+Finally, in Section~\ref{sec:sysreltnow}, we adapt the method from Section~\ref{sec:sysrel} for the adaptive setting,
 resulting in a formula for $\Rsysnow(t)$.
@@
 who presented the same residual life distribution model.
-However, \cite{2016:walter-coolen} did not consider any maintenance policies,
-and focus instead on a generalization of the RLD model using sets of priors for the component models.
-These sets of priors can be seen as parametric P-boxes,
-a certain kind of imprecise probability model \citep[see, e.g.,][]{itip}.
-Such models allow for vague and partial prior specifications,
-and provide sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.
-
-\subsection{Bayesian update of Weibull component models}
+However, \cite{2016:walter-coolen} did not consider maintenance policies,
+but focus instead on a generalization of the RLD model using sets of priors for the component models.
+%These sets of priors can be seen as parametric P-boxes,
+%a certain kind of imprecise probability model \citep[see, e.g.,][]{itip}.
+%Such models allow for vague and partial prior specifications,
+%and provide sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.
+
+\subsection{Bayesian update of the Weibull component models}
 \label{sec:weibull}
@@
 For each type $k$ component, we assume that the lifetime $T_{k,i}$ ($i=1,\ldots,N_k$, $k = 1, \ldots, K$)
-is Weibull distributed with fixed shape parameter $\beta_k > 0$,
+is Weibull distributed with scale parameter $\lambda_k$ and (fixed) shape parameter $\beta_k > 0$,
 in short $T_{k,i} \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
-with density and cdf
+with pdf (probability density function) and cdf (cumulative distribution function)
 \begin{align}
@@
 For $\beta_k=1$, one obtains the Exponential distribution with constant hazard rate as a special case.
-To keep things simple, we assume $\beta_k$ to be known.
-(We plan to extend the model to learn also $\beta_k$ in a later step,
-using, e.g., the discretized approach by \cite{1969:soland}.)
 The scale parameter $\lambda_k$ can be interpreted through the relation
@@
 in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
-Here, we have added the prior parameters $a_k$ and $b_k$ in notation
-to indicate that the prior over $\lambda$ depends on their values.
-
-The inverse Gamma is convenient because it is a conjugate prior,
-i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
-the prior parameters only need to be updated to obtain the posterior parameters,
+%Here, we have added the prior parameters $a_k$ and $b_k$ in notation
+%to indicate that the prior over $\lambda$ depends on their values.
+
+The inverse Gamma distribution is convenient because it is a conjugate prior,
+i.e., the posterior obtained by Bayes' rule is again an inverse Gamma distribution and thus easily tractable
+because only the prior parameters need to be updated to obtain the posterior parameters,
 so no numerical integation or simulation techniques are necessary.
@@
 
-In place of the usual parametrization in terms of $a_k$ and $b_k$,
+Instead of the usual parametrization in terms of $a_k$ and $b_k$,
 we use the parameters $\nk > 1$ and $\yk > 0$
@@
 Using \eqref{eq:lambdainterpret},
-we can thus translate an expert's statement of expected component lifetime into a corresponding value for $\yk$.
+we can thus translate an expert's statement of the expected component lifetime into a corresponding value for $\yk$.
 $\nk$ can be seen as a prior strength or pseudocount,
@@
 From the simple update rule \eqref{eq:ig-update}, we see that
-$\ykp$ is a weighted average of the prior parameter $\yk$ and the maximum likelihood (ML) estimator $\tautk/e_k$,
+$\ykp$ is a weighted average of the prior parameter $\yk$ and the maximum likelihood estimator (ML) $\tautk/e_k$,
 with weights proportional to $\nk$ and $e_k$, respectively.
@@
 Furthermore, $\V[\lambda\mid\nk,\yk] = (\yk)^2 / (1 - 1/\nk)$;
-for fixed $\yk$, a higher $\nk$ indicates thus 
+for fixed $\yk$, a higher $\nk$ indicates 
 that more probability mass is concentrated around $\yk$.
 
-Using \eqref{eq:abtony} and \eqref{eq:ig-update}, the posterior distribution over $\lambda_k$ is
+Using \eqref{eq:abtony} and \eqref{eq:ig-update}, the posterior distribution over $\lambda_k$ is given by
 \begin{align}
@@
 %to emphasize that the posterior is a synthesis of prior information and data.
-As this posterior \eqref{eq:ig-update-alpha} can be defined in terms of
+As this posterior can be defined in terms of
 the updated, posterior parameters $\nkp$ and $\ykp$,
@@
 posterior parameters as new prior parameters and update them again using new data.
-Indeed, we will use this property to use the extra information about components
+We will use this property to use the extra information about components
 that accumulates during operation of the system:
@@
 or could be taken directly equal to $\nk$ and $\yk$ if no test data is available.
-In both cases, the distribution $f(\lambda_l \mid \nkz, \ykz)$
+In both cases, the distribution $f(\lambda_k \mid \nkz, \ykz)$
 thus accounts for all knowledge on component type $k$ that is available at system start-up.
@@
 
-In analogue to the notation from Section~\ref{sec:weibull},
+In analogue to the notation used in Section~\ref{sec:weibull},
 let $N_k = \eknow + \cknow$ be the number of type $k$ components in the monitored system,
@@
 \end{align}
-The terms remaining under the integral form the core of an inverse gamma distribution \eqref{eq:ig-def}
+The terms remaining under the integral form the core of an inverse Gamma distribution \eqref{eq:ig-def}
 with parameters $\nknow + 1$ and $\nknow\yknow + (l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}))$,
@@
 Note that if one or several components have failed by $\tnow$,
-the system layout changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$,
-so we denote the current survival signature by $\Phinow(l_1,\ldots,l_K)$.
+the system reliability block diagram changes, and with it the survival signature $\Phi(l_1,\ldots,l_K)$.
+We denote the current survival signature by $\Phinow(l_1,\ldots,l_K)$.
 
 For each prediction time $t$,
-\eqref{eq:sysrel-tnow} is a sum over over $\prod_{k=1}^K (\cknow + 1)$ terms;
-however, some of these terms correspond to $\Phinow(l_1,\ldots,l_K) = 0$,
+\eqref{eq:sysrel-tnow} is a sum over $\prod_{k=1}^K (\cknow + 1)$ terms.
+However, some of these terms correspond to $\Phinow(l_1,\ldots,l_K) = 0$,
 which can thus be disregarded.
@@
 the grid of prediction values can be very fine.
-
-Next, we will describe an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
-a current residual life distribution,
-first in general, then for our implementation,
-where a fine discrete approximation of the RLD is obtained.
+%
+%Next, we will describe an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
+%a current residual life distribution,
+%first in general, then for our implementation,
+%where a fine discrete approximation of the RLD is obtained.
 

### 2016-12-01 cbm-rbd-paper.tex
comments SDF sec 5 and 6.0

@@
 
-We can now derive the adaptive and dynamic maintenance policy
+Now we can derive the adaptive and dynamic maintenance policy
 that resembles a CBM policy.
-Define the set of evaluation time points as $\{ \tnow : \tnow = m \delta, m \in \naturals_0\}$,
-%where $m = 0, 1, 2, \ldots$,
-%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
-with $\delta$ a sufficiently small time increment.
+Consider a set of evaluation time points $\tnow$.
 Instead of determining a threshold for a degradation signal like in usual CBM approaches,
@@
 A preventive maintenance action is initiated
-as soon as $\tausnow$ decreases below $\delta$.
+as soon as $\tausnow$ decreases below the time span to the next evaluation time.
 %continuing to the the next evaluation point $\tnow$ would carry the risk 
 %a time span chosen to reflect operational practicalities.
-This operational procedure is described in more detail in Section~\ref{sec:operationalprocedure};
+This dynamic and adaptive maintenance policy is described in more detail in Section~\ref{sec:operationalprocedure};
 a graphical overview is given in Figure~\ref{fig:procedure}.
@@
 The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
-by minimizing $\gnow(\tau)$, the expected unit cost rate for the current operational cycle.
-(An operational cycle begins with system start-up,
+by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
+An operational cycle begins with system start-up,
 and ends when either preventive maintenance is carried out,
-or a failure of the system occurs, with subsequent corrective maintenance.)
-This criterion, as detailed in Section~\ref{sec:costrate} below,
+or a failure of the system occurs, with subsequent corrective maintenance.
+This criterion, as detailed in Section~\ref{sec:costrate},
 %only assumes that $\Rsysnow(t)$ is given,
 only assumes that a RLD is given,
-and thus is not tied to our choice of component model.
+and thus is not tied to our choice for the component models.
 One could also consider alternative optimality criteria to determine $\tausnow$;
@@
 
-Section~\ref{sec:optim} then focuses on our choice of component model and the resulting form for $\Rsysnow(t)$,
+Section~\ref{sec:optim} then focuses on our choice for the component models and the resulting form for $\Rsysnow(t)$,
 and shows how $\tausnow$ is determined in this situation.
-Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
-and a small simulation study is presented in Section~\ref{sec:sim}.
+%Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
+%and a small simulation study is presented in Section~\ref{sec:sim}.
 
@@
 \begin{tikzpicture}
-[node distance=10mm,
+[node distance=6mm,
  font=\footnotesize,
- box/.style={draw, rectangle, thick, minimum height=6mm, minimum width=28mm, rounded corners=2mm},
+ box/.style={draw, rectangle, thick, minimum height=6mm, minimum width=15mm},
+ box2/.style={draw, rectangle, thick, minimum height=6mm, minimum width=28mm, rounded corners=2mm},
+ dec/.style={draw, shape=diamond, thick, minimum height=4mm, minimum width=4mm},
  pfeil/.style={-latex', very thick}]
-\node (startup) [box]                       {\parbox{20ex}{\centering system start-up\\ (all comp.\ new)}};
-\node (sysfail) [box, right=of startup]     {system failed?};
-\node (tauchck) [box, below=6mm of sysfail] {$\tausnow < \delta$?};
-\node (gotonxt) [box, below=6mm of tauchck] {\parbox{17ex}{\centering continue to\\ $\tnow = (m+1)\delta$}};
-\draw [thick, dashed, rounded corners=2mm] ($(gotonxt.south east) + (2mm,-1mm)$) rectangle ($(sysfail.north west) + (-5mm,1mm)$) node[above left=0mm and -33mm] {each $\tnow = m \delta, m \in \naturals_0$};
-\node [above left=0mm and -8mm of startup] {$t=0$};
-\node (correct) [box, right=of sysfail, minimum width=18mm] {\parbox{14ex}{\centering corrective\\ maintenance\\ (cost $c_c$)}};
-\node (prevent) [box, right=of tauchck, minimum width=18mm] {\parbox{14ex}{\centering preventive\\ maintenance\\ (cost $c_p$)}};
-\node (update) [box, below right=10mm and -4mm of prevent, minimum width=10mm] {\parbox{12ex}{\centering update parameters}};
-\draw[pfeil] (startup) -- (sysfail);
-\draw[pfeil] (sysfail) -- (tauchck) node[midway, right] {no};
-\draw[pfeil] (tauchck) -- (gotonxt) node[midway, right] {no};
-\draw[very thick] (gotonxt.west) -| ($(sysfail.west) + (-3mm,0mm)$);
-\draw[pfeil] (sysfail) -- (correct) node[midway, above] {yes};
-\draw[pfeil] (tauchck) -- (prevent) node[midway, above] {yes};
-\draw[pfeil] (correct) -| (update);
-\draw[pfeil] (prevent) -| (update);
-\draw[pfeil, dotted] (update) -| (startup) node[midway, below right] {start new cycle};
+\node (startup) [box] {\parbox{18ex}{\centering system start-up\\ $\tnow = 0, m= 0$\\ initial params.\\ $\nkz, \ykz$}};
+\node (mincrem) [box, below=57mm of startup] {$m = m + 1$};
+\node (cptfail) [dec, below right=9mm and 17mm] {\parbox{10ex}{\centering $\exists\, t_{k,i}$ s.t.\\ \rule{0ex}{2ex} \\ ?}};
+%$(m-1)\delta$\\ $ < t_{k,i} < $\\ $m\delta$}};
+\node at (cptfail) {$\scriptstyle \tnow < t_{k,i} < (m+1)\delta$};
+%\coordinate (mcoord) at ($(startup) * (0, -2)$) {};
+\node (nfltnow) [box, below=of cptfail] {\parbox{21ex}{\centering $\tnow = (m + 1)\delta$,\\ update parameters\\ to $\nknow, \yknow$}};
+\node (yfltnow) [box, right=of cptfail] {\parbox{21ex}{\centering $\tnow = t_{k,i}$,\\ update parameters\\ to $\nknow, \yknow$}};
+\node (sysfail) [dec, below=5.6mm of yfltnow] {\parbox{8ex}{\centering system\\ failed?}};
+\node (tausmde) [box, below=of nfltnow] {\parbox{21ex}{\centering determine $\tausnow$}};
+\node (taustki) [box, below=of sysfail] {\parbox{21ex}{\centering determine $\tausnow$}};
+\node (tausdel) [dec, below=of tausmde] {\parbox{10ex}{\centering $\tausnow$\\ \rule{2ex}{0ex}$< \delta$?}};
+\node (taudtki) [dec, below=of taustki] {\parbox{10ex}{$\tausnow <$\\ \phantom{?}}};
+\node at ($(taudtki) + (0,-2mm)$) {$\scriptstyle (m + 1) \delta - t_{k,i}$?};
+\node (corrmnt) [box, right=8.5mm of sysfail] {\parbox{21ex}{\centering corrective repair\\ at $\tnow$ (cost $c_c$)}};
+\node (prevmnt) [box, right=of taudtki] {\parbox{21ex}{\centering preventive repair\\ at $\tnow$ (cost $c_p$)}};
+\node (updatep) [box, below=7.5mm of corrmnt] {\parbox{21ex}{\centering set initial params.\\ for next cycle as\\ $\nkz = \nknow$\\ $\ykz = \yknow$}};
+%\coordinate (nocoord) at ($(taudtki) + (-1.8,-1.3)$) {};
+\coordinate (nocoord) at ($(taudtki) + (-1.8, 1.6)$) {};
+\coordinate (yscoord) at ($(tausdel) + ( 0  ,-1.5)$) {};
+\coordinate (nxtcoor) at ($(updatep) + ( 1.8, 0  )$) {};
+\draw[pfeil] (startup) |- ($(cptfail.west) + (0.1, 0.1)$);
+\draw[pfeil] (mincrem) |- ($(cptfail.west) + (0.1,-0.1)$);
+\draw[pfeil] (cptfail) -- (nfltnow) node[midway, left] {no};
+\draw[pfeil] (cptfail) -- (yfltnow) node[midway, above] {yes};
+\draw[pfeil] (yfltnow) -- (sysfail);
+\draw[pfeil] (nfltnow) -- (tausmde);
+\draw[pfeil] (sysfail) -- (taustki) node[midway, left] {no};
+\draw[pfeil] (sysfail) -- (corrmnt) node[midway, above] {yes};
+\draw[pfeil] (tausmde) -- (tausdel);
+\draw[pfeil] (taustki) -- (taudtki);
+\draw[pfeil] (tausdel) -| (mincrem) node[at start, above left] {no};
+\draw[very thick] (taudtki) -| (nocoord) node[near start, above] {no} -| (mincrem);
+\draw[pfeil] (taudtki) -- (prevmnt) node[midway, above] {yes};
+\draw[pfeil] (tausdel) -- (yscoord) -| (prevmnt) node[at start, above right] {yes};
+\draw[pfeil] (prevmnt) -- (updatep);
+\draw[pfeil] (corrmnt) -- (updatep);
+\draw[pfeil, dotted] (updatep) -- (nxtcoor) |- (startup) node[midway, above left] {start new cycle};
+%
+%\node (startup) [box]                       {\parbox{20ex}{\centering system start-up\\ (all comp.\ new)}};
+%\node (sysfail) [box, right=of startup]     {system failed?};
+%\node (tauchck) [box, below=6mm of sysfail] {$\tausnow < \delta$?};
+%\node (gotonxt) [box, below=6mm of tauchck] {\parbox{17ex}{\centering continue to\\ $\tnow = (m+1)\delta$}};
+%\draw [thick, dashed, rounded corners=2mm] ($(gotonxt.south east) + (2mm,-1mm)$) rectangle ($(sysfail.north west) + (-5mm,1mm)$) node[above left=0mm and -33mm] {each $\tnow = m \delta, m \in \naturals_0$};
+%\node [above left=0mm and -8mm of startup] {$t=0$};
+%\node (correct) [box, right=of sysfail, minimum width=18mm] {\parbox{14ex}{\centering corrective\\ maintenance\\ (cost $c_c$)}};
+%\node (prevent) [box, right=of tauchck, minimum width=18mm] {\parbox{14ex}{\centering preventive\\ maintenance\\ (cost $c_p$)}};
+%\node (update) [box, below right=10mm and -4mm of prevent, minimum width=10mm] {\parbox{12ex}{\centering update parameters}};
+%\draw[pfeil] (startup) -- (sysfail);
+%\draw[pfeil] (sysfail) -- (tauchck) node[midway, right] {no};
+%\draw[pfeil] (tauchck) -- (gotonxt) node[midway, right] {no};
+%\draw[very thick] (gotonxt.west) -| ($(sysfail.west) + (-3mm,0mm)$);
+%\draw[pfeil] (sysfail) -- (correct) node[midway, above] {yes};
+%\draw[pfeil] (tauchck) -- (prevent) node[midway, above] {yes};
+%\draw[pfeil] (correct) -| (update);
+%\draw[pfeil] (prevent) -| (update);
+%\draw[pfeil, dotted] (update) -| (startup) node[midway, below right] {start new cycle};
 \end{tikzpicture}
-\caption{Operational procedure under the proposed maintenance policy,
+\caption{Flowchart for the proposed maintenance policy,
 showing a single operational cycle,
-including the loop back to system startup that starts a new cycle.}
+including the loop back to system startup that starts a new cycle as a dashed arrow.}
+%For simplicity of presentation, we exclude the possibility that several component failure times
+%happen between the evaluation times $(m-1) \delta$ and $m \delta$.}
 \label{fig:procedure}
@@
 
-\subsection{Operational procedure}
+\subsection{Detailed description of the policy}
 \label{sec:operationalprocedure}
 
-Each operational cycle starts with system startup.
+Each operational cycle starts with a system startup.
 At this point in time, the system is in an (as good as) new state,
 i.e., all components in the system are (as good as) new and have not aged.
-A cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
+An operational cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
 or the system fails, which triggers a corrective maintenance action.
 
-During a cycle,
-$\tausnow$ is recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$,
-where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
+Define a grid of planned evaluation time points as $\{m \delta : m \in \naturals_0\}$,
+%where $m = 0, 1, 2, \ldots$,
+%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
+with $\delta$ a sufficiently small time increment.
+During an operational cycle,
+$\tausnow$ is recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
+%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
+However, if a component fails before the next $\tnow$ on the grid,
+$\tnow$ is set instead to the exact failure time $t_{k,i}$.
+Next, we check whether the system has failed due to this component failure.
+If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
+If the system has not failed, we calculate $\tausnow$ is for the current off-grid time $\tnow = t_{k,i}$,
+and move back onto the grid afterwards,
+unless there is another component failure before the next planned evaluation time.
+
 Frequent recalculation of $\tausnow$ is feasible
-when evaluation of the RLD is fast.
+when computation of the RLD is fast.
 Then, by evaluating the unit cost rate function $\gnow(\tau)$ on a discrete grid,
@@
 all components age, and also non-failure adds information to the component models.
-Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
-as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T},
-which gives a numerical example described in more detail in Section~\ref{sec:examples}.
+%Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
+%as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T},
+%which gives a numerical example described in more detail in Section~\ref{sec:examples}.
 %An alternative would be to update $\tausnow$ only when a component fails,
@@
 %as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
-
+%
 The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
-of the maintenance interval in an age based policy by trading off the costs of preventive and corrective maintenance;
-however, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
+of the maintenance interval in an age based policy by trading off the costs of preventive and corrective maintenance.
+However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
 our policy is adaptive and dynamic like a CBM policy. 
-As can happen for an age-based policy, the derived $\gnow(\tau)$ may also be monotonely decreasing.
-In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
-This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
-but also capable of indicating when corrective maintenance is the better option.
+%As can happen for an age-based policy, the derived $\gnow(\tau)$ may also be monotonely decreasing.
+%In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
+%This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
+%but also capable of indicating when corrective maintenance is the better option.
 %i.e., capable of choosing the maintenance policy.
 
-A preventive maintenance action is triggered at the smallest $m \in \naturals_0$
-such that $\tausnow < \delta$ for $\tnow = m \delta$.
-When $\tausnow$ falls below $\delta$,
-the optimal moment of maintenance is so close to present time $\tnow$
-that in continuing to the next $\tnow = (m+1)\delta$, one exceeds the optimal system failure risk
+Once $\tausnow$ is calculated, it is compared to the time span from the current $\tnow$ to the next planned evaluation time.
+If the current $\tnow$ is a time on the grid, then $\tnow = m \delta$ for some $m \in \naturals_0$.
+The next planned evaluation is then at $(m + 1) \delta$,
+and we compare $\tausnow$ to $\delta$.
+If $\tausnow < \delta$, a preventive maintenance action is triggered, incurring cost $c_p$,
+otherwise we attempt to move to the next planned evaluation point, by setting $m =  (m + 1)$.
+
+If the current $\tnow$ is instead an off-grid time corresponding to a component failure time $t_{k,i}$,
+then the next planned evaluation time is the next time on the grid.
+Let $m$ be such that $m \delta < t_{k,i} < (m + 1) \delta$,
+so the next time on the grid is $(m + 1) \delta$,
+and we compare $\tausnow$ with $(m + 1) \delta - t_{k,i}$.
+If $\tausnow < (m + 1) \delta - t_{k,i}$, a preventive maintenance action is triggered, incurring cost $c_p$,
+otherwise we attempt to move to the next planned evaluation point, which is still $(m + 1) \delta$.
+
+In both cases, we decide to maintain the system preventively
+when the optimal time to maintenance is closer to now than the next time we intend to re-evaluate $\tausnow$,
+since otherwise, in waiting to the next evaluation time,
+one would exceed the optimal system failure risk 
 as determined by the trade-off made by $\gnow(\cdot)$.
-This means that a preventive maintenance action should be carried out at $\tnow = m\delta$, which incurs cost $c_p$.
-When the system fails, instead a corrective maintenance action is carried out, incurring cost $c_c$.
-The current cycle ends when either preventive or corrective maintenance is carried out,
-and a new cycle starts with a system with all components (as good as) new.
-%choice of a failure threshold in usual CBM policies.
-%This failure threshold gives the level of the degradation signal where 
-%This additional downtime must be reflected in the cost parameter $c_u$ (see Section~\ref{sec:costrate} below).
-%Again, the cycle ends when maintenance work is completed.
-
-At the end of each cycle,
-the component information gained during the completed cycle is added to the component knowledge base
+When $\tausnow$ is instead further in the future than the next planned evaluation time,
+we can safely continue to the next evaluation time,
+without risking to miss the cost-optimal moment to preventively maintain the system.
+
+At the end of each operational cycle, i.e.,
+after maintaining the system either preventively or correctively,
+the component information gained during the completed operational cycle is added to the component knowledge base
 by updating the parameters $\nk$ and $\yk$ accordingly,
 %using failure and censoring times as of the end of the cycle.
-such that $\nkz$ and $\ykz$ for the next cycle account for the (censored) lifetimes observed during the previous cycle.
+such that $\nkz$ and $\ykz$ for the next operational cycle
+account for the (censored) lifetimes observed during the previous operational cycle.
 %We assume that both planned and unplanned maintenance action takes negligible time,
 
-The operational procedure is visualized in Figure~\ref{fig:procedure},
-displaying a single cycle,
-also including the loop back to system startup that starts a new cycle.
+Figure~\ref{fig:procedure} displays the flowchart for the policy,
+indicating the decisions that are repatedly encountered in a single operational cycle.
+The flowchart also contains the loop back to system startup that starts a new operational cycle.
 
 We assume that both preventive and corrective maintenance result in an (as good as) new system state by replacing all components,
-such that the system begins a new cycle always under the same conditions.
+such that the system begins a new operational cycle always under the same conditions.
 Replacement schemes that do not replace all components would require to account for the different ages of components in the system
@@
 that merits an investigation of its own,
-and we will comment on this in the Outlook (Section~\ref{sec:outlook}).
-
-As we use a one-cycle criterion, the time both preventive and corrective maintenance actions require
-does not matter directly for the determination of $\tausnow$.
-Longer downtime and other negative effects of corrective maintenance
-are instead accounted for through the costs parameters $c_p$ and $c_c$ used in the trade-off leading to $\tausnow$,
-as described next.
-
-%To find the optimal moment for maintenance based on the current system reliability function $\Rsysnow(t)$,
-%we minimize the expected average cost per time unit,
-%called the unit cost rate, $g(\tau)$,
-%leading to the cost-optimal moment of maintenance $\tau_*$.
-%(could be discounted as well, out of scope here.)
-
-\subsection{Expected unit cycle cost rate}
+and we will comment on this in Section~\ref{sec:outlook}.
+%
+%As we use a one-cycle criterion, the time both preventive and corrective maintenance actions require
+%does not matter directly for the determination of $\tausnow$.
+%Longer downtime and other negative effects of corrective maintenance
+%are instead accounted for through the costs parameters $c_p$ and $c_c$ used in the trade-off leading to $\tausnow$,
+%as described next.
+
+\subsection{Expected operational cycle cost rate}
 \label{sec:costrate}
@@
 we use the one-cycle cost rate as it is the most appropriate for our situation,
-where $\tausnow$ changes with every cycle, and indeed changes with $\tnow$ within each cycle.
-%since it considers only the costs with respect to the current cycle.
+where $\tausnow$ changes continuously.
 
 Let $c_p$ be the cost of preventive maintenance, and $c_c$ the cost of corrective (unplanned, breakdown) maintenance, where $c_p < c_c$.
-Usually, set-up costs, work costs and downtime costs are much higher for corrective maintenance,
+Usually, set-up costs, the actual maintenance costs (labor, new components) and downtime costs are much higher for corrective maintenance,
 such that often, $c_p \ll c_c$.
-CBM is known to be most effective when the ratio $c_p / c_c$ is small
-(\textbf{***cite de Jonge and Teunter working paper on relative benefit of CBM}).
-%
-As discussed above,
-we assume that both $c_p$ and $c_c$ include the cost of replacing all components in the system,
-such that every time a new cycle starts, the system is in the same state with all components (as good as) new.
 
@@
 conditioned on all information available at $\tnow$,
-and $\fsysnow(t)$ be the corresponding density.
+and $\fsysnow(t)$ be the corresponding probability density.
 Note that due to the conditional nature of $\Rsysnow(t)$,
 which gives the probability that the system functions at time $t$ given that it functions at $\tnow$,
-also $\fsysnow(t)$ is a conditional density,
+also $\fsysnow(t)$ is a conditional probability density,
 with support $\{t \in \reals : t > \tnow \}$.
@@
 c_p / (\tnow + \tau) & \text{if } \hspace{7.4ex} \tsysnow \ge \tnow + \tau \\
-c_u /  \tsysnow      & \text{if }        \tnow < \tsysnow  <  \tnow + \tau \,.
+c_c /  \tsysnow      & \text{if }        \tnow < \tsysnow  <  \tnow + \tau \,.
 \end{cases}
@@
 where $0$ corresponds to the time of system start-up.
-Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected unit cost rate
+Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected operational cycle cost rate
 \begin{align}
@@
             &= \frac{c_p}{\tnow + \tau} \Rsysnow(\tnow + \tau)
-              + c_u \int_0^\tau \frac{1}{\tnow + \theta} \fsysnow(\tnow + \theta) \dd \theta\,.
+              + c_c \int_0^\tau \frac{1}{\tnow + \theta} \fsysnow(\tnow + \theta) \dd \theta\,.
 \label{eq:gtnowtau}
 \end{align}
-Thus $\gnow(\tau)$ gives the unit cost rate that we expect to incur over the complete operational cycle
+Here, we assume that the time required to execute preventive and corrective maintenance
+can be neglected when compared with the duration of one operational cycle.
+%
+$\gnow(\tau)$ gives the cost rate that we expect to incur over the complete operational cycle
 when, at time $\tnow$, we schedule preventive maintenance for time $\tnow + \tau$,
@@
 which is a condition for $\fsysnow(\tnow + \theta)$ for values of $\theta$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
-This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
+%This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
 For our approach, however, this condition is not relevant,
@@
 
-Finally, $\tausnow := \arg\min \gnow(\tau)$
-is the cost-optimal moment of maintenance as of $\tnow$,
+$\tausnow := \arg\min \gnow(\tau)$
+is the cost-optimal time to maintenance as of $\tnow$,
 incorporating all that is known at current time $\tnow$.
@@
 %the optimal moment of maintenance on a prospective time scale.
-The minimal expected unit cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
-thus is, as of $\tnow$, the lowest unit cost rate for the current operational cycle
+The minimal expected operational cycle cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
+thus is, as of $\tnow$, the lowest cost rate for the current operational cycle
 that we can expected to attain.
@@
 since then, system failure becomes much more likely, leading to a higher risk of incurring the corrective maintenance cost $c_c$.
-Figure~\ref{fig:tauhist1fig2T} illustrates these relations in the scenario depicted in Figure~\ref{fig:ghist1fig2T}.
-
-As can be seen there and in the numerical examples in Section~\ref{sec:examples} below,
+Figure~\ref{fig:tauhist1fig2T} illustrates these relations for the scenario depicted in Figure~\ref{fig:ghist1fig2T}.
+%
+As can be seen there and in the numerical examples in Section~\ref{sec:examples},
 for continuous component lifetime distributions,
@@
 Common cause failures, i.e., failures of several components at the same time due to a shared root cause,
-are currently not accounted for in our model, as we assume component failures to be mutually independent
-given the component model parameters.
-Common cause failures will seriously influence the RLD and thus $\tausnow$,
-and we will comment on possible extensions in the Outlook (Section~\ref{sec:outlook}).
-
-Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
-for our choice of component model.
-%($\beta_k > 1$ $\forall k = 1,\ldots,K$ sufficient **???**)
-%***here, $\Rsysnow(\cdot)$ shifted such that $\tnow = 0$.
+are currently not accounted for in our model. %, as we assume component failures to be mutually independent
+%given the component model parameters.
+Such simulatenous failures will seriously influence the RLD and thus $\tausnow$.
+We will return to this in Section~\ref{sec:outlook}.
+%
+%Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
+%for our choice of component model.
 
@@
 assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
-and $c_u = 1$, $c_p = 0.2$.
-%$\tausnow$ (top left panel) first decreases slightly, then remains more or less constant during failure-free periods,
-$\tausnow$ (top panel) decrease weakens and attains a near-constant speed from about $\tnow = 2$ during failure-free periods,
-with discrete drops at the failures of components $P_2$, $P_3$ and $H$ only.
-%With the failure of $H$ at time $\tnow = 8$,
-$\tausnow$ falls below $\delta = 0.1$ at time $\tnow = 6$,
-triggering preventive maintenance of the system.
-$\tausnow = 1.60$ at $\tnow = 0$, this corresponds to the optimal maintenance time
-in an age-based policy that takes the system as monolithic. 
-Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
-the cost-optimal moment of maintenance on the absolute timescale (center panel),
-steadily increases, with small drops corresponding to drops in $\tausnow$,
-showing that as time progresses, accumulated information indicates that maintenance can be postponed.
-Consequently, $\gstarnow$ (bottom panel) is steadily decreasing,
-with small upward jumps at the failures of $P_2$ and $P_3$.
-%so the drops in $\tausnow$ do not entirely outweigh the higher likelihood of system failure
-%due to the failure of these components.
-%\textbf{***show $\Rsysnow(\tausnow)$???}
-At $\tnow = 6$, the expected unit cost rate is $0.033$,
-and so considerably lower than the expected cost rate of $0.2 / 1.6 = 0.125$
-for an age-based policy not accounting for component information.}
+and $c_u = 1$, $c_p = 0.2$.}
 \label{fig:tauhist1fig2T}
@@
 
-\subsection{Numerical optimization of the expected unit cycle cost rate}
+\subsection{Numerical optimization of the expected operational cycle cost rate}
 \label{sec:optim}
 
-For our choice of component model,
+For our choice of the component models,
 the resulting $\Rsysnow(t)$ as of \eqref{eq:sysrel-tnow}
@@
 covering the time span from $\tnow$ to some horizon time $\tnow + t_h$.
-(The choice of $t_h$ is discussed in more detail below.)
+%(The choice of $t_h$ is discussed in more detail below.)
 We calculate $\gnow(\tau)$ on the same grid,
@@
 Here, we approximate the integral in \eqref{eq:gtnowtau} numerically by a sum,
-where evaluations of $\fsysnow(t)$ are calculated via differences of $\Rsysnow(t)$ evaluations.
+where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$.
 %$\gnow(\tau)$ is likewise evaluated on a dense grid,
@@
 allowing for a near real-time update.
-
+%
 %***calculations in \textsf{R} can be vectorized and are thus fast.
@@
 
-%At time $\tnow$, the corresponding $\tausnow$ gives the optimal moment of maintenance in terms of time to elapse after $\tnow$,
-%so in the absolute time scale, the optimal moment of maintenance is at $\tnow + \tau_*^{\tnow}$.
-
 \section{Further elaboration of the case study}
@@
 
-We now elucidate in more detail the case study used for the previous illustrative figures.
+We now explain in more detail the case study used for the previous illustrative figures.
 We use the simplified automotive brake system as introduced in Section~\ref{sec:sysrel},
-see Figure~\ref{fig:brakesys-layout}.
-
-The cost parameters are chosen as $c_u = 1$, $c_p = 0.2$, % in all examples,
+see Figure~\ref{fig:brakesys-layout} for the reliability block diagram.
+
+The cost parameters are chosen as $c_c = 1$, $c_p = 0.2$, % in all examples,
 i.e., corrective maintenance is five times more costly than preventive maintenance.
@@
 
-The choice of prior parameters for the four component models are discussed in Section~\ref{sec:ex-prior};
-then, our maintenance policy is illustrated under three different exemplary failure time histories,
+The choice of prior parameters for the four component models are discussed in Section~\ref{sec:ex-prior}.
+Then, our maintenance policy is illustrated under three different exemplary failure time histories,
 described in Sections~\ref{sec:ex-1}, \ref{sec:ex-2} and \ref{sec:ex-3}.
-A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.
 
@@
 \end{tabular}
-\caption{Prior parameters for the four component types as used in subsequent numerical examples.
-The corresponding expected failure behaviour is visualized in Figure~\ref{fig:compprior1fig1}.}
+\caption{Prior parameters for the four component types as used in the numerical examples.}
+%The corresponding expected failure behaviour is visualized in Figure~\ref{fig:compprior1fig1}.}
 \label{tab:priorparams}
@@
 This is reflected in Figure~\ref{fig:tauhist1fig2T},
-where $\tausnow$ first decreases but then tends to increase during failure-free periods,
+***where $\tausnow$ first decreases but then tends to increase during failure-free periods,
 which is a consequence of adjusting prior expectations for type $C$ components
@@
 
-***move some text from figure~\ref{fig:tauhist1fig2T} caption to here or repeat?***
+Figure~\ref{fig:tauhist1fig2T}: 
+$\tausnow$ (left panel) decrease weakens and attains a near-constant speed from about $\tnow = 2$ during failure-free periods,
+with discrete drops at the failures of components $P_2$, $P_3$ and $H$ only.
+%With the failure of $H$ at time $\tnow = 8$,
+$\tausnow$ falls below $\delta = 0.1$ at time $\tnow = 6$,
+triggering preventive maintenance of the system.
+$\tausnow = 1.60$ at $\tnow = 0$, this corresponds to the optimal maintenance time
+in an age-based policy that takes the system as monolithic. 
+Since $\tausnow$ does not change dramatically most of the time, $\tstarnow$,
+the cost-optimal moment of maintenance on the absolute timescale (center panel),
+steadily increases, with small drops corresponding to drops in $\tausnow$,
+showing that as time progresses, accumulated information indicates that maintenance can be postponed.
+Consequently, $\gstarnow$ (right panel) is steadily decreasing,
+with small upward jumps at the failures of $P_2$ and $P_3$.
+%so the drops in $\tausnow$ do not entirely outweigh the higher likelihood of system failure
+%due to the failure of these components.
+%\textbf{***show $\Rsysnow(\tausnow)$???}
+At $\tnow = 6$, the expected unit cost rate is $0.033$,
+and so considerably lower than the expected cost rate of $0.2 / 1.6 = 0.125$
+for an age-based policy not accounting for component information.
 
@@
 
+A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.
 We now present a small simulation study

### 2016-12-01 cbm-rbd-paper.tex
writing sec 6

@@
 Note that the scale parameter for component type H is $1$,
-such that failure times for this component type are assumed to follow an Exponential distribution.
+such that the failure times for this component type are assumed to follow an Exponential distribution.
 In cases where only $H$ and one or both of $P_3$ and $P_4$ are functioning,
@@
 
-The expected component failure behaviour according to the parameter choices in Table~\ref{tab:priorparams}
+The expected component failure behaviour obtained by the parameter choices in Table~\ref{tab:priorparams}
 is visualized in Figure~\ref{fig:compprior1fig1},
 showing the prior predictive reliability function for a single component of each type.
-We see that, e.g., median prior expected failure times are
+Note that these functions are not plain Weibull reliability functions,
+but weighted averages over Weibull reliability functions according to the prior distribution over the scale parameter $\lambda_k$.
+We see that, e.g., the median prior expected failure times are
 $2.2$, $4.1$, $6.3$, and $3.1$ for type $C$, $H$, $M$, and $P$ components, respectively.
@@
 %for the four component types of the system depicted in Figure~\ref{fig:brakesys-layout},
-showing the expected failure behaviour.
-Note that each of these is not a plain Weibull reliability function,
-but a weighted average over Weibull reliability functions according to the prior distribution over the scale parameter.}
+showing the expected failure behaviour.}
 \label{fig:compprior1fig1}
@@
 In total, due to the late type $C$ failures, prior assumptions turn out to be somewhat pessimistic.
+
 This is reflected in Figure~\ref{fig:tauhist1fig2T},
-***where $\tausnow$ first decreases but then tends to increase during failure-free periods,
+where $\tausnow$ (left panel) first decreases quickly but then tends to decrease more slowly during failure-free periods,
 which is a consequence of adjusting prior expectations for type $C$ components
 due to their unexpected reliability.
-
-Figure~\ref{fig:tauhist1fig2T}: 
-$\tausnow$ (left panel) decrease weakens and attains a near-constant speed from about $\tnow = 2$ during failure-free periods,
-with discrete drops at the failures of components $P_2$, $P_3$ and $H$ only.
-%With the failure of $H$ at time $\tnow = 8$,
+Large drops of $\tausnow$ happen only at the failures of components $P_2$, $P_3$ and $H$
+at times 3, 4 and 8, respectively,
+as $\Rsysnow(t)$ changes considerably at these moments.
 $\tausnow$ falls below $\delta = 0.1$ at time $\tnow = 6$,
@@
 %\textbf{***show $\Rsysnow(\tausnow)$???}
-At $\tnow = 6$, the expected unit cost rate is $0.033$,
-and so considerably lower than the expected cost rate of $0.2 / 1.6 = 0.125$
-for an age-based policy not accounting for component information.
+At $\tnow = 6$, the expected operational cycle cost rate is $0.033$,
+and so considerably lower than the operational cycle cost rate of $0.2 / 1.6 = 0.125$
+that one obtains by maintaining the system preventively at time 1.6,
+as suggested by the age-based policy that disregards the information from component monitoring.
+In this example, using the component failure information allows to lower the cost rate by 73\%.
 
@@
 \caption{Illustration of the gains due to the parameter update at each $\tnow$,
-assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.
-$\tausnow$ (left panel) is consistently lower for the non-adaptive algorithm,
-same with $\tstarnow$ (center panel).
-This is because the adaptive algorithm recognizes that system components are more reliable than expected,
-leading to lower expected unit cost rates $\gstarnow$ (right panel).
-$\tausnow$ for the non-adaptive algorithm drops below $\delta = 0.1$ at $\tnow = 4$,
-while maintenance is triggered for the adaptive algorithm at $\tnow = 6$.
-The parameter update thus allows to run the system for two more time units,
-corresponding to a unit cost rate of $0.2 / 6 = 0.033$ instead of $0.2 / 4 = 0.05$,
-a reduction of 33\%.}
+assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$.}
 \label{fig:tauhist1fig3T}
@@
 
-The effect of this continuous parameter update is illustrated in Figure~\ref{fig:tauhist1fig3T}.
+The effect of the continuous parameter update in our policy is illustrated in Figure~\ref{fig:tauhist1fig3T}.
 There, the results as seen already in Figure~\ref{fig:tauhist1fig2T} are compared
-to the case when component parameters are not updated,
+to the case when component parameters are not updated during the operation of the system,
 while still accounting for the fact that components age,
@@
 %***so dynamic but not adaptive?***
-***We see that $\tausnow$ is steadily decreasing in the no update case,
+We see that $\tausnow$ (left panel) is decreasing more quickly in the no update case,
 with the jumps at component failure times being less pronounced than in the update case.
@@
 and maintenance is scheduled too early,
-leading to lower prospective ($\gstarnow$) and total ($\gtotalnow$) expected unit cost rates.
+%$\tausnow$ (left panel) is consistently lower for the non-adaptive algorithm,
+%same with $\tstarnow$ (center panel).
+%This is because the adaptive algorithm recognizes that system components are more reliable than expected,
+leading to lower expected operational cycle cost rates $\gstarnow$ (right panel).
+$\tausnow$ for the policy without parameter update drops below $\delta = 0.1$ at $\tnow = 4$,
+while maintenance is triggered for the algorithm with parameter update at $\tnow = 6$.
+The parameter update thus allows to run the system for two more time units,
+corresponding to a unit cost rate of $0.2 / 6 = 0.033$ instead of $0.2 / 4 = 0.05$,
+a reduction of 33\%.
 
@@
 as visualized in Figure~\ref{fig:tauhist2fig3T}.
-***$\tausnow$ values for the model with parameter updates vary around those obtained without parameter updates,
-same for $\tstarnow$ and $\gstarnow$.
-With $\delta = 0.1$, the moment of maintenance is $2.6$ and $2.5$, respectively,
-this shows that for this failure history, where there is indeed no need to update,
-and $\tausnow$ behaviour is dominated by the update of the system reliability block diagram.
+There, $\tausnow$ values for the policy with parameter updates vary around those obtained for the policy without parameter updates,
+and a similar behavior for $\tstarnow$ and $\gstarnow$ is observed.
+With $\delta = 0.1$, preventive maintenance is carried out at times $2.6$ and $2.5$ for the two policies, respectively.
+This shows that for this failure history, in which there is not much to be gained by the parameter update,
+$\tausnow$ behaviour is dominated by the update of the system reliability block diagram.
 Here, any differences due to the update are very small in comparison to the gains offered by the continuous update
@@
 %containing slightly early failures of type $P$ components.
-***With observed failure behaviour more or less in line with expectations,
-the model with and without continuous update perform similarly,
+With observed failure behaviour more or less in line with expectations,
+both the policies with and without continuous update perform similarly,
 unlike in case of the first failure history as depicted in Figure~\ref{fig:tauhist1fig3T},
@@
 with $C_2 = 0.1$, $C_3 = 0.2$, $C_4 = 0.8$ $H = 1$, $P_2 = 0.3$, $P_3 = 0.4$,
-and we follow the system until $\tnow = 1$.
-
-***see Figure~\ref{fig:tauhist4fig3T}
-
-***without update $\tausnow$ consistently higher,
-adaptive algorithm takes surprisingly early failures into account.
-Unlike in the other two scenarios, the overall trend for $\tstarnow$ is a decrease,
-expected cycle costs are underestimated without update***
-
-Model with update consistently suggests to maintain earlier,
-but for both models, $\tausnow$ drops below $\delta = 0.1$ upon the failure of H at $\tnow = 1$.
-Like in failure history 2, the structural information plays an important part in the policy.
-This aspect will be confirmed in the small simulation study described next.
+and we follow the system until $\tnow = 1$,
+see Figure~\ref{fig:tauhist4fig3T}.
+
+The policy without parameter update leads to consistently higher $\tausnow$ values,
+while the policy with parameter update takes the surprisingly early failures into account.
+Unlike in the other two failure histories, $\tstarnow$ is generally decreasing,
+indicating that maintenance should happen much earlier than expected initially.
+The policy with parameter update consistently suggests to maintain earlier than the policy without update,
+but for both models, $\tausnow$ drops below $\delta = 0.1$ upon the failure of H at $\tnow = 1$,
+obtaining an operational cycle cost rate of $0.2$.
+In contrast, 
+the age-based policy that disregards the information from component monitoring
+would have scheduled maintenance for time $1.6$,
+but it is very unlikely that the system will still function by that time.
+If the system fails between time 1 and time 1.6,
+then the age-based policy would lead to an operational cycle cost of $0.625$ to $1$,
+much higher than for our policy.
+%expected cycle costs are underestimated without update***
+
+Like in failure history 2, the structural information (which components still function?)
+seems to deliver a major part of the gains for our CBM policy,
+whereas the parameter update seems most effective in situations where
+component failures happen later than expected.
+These findings are confirmed by results from a small simulation study described next.
 
@@
 
-A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.
+%A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.
 We now present a small simulation study

### 2016-12-01 plotdefs.R

@@ -12,7 +12,8 @@ minirel <- list(theme(axis.title = element_blank()),
                 scale_y_continuous(breaks=c(0, 0.5, 1)))
 minirelsize <- 1.5
 
-ijarcols <- c("#b2df8a", "#1f78b4")
+#ijarcols <- c("#b2df8a", "#1f78b4")
+ijarcols <- c("#1f78b4", "#b2df8a")
 ijarcol <- scale_colour_manual(values = ijarcols)
 ijarfill <- scale_fill_manual(values = ijarcols)
 

### 2016-12-01 cbm-rbd-paper.tex
writing sec 8

@@
 %A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.
-We now present a small simulation study
-
-$\esys$ is the number of system failures,
-$\mrsys$ is the mean realized system runtime (I called this 'cycle length' before),
-$\bar{g}$ is the mean realized unit cost rate.
-
-CBM = condition-based maintenance
-ABM = age-based maintenance
-CM = corrective maintenance
-cpu = continuous parameter update
-epu = end of cycle parameter update
-npu = no parameter update
-
-Case 1: failure behaviour as expected,
-failure times simulated using Weibull scale parameters $\lambda_k = \ykz$ from Table~\ref{tab:priorparams}.
-
-Obviously, CM has always 5 system failures in the 5 cycles, while CBM and ABM (mostly) avoid system failures.
-Mean system runtimes are longest for CM because it runs the system until failure, but this leads to the highest mean unit cost rates.
-CBM with continuous parameter update has the lowest mean unit cost rate since it has the longest system runtimes without failures.
-The age-based policy without parameter update always schedules maintenance for $\tau_*^{(0)} = 1.6$, and as the system does not fail before this time in any of the simulations, the system runtime is always 1.6 and the unit cost rate is $0.2 / 1.6 = 0.125$.
+We conducted a small simulation study to illustrate the performance of our policy
+as compared to corrective and age-based policies.
+To be able to discern the effect of parameter learning over several operational cycles,
+we simulated component failure times for five subsequent operational cycles for each simulation repetition.
+We thus can compare policies that carry information gained in one operational cycle to the next operational cycle
+with policies that do not update component parameters at the end of an operational cycle.
+We also distinguish the condition-based maintenance policies with and without continuous parameter update
+as in Section~\ref{sec:examples}.
+In total, we compare the six maintenance policies listed in Table~\ref{tab:sim-abbrev},
+which also gives the abbreviations used in Figures~\ref{fig:br1sim1fig5Tt01}, \ref{fig:br1sim2fig5Tt01} and \ref{fig:br1sim3fig5Tt01}.
+
+\begin{table}
+\centering
+\begin{tabular}{ll}
+  \toprule
+Policy & Description \\
+  \midrule
+CBM-cpu & Condition-based maintenance (continuous parameter update)\\
+CBM-epu & Condition-based maintenance (end of cycle parameter update)\\
+CBM-npu & Condition-based maintenance (no parameter update)\\
+ABM-epu & Age-based maintenance (end of cycle parameter update)\\
+ABM-npu & Age-based maintenance (no parameter update)\\
+CM      & Corrective maintenance\\
+  \bottomrule
+\end{tabular}
+\caption{The six maintenance policies compared in the simulation study.}
+\label{tab:sim-abbrev}
+\end{table}
+
+We compare these policies by three simple performance measures,
+calculated for each repetition. %, which contains five operational cycles.
+$\esys$ is the number of system failures that occured when applying the policy,
+This is an integer between zero and five, as there are five operational cycles per repetition.
+$\mrsys$ is the mean realized system runtime,
+i.e., the average of the realized operational cycle length,
+taken over the five operational cycles per repetition.
+%(I called this 'cycle length' before),
+$\bar{g}$ is the mean realized operational cycle cost rate obtained over the five operational cycles.
+This is calculated as the sum of preventive and corrective maintenance costs incurred in the five operational cycles,
+divided by the sum of the five realized operational cycle lengths.
+%This is a weighted average of the realized operational cycle cost rate for each of the five operational cycles,
+%with weights proportional to the corresponding realized operational cycle length.
+%This equals
+
+We use again the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout},
+together with the prior parameters for the component models as given in Table~\ref{tab:priorparams},
+and assume that $c_c = 1$ and $c_p = 0.2$ like before.
+We study three data scenarios A, B and C, corresponding to failure times as expected, as well as
+failure times earlier and later than expected.
 
@@
 \includegraphics[width=\textwidth]{br1sim1fig5Tt01ac}
-\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
-where failure times are simulated according to prior parameters.}
+\caption{Simulation study with 20 repetitions, where each repetition consists of 5 subsequent operational cycles.
+Case A: $\lambda_k = \ykz$.}
 \label{fig:br1sim1fig5Tt01}
@@
 
-Case 2: failures earlier than expected,
-failure times simulated using
-$\lambda_k = 0.5 \ykz$ (Figure~\ref{fig:br1sim2fig5Tt01})
+\subsection{Case A: failure times as expected, $\lambda_k = \ykz$}
+\label{sec:case1}
+
+For this scenario, we simulated component failure times according to prior expectations,
+i.e., component failure times were simulated as Weibull failure times
+with the scale parameter $\lambda_k$ chosen as equal to the expert's prior guess $\ykz$
+for all four component types.
+The results are depicted in Figure~\ref{fig:br1sim1fig5Tt01}.
+
+Obviously, the corrective maintenance policy (CM) results in $\esys = 5$ for all 20 repetitions,
+as it cannot lead to preventive maintenance.
+In contrast, all condition-based (CBM) and age-based policies can avoid system failures entirely (with a single exception for ABM-epu).
+Mean system runtimes are longest for CM because it runs the system until failure,
+but this leads to the highest mean cost rates.
+The condition-based maintenance policy with continuous parameter update (CBM-cpu) obtains the lowest mean cost rates,
+since it leads to the longest system runtimes without system failures.
+CBM-epu and CBM-npu have slightly higher cost rates,
+as they lead to shorter system runtimes.
+The age-based policy without parameter update (ABM-npu)
+always schedules maintenance for $\tau_*^{(0)} = 1.6$.
+As the system does not fail before this time in any of the five operational cycles within the 20 repetitions,
+the mean realized system runtime is constantly $1.6$, with mean cost rate $0.2 / 1.6 = 0.125$.
 
@@
 \includegraphics[width=\textwidth]{br1sim2fig5Tt01ac}
-\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
-where failure times are simulated as being earlier ($0.5 \times$ MTTF) than expected.}
+\caption{Simulation study with 20 repetitions, where each repetition consists of 5 subsequent operational cycles.
+Case B: $\lambda_k = 0.5\ykz$.}
 \label{fig:br1sim2fig5Tt01}
@@
 
-Case 3: failures later than expected,
-failure times simulated using $\lambda_k = 2 \ykz$ from Table~\ref{tab:priorparams}.
+\subsection{Case B: failure times earlier than expected, $\lambda_k = 0.5 \ykz$}
+\label{sec:case2}
+
+For the second scenario,
+component failure times were simulated as being earlier than expected,
+by choosing $\lambda_k$ for all component types as half the size of the expert's prior guess,
+i.e., $\lambda_k = 0.5 \ykz$ for all $k =$ C, H, M, P.
+%($0.5 \times$ MTTF) than expected.
+The results are depicted in Figure~\ref{fig:br1sim2fig5Tt01}.
+
+Here, both corrective and age-based policies cannot avoid system failures entirely.
+The condition-based policies result in two to three system failures in the $20 \times 5 = 100$ system runs,
+whereas the age-based policies result in nine to ten system failures.
+System runtimes are less variable for the age-based policies
+since they do not use the current system structure information, %available information on the component level,
+i.e., which components have failed and which not. %during operational cycles
+System runtimes are more variable for the condition-based policies,
+but longer on average, leading to lower realized cost rates.
+Again, CBM-cpu performs slightly better than CBM-epu
+as it has the possibility to learn within an operational cycle as well.
+CBM-npu does surprisingly well, considering that it never updates prior component parameters. 
+This confirms the observation from Section~\ref{sec:ex-3}
+that current system structure information delivers a major part of the gains for our CBM policy.
 
@@
 \includegraphics[width=\textwidth]{br1sim3fig5Tt01ac}
-\caption{***Simulation study, each repetition consists of simulating 5 subsequent operational cycles,
-where failure times are simulated as being later ($2 \times$ MTTF) than expected.}
+\caption{Simulation study with 20 repetitions, where each repetition consists of 5 subsequent operational cycles.
+Case C: $\lambda_k = 2\ykz$.}
 \label{fig:br1sim3fig5Tt01}
@@
 
-% ------------- overview figures ----------------------------------
+\subsection{Case C: failure times later than expected, $\lambda_k = 2 \ykz$}
+\label{sec:case3}
+
+The third scenario consists of component failure times taht are later than expected,
+obtained by simulating Weibull lifetimes using $\lambda_k = 2 \ykz$ for all four component types.
+The results are depicted in Figure~\ref{fig:br1sim3fig5Tt01}.
+
+As the expert's information now underestimates component lifetimes,
+all policies (except the corrective policy) act quite cautiously,
+leading to complete avoidance of system failures.
+However, the mean system runtimes $\mrsys$ exhibit
+a clear hierarchy between age-based and condition-based policies,
+and within these two groups a clear effect of the parameter update strategy.
+Here, CBM-cpu obtains the longest system runtimes, and thus the lowest cost rates,
+with a clear advantage over CBM-epu and CBM-npu.
+
+Overall, it seems that CBM-cpu can play its adaptive strengths most effectively
+when prior assumptions were too pessimistic,
+while also performing well when prior assumptions were correct or too optimistic.
+%This means that experts may confidently tend towards pessimistic specifications
+%of the component mean time to failures $\yzk$.
+
+% ------------- old overview figures ----------------------------------
 \iffalse
@@
 
-*** study other replacement schemes, e.g., replacing only failed components:
-when repaired/replaced components are present in system,
-then one needs to use actual ages (and not time since system startup) in parameter update,
-introduces new component type for $\Rsysnow(t)$ calculation but with same posterior parameters as unreplaced component type.
-Repaired/replaced components require the creation of a separate type in the survival signature decomposition
-and thus the calculation of separate posterior predictive probabilities
-$P(C^k_t = l_k \mid \nkz,\ykz,\vectknow)$,
-which use, however, the same hyperparameter learning (using actual component ages) as the `parent type'.
-
-***common-cause failures will seriously reduce RLD in a way currently not covered by our model.
-This needs to be implemented on the level of component models,
-specifically $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ 
-(not a product anymore if common-case failures can affect several component times at once).
-Combine ideas from \cite{2015:coolen-coolen-maturi} and \cite{Troffaes2014a}.
-
-*** move to sets of priors, set of residual life distributions like in \cite{2016:walter-coolen}.
-Leads to set of $\gnow(\tau)$, finding (set of) $\tausnow$ is then non-trivial,
-needs decision criteria from imprecise probability literature like E-admissibility, maximality, or maximin
-\citep[see, e.g., \S 9***][]{itip}.
-
-*** to use the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
-we would need to add interval-censored data (failure has happened between last and current inspection)
+In this paper, we have proposed a new condition-based maintenance policy
+for systems based on monitoring of the functioning of components.
+We use the survival signature to compute system reliability functions
+based on component models, and propose to use Weibull component models
+with conjugate priors to express expert knowledge.
+The resulting policy shows promising results in
+different numerical exmples and a small simulation study.
+
+There are several aspects in our modelling that warrant further investigation.
+So far, we assume that component failure times are observed precisely via monitoring.
+In many applications however, the component status can only be determined
+at inspections, leading to interval-censored failure time observations.
+Extending the model to account for interval-censored failure times
+would allow to derive a condition-based maintenance policy with inspections,
+which determines the optimal moment of inspection of the system.
+%*** extend the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
+%we would need to add interval-censored data (failure has happened between last and current inspection)
+
+As mentioned at the end of Section~\ref{sec:costrate},
+we currently disregard the possibility of common cause failures,
+i.e., simultaneous failures with a shared root cause.
+Common cause failures seriously reduce the system reliability,
+and can lead to sudden system failures.
+To offer a realistic estimation of the optimal time to maintenance $\tausnow$,
+the system RLD $\Rsys(t)$ needs to account for such failures.
+%This needs to be implemented on the level of component models,
+%specifically $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ 
+%(not a product anymore if common-case failures can affect several component types at once).
+When common cause failures can affect several component types at once,
+the joint posterior predictive probabilities $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ in \eqref{eq:sysrel-survsign}
+cannot be obtained as a product of component posterior predictive probabilities.
+We think that by combining ideas from \cite{2015:coolen-coolen-maturi} and \cite{Troffaes2014a},
+the proposed policy could be extended to accomodate common cause failures.
+
+In our policy, we assumed that in both preventive and corrective repair
+all components are restored an as good as new state.
+An obvious alternative is to only replace the failed components instead,
+but would this offer any advantage?
+Furthermore, could it be even optimal to repair a subset of the failed components only?
+Such selective component replacement schemes
+seem to be a promising area for research.
+To account for different ages of components at system startup,
+one could introduce artificial component types in \eqref{eq:sysrel-survsign},
+grouping components both by type and by age.
+However, computational complexity increases with the number of component types,
+%and the conceptual algorithmic advantage of the survival signature vanishes
+%when each component forms its own type
+so it seems most promising to replace batches of components,
+or all components of one type.
+%*** study other replacement schemes, e.g., replacing only failed components:
+%when repaired/replaced components are present in system,
+%then one needs to use actual ages (and not time since system startup) in parameter update,
+%introduces new component type for $\Rsysnow(t)$ calculation but with same posterior parameters as unreplaced component type.
+%Repaired/replaced components require the creation of a separate type in the survival signature decomposition
+%and thus the calculation of separate posterior predictive probabilities
+%$P(C^k_t = l_k \mid \nkz,\ykz,\vectknow)$,
+%which use, however, the same hyperparameter learning (using actual component ages) as the `parent type'.
+
+Another promising extension would be to use sets of conjugate priors for the component models.
+This approach is described in \cite{2016:walter-coolen},
+leading to sets of current residual life distributions $\Rsys(t)$.
+Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
+The determination of the (set of) optimal time(s) to maintenance $\tausnow$
+is then non-trivial,
+and would involve decision criteria discussed in the imprecise probability literature,
+like E-admissibility, maximality, or maximin \citep[see, e.g., \S 8][]{itip}.
 
@@
 
-CAMPI
-
-Frank Coolen for inspiring discussions
+Gero Walter was supported by the DINALOG project CAMPI
+(``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'').
+
+Both authors would like to thank Frank Coolen for inspiring discussions
+and valuable hints on maintenance optimization criteria.
 

### 2016-12-01 cbm-rbd-paper.tex
sdf comments sec 1

@@
 \begin{abstract}
-We propose a new way of developing a condition-based maintenance policy for complex systems,
-based not on a one-dimensional continuous degradation signal,
-but on the status of all components within a system.
+We propose a new condition-based maintenance policy for complex systems,
+based on the status (working, defective) of all components within a system,
+as well as the relaibility block diagaram of the system.
 
@@
 a generalization of the system signature allowing for multiple component types,
-we obtain a predictive distribution for system survival time
+we obtain a predictive distribution for the system survival time
 %(also known as RUL, remaining useful life)
-(known as residual life distribution, RLD)
+(also known as residual life distribution, RLD)
 based on which of the system's components currently function or not,
@@
 
-Component time to failure is modeled by a Weibull distribution with fixed shape parameter.
+The time to failure of the components of the system
+is modeled by a Weibull distribution with a fixed shape parameter.
 The scale parameter is iteratively updated in a Bayesian fashion
 using the current (censored and non-censored) component lifetimes.
-Each component type has a separate model that may also include test data.
-
-The cost-optimal moment of repair for the system is obtained by minimizing the one-cycle unit cost rate.
-The unit cost rate is recalculated at fixed time points,
-leading to a dynamic policy since the aging of components and possible failures will change the cost-optimal moment of repair.
+Each component type has a separate (Weibull) model that may also include test data.
+
+The cost-optimal moment of replacement for the system is obtained by minimizing
+the expected cost rate per unit of time.
+The unit cost rate is recalculated when components fail
+or at the end of every (very short) fixed inter-inspection interval,
+leading to a dynamic maintenance policy,
+since the aging of components and possible failures will change the cost-optimal moment of repair in the course of time.
+Via numerical experiments, some insight into the performance of the policy is given.
 \end{abstract}
@@
 \begin{keyword}
-condition-based maintenance \sep system reliability \sep remaining useful life \sep survival signature \sep one-cycle unit cost rate\end{keyword}
+condition-based maintenance \sep system reliability \sep remaining useful life \sep survival signature \sep unit time cost rate\end{keyword}
 \end{frontmatter}
@@
 
-***main message:
-can do CBM for systems without degradation signal,
-especially useful for redundant systems,
-dynamic policy using one-cycle unit cost rate (exact, unlike renewal theorem based!),
-using iterative Bayesian update of component models,
-thus taking all information into account (history and current status)
-
-***Bayesian approach allows component models to include expert info, test data (if available),
-and information that can be gained from the behaviour of components in the running system
-in the form of censored and non-censored component lifetimes
-
-***we argue that our approach is CBM because it takes current system state into account
-and adjusts the moment of maintenance accordingly.
-
+Both in practice and academics,
+there is a growing interest in CBM (condition-based maintenance), see e.g.,
+\citet[pp.~15--55]{2016:oldekeizer}
+The central idea behind CBM is to maintain systems or components at the right time,
+i.e., before they fail, but not too early, in order to keep their reliability high and operating costs low.
+In this context a trade-off is made between the risk of failure during operation
+(which can lead to costly downtime: idle workforce, missed production, penalties, loss of reputation)
+and the costs of premature maintenance (wasting potential component or system lifetime,
+downtime cost, cost of executing unnecessary maintenance activities).
+
+Among the reasons for the above interest are the importance of increasingly short and
+reliable delivery times, and decreasing profit margins due to worldwide competition.
+All kinds of technical improvements have made it possible % it is more / better / earlier possible
+to estimate the condition of systems as a whole as well as their undelying components,
+whereas the cost for these technologies is decreasing rapidly,
+making the use of CBM policies even more feasible.
+
+Most CBM policies are based on a directly observable, continuously measurable condition or degradation signal.
+Alternatively, such a signal or health status is constructed
+using indirect measurements to determine the remaining useful life or time to failure of a system,
+see, e.g., \citet{2014:rul-review, 2011:rul-review-statistical}.
+
+In this paper, we propose an inspection-based CBM policy
+for when no degradation signal for the system is available,
+but where the status (working or not working) of the components can be monitored continuously.
+In this situation, one can use the system's reliability block diagram
+and information with respect to the status of its components
+to directly calculate the system residual life distribution (RLD),
+and base the maintenance policy for the system on this distribution.
+(In fact, our CBM policy can be seen as based on a multivariate degradation signal,
+where each component sends a binary signal, and the reliability block diagram is used for sensor fusion.)
+
+There are 3 types of triggers to review the system in our new policy:
+at the end of each very short inspection interval (1),
+directly after the failure of a component where the system still functions (2),
+and directly after the failure of a component due to which the system as a whole no longer can function (3).
+
+In case of a trigger of type (1),
+the currently used model for system failure times is updated
+to account for the aging of components,
+and the extra lifetime observed for the components.
+The latter information is taken into account via right-censored observations
+in a Bayesian parameter update step.
+
+In case of a trigger of type (2),
+when a component has failed since the last inspection but the system is still functioning,
+also the reliability block diagram of the system is updated.
+Based on the above changes,
+it is determined in both cases whether the system should be replaced now,
+or that this decision should be postponed until the next planned inspection moment,
+accepting the risk of a system breakdown before.
+In this context, the optimal moment of maintenance
+is calculated based on minimizing the expected maintenance-related cost per unit of time for the present operational cycle,
+where an operational cycle starts with a new system, and ends after this system has been replaced by a(n as good as) new system.
+
+In case of a trigger of type (3),
+the currently used model for system failure times is updated
+like in case of a trigger of type (2)
+to account for the information gained on components
+until the moment of system failure.
+Hereafter, a new system is installed,
+using the updated models for all components based on the insight obtained from the concluded operational cycle.
+
+At first sight, the above quasi-continous updating of the component failure models,
+and the system reliability block diagram,
+as well as redetermining the best moment to replace the system,
+seems to result in a (very) nervous maintenance policy.
+However, due to the very short calculation times,
+only at certain moments in time people involved in the execution of maintenance tasks
+need to receive detailed information,
+whereas during the remaining time,
+all can be handled automatically, as done at the moment within, e.g., many safety systems.
+
+The setup of the rest of the paper is as follows.
+In Section~\ref{sec:literature}, we show our contribution to the CBM literature.
+Next, in Sections~\ref{sec:sysrel}, \ref{sec:adaptive-sysrel-weibull} and \ref{sec:policy},
+the three main steps in our policy are discussed in detail.
+Hereafter, in Sections~\ref{sec:examples} and \ref{sec:sim},
+our policy is applied further to an example.
+Finally, in Section~\ref{sec:outlook},
+a short summary and our main conclusions are given,
+followed by some suggestions for further research.
+
+\iffalse
+% ----------------------------------------------------------------------------------------------------
 \subsection*{---------------------}
@@
 %but in practice threshold often not known
-
 \subsection*{---------------------}
@@
 and we allow for set-up time
-
-\section{Literature***}
+\fi
+% ----------------------------------------------------------------------------------------------------
+
+\section{Literature review}
+\label{sec:literature}
 

### 2016-12-01 cbm-rbd-paper.tex
sdf comments sec 2

@@
 and information with respect to the status of its components
-to directly calculate the system residual life distribution (RLD),
+to directly calculate the system residual life distribution,
 and base the maintenance policy for the system on this distribution.
@@
 In case of a trigger of type (1),
-the currently used model for system failure times is updated
+the currently used model for component failure times is updated
 to account for the aging of components,
@@
 In case of a trigger of type (3),
-the currently used model for system failure times is updated
-like in case of a trigger of type (2)
+the currently used component failure time distributions are updated
+like in case of a trigger of type (1) and (2)
 to account for the information gained on components
@@
 
+Although there is a lot of literature on CBM policies for multi-component systems,
+see, e.g., \citet{2016:oldekeizer},
+we found only a few papers having some relation to our approach.
+
+The paper that comes closest to this paper is the paper by \citet{2013:si-et-al}.
+In that paper, the condition of a system is inspected,
+where the moment of the next inspection is determined via an updated degradation path based on the present condition of the system.
+The authors provide exact expressions for the RUL (remaining useful lifetime) distribution,
+also known as residual life distribution (RLD),
+which is updated in an empirical Bayesian framework using conjugate priors.
+The RLD is used to construct a replacement decision model using a cost rate.
+
+One of the main differences between \citet{2013:si-et-al} and our paper
+is that we use component status data and the system reliability block diagram instead of the degradation signal
+as basis for calculating the system RUL.
+Another main difference is that our policy can be applied to arbitrary system configurations
+(i.e., arbitrary reliability block diagrams with arbitrary components),
+whereas the method given by \citet{2013:si-et-al} can only be applied to single components.
+A third difference concerns how the cost rate is calculated.
+\citet{2013:si-et-al} calculate this rate using the renewal-reward theory approximation.
+Essential for using the renewal-reward theory for calculating the expected cost per unit of time
+is that the relevant characteristics of the system considered and its environment are not changing,
+i.e. that the failure behavior of the system,
+in essence its relibability function, does not change over time,
+and that we use the same policy with the same parameter values during a statistically long enough period of time.
+However, due to the update method related to the CBM policy presented in this paper
+like in \citet{2013:si-et-al}, we cannot use this approximate calculation method,
+and therefore use the exact formula for the average cost per unit of time.
+
+Another paper that includes some of the aspects included in our paper is the paper by \citet{2012:sun-et-al}.
+The authors construct a health index for a system based on sensor measurements,
+where the health status prediction is updated sequentially,
+resulting in a RUL distribution like with our method.
+However, in contrast to our paper, the authors do not link their RUL distribution to any maintenance decisions.
+
+\citet{2011:kim-et-al} developed a periodic monitoring CBM policy
+where a maintenance decision is triggered when a Bayesian control chart
+(a sequentially updated health indicator) exceeds a control limit (threshold)
+that is determined by minimizing the expected average cost per time unit.
+We use the same cost criterion, but base the maintenance policy decision directly on our exact RLD.
+
+To summarize the main contribution of our paper,
+it introduces a CBM-like policy that does not require knowledge of the degradation path of the system,
+but can take into account continuous changes in the system reliability block diagram,
+as well as changes in the component failure time distribution.
+
+% ----------------------------------------------------------------------------------------------------
+\iffalse
 ***CBM via RUL/RLD, $M^*$ out of $N$ policies?
-
 ***also generally Bayesian methods in maintenance optimization?
-
 ***cite CBM review Olde Keizer, Flapper, Teunter, and other refs from it?
@@
 Our approach is different, as we get an exact formulation for the system RUL directly.
-
 \end{scriptsize}
+\fi
+% ----------------------------------------------------------------------------------------------------
 

### 2016-12-01 cbm-rbd-paper.tex
final polishing

@@
 as well as the relaibility block diagaram of the system.
-
+%
 By means of the survival signature,
 a generalization of the system signature allowing for multiple component types,
-we obtain a predictive distribution for the system survival time
+we obtain a predictive distribution for the system survival time,
 %(also known as RUL, remaining useful life)
-(also known as residual life distribution, RLD)
+also known as residual life distribution,
 based on which of the system's components currently function or not,
@@
 using the current (censored and non-censored) component lifetimes.
-Each component type has a separate (Weibull) model that may also include test data.
+Each component type has a separate Weibull model that may also include test data.
 
@@
 
-In this paper, we propose an inspection-based CBM policy
+In this paper, we propose a kind of inspection-based CBM policy
 for when no degradation signal for the system is available,
@@
 and base the maintenance policy for the system on this distribution.
-(In fact, our CBM policy can be seen as based on a multivariate degradation signal,
-where each component sends a binary signal, and the reliability block diagram is used for sensor fusion.)
+In fact, our CBM policy can be seen as based on a multivariate degradation signal,
+where each component sends a binary signal, and the reliability block diagram is used for sensor fusion.
 
@@
 and directly after the failure of a component due to which the system as a whole no longer can function (3). 
+We denote each review of the system in reaction to these triggers by `evaluation',
+since the system RLD is re-evaluated at each of these time points.
+We use the term `evaluation' in place of the term `inspection',
+because the re-evaluation of the system RLD does not require a physical inspection,
+as we assume to learn of the exact failure times of components online via continuous monitoring.
 
@@
 it is determined in both cases whether the system should be replaced now,
-or that this decision should be postponed until the next planned inspection moment,
+or that this decision should be postponed until the next planned evaluation moment,
 accepting the risk of a system breakdown before.
@@
 is calculated based on minimizing the expected maintenance-related cost per unit of time for the present operational cycle,
-where an operational cycle starts with a new system, and ends after this system has been replaced by a(n as good as) new system.
+where an operational cycle starts with a new system, and ends after this system has been replaced by an as good as new system.
 
@@
 The setup of the rest of the paper is as follows.
-In Section~\ref{sec:literature}, we show our contribution to the CBM literature.
+In Section~\ref{sec:literature}, we describe our contribution to the CBM literature.
 Next, in Sections~\ref{sec:sysrel}, \ref{sec:adaptive-sysrel-weibull} and \ref{sec:policy},
@@
 but can take into account continuous changes in the system reliability block diagram,
-as well as changes in the component failure time distribution.
+as well as changes in the component failure time distributions.
 
@@
 Overall, it seems that CBM-cpu can play its adaptive strengths most effectively
-when prior assumptions were too pessimistic,
-while also performing well when prior assumptions were correct or too optimistic.
+when prior assumptions are too pessimistic,
+while also performing well when prior assumptions are correct or too optimistic.
 %This means that experts may confidently tend towards pessimistic specifications
@@
 
-\section{Outlook}
+\section{Summary and outlook}
 \label{sec:outlook}
@@
 We use the survival signature to compute system reliability functions
-based on component models, and propose to use Weibull component models
+for given component models, and propose to use Weibull component models
 with conjugate priors to express expert knowledge.
@@
 So far, we assume that component failure times are observed precisely via monitoring.
-In many applications however, the component status can only be determined
+However, in many applications, the component status can only be determined
 at inspections, leading to interval-censored failure time observations.
 Extending the model to account for interval-censored failure times
-would allow to derive a condition-based maintenance policy with inspections,
-which determines the optimal moment of inspection of the system.
+would allow to derive a condition-based maintenance policy with wider-spaced inspections,
+which could also determine the optimal moment for the next inspection of the system.
 %*** extend the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
@@
 To offer a realistic estimation of the optimal time to maintenance $\tausnow$,
-the system RLD $\Rsys(t)$ needs to account for such failures.
+the system RLD $\Rsys(t)$ needs to account for such failures when they are possible.
 %This needs to be implemented on the level of component models,
@@
 the joint posterior predictive probabilities $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ in \eqref{eq:sysrel-survsign}
-cannot be obtained as a product of component posterior predictive probabilities.
+cannot be obtained as a product of component posterior predictive probabilities any more.
 We think that by combining ideas from \cite{2015:coolen-coolen-maturi} and \cite{Troffaes2014a},
@@
 In our policy, we assumed that in both preventive and corrective repair
-all components are restored an as good as new state.
-An obvious alternative is to only replace the failed components instead,
+all components are restored to an as good as new state.
+An obvious alternative is to only replace the failed components,
 but would this offer any advantage?

### 2016-12-01 cbm-rbd-paper.tex
abstract and keywords for submission

@@
 based on the status (working, defective) of all components within a system,
-as well as the relaibility block diagaram of the system.
+as well as the reliability block diagaram of the system.
 %

### 2016-12-01 cbm-rbd-paper.tex
final stuff for submission

@@
 We consider the well-known Weibull model for component lifetimes,
-which is used in a wide variety of reliability studies \textbf{***more motivation Weibull***}. 
+which is used in a wide variety of reliability studies. 
 To keep things simple, we assume that the shape parameter of the Weibull distribution is known,
@@
 This dynamic and adaptive maintenance policy is described in more detail in Section~\ref{sec:operationalprocedure};
-a graphical overview is given in Figure~\ref{fig:procedure}.
+a flow chart for the policy is given in Figure~\ref{fig:procedure}.
 
@@
 During an operational cycle,
-$\tausnow$ is recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
+$\tausnow$ is usually recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
 %where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.

### 2016-12-01 sim-study-2.R
save sim study objects

@@ -489,4 +489,13 @@ pdf("br1sim4fig5T.pdf", width = 6, height = 6)
 br1sim4fig5T
 dev.off()
 
+
+#
+
+# save stuff
+ststr <- paste("br1sim", 1:3, sep="")
+enstr <- c("Tt01", "prTt01", "prprTt01", "a", "apr", "c")
+savelist <- as.vector(sapply(ststr, function(brstr) paste(brstr, enstr, sep="")))
+save(list = savelist, file = "papersimobjects")
+
 #

### 2016-12-01 sim-study-2.R
load sim study objects

@@ -497,5 +497,6 @@ ststr <- paste("br1sim", 1:3, sep="")
 enstr <- c("Tt01", "prTt01", "prprTt01", "a", "apr", "c")
 savelist <- as.vector(sapply(ststr, function(brstr) paste(brstr, enstr, sep="")))
 save(list = savelist, file = "papersimobjects")
+load("papersimobjects")
 
 #

### 2017-03-07 answer-to-reviewers.tex
Setup answer to reviewers

\documentclass[authoryear]{elsarticle}

% ------------ packages -------------

\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{graphicx}
\usepackage[english]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{sidecap}

\usepackage{url}
\usepackage[bookmarks]{hyperref}

%\usetikzlibrary{shapes.misc,fit}
\usetikzlibrary{%
   arrows,%
   calc,%
   fit,%
   patterns,%
   plotmarks,%
   shapes.geometric,%
   shapes.misc,%
   shapes.symbols,%
   shapes.arrows,%
   shapes.callouts,%
   shapes.multipart,%
   shapes.gates.logic.US,%
   shapes.gates.logic.IEC,%
   er,%
   automata,%
   backgrounds,%
   chains,%
   topaths,%
   trees,%
   petri,%
   mindmap,%
   matrix,%
   calendar,%
   folding,%
   fadings,%
   through,%
   patterns,%
   positioning,%
   scopes,%
   decorations.fractals,%
   decorations.shapes,%
   decorations.text,%
   decorations.pathmorphing,%
   decorations.pathreplacing,%
   decorations.footprints,%
   decorations.markings,%
   shadows}

%\usepackage{hyperref}
%\usepackage[bookmarks]{hyperref}
%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}

% ------------ custom defs -------------

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}
\newcommand{\posrealszero}{\reals_{\ge 0}}
\newcommand{\naturals}{\mathbb{N}}

\newcommand{\dd}{\,\mathrm{d}}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{{\bm#1}}

\newcommand{\uz}{^{(0)}} % upper zero
\newcommand{\un}{^{(n)}} % upper n
\newcommand{\ui}{^{(i)}} % upper i

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ol}[1]{\overline{#1}}

\newcommand{\Tsys}{T_\text{sys}}

\newcommand{\Rsys}{R_\text{sys}}
\newcommand{\lRsys}{\ul{R}_\text{sys}}
\newcommand{\uRsys}{\ol{R}_\text{sys}}

\newcommand{\fsys}{f_\text{sys}}
\newcommand{\Fsys}{F_\text{sys}}
\newcommand{\lFsys}{\ul{F}_\text{sys}}
\newcommand{\uFsys}{\ol{F}_\text{sys}}

\newcommand{\lgt}{\ul{g}}
\newcommand{\ugt}{\ol{g}}

\newcommand{\E}{\operatorname{E}}
\newcommand{\V}{\operatorname{Var}}
\newcommand{\wei}{\operatorname{Wei}} % Weibull Distribution
\newcommand{\ig}{\operatorname{IG}}   % Inverse Gamma Distribution

\newcommand{\El}{\ul{\operatorname{E}}}
\newcommand{\Eu}{\ol{\operatorname{E}}}

\def\yz{y\uz}
\def\yn{y\un}
%\def\yi{y\ui}
\newcommand{\yfun}[1]{y^{({#1})}}
\newcommand{\yfunl}[1]{\ul{y}^{({#1})}}
\newcommand{\yfunu}[1]{\ol{y}^{({#1})}}

\def\ykz{y\uz_k}
\def\ykn{y\un_k}

\def\yzl{\ul{y}\uz}
\def\yzu{\ol{y}\uz}
\def\ynl{\ul{y}\un}
\def\ynu{\ol{y}\un}
\def\yil{\ul{y}\ui}
\def\yiu{\ol{y}\ui}

\def\ykzl{\ul{y}\uz_k}
\def\ykzu{\ol{y}\uz_k}
\def\yknl{\ul{y}\un_k}
\def\yknu{\ol{y}\un_k}

\newcommand{\ykzfun}[1]{y\uz_{#1}}
\newcommand{\ykzlfun}[1]{\ul{y}\uz_{#1}}
\newcommand{\ykzufun}[1]{\ol{y}\uz_{#1}}

\def\nz{n\uz}
\def\nn{n\un}
%\def\ni{n\ui}
\newcommand{\nfun}[1]{n^{({#1})}}
\newcommand{\nfunl}[1]{\ul{n}^{({#1})}}
\newcommand{\nfunu}[1]{\ol{n}^{({#1})}}

\def\nkz{n\uz_k}
\def\nkn{n\un_k}
\newcommand{\nkzfun}[1]{n\uz_{#1}}
\newcommand{\nkzlfun}[1]{\ul{n}\uz_{#1}}
\newcommand{\nkzufun}[1]{\ol{n}\uz_{#1}}

\def\nzl{\ul{n}\uz}
\def\nzu{\ol{n}\uz}
\def\nnl{\ul{n}\un}
\def\nnu{\ol{n}\un}
\def\nil{\ul{n}\ui}
\def\niu{\ol{n}\ui}

\def\nkzl{\ul{n}\uz_k}
\def\nkzu{\ol{n}\uz_k}
\def\nknl{\ul{n}\un_k}
\def\nknu{\ol{n}\un_k}

\def\yknow{y_k^{(\tnow)}}
\def\nknow{n_k^{(\tnow)}}

\newcommand{\nk}{n_k}
\newcommand{\nkp}{n_k'}
\newcommand{\yk}{y_k}
\newcommand{\ykp}{y_k'}

\def\taut{\tau(\vec{t})}
\def\ttau{\tilde{\tau}}
\def\ttaut{\ttau(\vec{t})}
\def\tautk{\tau(\vec{t}_k)}

\def\MZ{\mathcal{M}\uz}
\def\MN{\mathcal{M}\un}

\def\MkZ{\mathcal{M}\uz_k}
\def\MkN{\mathcal{M}\un_k}

\def\PkZ{\Pi\uz_k}
\def\PkN{\Pi\un_k}
\newcommand{\PZi}[1]{\Pi\uz_{#1}}

\def\tnow{t_\text{now}}
\def\tpnow{t^+_\text{now}}

\newcommand{\Rsysnow}{R^{(t_\text{now})}_\text{sys}}
\newcommand{\Tsysnow}{T^{(t_\text{now})}_\text{sys}}
\newcommand{\tsysnow}{t^{(t_\text{now})}_\text{sys}}
\newcommand{\fsysnow}{f^{(t_\text{now})}_\text{sys}}
\def\eknow{e_k^{(\tnow)}}
\def\cknow{c_k^{(\tnow)}}
\def\vectknow{\vec{t}_k^{(\tnow)}}
\def\Phinow{\Phi^{(\tnow)}}
\newcommand{\gnow}{g^{(\tnow)}}
\newcommand{\tausnow}{\tau_*^{(\tnow)}}
\newcommand{\tprep}{\tau_{\text{prep}}}
\newcommand{\tthresh}{\tau_{\text{thresh}}}
\newcommand{\tstarnow}{t_*^{(\tnow)}}
\newcommand{\gstarnow}{g_*^{(\tnow)}}
\newcommand{\gtotalnow}{g_\text{total}^{(\tnow)}}
\newcommand{\esys}{e_\text{sys}}
\newcommand{\mrsys}{\bar{r}_\text{sys}}

% ------------ options -------------

\allowdisplaybreaks

\journal{RESS}

\begin{document}

% ------------ frontmatter -------------

\begin{frontmatter}
\title{Answer to Reviewers' Comments on our Manuscript
``Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability''}

\author[tue]{Gero Walter}
\ead{g.m.walter@tue.nl}
\author[tue]{Simme Douwe Flapper}
\ead{s.d.p.flapper@tue.nl}

\address[tue]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, Netherlands}

\begin{abstract}
We would like to thank the three anonymous reviewers for their detailed and constructive comments,
and their overall positive votum***.
We reproduce their comments here verbatim, with our answers interlaced.
Our answers are typeset in \emph{italic}.
\end{abstract}
\end{frontmatter}

% ------------ comments & answers -------------

\section*{Reviewer 1}

This paper proposes a condition-based maintenance (CBM) policy under a Bayesian framework. The key technique is to use the Bayesian method to update the reliability of each component based on the failure and censoring times observed so far. The probability distribution of each component type is assumed to be Weibull. For convenience, a conjugate prior distribution (inverse Gamma in the paper) is utilized for the Weibull scale parameter while assuming the shape parameter is known. Upon updating the posterior distribution for each component type, the conditional reliability of the system is updated based on the status of working/failed components, and the reliability diagram and signature of system. The object considered in the CBM policy is to minimize the expected cost rate of operational (inspection) cycle by determining the moment of replacement for the system.

The paper is well-written and the idea is clearly presented and demonstrated.
The problem is that it might have a significant overlap with the other paper the leading author submitted to another journal.

\smallskip

\emph{The other paper Reviewer 1 mentions here is:}

\nocite{2016:walter-coolen}
\bibliographystyle{elsarticle-harv}
\bibliography{refs}
\smallskip

\emph{We cite this paper in our manuscript in Section~4,
clearly stating, in the last paragraph before Section~4.1,
that our manuscript and the cited paper share the same basic approach, namely
Weibull component models with conjugate inverse Gamma prior
combined with a survival signature approach to calculate the system remaining life distribution (RLD).
As mentioned there, however, the focus of these two works is entirely different.
The cited paper develops an approach to use \textbf{sets} of inverse Gamma priors,
to allow for a sophisticated modeling of uncertainties in the component models,
resulting in \textbf{sets} of RLDs which are the ultimate result of the paper.
Instead, the present manuscript uses the basic approach to develop a \textbf{maintenance policy},
using the RLD as input for an optimization of the mean cost rate to find the cost-optimal moment of system maintenance.
Sections~4.1 to 4.3 describe the approach used for RLD calculation
in a similar way than the cited paper,
but with notation adapted to the manuscript's objective, i.e., defining a maintenance policy.
For readers to be able to understand our approach,
we considered it necessary to include a detailed description of the RLD calculation,
and not just refering to the paper. ***change wording in the paper?***
}

\medskip

I have the following questions that I hope the authors can answer.\\
Questions:
\begin{enumerate}
\item In cases of pessimistic and optimistic priors, should we continually update or do not update component reliability in terms of minimizing the overall cos[t]?

\smallskip

\emph{In both cases, it is optimal to continually update the component model parameters.
This is exemplarily shown in the case study in Section~6, with more systematic evidence given in Section~7.
In Section~6.2, the case of failures happening later than expected, i.e., a pessimistic prior is considered,
and the last paragraph before Section~6.3 (beginning with ``The effect of the continuous parameter update \ldots'')
gives a detailed explanation.
Section~6.3 studies a case with failure times earlier than expected, i.e., with too optimistic prior.
Here, as described in the text, both the approach with and without continuous parameter update
trigger maintenance at the same time, leading to the same costs.
However, Figure~8 shows that without continuous parameter update, the system RLD is overestimated,
which may lead to an excess risk of system failure.
This is confirmed in the simulation study in Section~7.2, Figure~10,
where the continuous update approach (CBM-cpu) can be seen to lead to slightly lower mean cost rates
than the approach without continuous parameter update (CBM-epu and CBM-npu).
Citing the last sentence of Section~7,
``[o]verall, it seems that CBM-cpu can play its adaptive strengths most effectively
when prior assumptions are too pessimistic,
while also performing well when prior assumptions are correct or too optimistic.''\\
***change some wording?***\\
***impossible to know beforehand if priors too optimistic or too pessimistic***}
%
\item For the example system, I think we can simply use the key stone method (use H as the key stone) to calculate the system reliability when the components are independent.  Is it necessary to use system signature?

\smallskip

\emph{The example system was deliberately chosen to be very simple,
and for such a system, indeed a simpler methodology like the key stone method (***??) could very well suffice.
However, our survival signature based method is also applicable for larger systems where no one component
can be singled out as the reliability-limiting force***\\
***add a note on simplicity at example intro in Section~3?***\\
***use more complex system for simulation study?***}
\end{enumerate}

\section*{Reviewer 2}

The manuscript proposes a condition-based preventive maintenance policy for multi-component systems. The objective is to minimise certain cost rate by means of scheduling preventive maintenance interventions. The failure probabilities and the residual life distribution are updated in a Bayesian fashion as new information of the system’s evolution is gathered. The components are assumed to fail independently, but they are interrelated and the failure of a single component may have an effect in other surrogate elements.

The problem addressed is important and the methodology well-grounded. However, the manuscript requires some important work before it can be accepted.

The English writing is good. However, the paper needs to be reviewed as some sections lack a proper structure and the argument is hard to follow. In particular Section~5 must be completely rewritten.

More specific comments are summarised in the two following sections:

\subsection*{Technical comments}

\begin{itemize}
\item The notational choice does not seem to be the most appropriate. The use of $\tnow$ is confusing and makes the reading of the paper cumbersome. I will suggest to use something more direct, as $t_j$, where $j=1,\ldots$ represents the $j$th scheduled intervention. With that choice, the notation $\tau^{\tnow}_*$ can be simplified to $\tau^*_j$ without any loss of generality of information. Moreover, with this notational choice (or a similar one) the expression $t_j=j \delta$ becomes natural and. [sic!]

\item The claim in the first paragraph of Section 5 is a strong one and should be properly proved or, at least, a reference must be provided.

\item In Section 5.1, the authors indicate that if, for a given time $\tnow$, $\tau_*^{\tnow}<\delta$, then a preventive maintenance is triggered. I wonder if it will not be better to wait until $\tau_*^{\tnow}$? Given that $\tau_*^{\tnow}$ is---by definition---the optimal intervention time, it seems that the best action is to intervene precisely at that time.

\item It seems that the authors assume constant preventive and corrective maintenance costs. However, in practice one finds that maintenance costs are often state dependent. Is their model suitable for this? Is it robust to different cost structures? How will their results be affected?

\item Throughout the manuscript it is assumed that the survival signature, $\phi$, is a given parameter of the problem and no further details are given. Even though this may be correct for any real life application of their methodology, for the sake of completeness I will suggest to either include the complete version of Table 1(maybe as an appendix) or to provide a closed form of the corresponding survival signature for their toy example.

\item Five subsequent operation cycles seems to be a rather short simulation horizon. I will suggest the authors to extend their analysis to, at least, 20-25 cycles.

\item Beside the didactical advantages of the small example, the authors should consider a more realistic framework for testing their model. Results should be provided for a larger scale simulation exercise.
\end{itemize}

\subsection*{General Comments}

\begin{itemize}
\item The authors claim that no degradation signal is used for monitoring the system’s state. However, they mention that the status of the components can be monitored continuously. How can this be done? This question becomes more important when the authors mention that certain inspections (which reveal the status of the systems) can be conducted periodically. This seems to be in contradiction with the continuous monitoring mentioned above. Could the authors be so kind to clarify this?

\item The fourth paragraph in Section 1, starting with “In this paper…” must be rewritten. Their argument is not clear and it may seem contradictory; e.g. “no degradation signal for the system is available” and later “each component sends a binary signal”. At the end, it is not clear how information is collected.

\item The definition of an operational cycle in the first paragraph of page 3 seems to be in conflict with the one provided elsewhere in the manuscript, in particular page 11, Section 5.

\item I suggest the authors to define all the acronyms on their first use. For example, CBM is used throughout the text, but never defined; and RDL is used from page 2, but not defined until page 3 (in Section 2).

\item The assumption of independence of the components, that appears for the first time in page 5, must be mentioned earlier in the paper.

\item Some variables are not properly defined, e.g. $\Rsys$ or $\Tsys$. The meaning of $C^k_l$ can be guessed from the context, but for completeness should be clearly stated.

\item As it seems, some of the results in section 4 have been developed elsewhere by one of the authors of this paper. Given that Section 4.1 does not add to the understanding of the problem under discussion, I will suggest to omit it or to include it as an appendix to the manuscript. This is only an opinion and I will understand if the authors decide to ignore my comment.

\item I suggest to place Figure 2 somewhere after parameters $m$ and $\delta$ are defined and the maintenance policy is described in Section 5.1 (for example at the end of the section). Otherwise, it is hard to follow.

\item A timeline sketch depicting the evolution of the policy on time, where the different elements of a time grid are illustrated, will be welcome.

\item Even though the use of the zero sub-indexed double struck capital N is correct for positive naturals and zero, I think that the simpler double struck capital N is enough. The context makes evident the inclusion of zero.

\item In page 13, paragraph 2, line 7, please remove “is” from the sentence “is for the current off-grid time”.

\item Frequent references to function $g$, which is only defined later in Section 5.2, make the lecture of the manuscript difficult. I suggest to rewrite the section seeking for all elements to be introduced in a more orderly fashion.

\item As Section 8 concludes the manuscript, I will suggest to refer to it as “the conclusion” rather than Section 8; e.g. at the end of sections 5.1 and 5.2.
\end{itemize}

\section*{Reviewer 3}

The paper is well structured, well written and technically accurate. The numerical experiments are particularly interesting. I recommend the acceptation of the paper after a revision.

The weak point of the work is related to the different hypothesis which significantly simplify the modeling framework. More precisely:

\begin{enumerate}
\item All the components have the same lifetime model (namely the Weibull distribution) with a known fixed shape parameter which is not discussed. Only the scale parameter is updated and directly associated with the mean lifetime if the shape parameter is known.

\item In the introduction the authors claim that ``the system RLD does not require a physical inspection’’ because the failure time of each component is detected online via continuous monitoring. This hypothesis seems to be very strong as it requires a costly related instrumentation. Most of the time, systems with redundancies are not monitored in a such way. if a specific application field is inferred, please give it explicitly. It could be interesting to discuss shortly the sensitivity of the proposed maintenance policy to non-detection of some components failures.

\item The maintenance of the system is always a replacement of the whole system by an as good as new one. This hypothesis is hard to accept especially if all the components are continuously monitored.

\end{enumerate}

Some additional comments or remarks are given hereafter to help improving the paper.

\begin{itemize}
\item The literature review has a strong focus on papers that are very close to the proposed one. There are some ambiguities about what the authors call ``papers having some relation to their approach’’. For example the paper by Si et al. (2013) is referred first as a paper where the inspection of the system condition lead to the choice of the moment for the next inspection. There are a lot of (older) papers with that specificity. The reason why Si et al. (2013) has been chosen is probably the RUL update in a Bayesian framework. It is not clear at this stage.

\item Page 1, last line: Maintaining systems or components at the right time is the central idea of all the maintenance policies, not only for CBM. The specificity of CBM is to take the decision about maintenance on the basis of the on-line system condition.

\item Page 2, line 18 from top: The phrase ``a kind of inspection-based CBM policy’’ is maladjusted. The paper does not deal with inspection. The system is supposed to be continuously monitored (and re-evaluated from times to times). It would also be interesting to give in details the specific points which make the proposed policy a ``kind of’’ CBM policy.

\item Page 2, line 15 from bottom: Please explain the acronym ``RLD’’ the first time it is used.

\item Page 4, line 5 from top: Please explain more precisely the meaning of ``this approximate calculation method’’.

\item Page 6, line 11 from bottom: It would be interesting for the reader to know explicitly which sections of the paper follow closely ``Walter and Coolen (2016)’’ to help identifying precisely the original part of the work.

\item Page 7: The choice of the inverse Gamma distribution as a prior is interesting for mathematical reasons. Are there some possible tests to justify this choice from data?

\item Page 13, section 5.1: The grid of planned evaluation time points is defined with a ``sufficiently small’’ time increment. What does it mean quantitatively? It seems that if $\delta$ is very small the maintenance time will be almost given by $\tau_*^{\tnow}$.

\item Page 14, first paragraph: Is it possible to determine the number of operational cycles which is necessary to improve significantly the values of the parameters? It seems that after a certain amount of time the updates will have a negligible effect.

\item Page 14, Equation (14): Is it possible to have some elements about the variance of the unit cost rate?

\item Page 15, line 12 from bottom: Please replace ``the costs rate’’ by ``the mean cost rate’’.

\end{itemize}

\end{document}

### 2017-03-08 answer-to-reviewers.tex
Error in Table 1, thoughts on technical comments by Reviewer 2

@@
 
+\smallskip
+
+\emph{***We rewrote Section~5 according to the reviewer's suggestions.***}
+
+\smallskip
+
 More specific comments are summarised in the two following sections:
@@
 
+\smallskip
+
+\emph{***This conflicts with our approach that evaluates the RLD and $\tausnow$ also at the exact times of component failures***}
+
 \item The claim in the first paragraph of Section 5 is a strong one and should be properly proved or, at least, a reference must be provided.
+
+\smallskip
+
+\emph{***unclear which claim exactly he refers to, maybe to
+``Close to system startup, $\tausnow$ will be large;
+but as components in the system age and some indeed fail over time, $\tausnow$ will typically decrease.'' ???
+It will be hard to prove this formally, as $\tausnow$ is a result of an optimization over the re-estimated RLD.
+But informally, this is clear: when a component fails, this is taken up by the RLD calculation,
+such the probability mass of the RLD is moving closer to $\tnow$,
+which leads to $\tausnow$ being closer to $\tnow$ as well.***}
 
@@
 Given that $\tau_*^{\tnow}$ is---by definition---the optimal intervention time, it seems that the best action is to intervene precisely at that time.
+
+\smallskip
+
+\emph{***Hm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
+I could change the simulations to execute repair at time $\tnow + \tausnow$,
+but then one needs to check whether there is a component failure (and with it, a system failure)
+between time $\tnow$ and $\tnow + \tausnow$, making the policy flow chart even more complex.
+If we keep it as it is, we need to explain $\delta$ better as being very small such that repair at $\tnow$ or $\tnow + \tausnow$
+do not make a big difference and that without $\delta$, we get a situation like in the paradox of Achilles and the tortoise.}
 
@@
 
-\item Throughout the manuscript it is assumed that the survival signature, $\phi$, is a given parameter of the problem and no further details are given.
-Even though this may be correct for any real life application of their methodology, for the sake of completeness I will suggest to either include the complete version of Table 1(maybe as an appendix) or to provide a closed form of the corresponding survival signature for their toy example.
+\smallskip
+
+\emph{***We need to add a comment on this in Section~8. It is possible to have costs dependent on time and on system state,
+method works in the same way, $\tausnow$ will be more variable then.
+Relation to our simplifying assumption that all components are replaced in a maintenance action?***}
+
+\item Throughout the manuscript it is assumed that the survival signature, $\Phi$, is a given parameter of the problem and no further details are given.
+Even though this may be correct for any real life application of their methodology, for the sake of completeness I will suggest to either include the complete version of Table 1 (maybe as an appendix) or to provide a closed form of the corresponding survival signature for their toy example.
+
+\smallskip
+
+\emph{***Upon re-inspection of Table~1, we have found some errors that we have now corrected,
+and would like to apologize for the confusion that the errors may have caused.
+We now exemplarily show how $\Phi$ is obtained for the case of $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
+and give an explanation on how the omitted rows in Table~1 can be easily determined by the reader.\\
+{\scriptsize
+(1) Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
+If the resulting row is not in Table~1, then the corresponding $\Phi$ is $0$.\\
+(2) Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
+If the resulting row is not in Table~1, then the corresponding $\Phi$ is $1$.}\\
+Also add complete table in Appendix, or formula for $\Phi$ based on structure function???***}
 
@@
 
+\smallskip
+
+\emph{***??? We can do more subsequent operation cycles,
+but I would think more repetitions (say, 100 instead of 20) would be better.
+Maybe emphasize that we use a single-cycle optimization criterion,
+not a renewal-based criterion that indeed holds only for a large number of cycles?
+Also, for many cycles the difference between CBM-cpu and CBM-epu will decrease.***}
+
 \item Beside the didactical advantages of the small example, the authors should consider a more realistic framework for testing their model.
 Results should be provided for a larger scale simulation exercise.
+
+\smallskip
+
+\emph{***We decided to use the simple example also in the simulation study to keep the paper shorter,
+but another, more complex system would be possible, only extending computation times.
+But what should this more complex system look like? We would need to think of a realistic example...***}
 \end{itemize}

### 2017-03-08 answer-to-reviewers.tex
proper introduction of acronyms

@@
 
-\emph{***Hm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
+\emph{***Hmmm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
 I could change the simulations to execute repair at time $\tnow + \tausnow$,
@@
 \emph{***Upon re-inspection of Table~1, we have found some errors that we have now corrected,
-and would like to apologize for the confusion that the errors may have caused.
+and would like to apologize for the confusion that these errors may have caused.
 We now exemplarily show how $\Phi$ is obtained for the case of $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
@@
 If the resulting row is not in Table~1, then the corresponding $\Phi$ is $1$.}\\
-Also add complete table in Appendix, or formula for $\Phi$ based on structure function???***}
+Also add complete table in Appendix, or formula for $\Phi$ based on structure function???
+Also note here that there is software to calculate $\Phi$?***}
 
@@
 
+\smallskip
+
+\emph{***??? We seem to have confused the reviewer thoroughly.
+We need to clarify that we do not use a \textbf{usual} degradation signal, like vibration measurements.
+But we do get a continuous signal from the components of the system, telling us whether they work or not.
+I need to check again if we say somewhere that we do inspections periodically, which is not true.
+We re-evaluate the RLD periodically (and additionally at times of component failures).***}
+
 \item The fourth paragraph in Section 1, starting with “In this paper…” must be rewritten.
@@
 
+\smallskip
+
+\emph{***Again, we need to clarify that we do not use a \textbf{usual} degradation signal for the \textbf{system as a whole},
+but that the component status information (working or not) can be seen as a special kind of multivariate system degradation signal.
+I would also do not call our approach ``inspection-based'', as we now do in that paragraph.}
+
 \item The definition of an operational cycle in the first paragraph of page 3 seems to be in conflict with the one provided elsewhere in the manuscript, in particular page 11, Section 5.
+
+\smallskip
+
+\emph{p.~3: ``where an operational cycle starts with a new system,
+and ends after this system has been replaced by an as good as new system''\\
+Section~5: ``An operational cycle begins with system start-up,
+and ends when either preventive maintenance is carried out, or a failure of the system occurs,
+with subsequent corrective maintenance.''\\
+*** I don't quite see the conflict, maybe mention in Sec~5 directly after that sentence that maintenance means replacing the whole system?
+And write on p.~3 ``begins with the start-up of a new system'', or even
+``An operational cycle spans the time between two consecutive system maintenance actions / replacements.
+We thus optimize the unit cost rate calculated over the time since the last system replacement.''
+?***}
 
@@
 For example, CBM is used throughout the text, but never defined; and RDL is used from page 2, but not defined until page 3 (in Section 2).
+
+\smallskip
+
+\emph{CBM was defined in the first line of Section~1, where we wrote ``CBM (condition-based maintenance)''.
+We now write ``condition-based maintenance (CBM)'' instead.
+We are sorry that we did define RLD too late, and now define it at the first use on page~2.***}
 

### 2017-03-08 cbm-rbd-paper.tex
Error in Table 1, thoughts on technical comments by Reviewer 2
proper introduction of acronyms

@@
 Both in practice and academics,
-there is a growing interest in CBM (condition-based maintenance), see e.g.,
+there is a growing interest in condition-based maintenance (CBM), see e.g.,
 \citet[pp.~15--55]{2016:oldekeizer}
@@
 and information with respect to the status of its components
-to directly calculate the system residual life distribution,
+to directly calculate the system residual life distribution (RLD),
 and base the maintenance policy for the system on this distribution.
@@
 where the moment of the next inspection is determined via an updated degradation path based on the present condition of the system.
-The authors provide exact expressions for the RUL (remaining useful lifetime) distribution,
-also known as residual life distribution (RLD),
+The authors provide exact expressions for the RLD,
+also known as RUL (remaining useful lifetime) distribution,
 which is updated in an empirical Bayesian framework using conjugate priors.
@@
 is that we use component status data and the system reliability block diagram instead of the degradation signal
-as basis for calculating the system RUL.
+as basis for calculating the system RLD.
 Another main difference is that our policy can be applied to arbitrary system configurations
@@
 is that the relevant characteristics of the system considered and its environment are not changing,
-i.e. that the failure behavior of the system,
+i.e.\ that the failure behavior of the system,
 in essence its relibability function, does not change over time,
-and that we use the same policy with the same parameter values during a statistically long enough period of time.
+and that the same policy with the same parameter values is used for a statistically long enough period of time.
 However, due to the update method related to the CBM policy presented in this paper
@@
 0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
-0 & 1 & 1 & 1 & 0.62 & & 1 & 1 & 1 & 1 & 0.62 \\ 
-0 & 1 & 1 & 2 & 0.92 & & 1 & 1 & 1 & 2 & 0.92 \\ 
-0 & 1 & 2 & 1 & 0.75 & & 1 & 1 & 2 & 1 & 0.75 \\ 
-0 & 1 & 2 & 2 & 0.97 & & 1 & 1 & 2 & 2 & 0.97 \\ 
-0 & 1 & 3 & 1 & 0.88 & & 1 & 1 & 3 & 1 & 0.88 \\ 
+0 & 1 & 1 & 1 & 0.50 & & 1 & 1 & 1 & 1 & 0.62 \\ 
+0 & 1 & 1 & 2 & 0.83 & & 1 & 1 & 1 & 2 & 0.92 \\ 
+0 & 1 & 2 & 1 & 0.50 & & 1 & 1 & 2 & 1 & 0.75 \\ 
+0 & 1 & 2 & 2 & 0.83 & & 1 & 1 & 2 & 2 & 0.97 \\ 
+0 & 1 & 3 & 1 & 0.50 & & 1 & 1 & 3 & 1 & 0.88 \\ 
+0 & 1 & 3 & 2 & 0.83 \\
+0 & 1 & 4 & 1 & 0.50 \\
+0 & 1 & 4 & 2 & 0.83 \\
    \bottomrule

### 2017-03-17 answer-to-reviewers.tex
Reviewer 2 general comments completed, including small changes in manuscript

@@
 and their overall positive votum***.
-We reproduce their comments here verbatim, with our answers interlaced.
-Our answers are typeset in \emph{italic}.
+We reproduce their comments here verbatim,
+and have numbered the reviewers' comments and questions to allow for easy referencing. 
+Our answers are interlaced and typeset in \emph{italic}.
 \end{abstract}
@@
 we considered it necessary to include a detailed description of the RLD calculation,
-and not just refering to the paper. ***change wording in the paper?***
+and not just refering to the paper.
 }
@@
 
-\begin{itemize}
+\begin{enumerate}
 \item The notational choice does not seem to be the most appropriate.
@@
 
-\emph{***This conflicts with our approach that evaluates the RLD and $\tausnow$ also at the exact times of component failures***}
+\emph{***This conflicts with our approach that evaluates the RLD and $\tausnow$ also at the exact times of component failures!***\\
+maybe something like
+$\big\{ t_j: (t_j = m\delta, m \in \naturals_0) \cup (t_j = t_{k,i}, k \in \{1,\ldots,K\}, i \in \{1,\ldots, N_k\}) \big\}$ ???
+But this is also quite complex!***}
 
@@
 But what should this more complex system look like? We would need to think of a realistic example...***}
-\end{itemize}
+\end{enumerate}
 
@@
 
-\begin{itemize}
+\begin{enumerate}
 \item The authors claim that no degradation signal is used for monitoring the system’s state.
@@
 We now write ``condition-based maintenance (CBM)'' instead.
-We are sorry that we did define RLD too late, and now define it at the first use on page~2.***}
+We are sorry that we indeed defined RLD too late, and now define it at the first use on page~2.***}
 
@@
 
+\smallskip
+
+\emph{*** yes, we should mention this in the introduction.}
+
 \item Some variables are not properly defined, e.g. $\Rsys$ or $\Tsys$. The meaning of $C^k_l$ can be guessed from the context, but for completeness should be clearly stated.
+
+\smallskip
+
+\emph{***We define $\Rsys(t) = P(\Tsys > t)$ on p.~5 above Equation~1,
+but indeed did not introduce $\Tsys$ as the random failure time of the system.
+We do so now in *** (start of Section~3?)}
 
@@
 
+\smallskip
+
+\emph{*** Section~4.1 introduces the Weibull component models
+and the conjugate inverse Gamma prior distribution in our non-standard parametrization,
+explaining the Bayesian parameter update step for right-censored lifetimes.
+We think that Section~4.1 is crucial to the understanding of our method,
+especially for readers not familiar with Bayesian approaches.
+As mentioned in our answer to Reviewer~1's main comment,
+Sections~4.1 to 4.3 combine results from several parts of the cited manuscript
+in a from that is adapted to the purpose of the present manuscript.
+We thus think that it is preferable to keep Section~4.1 within the main part of the manuscript.}
+
 \item I suggest to place Figure 2 somewhere after parameters $m$ and $\delta$ are defined and the maintenance policy is described in Section 5.1 (for example at the end of the section).
@@
 
+\smallskip
+
+\emph{We had placed Figure~2 (depicting the flowchat for the policy) directly before Section~5.1 which explains the policy,
+and agree that it should appear during or after Section~5.1 to avoid confusion.***}
+
 \item A timeline sketch depicting the evolution of the policy on time, where the different elements of a time grid are illustrated, will be welcome.
+
+\smallskip
+
+\emph{We agree with Reviewer~2 that such a sketch is helpful, and provide it now as Figure~***.}
 
@@
 
+\smallskip
+
+\emph{??? Reviewer~2 suggests to use $\naturals$ in place of $\naturals_0$.
+***I don't think this is a good idea, with $\naturals_0$ we emphasize that
+we evaluate the RLD for the first time directly at system startup time 0.***}
+
 \item In page 13, paragraph 2, line 7, please remove “is” from the sentence “is for the current off-grid time”.
+
+\smallskip
+
+\emph{Thanks for pointing this out, done.}
 
@@
 
+\smallskip
+
+\emph{***We rewrote the entire section as requested, and hope that this is now more clear.
+Our intention was to establish the cost rate function $g^{(\tnow)}(\cdot)$ as a generic function first
+and to explain the details of its calculation later***}
+
 \item As Section 8 concludes the manuscript, I will suggest to refer to it as “the conclusion” rather than Section 8; e.g. at the end of sections 5.1 and 5.2.
-\end{itemize}
+
+\smallskip
+
+\emph{***Agreed, we now write ``the conclusion (Section~8)''.}
+\end{enumerate}
 
@@
 
-\begin{itemize}
+\begin{enumerate}
 \item The literature review has a strong focus on papers that are very close to the proposed one.
@@
 
-\end{itemize}
+\end{enumerate}
 

### 2017-03-17 cbm-rbd-paper.tex
Reviewer 2 general comments completed, including small changes in manuscript

@@
 If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
-If the system has not failed, we calculate $\tausnow$ is for the current off-grid time $\tnow = t_{k,i}$,
+If the system has not failed, we calculate $\tausnow$ for the current off-grid time $\tnow = t_{k,i}$,
 and move back onto the grid afterwards,
@@
 that merits an investigation of its own,
-and we will comment on this in Section~\ref{sec:outlook}.
+and we will comment on this in the conclusion (Section~\ref{sec:outlook}).
 %
@@
 Such simulatenous failures will seriously influence the RLD and thus $\tausnow$.
-We will return to this in Section~\ref{sec:outlook}.
+We will return to this in the conclusion (Section~\ref{sec:outlook}).
 %

### 2017-03-17 answer-to-reviewers.tex
Reviewer 3 comments answers draft

@@
 
-\emph{***We define $\Rsys(t) = P(\Tsys > t)$ on p.~5 above Equation~1,
+\emph{***We defined $\Rsys(t) := P(\Tsys > t)$ on p.~5 above Equation~1,
 but indeed did not introduce $\Tsys$ as the random failure time of the system.
@@
 Sections~4.1 to 4.3 combine results from several parts of the cited manuscript
-in a from that is adapted to the purpose of the present manuscript.
+in a form that is adapted to the purpose of the present manuscript.
 We thus think that it is preferable to keep Section~4.1 within the main part of the manuscript.}
@@
 
+\smallskip
+
+\emph{We agree that the assumption of a fixed known shape parameter is a serious limitation of our approach. 
+We added a comment on this in the conclusion,
+repeating a comment from the beginning of Section~4, where we wrote:
+``The model could be extended to learn also the shape parameter in a later step,
+using, e.g., the discretized approach by Soland (1969).''
+We now also emphasize in the conclusion that the proposed method should be seen as a first step towards
+a completely new class of CBM policies.***}
+
 \item In the introduction the authors claim that ``the system RLD does not require a physical inspection’’ because the failure time of each component is detected online via continuous monitoring.
@@
 
+\smallskip
+
+\emph{***We have added a short discussion related to the non-detection of component failures in the conclusion.
+We were mostly thinking of systems where a failure of a component is immediately eminent,
+but the measurement of the component's health degree is very difficult or too costly.
+This is, e.g., the case for components in power systems, where failure of a certain component
+is reflected in a loss of current (detectable from the control centre),
+but proper health monitoring is cumbersome and costly.
+***}
+
 \item The maintenance of the system is always a replacement of the whole system by an as good as new one. This hypothesis is hard to accept especially if all the components are continuously monitored.
 
+\smallskip
+
+\emph{***Agreed, this is another important simplifying assumption that we needed to make in this manuscript,
+which should be seen as a first step towards a completely new class of CBM policies.
+We originally mentioned this in the description of the policy but only at the end of Section~5.1,
+and commented on this in the fourth paragraph of the conclusion (Section~8), bottom of p.~25.
+In the re-write of Section~5, we tried to emphasize the pilot character of our approach,
+mentioning the restricting assumptions more prominently.***}
 \end{enumerate}
@@
 There are a lot of (older) papers with that specificity.
-The reason why Si et al.
-(2013) has been chosen is probably the RUL update in a Bayesian framework.
+The reason why Si et al.~(2013) has been chosen is probably the RUL update in a Bayesian framework.
 It is not clear at this stage.
+
+\smallskip
+
+\emph{***We did mention right in the first paragraph of the discussion of Si et al.~(2013)
+that they use an empirical Bayesian framework,
+but now also state explicitely that the use of a Bayesian approach is a main reason why we consider this paper relevant for the discussion.}
 
@@
 The specificity of CBM is to take the decision about maintenance on the basis of the on-line system condition.
+
+\smallskip
+
+\emph{***??? rewrite???}
 
@@
 
+\smallskip
+
+\emph{Agreed, we deleted that notion, and hope to be more clear now here.***}
+
 \item Page 2, line 15 from bottom: Please explain the acronym ``RLD’’ the first time it is used.
+
+\smallskip
+
+\emph{We are sorry that we defined RLD too late, and now define it at the first use.}
 
@@
 
+\smallskip
+
+\emph{We replaced ``this approximate calculation method’’ with ``the renewal-reward theory based calculation method''
+in the hope to make this more clear.}
+
 \item Page 6, line 11 from bottom: It would be interesting for the reader to know explicitly which sections of the paper follow closely ``Walter and Coolen (2016)’’ to help identifying precisely the original part of the work.
+
+\smallskip
+
+\emph{Agreed, the respective sections are now added.}
 
@@
 
+\smallskip
+
+\emph{It is not possible to use data for testing the adequacy of the parametric family of the prior,
+as it is supposed to reflect the expert's opinion.
+So the actual question is rather whether inverse Gamma distributions can adequately reflect the expert's opinions.
+A tool to help answering that question are prior predictive distributions.
+They give a distribution for the failure times that can be expected according to the expert's choice of prior
+(here: inverse Gamma with specific parameters)
+\textbf{in combination with the assumed sample model} (here: Weibull).
+Figure~6 (previously Figure~5)*** depicts prior predictive reliability functions for the priors in the case study of Section~6,
+as a way to visualize the choice of prior parameters given in Table~2 in the context of the Weibull model.
+When an expert feels that these prior predictive reliability functions do not correspond to the failure time distribution (s)he postulates,
+and no change of prior parameters can approximate the postulated failure time distribution,
+then the prior family would seem inappropriate,
+under the condition that the sample model is indeed correct.
+(Methods for checking the sample model are discussed, e.g., in
+Bayarri and Berger (2000), ``P values for composite null models'',
+Journal of the American Statistical Association 95(452): 1127–1142.)}
+
 \item Page 13, section 5.1: The grid of planned evaluation time points is defined with a ``sufficiently small’’ time increment.
 What does it mean quantitatively?
-It seems that if $\delta$ is very small the maintenance time will be almost given by $\tau_*^{\tnow}$.
+It seems that if $\delta$ is very small the maintenance time will be almost given by $\tau_*^{(\tnow)}$.
+
+\smallskip
+
+\emph{***depends on the scale of failure times? seconds / minutes? ??? not sure what is meant by the second sentence.}
 
@@
 
+\smallskip
+
+\emph{***Indeed, after a certain time the parameter $y_k$ (the expected value of the Weibull scale parameter $\lambda_k$)
+will not change by much during the update in Equation (7).
+However, the strength parameter $n_k$ will continue to increase,
+since the other part of (7) reads $n'_k = n_k + e_k$, i.e.,
+$n_k$ is incremented by 1 for each observed failure.
+The consequence is that the posterior distribution over $\lambda_k$ becomes ever more pointed
+(the variance of the posterior approaches zero),
+leading to the posterior predictive approaching the Weibull with $\lambda_k$ equal to $y_k$.
+Stopping to update would make only sense when the posterior is practically equal to a point mass on $y_k$.
+However, this holds only if a component's failure behaviour does not change.
+Updating allows to automatically adapt to any changes in the failure behaviour.}
+
 \item Page 14, Equation (14): Is it possible to have some elements about the variance of the unit cost rate?
 
-\item Page 15, line 12 from bottom: Please replace ``the costs rate’’ by ``the mean cost rate’’.
+\smallskip
 
+\emph{***??? In Equation~(15), the unit cost rate $\gnow(\tau)$ is defined as
+$\gnow(\tau) = \E[g(\tau \mid \Tsysnow)]$,
+i.e., as expectation of the conditioned unit cost rate $g(\tau \mid \Tsysnow)$ from Equation~(14).
+We do not think the variance of the conditioned unit cost rate,
+$\text{V}[g(\tau \mid \Tsysnow)]$ is instructive for the purposes of our manuscript.}
+
+\item Page 15, line 12 from bottom: Please replace ``the costs rate’’ [sic!] by ``the mean cost rate’’.
+
+\smallskip
+
+\emph{We wrote ``$\gnow(\tau)$ gives the cost rate that we expect to incur [...]'',
+which includes the notion of mean via ``expect'', and we hope this is clear enough.*** (???)}
 \end{enumerate}

### 2017-03-17 cbm-rbd-paper.tex
Reviewer 3 comments answers draft

@@
 
+***While we also use a Bayesian approach to provide exact expressions for the RLD,***
 One of the main differences between \citet{2013:si-et-al} and our paper
-is that we use component status data and the system reliability block diagram instead of the degradation signal
+is that we use component status data and the system reliability block diagram instead of a continuous degradation signal
 as basis for calculating the system RLD.
@@
 However, due to the update method related to the CBM policy presented in this paper
-like in \citet{2013:si-et-al}, we cannot use this approximate calculation method,
+like in \citet{2013:si-et-al}, we cannot use the renewal-reward theory based calculation method,
 and therefore use the exact formula for the average cost per unit of time.
@@
 
-The model description below follows closely \cite{2016:walter-coolen},
+The model description below follows closely \cite[\S 2, \S 4.1 -- \S 4.3]{2016:walter-coolen},
 who presented the same residual life distribution model.
 However, \cite{2016:walter-coolen} did not consider maintenance policies,
-but focus instead on a generalization of the RLD model using sets of priors for the component models.
+but focus instead on a generalization of the RLD model by using imprecise probability models*** for the component models.
 %These sets of priors can be seen as parametric P-boxes,
@@
 \begin{tikzpicture}
+\node {exemplary timeline};
+\end{tikzpicture}
+\caption{***exemplary timeline sketch}
+\label{fig:timeline}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
 [node distance=6mm,
@@
 The resulting policy shows promising results in
-different numerical exmples and a small simulation study.
+different numerical examples and a small simulation study.
 
@@
 %we would need to add interval-censored data (failure has happened between last and current inspection)
+
+***estimate and update also Weibull shape parameter***
+
+***non-detection of component failures***
 

### 2017-03-18 answer-to-reviewers.tex
further tweaks, sending to SDF now

@@
 Instead, the present manuscript uses the basic approach to develop a \textbf{maintenance policy},
-using the RLD as input for an optimization of the mean cost rate to find the cost-optimal moment of system maintenance.
+using \textbf{a single} RLD as input for an optimization of the mean cost rate to find the cost-optimal moment of system maintenance.
 Sections~4.1 to 4.3 describe the approach used for RLD calculation
@@
 which may lead to an excess risk of system failure.
-This is confirmed in the simulation study in Section~7.2, Figure~10,
+This is confirmed in the simulation study in Section~7.2, Figure~11 (previously Figure~10),
 where the continuous update approach (CBM-cpu) can be seen to lead to slightly lower mean cost rates
@@
 \emph{The example system was deliberately chosen to be very simple,
-and for such a system, indeed a simpler methodology like the key stone method (***??) could very well suffice.
-However, our survival signature based method is also applicable for larger systems where no one component
-can be singled out as the reliability-limiting force***\\
+and for such a system, indeed a simpler methodology like the keystone method could very well suffice.
+However, our survival signature based method is also applicable for larger systems where the keystone method
+is not applicable or cumbersome.
+Furthermore, the \textsf{R} package \texttt{ReliabilityTheory} allows to easily calculate the
+survival signature from a given system graph.\\
+%no one component can be singled out as the reliability-limiting force.\\
 ***add a note on simplicity at example intro in Section~3?***\\
@@
 We now exemplarily show how $\Phi$ is obtained for the case of $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
-and give an explanation on how the omitted rows in Table~1 can be easily determined by the reader.\\
-{\scriptsize
-(1) Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
-If the resulting row is not in Table~1, then the corresponding $\Phi$ is $0$.\\
-(2) Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
-If the resulting row is not in Table~1, then the corresponding $\Phi$ is $1$.}\\
-Also add complete table in Appendix, or formula for $\Phi$ based on structure function???
-Also note here that there is software to calculate $\Phi$?***}
+and give an explanation on how the omitted rows in Table~1 can be easily determined by the reader.}
+%{\scriptsize
+%(1) Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
+%If the resulting row is not in Table~1, then the corresponding $\Phi$ is $0$.\\
+%(2) Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
+%If the resulting row is not in Table~1, then the corresponding $\Phi$ is $1$.}\\
+%Also add complete table in Appendix, or formula for $\Phi$ based on structure function???
+%Also note here that there is software to calculate $\Phi$?***}
 
@@
 \emph{***??? We can do more subsequent operation cycles,
-but I would think more repetitions (say, 100 instead of 20) would be better.
+but I would think more repetitions (say, 50 or 100 instead of 20) would be better.
 Maybe emphasize that we use a single-cycle optimization criterion,
@@
 
-\emph{***??? We seem to have confused the reviewer thoroughly.
+\emph{***??? It seems we have confused the reviewer thoroughly.
 We need to clarify that we do not use a \textbf{usual} degradation signal, like vibration measurements.
-But we do get a continuous signal from the components of the system, telling us whether they work or not.
+But we do get a (time-) continuous signal from the components of the system, telling us whether they work or not.
 I need to check again if we say somewhere that we do inspections periodically, which is not true.
@@
 
-\emph{We had placed Figure~2 (depicting the flowchat for the policy) directly before Section~5.1 which explains the policy,
+\emph{We had placed Figure~2 (depicting the flowchat for the policy, now Figure~3) directly before Section~5.1 which explains the policy,
 and agree that it should appear during or after Section~5.1 to avoid confusion.***}
@@
 
-\emph{We agree with Reviewer~2 that such a sketch is helpful, and provide it now as Figure~***.}
+\emph{We agree with Reviewer~2 that such a sketch is helpful, and provide it now as Figure~2.}
 
@@
 using, e.g., the discretized approach by Soland (1969).''
-We now also emphasize in the conclusion that the proposed method should be seen as a first step towards
+We now also emphasize in the introduction and the conclusion that the proposed method should be seen as a first step towards
 a completely new class of CBM policies.***}
@@
 This is, e.g., the case for components in power systems, where failure of a certain component
-is reflected in a loss of current (detectable from the control centre),
-but proper health monitoring is cumbersome and costly.
+is usually reflected in a loss of current (detectable from the control centre),
+but proper health monitoring (going beyond working yes/no) is cumbersome and costly.
 ***}
@@
 and commented on this in the fourth paragraph of the conclusion (Section~8), bottom of p.~25.
-In the re-write of Section~5, we tried to emphasize the pilot character of our approach,
+In the introduction and the complete re-write of Section~5, we tried to emphasize the pilot character of our approach,
 mentioning the restricting assumptions more prominently.***}
@@
 
-\emph{We are sorry that we defined RLD too late, and now define it at the first use.}
+\emph{We are sorry that we defined RLD too late, and now define it at first use.}
 
@@
 as it is supposed to reflect the expert's opinion.
-So the actual question is rather whether inverse Gamma distributions can adequately reflect the expert's opinions.
+So the crucial question is rather whether inverse Gamma distributions can adequately reflect the expert's opinions.
 A tool to help answering that question are prior predictive distributions.
@@
 Bayarri and Berger (2000), ``P values for composite null models'',
-Journal of the American Statistical Association 95(452): 1127–1142.)}
+Journal of the American Statistical Association 95(452): 1127–1142.)\\
+***add this reference to the paper?***}
 
@@
 (the variance of the posterior approaches zero),
-leading to the posterior predictive approaching the Weibull with $\lambda_k$ equal to $y_k$.
+such that the posterior predictive distribution approaches the Weibull distribution with $\lambda_k$ equal to $y_k$.
 Stopping to update would make only sense when the posterior is practically equal to a point mass on $y_k$.

### 2017-03-18 cbm-rbd-paper.tex
further tweaks, sending to SDF now

@@
 because the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.
+***The omitted rows from Table~\ref{tab:brakesys-survsign} can be determined as follows:
+\begin{itemize}
+\item Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
+If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding $\Phi$ is $0$.
+\item Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
+If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding $\Phi$ is $1$.
+\end{itemize} 
+***As an example, Consider the case $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
+i.e., $M$ has failed, $H$ functions, $C_1$ -- $C_4$ have failed, and one of $P_1$ -- $P_4$ functions.
+The system functions only if the single functioning type $P$ component is either $P_3$ or $P_4$.
+As the type $P$ components are exchangeable, each has the same probability of being the functioning component,
+and so the probability of $P_3$ or $P_4$ being the functioning component is $0.5$, and $\Phi(0, 1, 0, 1) = 0.5$.
+
+The \textsf{R} package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
+provides a convenient function to calculate the survival signature based on a given graph.
 
@@
 
-***non-detection of component failures***
-
 As mentioned at the end of Section~\ref{sec:costrate},
@@
 
+***different cost structures, let repair costs depend on number of failed components?***
+
+***non-detection of component failures***
+
 Another promising extension would be to use sets of conjugate priors for the component models.

### 2017-03-31 cbm-rbd-paper.tex
revision documents

@@
 
-The third scenario consists of component failure times taht are later than expected,
+The third scenario consists of component failure times that are later than expected,
 obtained by simulating Weibull lifetimes using $\lambda_k = 2 \ykz$ for all four component types.

### 2017-04-04 answer-to-reviewers.tex
work on revision and answers to reviewers 1 & 2

@@
 
-\address[tue]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, Netherlands}
+\address[tue]{School of Industrial Engineering, Eindhoven University of Technology,\\ Eindhoven, The Netherlands}
 
@@
 We would like to thank the three anonymous reviewers for their detailed and constructive comments,
-and their overall positive votum***.
+and their overall positive votum.
 We reproduce their comments here verbatim,
@@
 Sections~4.1 to 4.3 describe the approach used for RLD calculation
-in a similar way than the cited paper,
+in a similar way as in the cited paper,
 but with notation adapted to the manuscript's objective, i.e., defining a maintenance policy.
@@
 
-\emph{In both cases, it is optimal to continually update the component model parameters.
+\emph{In both cases, it is optimal to continuously update the component model parameters.
 This is exemplarily shown in the case study in Section~6, with more systematic evidence given in Section~7.
@@
 which may lead to an excess risk of system failure.
-This is confirmed in the simulation study in Section~7.2, Figure~11 (previously Figure~10),
+***This is confirmed in the simulation study in Section~7.2, Figure~11 (previously Figure~10),
 where the continuous update approach (CBM-cpu) can be seen to lead to slightly lower mean cost rates
-than the approach without continuous parameter update (CBM-epu and CBM-npu).
-Citing the last sentence of Section~7,
-``[o]verall, it seems that CBM-cpu can play its adaptive strengths most effectively
+than the approach without continuous parameter update (CBM-epu and CBM-npu).\\
+%
+***new simulation scenario to illustrate this!***\\
+%
+***Citing the last sentence of Section~7,
+``[o]verall, it seems that CBM-cpu can play ***exert?*** its adaptive strengths most effectively
 when prior assumptions are too pessimistic,
 while also performing well when prior assumptions are correct or too optimistic.''\\
-***change some wording?***\\
+%
 ***impossible to know beforehand if priors too optimistic or too pessimistic***}
@@
 \emph{The example system was deliberately chosen to be very simple,
-and for such a system, indeed a simpler methodology like the keystone method could very well suffice.
-However, our survival signature based method is also applicable for larger systems where the keystone method
-is not applicable or cumbersome.
-Furthermore, the \textsf{R} package \texttt{ReliabilityTheory} allows to easily calculate the
-survival signature from a given system graph.\\
+and for such a system, indeed a simpler methodology like the keystone method can very well suffice.
+However, our survival signature based method is also applicable for larger systems ***with hundreds or thousands of components,
+where the keystone method is usually not practical anymore.***\\
+***find surv sign papers with complex systems and add citations***
+Furthermore, the \textsf{R} package \texttt{ReliabilityTheory} allows to automatically calculate the
+survival signature from any given system graph.\\
 %no one component can be singled out as the reliability-limiting force.\\
-***add a note on simplicity at example intro in Section~3?***\\
-***use more complex system for simulation study?***}
+***add a note on simplicity (to understand what's going on) at example intro in Section~3?***}
 \end{enumerate}
@@
 
-\emph{***We need to add a comment on this in Section~8. It is possible to have costs dependent on time and on system state,
-method works in the same way, $\tausnow$ will be more variable then.
-Relation to our simplifying assumption that all components are replaced in a maintenance action?***}
+\emph{***Yes, we indeed assumed constant cost parameters in our manuscript.
+We now comment on this in the Section~8, where we now state that our model allows
+to let costs depend on time and on system state in the optimization step.
+***Such dependencies will lead to a more variable $\tausnow$***
+}
 
@@
 
-\emph{***Upon re-inspection of Table~1, we have found some errors that we have now corrected,
+\emph{Upon re-inspection of Table~1, we have found some errors that we have now corrected,
 and would like to apologize for the confusion that these errors may have caused.
+(We did all calculations with the correct survival signature though.)
 We now exemplarily show how $\Phi$ is obtained for the case of $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
@@
 
-\emph{***??? We can do more subsequent operation cycles,
-but I would think more repetitions (say, 50 or 100 instead of 20) would be better.
-Maybe emphasize that we use a single-cycle optimization criterion,
-not a renewal-based criterion that indeed holds only for a large number of cycles?
-Also, for many cycles the difference between CBM-cpu and CBM-epu will decrease.***}
+\emph{***We agree that the simulation study in our submitted manuscript was rather small,
+and thus have extended the simulation to not only to 25 subsequent cycles,
+but also increased the number of repetitions from 20 to 100 for each policy and scenario.
+Furthermore, we added a fourth scenario to better illustrate the advantage of the policy
+using continuous parameter update.***}
 
@@
 
-\emph{***We decided to use the simple example also in the simulation study to keep the paper shorter,
-but another, more complex system would be possible, only extending computation times.
-But what should this more complex system look like? We would need to think of a realistic example...***}
+\emph{***We decided to use the simple example also in the simulation study ***to provide clear insights
+that could get lost with a more complex example.***
+Generally, more complex systems are possible, only extending computation times,
+and we comment on the scalability of our approach in Section***.}
 \end{enumerate}
@@
 
-\emph{***??? It seems we have confused the reviewer thoroughly.
-We need to clarify that we do not use a \textbf{usual} degradation signal, like vibration measurements.
-But we do get a (time-) continuous signal from the components of the system, telling us whether they work or not.
-I need to check again if we say somewhere that we do inspections periodically, which is not true.
-We re-evaluate the RLD periodically (and additionally at times of component failures).***}
+\emph{We would like to apologize to Reviewer 2,
+and agree that our manuscript was indeed very confusing in this point.
+We completely rewrote the introduction and other relevant parts,
+hopefully making more clear now that 
+we do not use a \textbf{usual} domain-continuous degradation signal, like, e.g., vibration measurements.
+Instead, we assume a time-continuous signal from the components of the system, telling us only whether they work or not.
+We also previously denoted our frequent re-evaluation of the system RLD by ``inspections'',
+which was indeed not adequate, and have changed our wording and explanations.***}
 
@@
 
-\emph{***Again, we need to clarify that we do not use a \textbf{usual} degradation signal for the \textbf{system as a whole},
-but that the component status information (working or not) can be seen as a special kind of multivariate system degradation signal.
-I would also do not call our approach ``inspection-based'', as we now do in that paragraph.}
+\emph{***Agreed, this is one of the paragraphs that we changed substantially as mentioned in the answer to the previous question,
+and we hope that our argument is now more clear.***}
+%Again, we need to clarify that we do not use a \textbf{usual} degradation signal for the \textbf{system as a whole},
+%but that the component status information (working or not) can be seen as a special kind of multivariate system degradation signal.
+%I would also do not call our approach ``inspection-based'', as we now do in that paragraph.
 
@@
 
-\emph{*** yes, we should mention this in the introduction.}
+\emph{*** yes, we should mention this in the introduction.***}
 
@@
 
-\emph{***We defined $\Rsys(t) := P(\Tsys > t)$ on p.~5 above Equation~1,
+\emph{We wrote $\Rsys(t) = P(\Tsys > t)$ on p.~5 above Equation~1,
 but indeed did not introduce $\Tsys$ as the random failure time of the system.
-We do so now in *** (start of Section~3?)}
+We do so now at the start of Section~3.
+$C^k_t$ is now properly defined in the text below Equation~1.}
 
@@
 
-\emph{*** Section~4.1 introduces the Weibull component models
+\emph{Section~4.1 introduces the Weibull component models
 and the conjugate inverse Gamma prior distribution in our non-standard parametrization,
@@
 \emph{We had placed Figure~2 (depicting the flowchat for the policy, now Figure~3) directly before Section~5.1 which explains the policy,
-and agree that it should appear during or after Section~5.1 to avoid confusion.***}
+and agree that it should appear during or after Section~5.1 to avoid confusion.}
 
@@
 
-\emph{We agree with Reviewer~2 that such a sketch is helpful, and provide it now as Figure~2.}
+\emph{We agree with Reviewer~2 that such a sketch is helpful, and now provide two such sketches in Figure~2.}
 
@@
 
-\emph{??? Reviewer~2 suggests to use $\naturals$ in place of $\naturals_0$.
-***I don't think this is a good idea, with $\naturals_0$ we emphasize that
-we evaluate the RLD for the first time directly at system startup time 0.***}
+\emph{By using $\naturals_0$ and not $\naturals$ as suggested by Reviewer 2,
+we intended to emphasize that the system RLD is evaluated for the first time directly at system startup time 0.
+***still keep it???***}
 
@@
 
-\emph{***We rewrote the entire section as requested, and hope that this is now more clear.
-Our intention was to establish the cost rate function $g^{(\tnow)}(\cdot)$ as a generic function first
-and to explain the details of its calculation later***}
+\emph{***Our intention was to establish the cost rate function $g^{(\tnow)}(\cdot)$ as a generic function first
+and to explain the details of its calculation later.
+We rewrote the entire section as requested, and hope that also this is now more clear.***}
 
@@
 
-\emph{***Agreed, we now write ``the conclusion (Section~8)''.}
+\emph{Agreed, we now write ``the conclusion (Section~8)''.}
 \end{enumerate}

### 2017-04-04 cbm-rbd-paper.tex
work on revision and answers to reviewers 1 & 2

@@
 
-\address[tue]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, Netherlands}
+\address[tue]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, The Netherlands}
 
@@
 The unit cost rate is recalculated when components fail
-or at the end of every (very short) fixed inter-inspection interval,
+or at the end of every (very short) fixed inter-inspection interval***,
 leading to a dynamic maintenance policy,
@@
 
-Here we describe how the system reliability function, given the system reliability block diagram and arbitrary component models,
+Let $\Tsys$ be the time to failure of the system,
+and $\Rsys(t) := P(\Tsys > t)$ be the system reliability function.
+Here we describe how $\Rsys(t)$, given the system reliability block diagram and arbitrary component models,
 can be efficiently calculated using the survival signature.
@@
 \end{align}
-where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$.
-The last equality holds as we assume that components fail independently.
+where $C^k_t$ is the number of type $k$ components functioning at time $t$,
+and $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$.
+The last equality holds as we assume that components of different types fail independently.
 Note that for coherent systems, the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
@@
 \end{itemize} 
-***As an example, Consider the case $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
+The \textsf{R} package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
+provides a convenient function to calculate the survival signature table based on a given graph.
+***To illustrate how the table entries are generated,
+consider the case $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
 i.e., $M$ has failed, $H$ functions, $C_1$ -- $C_4$ have failed, and one of $P_1$ -- $P_4$ functions.
 The system functions only if the single functioning type $P$ component is either $P_3$ or $P_4$.
-As the type $P$ components are exchangeable, each has the same probability of being the functioning component,
-and so the probability of $P_3$ or $P_4$ being the functioning component is $0.5$, and $\Phi(0, 1, 0, 1) = 0.5$.
-
-The \textsf{R} package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
-provides a convenient function to calculate the survival signature based on a given graph.
+As the type $P$ components are exchangeable, each of $P_1$ -- $P_4$ has the same probability of being the functioning component,
+and so the probability of $P_3$ or $P_4$ being the functioning component is $2 / 4$, thus $\Phi(0, 1, 0, 1) = 0.5$.
 

### 2017-04-04 answer-to-reviewers.tex
typo and reviewer3q1

@@
 
-\emph{We had placed Figure~2 (depicting the flowchat for the policy, now Figure~3) directly before Section~5.1 which explains the policy,
+\emph{We had placed Figure~2 (depicting the flowchart for the policy, now Figure~3) directly before Section~5.1 which explains the policy,
 and agree that it should appear during or after Section~5.1 to avoid confusion.}
@@
 
-\emph{We agree that the assumption of a fixed known shape parameter is a serious limitation of our approach. 
+\emph{Yes, each component type has an individual Weibull model assigned,
+where the (component type specific) shape parameter is assumed to be fixed and known.
+We agree that the assumption of a fixed known shape parameter is a serious limitation of our approach. 
 We added a comment on this in the conclusion,
@@
 using, e.g., the discretized approach by Soland (1969).''
-We now also emphasize in the introduction and the conclusion that the proposed method should be seen as a first step towards
-a completely new class of CBM policies.***}
+We now also emphasize in the introduction and the conclusion that the method as described in the manuscript is deliberately kept simple
+to allow for a clear and straight-forward demonstration of the general approach.
+For a practical application, one should indeed update the shape parameter as well,
+but in our view, adding this simple but notationally cumbersome feature would obstruct the goal of this manuscript.***}
 

### 2017-04-11 answer-to-reviewers.tex
work on revision sec 1&2

@@
 
-\emph{***Agreed, this is another important simplifying assumption that we needed to make in this manuscript,
+\emph{***new text by SDF in email 2017-04-05:\\
+{\scriptsize
+At first sight, replacing a complete system when only some parts of it are defective may seem strange.
+However, there are many real life examples, including from daily life.
+So called complete clustering (Olde Keizer et al, 2017)
+may be optimal in case of a very strong economic dependence between the different parts of a system,
+e.g., due to a very high fixed set-up cost independent of the maintenance activities to be done
+as is the case of installations/facilities used in the generation and distribution of oil and gas.
+Note that often for safety reasons, the latter installations/facilities are monitored continuously.
+There also may be technical dependencies between parts of a system that may require combined replacement,
+like in the case of replacing the cassette of a bike often also requiring to replace the chain,
+or the tires of an airplane which are required to have the same thickness.
+But also complete systems are replaced because replacing one or more of its parts may take much longer,
+which may result in large production losses.
+Another reason can be that there may be a high probability that when individual parts are replaced,
+other parts will be damaged/have to be damaged, requiring their replacement too.
+}\\
+***2 references to M.Shafiee et al (???)***\\
+***Agreed, this is another important simplifying assumption that we needed to make in this manuscript,
 which should be seen as a first step towards a completely new class of CBM policies.

### 2017-04-11 cbm-rbd-paper.tex
work on revision sec 1&2

@@
 leading to a dynamic maintenance policy,
-since the aging of components and possible failures will change the cost-optimal moment of repair in the course of time.
+since the aging of components and possible failures will change the cost-optimal moment of replacement in the course of time.
 Via numerical experiments, some insight into the performance of the policy is given.
@@
 there is a growing interest in condition-based maintenance (CBM), see e.g.,
-\citet[pp.~15--55]{2016:oldekeizer}
+\citet{2017:oldekeizer}
 The central idea behind CBM is to maintain systems or components at the right time,
@@
 All kinds of technical improvements have made it possible % it is more / better / earlier possible
-to estimate the condition of systems as a whole as well as their undelying components,
+to estimate the condition of systems as a whole as well as their underlying components,
 whereas the cost for these technologies is decreasing rapidly,
@@
 
-In this paper, we propose a kind of inspection-based CBM policy
-for when no degradation signal for the system is available,
-but where the status (working or not working) of the components can be monitored continuously.
+In this paper, we propose a new kind of inspection-based CBM policy*** (drop inspection-based???***)
+for when no such usual degradation signal for the system is available,
+but where the status (working or not working) of the components can be monitored (quasi-) continuously,
+i.e., observed every $\delta$ time units, where $\delta$ is very small compared to the lifetimes of components. 
 In this situation, one can use the system's reliability block diagram
@@
 and base the maintenance policy for the system on this distribution.
-In fact, our CBM policy can be seen as based on a multivariate degradation signal,
+In fact, our CBM policy can also be seen as based on a multivariate degradation signal,
 where each component sends a binary signal, and the reliability block diagram is used for sensor fusion.
 
-There are 3 types of triggers to review the system in our new policy:
-at the end of each very short inspection interval (1),
+In our new policy, there are three types of triggers to review the system:
+at the end of each very short time interval $\delta$ (1),
 directly after the failure of a component where the system still functions (2),
@@
 In case of a trigger of type (2),
-when a component has failed since the last inspection but the system is still functioning,
+when a component has failed since the last observation but the system is still functioning,
 also the reliability block diagram of the system is updated.
@@
 accepting the risk of a system breakdown before.
-In this context, the optimal moment of maintenance
-is calculated based on minimizing the expected maintenance-related cost per unit of time for the present operational cycle,
+To determine the latter,
+we calculate the `optimal' next observation moment
+based on minimizing the expected maintenance-related cost per per unit of time for the present operational cycle,
 where an operational cycle starts with a new system, and ends after this system has been replaced by an as good as new system.
+
+When the `optimal' next observation moment is before the next observation of the component status, we replace the system now;
+else we wait for the next component status observation moment.
+The reason behind this decision is that $\delta$ usually is the shortest inter-observation period
+that can be realized from a hardware point of view.
+Note that strictly speaking, this decision may not be optimal.
+However, because $\delta$ is very small when compared to the prior estimates of the lifetime of the components,
+at the time that the next `optimal' observation moment is before the next observation of the status of the still active components,
+we usually already have done better than without updating as described in this paper.
+
+In this context it is also important to realize that our method
+doesn't necessarily result in the actual optimal replacement solution for another reason,
+inherent to using updated information for decisions,
+when these updates can indicate that the former estimates were too optimistic or pessimistic.
+The reason for this is that for some components,
+a too pessimistic prior probability density function (pdf)
+may lead to an increase in system reliability over time without any intervention.
+Whether or not this will be the case, as well as until when this kind of increase can occur,
+is uncertain at every moment in time.
+(***This kind of uncertainty about the probabilistic behaviour itself is very often neglected in operations research literature.***)
+Determining the next `optimal' observation moment can thus only indicate wherther or not waiting with the replacement
+may result in lower or higher cost per unit of time,
+i.e., only indicates a local optimum,
+but not necessarily a global one.
 
@@
 Hereafter, a new system is installed,
-using the updated models for all components based on the insight obtained from the concluded operational cycle.
+using the updated models for all components based on the insight obtained from the finished operational cycles so far.
 
@@
 whereas during the remaining time,
-all can be handled automatically, as done at the moment within, e.g., many safety systems.
+all can be handled automatically, as currently done within, e.g., many safety systems.
 
@@
 
-\iffalse
-% ----------------------------------------------------------------------------------------------------
-\subsection*{---------------------}
-***general discussion on CBM as usual
-
-***Condition-based maintenance (CBM) has received considerable attention in the literature.
-The central idea is to maintain technical systems or components at just the right time,
-that is, before they fail,
-but not too early, in order to keep reliability high and operating costs low.
-%most fully use the component's or system's lifetime and to save on maintenance work
-
-***trade-off between risk of failure during operation
-(can lead to costly downtime: idle workforce, missed production, penalties, loss of reputation)
-and costs of premature maintenance
-(wasting potential component / system lifetime, downtime cost, cost of maintenance work)
-
-***so CBM must be based on some information about the state or health of the component / system.
-Two ways: continuous monitoring CBM and inspection-based CBM.
-
-***Continuous monitoring CBM policies are usually derived
-using a directly observable continuously measurable condition / degradation signal,
-or constructs such a signal or health status using indirect measurements.
-Estimated time till failure (RUL) \citep{2014:rul-review, 2011:rul-review-statistical}
-via distance of current signal level to a fixed known failure threshold.
-
-***Inspection-based CBM via delay time model, modeling the time between detectable degradation and failure,
-again time till failure via distance of current degradation level to fixed known failure threshold.
-
-***In both cases, maintenance decision via control limit / threshold for the signal
-(RUL not explicitely calculated)
-by minimizing the expected unit cost rate,
-which is often approximated using the renewal reward theorem.
-%but in practice threshold often not known
-\subsection*{---------------------}
-
-Here we propose a different approach to CBM
-for the case when no degradation signal for the system is available,
-but system components can be identified and their functioning status
-(working or not working) can be monitored.
-In this situation, one can use the system's layout in reliability terms
-(i.e., its reliability block diagram) and information on components' status
-to directly calculate the residual life distribution (RLD),
-and base the maintenance policy on this distribution.
-(In fact, our approach can be seen as CBM based on a multivariate degradation signal,
-where each component sends a binary signal, and the reliability block diagram is used
-for sensor fusion.)
-
-Our approach can also be seen as a generalization of policies for $k$ out of $N$ systems to arbitrary system layouts.
-Furthermore, our approach allows for multiple types of components in the system,
-with each component type having its own failure behaviour.
-
-%We use a parametric model not for a degradation signal of the system or for the delay time, but for component lifetimes:
-For each component type, we use the well-known Weibull distribution to model component lifetimes.
-To keep the model simple and to demonstrate its feasability, we assume the shape parameter for each component type to be known,
-focusing on learning of the scale parameter,
-and that components fail independently.
-These simplifying assumptions will often not hold in practice,
-then the model can serve as a first approximation.
-Generally, we see our contribution as opening up an entirely new way to derive CBM policies,
-and thus consider the model in this paper more as a proof of concept,
-where extension to more realistic models must happen in a second step.
-As an example, it is possible to extend the model to learn also the shape parameter along the lines of
-\cite{1969:soland},
-but this is not included here as it would complicate presentation.
-%need only to observe when a component fails,
-%and expert information about expected component failure times.
-
-The Bayesian approach to the Weibull model \citep[see, e.g.,][]{1996:mazzuchi-soyer} allows to integrate, for each component type,
-three sources of information: expert knowledge, data from component tests,
-and the status of components in the monitored system. %, i.e., current system condition.
-These information sources are integrated into a single component model
-using the iterative nature of Bayesian updating,
-leading to a so-called posterior predictive distribution for the number of components surviving at any time in the future.
-
-These predictive distributions are then used to calculate the exact distribution of system residual life
-using the survival signature \citep{2012:survsign}.
-(***we therefore accomplish the same as \cite{2013:si-et-al} for their situation.)
-
-By its Bayesian nature, the system residual life distribution adequately reflects the uncertainties %in RUL estimation
-related to modeling and prediction \citep{2015:sankararaman},
-readily adapting to any changes in component behaviour.
-The use of conjugate priors means that we get explicit formulas for the RLD,
-so no numerical integration or simulation techniques are necessary.
-This allows for a very frequent, or even real-time, update of the RLD,
-taking into account the changed structure when components have failed
-and the information gain from updating the component reliability distributions.
-
-Based on the RLD at any current time $\tnow$,
-the optimal moment of maintenance given all information available at $\tnow$
-is then determined by minimizing the expected one-cycle unit cost rate.
-The expected one-cycle unit cost rate, also known as one-cycle criterion
-\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen},
-makes the trade-off between preventive and corrective maintenance according to the current cycle only,
-unlike the usually employed renewal based criterion,
-which approximates the unit cost rate using a renewal argument \citep[p.~296]{1996:mazzuchi-soyer},
-but is not suited for situations where one may whish to change the strategy per cycle \citep{2006:coolen-schrijner-coolen}.
-
-Since the RLD changes with current time $\tnow$,
-the corresponding optimal moment of maintenance $\tausnow$ changes as well,
-leading to a dynamic adaptive maintenance policy,
-similar to a CBM policy based on a continuosly monitored degradation signal.
-However, unlike such threshold-based CBM policies,
-our approach allows to easily take into account the time needed to set up maintenance work (known as set-up time),
-since it gives the optimal moment of maintenance as a time beyond current time $\tnow$,
-and maintenance can be initiated as soon as $\tausnow$ equals the set-up time.
-
-In this paper, we assume that at the moment of maintenance,
-all components in the system are replaced,
-so the cost parameters in the unit cost rate must be determined accordingly.
-One could instead consider other replacement schemes (e.g., replacing only the failed components),
-or indeed optimize the unit cost rate over all possible replacement schemes,
-since our method for RLD calculation can handle differently aged components. 
-However, optimizing over replacement schemes opens up a full research programme on its own,
-and for situations with high set-up costs,
-as is typical for CBM applications,
-the replace-all scheme is most likely the cost-optimal strategy.
-
-***figure of process: component priors $\to$ component posteriors $\to$ system RLD $\to$ $\gnow(\tau)$ $\to$ $\tausnow$
-
-***operation: recalculate $\tausnow$ at fixed dense grid of time points (quasi-continuous),
-this makes sense even when no failures happen because the fact that components in the system still function
-gives information on component distributions;
-alternatively, do the recalculation every time when a component fails (failures contain the most information)
-
-***model allows also to switch to corrective policy when $\gnow(\tau)$ monotonely decreasing (then $\tausnow \to \infty$)
-
-***Expert input in our model is, for each component type,
-Weibull shape parameter, expected failure time (translated to scale parameter),
-and expert info weight (how sure about mean failure time guess).
-Component test data (can include right-censored observations) is optional.
-Further input is system layout (reliability block diagram indicating which component belongs to which type)
-and the cost parameters $c_p$ and $c_u$.
-
-***here all expressed in time, but could also be in usage (number of cycles, etc).
-
-***compare to $M^*$ out of $N$ policy:
-we are dynamic (would mean for a $M^*$ out of $N$ policy that $M^*$ decreases over time due to component aging),
-we learn about component lifetimes,
-and we allow for set-up time
-\fi
-% ----------------------------------------------------------------------------------------------------
-
 \section{Literature review}
@@
 Although there is a lot of literature on CBM policies for multi-component systems,
-see, e.g., \citet{2016:oldekeizer},
+see, e.g., \citet{2017:oldekeizer},
 we found only a few papers having some relation to our approach.
@@
 ***While we also use a Bayesian approach to provide exact expressions for the RLD,***
-One of the main differences between \citet{2013:si-et-al} and our paper
+one of the main differences between \citet{2013:si-et-al} and our paper
 is that we use component status data and the system reliability block diagram instead of a continuous degradation signal
@@
 and that the same policy with the same parameter values is used for a statistically long enough period of time.
-However, due to the update method related to the CBM policy presented in this paper
-like in \citet{2013:si-et-al}, we cannot use the renewal-reward theory based calculation method,
+However, due to the update method related to the CBM policy presented in this paper, %like in \citet{2013:si-et-al},
+we cannot use the renewal-reward theory based calculation method,
 and therefore use the exact formula for the average cost per unit of time.
 
-Another paper that includes some of the aspects included in our paper is the paper by \citet{2012:sun-et-al}.
+Another paper that includes some of the aspects covered in our paper is the paper by \citet{2012:sun-et-al}.
 The authors construct a health index for a system based on sensor measurements,
@@
 as well as changes in the component failure time distributions.
-
-% ----------------------------------------------------------------------------------------------------
-\iffalse
-***CBM via RUL/RLD, $M^*$ out of $N$ policies?
-***also generally Bayesian methods in maintenance optimization?
-***cite CBM review Olde Keizer, Flapper, Teunter, and other refs from it?
-
-Example for Bayesian method in CBM via inspections: \cite{2007:wang-jia}
-propose a model that uses Bayesian updating,
-but the model aims to identify an optimal inspection interval.
-%This is CBM via inspections, not CBM via continuous monitoring as we aim to do.
-
-\begin{scriptsize}
-Wang \& Jia (2007) have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
-model for delay time (time between defect and failure) is Weibull $h \sim \wei(\alpha,\beta)$,
-and each of $\lambda, \alpha, \beta$ has a Gamma prior distribution.
-The expected overall cost rate is then used to find a cost-optimal inspection interval.
-For this they assume that failures are immediately repaired,
-and defects found in an inspection are repaired during inspection.
-
-They use prior predictive distributions for certain statistics (number of defects, number of failures, \ldots between $0$ and $T$)
-to obtain prior values for the Gamma hyperparameters,
-by solving prior predictive equations -- but give no detail on how they actually do this.
-
-In the end they actually do not advocate to calculate the posterior expected cost rate (15),
-but rather plug in posterior estimates for $\lambda, \alpha, \beta$,
-so neglecting uncertainty in estimation.
-(We do not assume a parametric distribution for delay time,
-it rather arises as a consequence of the system layout and component failure distributions.)
-
-\end{scriptsize}
-
-Example for Bayesian method in CBM with continuous monitoring: \cite{2011:elwany-et-al}
-(exponential degradation model, whose parameters $\theta'$ and $\beta$ each have a prior
-which is updated using the degradation signal history,
-and use total expected infinite-horizon discounted cost to determine the maintenance policy,
-RUL not explicitely calculated)
-
-Example for Bayesian method in prediction of system remaining useful life: \cite{2012:sun-et-al}
-(constructs health index for a system based on sensor measurements,
-health status prediction is updated sequentially,
-leads to RUL distribution like our method,
-but no link from RUL to maintenance decision)
-
-\cite{2013:si-et-al} do CBM with continuous monitoring for a single component,
-taking into account the whole degradation path history.
-The authors provide exact expressions for the RUL distribution, which is updated in an empirical Bayesian framework using conjugate priors.
-The RUL distribution is used to construct a replacement decision model using the unit cost rate via renewal reward
-(eq. 35)\\
-***this is most similar to what we do: exact RUL distribution $\to$ maintenance decision,
-but we have component status instead of degradation signal as basis for RUL,
-and we model epistemic uncertainties!\\
-
-\cite{2011:kim-et-al} develop a periodic monitoring CBM policy
-where a maintenance decision is triggered when
-a Bayesian control chart (a sequentially updated health indicator) %posterior probability that system is in a 'warning' state
-exceeds a control limit (threshold) that is determined
-by minimizing the expected average cost per time unit.
-(We use the same cost criterion, but base the maintenance decision directly on our exact RUL estimation.)
-
-***typical recent example for Bayesian network models in maintenance -- could also cover system reliabilty terrain***
-maybe Jones et al (RESS 95:3, 2010) ``The use of Bayesian network modelling for maintenance planning in a manufacturing industry'',
-or Bouaziz et al (2013) ``Towards Bayesian network methodology for predicting equipment health factor of complex semiconductor systems''
-
-\begin{scriptsize}
-Bayesian networks (BNs) are a very general method to jointly model multiple dependent random variables in a Bayesian way. 
-This needs assessments of conditional independece relations, and conditional probability models for each variable,
-the latter often in form of conditional probability tables (discrete variables).
-A Bayesian network models probabilistic relations between variables,
-unlike a reliability block diagram, which gives a deterministic relation
-between the status of components and the system state.
-
-One could model a system as a BN (each component is a variable),
-but that would add a lot of complications.
-Most algorithms for BNs assume discrete distributions,
-and do not scale well to large networks (many tasks are NP-hard).
-
-The above papers seem to use a BN to model a degradation signal or (system) health index (have to check again to be sure).
-Our approach is different, as we get an exact formulation for the system RUL directly.
-\end{scriptsize}
-\fi
-% ----------------------------------------------------------------------------------------------------
 

### 2017-04-11 intro-notes.tex
work on revision sec 1&2

\iffalse
% ----------------------------------------------------------------------------------------------------
\subsection*{---------------------}
***general discussion on CBM as usual

***Condition-based maintenance (CBM) has received considerable attention in the literature.
The central idea is to maintain technical systems or components at just the right time,
that is, before they fail,
but not too early, in order to keep reliability high and operating costs low.
%most fully use the component's or system's lifetime and to save on maintenance work

***trade-off between risk of failure during operation
(can lead to costly downtime: idle workforce, missed production, penalties, loss of reputation)
and costs of premature maintenance
(wasting potential component / system lifetime, downtime cost, cost of maintenance work)

***so CBM must be based on some information about the state or health of the component / system.
Two ways: continuous monitoring CBM and inspection-based CBM.

***Continuous monitoring CBM policies are usually derived
using a directly observable continuously measurable condition / degradation signal,
or constructs such a signal or health status using indirect measurements.
Estimated time till failure (RUL) \citep{2014:rul-review, 2011:rul-review-statistical}
via distance of current signal level to a fixed known failure threshold.

***Inspection-based CBM via delay time model, modeling the time between detectable degradation and failure,
again time till failure via distance of current degradation level to fixed known failure threshold.

***In both cases, maintenance decision via control limit / threshold for the signal
(RUL not explicitely calculated)
by minimizing the expected unit cost rate,
which is often approximated using the renewal reward theorem.
%but in practice threshold often not known
\subsection*{---------------------}

Here we propose a different approach to CBM
for the case when no degradation signal for the system is available,
but system components can be identified and their functioning status
(working or not working) can be monitored.
In this situation, one can use the system's layout in reliability terms
(i.e., its reliability block diagram) and information on components' status
to directly calculate the residual life distribution (RLD),
and base the maintenance policy on this distribution.
(In fact, our approach can be seen as CBM based on a multivariate degradation signal,
where each component sends a binary signal, and the reliability block diagram is used
for sensor fusion.)

Our approach can also be seen as a generalization of policies for $k$ out of $N$ systems to arbitrary system layouts.
Furthermore, our approach allows for multiple types of components in the system,
with each component type having its own failure behaviour.

%We use a parametric model not for a degradation signal of the system or for the delay time, but for component lifetimes:
For each component type, we use the well-known Weibull distribution to model component lifetimes.
To keep the model simple and to demonstrate its feasability, we assume the shape parameter for each component type to be known,
focusing on learning of the scale parameter,
and that components fail independently.
These simplifying assumptions will often not hold in practice,
then the model can serve as a first approximation.
Generally, we see our contribution as opening up an entirely new way to derive CBM policies,
and thus consider the model in this paper more as a proof of concept,
where extension to more realistic models must happen in a second step.
As an example, it is possible to extend the model to learn also the shape parameter along the lines of
\cite{1969:soland},
but this is not included here as it would complicate presentation.
%need only to observe when a component fails,
%and expert information about expected component failure times.

The Bayesian approach to the Weibull model \citep[see, e.g.,][]{1996:mazzuchi-soyer} allows to integrate, for each component type,
three sources of information: expert knowledge, data from component tests,
and the status of components in the monitored system. %, i.e., current system condition.
These information sources are integrated into a single component model
using the iterative nature of Bayesian updating,
leading to a so-called posterior predictive distribution for the number of components surviving at any time in the future.

These predictive distributions are then used to calculate the exact distribution of system residual life
using the survival signature \citep{2012:survsign}.
(***we therefore accomplish the same as \cite{2013:si-et-al} for their situation.)

By its Bayesian nature, the system residual life distribution adequately reflects the uncertainties %in RUL estimation
related to modeling and prediction \citep{2015:sankararaman},
readily adapting to any changes in component behaviour.
The use of conjugate priors means that we get explicit formulas for the RLD,
so no numerical integration or simulation techniques are necessary.
This allows for a very frequent, or even real-time, update of the RLD,
taking into account the changed structure when components have failed
and the information gain from updating the component reliability distributions.

Based on the RLD at any current time $\tnow$,
the optimal moment of maintenance given all information available at $\tnow$
is then determined by minimizing the expected one-cycle unit cost rate.
The expected one-cycle unit cost rate, also known as one-cycle criterion
\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen},
makes the trade-off between preventive and corrective maintenance according to the current cycle only,
unlike the usually employed renewal based criterion,
which approximates the unit cost rate using a renewal argument \citep[p.~296]{1996:mazzuchi-soyer},
but is not suited for situations where one may whish to change the strategy per cycle \citep{2006:coolen-schrijner-coolen}.

Since the RLD changes with current time $\tnow$,
the corresponding optimal moment of maintenance $\tausnow$ changes as well,
leading to a dynamic adaptive maintenance policy,
similar to a CBM policy based on a continuosly monitored degradation signal.
However, unlike such threshold-based CBM policies,
our approach allows to easily take into account the time needed to set up maintenance work (known as set-up time),
since it gives the optimal moment of maintenance as a time beyond current time $\tnow$,
and maintenance can be initiated as soon as $\tausnow$ equals the set-up time.

In this paper, we assume that at the moment of maintenance,
all components in the system are replaced,
so the cost parameters in the unit cost rate must be determined accordingly.
One could instead consider other replacement schemes (e.g., replacing only the failed components),
or indeed optimize the unit cost rate over all possible replacement schemes,
since our method for RLD calculation can handle differently aged components. 
However, optimizing over replacement schemes opens up a full research programme on its own,
and for situations with high set-up costs,
as is typical for CBM applications,
the replace-all scheme is most likely the cost-optimal strategy.

***figure of process: component priors $\to$ component posteriors $\to$ system RLD $\to$ $\gnow(\tau)$ $\to$ $\tausnow$

***operation: recalculate $\tausnow$ at fixed dense grid of time points (quasi-continuous),
this makes sense even when no failures happen because the fact that components in the system still function
gives information on component distributions;
alternatively, do the recalculation every time when a component fails (failures contain the most information)

***model allows also to switch to corrective policy when $\gnow(\tau)$ monotonely decreasing (then $\tausnow \to \infty$)

***Expert input in our model is, for each component type,
Weibull shape parameter, expected failure time (translated to scale parameter),
and expert info weight (how sure about mean failure time guess).
Component test data (can include right-censored observations) is optional.
Further input is system layout (reliability block diagram indicating which component belongs to which type)
and the cost parameters $c_p$ and $c_u$.

***here all expressed in time, but could also be in usage (number of cycles, etc).

***compare to $M^*$ out of $N$ policy:
we are dynamic (would mean for a $M^*$ out of $N$ policy that $M^*$ decreases over time due to component aging),
we learn about component lifetimes,
and we allow for set-up time
\fi
% ----------------------------------------------------------------------------------------------------

% ----------------------------------------------------------------------------------------------------
\iffalse
***CBM via RUL/RLD, $M^*$ out of $N$ policies?
***also generally Bayesian methods in maintenance optimization?
***cite CBM review Olde Keizer, Flapper, Teunter, and other refs from it?

Example for Bayesian method in CBM via inspections: \cite{2007:wang-jia}
propose a model that uses Bayesian updating,
but the model aims to identify an optimal inspection interval.
%This is CBM via inspections, not CBM via continuous monitoring as we aim to do.

\begin{scriptsize}
Wang \& Jia (2007) have a model for defects arrival (homogeneous Poisson process with rate $\lambda$, so no aging),
model for delay time (time between defect and failure) is Weibull $h \sim \wei(\alpha,\beta)$,
and each of $\lambda, \alpha, \beta$ has a Gamma prior distribution.
The expected overall cost rate is then used to find a cost-optimal inspection interval.
For this they assume that failures are immediately repaired,
and defects found in an inspection are repaired during inspection.

They use prior predictive distributions for certain statistics (number of defects, number of failures, \ldots between $0$ and $T$)
to obtain prior values for the Gamma hyperparameters,
by solving prior predictive equations -- but give no detail on how they actually do this.

In the end they actually do not advocate to calculate the posterior expected cost rate (15),
but rather plug in posterior estimates for $\lambda, \alpha, \beta$,
so neglecting uncertainty in estimation.
(We do not assume a parametric distribution for delay time,
it rather arises as a consequence of the system layout and component failure distributions.)

\end{scriptsize}

Example for Bayesian method in CBM with continuous monitoring: \cite{2011:elwany-et-al}
(exponential degradation model, whose parameters $\theta'$ and $\beta$ each have a prior
which is updated using the degradation signal history,
and use total expected infinite-horizon discounted cost to determine the maintenance policy,
RUL not explicitely calculated)

Example for Bayesian method in prediction of system remaining useful life: \cite{2012:sun-et-al}
(constructs health index for a system based on sensor measurements,
health status prediction is updated sequentially,
leads to RUL distribution like our method,
but no link from RUL to maintenance decision)

\cite{2013:si-et-al} do CBM with continuous monitoring for a single component,
taking into account the whole degradation path history.
The authors provide exact expressions for the RUL distribution, which is updated in an empirical Bayesian framework using conjugate priors.
The RUL distribution is used to construct a replacement decision model using the unit cost rate via renewal reward
(eq. 35)\\
***this is most similar to what we do: exact RUL distribution $\to$ maintenance decision,
but we have component status instead of degradation signal as basis for RUL,
and we model epistemic uncertainties!\\

\cite{2011:kim-et-al} develop a periodic monitoring CBM policy
where a maintenance decision is triggered when
a Bayesian control chart (a sequentially updated health indicator) %posterior probability that system is in a 'warning' state
exceeds a control limit (threshold) that is determined
by minimizing the expected average cost per time unit.
(We use the same cost criterion, but base the maintenance decision directly on our exact RUL estimation.)

***typical recent example for Bayesian network models in maintenance -- could also cover system reliabilty terrain***
maybe Jones et al (RESS 95:3, 2010) ``The use of Bayesian network modelling for maintenance planning in a manufacturing industry'',
or Bouaziz et al (2013) ``Towards Bayesian network methodology for predicting equipment health factor of complex semiconductor systems''

\begin{scriptsize}
Bayesian networks (BNs) are a very general method to jointly model multiple dependent random variables in a Bayesian way. 
This needs assessments of conditional independece relations, and conditional probability models for each variable,
the latter often in form of conditional probability tables (discrete variables).
A Bayesian network models probabilistic relations between variables,
unlike a reliability block diagram, which gives a deterministic relation
between the status of components and the system state.

One could model a system as a BN (each component is a variable),
but that would add a lot of complications.
Most algorithms for BNs assume discrete distributions,
and do not scale well to large networks (many tasks are NP-hard).

The above papers seem to use a BN to model a degradation signal or (system) health index (have to check again to be sure).
Our approach is different, as we get an exact formulation for the system RUL directly.
\end{scriptsize}
\fi
% ----------------------------------------------------------------------------------------------------

### 2017-04-11 cbm-rbd-paper.tex
work on revision sec 3&4

@@
 consisting of four component types $M$, $H$, $C$ and $P$,
-with reliability block diagram as depicted in Figure~\ref{fig:brakesys-layout}.
+with the reliability block diagram as depicted in Figure~\ref{fig:brakesys-layout}.
 The master brake cylinder ($M$) activates all four wheel brake cylinders ($C_1$ -- $C_4$),
@@
 omitting the entries for which $\Phi(l_M, l_H, l_C, l_P) = 0$ or $\Phi(l_M, l_H, l_C, l_P) = 1$,
-because the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.
-***The omitted rows from Table~\ref{tab:brakesys-survsign} can be determined as follows:
-\begin{itemize}
-\item Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
-If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding $\Phi$ is $0$.
-\item Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
-If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding $\Phi$ is $1$.
-\end{itemize} 
-The \textsf{R} package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
-provides a convenient function to calculate the survival signature table based on a given graph.
-***To illustrate how the table entries are generated,
+since the full table would contain $\prod_{k=1}^K (N_k + 1) = 2 \times 2 \times 5 \times 5 = 100$ rows.
+%
+To illustrate how the table entries are obtained,
 consider the case $l_M = 0, l_H = 1, l_C = 0, l_P = 1$,
@@
 and so the probability of $P_3$ or $P_4$ being the functioning component is $2 / 4$, thus $\Phi(0, 1, 0, 1) = 0.5$.
+%
+The omitted rows from Table~\ref{tab:brakesys-survsign} can be determined as follows:
+\begin{itemize}
+\item Take a row, decrease $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
+If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding value of $\Phi$ is $0$.
+\item Take a row, increase $l_k$ for one $k \in \{M, H, C, P\}$ by 1.
+If the resulting row is not in Table~\ref{tab:brakesys-survsign}, then the corresponding value of $\Phi$ is $1$.
+\end{itemize} 
+The \textsf{R} package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
+provides a convenient function to calculate the survival signature table based on any given graph.
 
@@
 
-We consider the well-known Weibull model for component lifetimes,
+We consider the well-known Weibull model for the component lifetimes,
 which is used in a wide variety of reliability studies. 
@@
 
-By using a Bayesian approach, described in Section~\ref{sec:weibull},
+By using the Bayesian approach described in Section~\ref{sec:weibull},
 our component model allows to include both expert assessments and test data (if available),
@@
 who presented the same residual life distribution model.
-However, \cite{2016:walter-coolen} did not consider maintenance policies,
-but focus instead on a generalization of the RLD model by using imprecise probability models*** for the component models.
+However, \cite{2016:walter-coolen} do not consider maintenance policies,
+but focus instead on a generalization of the RLD model by using imprecise probability models for the component lifetimes.
 %These sets of priors can be seen as parametric P-boxes,
@@
 
-\subsection{Component posterior predictive distributions at $\tnow$}
+\subsection{Component posterior predictive distributions determined at $\tnow$}
 \label{sec:postpred}
@@
 the component models can be further updated
-using information gained from the current run of the system until $\tnow$:
-Any failure times of failed components,
+using information gained from the current operational cycle as of $\tnow$: %run of the system until $\tnow$:
+failure times of failed components,
 and the right-censoring time $\tpnow$ for each non-failed component,
@@
 let $N_k = \eknow + \cknow$ be the number of type $k$ components in the monitored system,
-where $\eknow$ is the number of components that have failed by $\tnow$,
-and $\cknow$ is the number of components that have not failed by $\tnow$.
+where $\eknow$ denotes the number of type $k$ components that have failed by $\tnow$ during the current operational cycle,
+and $\cknow$ denotes the number of type $k$ components that have not failed by $\tnow$ during the current operational cycle.
 We can thus collect these observations, as of $\tnow$, in a vector
@@
 
-\subsection{Conditional system reliability function at $\tnow$}
+\subsection{Conditional system reliability function determined at $\tnow$}
 \label{sec:sysreltnow}
@@
 Since this is the distribution of system reliability conditional on the system surviving until $\tnow$,
-we have that $\Rsysnow(\tnow) = 1$ for any $\tnow$.
+we have that $\Rsysnow(\tnow) = 1$ for any $\tnow$ before system failure.
 Note that if one or several components have failed by $\tnow$,

### 2017-04-12 cbm-sys-other-priorplot.R
extended simulation: start preparing files

@@ -1,0 +1,39 @@
+# component prior predictive reliability functions to visualize prior assumptions
+
+source("cbm-sys-other.R")
+
+comphor <- 10; complen <- 201
+onecomp <- graph.formula(s -- 1 -- t)
+Ccomp <- setCompTypes(onecomp, list(C = "1"))
+Hcomp <- setCompTypes(onecomp, list(H = "1"))
+Mcomp <- setCompTypes(onecomp, list(M = "1"))
+Pcomp <- setCompTypes(onecomp, list(P = "1"))
+Crel1 <- sysrelnowhor(computeSystemSurvivalSignature(Ccomp), br1n0y0[1], br1beta[1], brfts0[1],
+                      tnow = 0, hor = comphor, seqlen = complen)
+Hrel1 <- sysrelnowhor(computeSystemSurvivalSignature(Hcomp), br1n0y0[2], br1beta[2], brfts0[2],
+                      tnow = 0, hor = comphor, seqlen = complen)
+Mrel1 <- sysrelnowhor(computeSystemSurvivalSignature(Mcomp), br1n0y0[3], br1beta[3], brfts0[3],
+                      tnow = 0, hor = comphor, seqlen = complen)
+Prel1 <- sysrelnowhor(computeSystemSurvivalSignature(Pcomp), br1n0y0[4], br1beta[4], brfts0[4],
+                      tnow = 0, hor = comphor, seqlen = complen)
+compdf1 <- rbind(data.frame(Crel1, comp = "C"), data.frame(Hrel1, comp = "H"),
+                 data.frame(Mrel1, comp = "M"), data.frame(Prel1, comp = "P"))
+# in different facets
+compprior1fig1 <- ggplot(compdf1, aes(x = t, y = rel)) + geom_line(aes(group = comp)) + 
+  ylab("Reliability") + scale_x_continuous(breaks=seq(0, 10, by=2), minor_breaks=0:10) +
+  facet_wrap(~ comp, nrow = 2, scales = "free_y") + coord_cartesian(ylim = c(0, 1))
+pdf("compprior1fig1.pdf", width = 6, height = 4)
+print(compprior1fig1)
+dev.off()
+# as different linetypes
+compprior1fig2 <- ggplot(compdf1, aes(x = t, y = rel)) + geom_line(aes(linetype = comp)) + 
[…]

### 2017-04-12 cbm-sys-other.R

@@ -2,9 +2,9 @@
 # CBM systems paper - code for example figs - define system with other prior
 # --------------------------------------------------------------------------- #
 
-source("weibull-sys-functions.R")
-source("cbm-sim2.R")
-source("plotdefs.R")
+#source("weibull-sys-functions.R")
+#source("cbm-sim2.R")
+#source("plotdefs.R")
 
 # full system for prior
 br <- graph.formula(s -- M -- C1:C2:C3:C4, P1:P2:P3:P4 -- t,
@@ -13,10 +13,9 @@ brctypes <- list("C"=c("C1", "C2", "C3", "C4"), "H"=c("H"), "M"=c("M"), "P"=c("P
 br <- setCompTypes(br, brctypes)
 brsysign <- computeSystemSurvivalSignature(br)
 
-brplotlayout <- matrix(c(0, 1, rep(2,4), rep(3, 4), 4, 1,
-                         0, 0, rep(seq(1.5, -1.5), 2), 0, -1), ncol = 2)
-plot(br, layout = brplotlayout)
-
+#brplotlayout <- matrix(c(0, 1, rep(2,4), rep(3, 4), 4, 1,
+#                         0, 0, rep(seq(1.5, -1.5), 2), 0, -1), ncol = 2)
+#plot(br, layout = brplotlayout)
 
 # order is C H M P
 br1beta <- c(2, 1, 2.5, 1.5)
@@ -28,41 +27,5 @@ br1n0y0 <- list(C=c(br1n0[1], failuretolambda(br1mttf[1], br1beta[1])),
                 P=c(br1n0[4], failuretolambda(br1mttf[4], br1beta[4])))
 brfts0 <- list(C=NULL, H=NULL, M=NULL, P=NULL)
 
-# component prior predictive reliability functions to visualize prior assumptions
-comphor <- 10; complen <- 201
-onecomp <- graph.formula(s -- 1 -- t)
-Ccomp <- setCompTypes(onecomp, list(C = "1"))
-Hcomp <- setCompTypes(onecomp, list(H = "1"))
-Mcomp <- setCompTypes(onecomp, list(M = "1"))
-Pcomp <- setCompTypes(onecomp, list(P = "1"))
-Crel1 <- sysrelnowhor(computeSystemSurvivalSignature(Ccomp), br1n0y0[1], br1beta[1], brfts0[1],
-                      tnow = 0, hor = comphor, seqlen = complen)
[…]

### 2017-04-12 extsim-case-a.R

@@ -1,0 +1,17 @@
+# --------------------------------------------------------------------------- #
+# CBM systems paper - extended simulation study for revision -
+# Case A: failure times as expected
+# --------------------------------------------------------------------------- #
+
+# packages, code files, example system
+source("extsim-setup.R")
+
+# simulate 100 25-cycle machines with priors as given
+set.seed(2211)
+br1sim5cycle20data1 <- list()
+for (i in 1:20){
+  br1sim5cycle20data1[[i]] <- brWeibullData(5, br1beta, br1mttf)
+}
+
+
+#

### 2017-04-12 extsim-makeplots.R

@@ -1,0 +1,31 @@
+# --------------------------------------------------------------------------- #
+# CBM systems paper - extended simulation study for revision - make plots
+# --------------------------------------------------------------------------- #
+
+# load packages
+library(actuar)
+library(ReliabilityTheory)
+library(reshape2)
+library(ggplot2)
+library(gridExtra)
+
+# code files (these contain also the plotting functions)
+source("weibull-sys-functions.R") 
+source("cbm-sim2.R")
+
+# plot definitions and summary functions
+source("plotdefs.R")
+source("extsim-summaryfunctions.R")
+
+# load simulation objects
+# load()
+
+# Case A: failure times as expected
+
+# Case B: failure times earlier than expected
+
+# Case C: failure times later than expected
+
+# Case D: varying failure time behaviour
+
+#

### 2017-04-12 extsim-setup.R

@@ -1,0 +1,20 @@
+# --------------------------------------------------------------------------- #
+# CBM systems paper - extended simulation study for revision - simulation setup
+# --------------------------------------------------------------------------- #
+
+# install packages if necessary
+install.packages(c("actuar", "ReliabilityTheory", "reshape2"))
+
+# load packages
+library(actuar)
+library(ReliabilityTheory)
+library(reshape2)
+
+# code files
+source("weibull-sys-functions.R") # contains also plotting functions that work only with ggplot2 and gridExtra
+source("cbm-sim2.R")
+
+# the example system
+source("cbm-sys-other.R")
+
+#

### 2017-04-12 extsim-summaryfunctions.R

@@ -1,0 +1,45 @@
+# --------------------------------------------------------------------------- #
+# CBM systems paper - extended simulation study for revision - 
+# summary and labeller functions for objects generated by the simulations
+# --------------------------------------------------------------------------- #
+
+simsummary <- function(simlist){
+  data.frame(id = 1:length(simlist),
+             nfails = sapply(simlist, function(res) sum(res$tfunc != res$tend)),
+             meantend = sapply(simlist, function(res) mean(res$tend)),
+             meancostrate = sapply(simlist, function(res) weighted.mean(res$costrate, res$tend)))
+}
+
+simsummary2 <- function(simlist){
+  nrep <- length(simlist)
+  ncyc <- length(simlist[[1]]$tend)
+  data.frame(repid = rep(1:nrep, each = ncyc),
+             cycid = rep(1:ncyc, nrep),
+             failed = as.vector(sapply(simlist, function(res) res$tfunc != res$tend)),
+             tend = as.vector(sapply(simlist, function(res) res$tend)),
+             costrate = as.vector(sapply(simlist, function(res) res$costrate)))
+}
+
+simlabeller <- as_labeller(c(nfails = "Number of system failures",
+                             meantend = "Average cycle length",
+                             meancostrate = "Average unit cost rate"))
+simlabeller2 <- as_labeller(c(nfails = "Number of system failures",
+                              meantend = "Average cycle length",
+                              meancostrate = "Average unit cost rate",
+                              "Continuous update" = "Continuous update",
+                              "Cycle end update" = "Cycle end update",
+                              "No update" = "No update",
+                              "Age-based with update" = "Age-based with update",
+                              "Age-based without update" = "Age-based without update",
+                              "Corrective" = "Corrective"))
+simlabeller3 <- as_labeller(c(nfails = expression(n[failures]),
+                              meantend = expression(bar(t)[sys]),
+                              meancostrate = expression(bar(g)),
+                              "Continuous update" = "CBMcpu",
+                              "Cycle end update" = "CBMepu",
+                              "No update" = "CBMnpu",
+                              "Age-based with update" = "ABMepu",
+                              "Age-based without update" = "ABMnpu",
+                              "Corrective" = "CM"))
+
+#

### 2017-04-12 weibull-sys-functions.R

@@ -4,11 +4,12 @@
 #       Author: Gero Walter (g.m.walter@tue.nl, gero@gmx.at)                  #
 ###############################################################################
 
-library(actuar) # provides dinvgamma(x, shape, scale) where shape = alpha and scale = beta
-library(ReliabilityTheory)
-library(ggplot2)
-library(reshape2)
-library(gridExtra)
+# load libraries if not yet loaded
+# library(actuar) # provides dinvgamma(x, shape, scale) where shape = alpha and scale = beta
+# library(ReliabilityTheory)
+# library(ggplot2)
+# library(reshape2)
+# library(gridExtra)
 
 # translate lambda parameter of weibull to expected failure time
 # lambda - scale parameter of weibull

### 2017-04-12 extsim-case-a.R
extended simulation: preparing files

@@ -8,10 +8,53 @@ source("extsim-setup.R")
 
 # simulate 100 25-cycle machines with priors as given
 set.seed(2211)
-br1sim5cycle20data1 <- list()
-for (i in 1:20){
-  br1sim5cycle20data1[[i]] <- brWeibullData(5, br1beta, br1mttf)
+repetitions <- 100
+opcycles <- 25
+Asimdata <- list()
+for (i in 1:repetitions){
+  Asimdata[[i]] <- brWeibullData(opcycles, br1beta, br1mttf)
 }
 
+# result lists
+AsimCBMcpu <- list() # our model
+AsimCBMepu <- list() # do not update params during cycle, but at end of cycle 
+AsimCBMnpu <- list() # never update params
+AsimABMepu <- list() # age-based policy with parameter update
+AsimABMnpu <- list() # age-based policy without parameter update
+AsimCM <- list()     # corrective policy
+
+# run simulations (six separate loops possible - use plyr::llply or lapply instead?)
+for (i in 1:repetitions){
+  #cat("Repetition", i, ": CBM-cpu\n")
+  AsimCBMcpu[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = Asimdata[[i]], n0y0 = br1n0y0,
+                               beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.1, seqlen = 401,
+                               onecycle = FALSE)
+  #cat("Repetition", i, ": CBM-epu\n")
+  AsimCBMepu[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = Asimdata[[i]], n0y0 = br1n0y0,
+                               beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.1, seqlen = 401,
+                               prior = TRUE, onecycle = FALSE)
+  #cat("Repetition", i, ": CBM-npu\n")
+  AsimCBMnpu[[i]] <- simNcycle(sys = br, ctypes = brctypes, compfts = Asimdata[[i]], n0y0 = br1n0y0,
+                               beta = br1beta, tnowstep = 0.1, hor = 4, thresh = 0.1, seqlen = 401,
+                               prior = TRUE, cycleupdate = FALSE, onecycle = FALSE)
+  #cat("Repetition", i, ": ABM-epu\n")
[…]

### 2017-04-12 extsim-makeplots.R

@@ -17,10 +17,37 @@ source("cbm-sim2.R")
 source("plotdefs.R")
 source("extsim-summaryfunctions.R")
 
-# load simulation objects
+# Case A: failure times as expected
+
+## load simulation objects
 # load()
 
-# Case A: failure times as expected
+## apply summary functions
+br1sim1Tt01summary <- simsummary(br1sim1Tt01)
+br1sim1prTt01summary <- simsummary(br1sim1prTt01)
+br1sim1prprTt01summary <- simsummary(br1sim1prprTt01)
+
+br1sim1asummary <- simsummary(br1sim1a)
+br1sim1aprsummary <- simsummary(br1sim1apr)
+br1sim1csummary <- simsummary(br1sim1c)
+
+br1sim1Tt01acsummaryall <- rbind(data.frame(sim = "CBM-cpu", br1sim1Tt01summary),
+                                 data.frame(sim = "CBM-epu", br1sim1prTt01summary),
+                                 data.frame(sim = "CBM-npu", br1sim1prprTt01summary),
+                                 data.frame(sim = "ABM-epu", br1sim1asummary),
+                                 data.frame(sim = "ABM-npu", br1sim1aprsummary),
+                                 data.frame(sim = "CM", br1sim1csummary))
+names(br1sim1Tt01acsummaryall)[3:5] <- c(expression(e[sys]), expression(bar(r)[sys]), expression(bar(g)))
+
+## the plot
+br1sim1fig5Tt01ac <- ggplot(melt(br1sim1Tt01acsummaryall, c("id", "sim")), aes(x = id, y = value)) +
+  geom_line(aes(group = sim), size = 0.3) + geom_point(aes(group = sim), size = 0.5) + 
+  facet_grid(variable ~ sim, scales = "free_y", labeller = label_parsed) +
+  xlab("5-cycle repetition number") + theme(axis.title.y = element_blank())
+pdf("br1sim1fig5Tt01ac.pdf", width = 6, height = 3)
+br1sim1fig5Tt01ac
+dev.off()
+
 
 # Case B: failure times earlier than expected
 

### 2017-04-12 extsim-setup.R

@@ -3,12 +3,12 @@
 # --------------------------------------------------------------------------- #
 
 # install packages if necessary
-install.packages(c("actuar", "ReliabilityTheory", "reshape2"))
+install.packages(c("actuar", "igraph", "ReliabilityTheory", "reshape2"))
 
 # load packages
 library(actuar)
 library(ReliabilityTheory)
-library(reshape2)
+library(reshape2) # might not be necessary
 
 # code files
 source("weibull-sys-functions.R") # contains also plotting functions that work only with ggplot2 and gridExtra

### 2017-05-10 cbm-rbd-paper.tex
timeline figure done

@@
 that resembles a CBM policy.
+Figure~\ref{fig:timeline} shows two example time lines for the system,
+starting each with a new system (operational cycle) at t=0.
+
+***explain figure, triggers 1, 2, 3***
+
 Consider a set of evaluation time points $\tnow$.
@@
 \begin{tikzpicture}
-\node {exemplary timeline};
+%[tausnow/.style={|-|, line width=0.5mm}]
+[ tausnow/.style={line width=0.8mm},
+  pfeil/.style={-latex', line width=0.5mm, shorten >=1mm}] 
+\draw[-latex', very thick] (-0.2, -0.5) -- (5.5, -0.5) node[below] {$t$};
+\draw (0, -0.4) -- (0, -0.6) node[below] {$0$};
+\foreach \x in {1, 2, 3, 4, 5}
+ {\draw (\x, -0.4) -- (\x, -0.6) node[below] {$0.\x$};
+  \draw[dotted] (\x, -0.4) -- (\x, \x); }
+\draw[thick, decorate, decoration=brace] (1, -1) -- (0, -1) node[midway,below] {$\delta$};
+\draw[dashed] (0, 0) -- (5,5);
+\draw[tausnow] (0  , 0  ) -- (2.3, 0  ) node[at start, left] {$\tau_*^{(0)}$};
+\draw[tausnow] (1  , 1  ) -- (2.9, 1  ) node[at start, left] {$\tau_*^{(0.1)}$};
+\draw[tausnow] (2  , 2  ) -- (4.2, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
+\draw (2.4, -0.4) circle (0.8mm) edge[dotted] (2.4, 2.4);
+%\node[draw,shape=diamond] (f1) at (2.4, -0.4) {}; % edge[dotted] (2.4, 2.4);
+\draw[tausnow] (2.4, 2.4) -- (3.9, 2.4) node[at start, left] {$\tau_*^{(0.24)}$};
+\draw[tausnow] (3  , 3  ) -- (4.4, 3  ) node[at start, left] {$\tau_*^{(0.3)}$};
+\draw (3.6, -0.4) circle (0.8mm) edge[dotted] (3.6, 3.6);
+\draw[tausnow] (3.6, 3.6) -- (4.3, 3.6) node[at start, left] {$\tau_*^{(0.36)}$};
+\draw[tausnow] (4  , 4  ) -- (4.7, 4  ) node[at start, left] {$\tau_*^{(0.4)}$};
+\node (box1) at (1,4) {\parbox{12ex}{\small preventive\\ replacement\\ at $\tnow = 0.4$\\ as $\tau_*^{(0.4)} < \delta$}};
+\draw[pfeil] (box1) edge[out=20, in=120] (4,4);
+\begin{scope}[xshift=7cm]
+\draw[-latex', very thick] (-0.2, -0.5) -- (3.5, -0.5) node[below] {$t$};
+\draw (0, -0.4) -- (0, -0.6) node[below] {$0$};
+\foreach \x in {1, 2, 3}
+ {\draw (\x, -0.4) -- (\x, -0.6) node[below] {$0.\x$};
+  \draw[dotted] (\x, -0.4) -- (\x, \x); }
+\draw[thick, decorate, decoration=brace] (1, -1) -- (0, -1) node[midway,below] {$\delta$};
+\draw[dashed] (0, 0) -- (3,3);
+\draw[tausnow] (0  , 0  ) -- (2.3, 0  ) node[at start, left] {$\tau_*^{(0)}$};
+\draw[tausnow] (1  , 1  ) -- (2.9, 1  ) node[at start, left] {$\tau_*^{(0.1)}$};
+\draw (1.4, -0.4) circle (0.8mm) edge[dotted] (1.4, 1.4);
+\draw[tausnow] (1.4, 1.4) -- (2.8, 1.4) node[at start, left] {$\tau_*^{(0.14)}$};
+\draw[tausnow] (2  , 2  ) -- (3.3, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
+\draw[fill] (2.7, -0.4) circle (0.8mm) edge[dotted] (2.7, 2.7);
+\node (box2) at (1,4) {\parbox{13ex}{\small corrective\\ replacement\\ at $\tnow = 0.27$\\ due to system failure}};
+\draw[pfeil] (box2) edge[out=10, in=90] (2.7,2.7);
+\end{scope}
 \end{tikzpicture}
-\caption{***exemplary timeline sketch}
+\caption{Two exemplary timelines for the suggested maintenance policy.
+The horizontal bars depict, for subsequent times $\tnow$,
+the time to the next economically optimal inspection $\tausnow$.
+The times $\tnow$ for which $\tausnow$ is evaluated are
+at regular intervals $\delta, 2\delta, 3\delta,\ldots$ (trigger 1),
+and at the time of component failures (trigger 2),
+marked by a circle on the time axis.
+Failures that lead to the whole system failing (trigger 3) are marked by a filled circle.
+The calculation of $\tausnow$ is described in detail in Section~***.}
 \label{fig:timeline}

### 2017-05-10 cbm-rbd-paper.tex
work on intro again, setup sec 5

@@
 \citet{2017:oldekeizer}
-The central idea behind CBM is to maintain systems or components at the right time,
-i.e., before they fail, but not too early, in order to keep their reliability high and operating costs low.
+The central idea behind CBM is to maintain systems or components at exactly the right time,
+i.e., just before they fail, %but not too early,
+in order to keep their reliability high and operating costs low.
 In this context a trade-off is made between the risk of failure during operation
@@
 
-Most CBM policies are based on a directly observable, continuously measurable condition or degradation signal.
+Most CBM policies are based on a directly observable, continuously measurable condition or degradation signal,
+e.g., the amount of vibration in case of rotating equipment.
 Alternatively, such a signal or health status is constructed
@@
 In this paper, we propose a new kind of inspection-based CBM policy*** (drop inspection-based???***)
-for when no such usual degradation signal for the system is available,
-but where the status (working or not working) of the components can be monitored (quasi-) continuously,
-i.e., observed every $\delta$ time units, where $\delta$ is very small compared to the lifetimes of components. 
+for when no such \emph{usual} degradation signal for the system is available,
+but where the status (working or not working) of the system's components can be monitored (quasi-) continuously.
+%i.e., observed every $\delta$ time units, where $\delta$ is very small compared to the lifetimes of components. 
 In this situation, one can use the system's reliability block diagram
@@
 In our new policy, there are three types of triggers to review the system:
-at the end of each very short time interval $\delta$ (1),
-directly after the failure of a component where the system still functions (2),
-and directly after the failure of a component due to which the system as a whole no longer can function (3). 
-We denote each review of the system in reaction to these triggers by `evaluation',
-since the system RLD is re-evaluated at each of these time points.
+(1) at the end of each very short time interval $\delta$ 
+(where $\delta$ is very short compared to the lifetimes of components),
+(2) directly after the failure of a component where the system still functions,
+and (3) directly after the failure of a component due to which the system as a whole no longer can function. 
+We denote each review of the system in reaction to triggers (1) and (2) by `evaluation',
+since the system RLD is re-evaluated at each of these time points,
+and a decision is made on whether preventive maintenance should be carried out or not.
 We use the term `evaluation' in place of the term `inspection',
@@
 In case of a trigger of type (1),
-the currently used model for component failure times is updated
+the currently used models for component failure times are updated
 to account for the aging of components,
@@
 in a Bayesian parameter update step.
-
 In case of a trigger of type (2),
-when a component has failed since the last observation but the system is still functioning,
-also the reliability block diagram of the system is updated.
+where a component has failed but the system is still functioning,
+in addition to the component models also the reliability block diagram of the system is updated.
 Based on the above changes,
@@
 To determine the latter,
-we calculate the `optimal' next observation moment
+we calculate the `optimal' next evaluation moment %moment for system replacement***
 based on minimizing the expected maintenance-related cost per per unit of time for the present operational cycle,
@@
 
-When the `optimal' next observation moment is before the next observation of the component status, we replace the system now;
-else we wait for the next component status observation moment.
-The reason behind this decision is that $\delta$ usually is the shortest inter-observation period
-that can be realized from a hardware point of view.
-Note that strictly speaking, this decision may not be optimal.
+When the `optimal' next evaluation moment is before the next planned evaluation moment, we replace the system now;
+else we wait for the next planned evaluation moment.
+The reason behind this decision is that $\delta$ is taken as %usually is 
+%the shortest interval for which re-evaluation of the system RLD will show any difference***
+%the shortest inter-observation period that can be realized from a hardware point of view.
+the shortest inter-evaluation period that can be realized from a hardware point of view*** / 
+the time granularity according to which maintenance actions can be reasonably triggered***.
+To illustrate, for component with lifetimes measuring in days,
+$\delta$ should be in the order of minutes;
+for components with lifetimes measuring in months,
+$\delta$ could be one day.
+
+Note that strictly speaking, this decision procedure may not be optimal.
 However, because $\delta$ is very small when compared to the prior estimates of the lifetime of the components,
 at the time that the next `optimal' observation moment is before the next observation of the status of the still active components,
-we usually already have done better than without updating as described in this paper.
+we usually already have done much better than without updating as described in this paper.
 
@@
 is uncertain at every moment in time.
-(***This kind of uncertainty about the probabilistic behaviour itself is very often neglected in operations research literature.***)
-Determining the next `optimal' observation moment can thus only indicate wherther or not waiting with the replacement
+(***As a sidenote,
+this kind of uncertainty about the probabilistic behaviour itself is very often neglected in operations research literature.***)
+Determining the next `optimal' evaluation moment can thus only indicate whether or not waiting with the replacement
 may result in lower or higher cost per unit of time,
@@
 In case of a trigger of type (3),
+where the failure of a component leads to the whole system failing,
 the currently used component failure time distributions are updated
@@
 
+%***start with $\tausnow$???
 Now we can derive the adaptive and dynamic maintenance policy
@@
 starting each with a new system (operational cycle) at t=0.
+As described in Section~\ref{intro},
+the health of the system is re-evaluated at
+
+two kinds of triggers
+
+health of system via $\tausnow$, which is described in detail in Section~***
+
+In the left timeline example,
 
@@
 \draw[tausnow] (2  , 2  ) -- (4.2, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
-\draw (2.4, -0.4) circle (0.8mm) edge[dotted] (2.4, 2.4);
+\draw (2.4, -0.5) circle (0.8mm) edge[dotted] (2.4, 2.4);
 %\node[draw,shape=diamond] (f1) at (2.4, -0.4) {}; % edge[dotted] (2.4, 2.4);
@@
 \draw[tausnow] (3  , 3  ) -- (4.4, 3  ) node[at start, left] {$\tau_*^{(0.3)}$};
-\draw (3.6, -0.4) circle (0.8mm) edge[dotted] (3.6, 3.6);
+\draw (3.6, -0.5) circle (0.8mm) edge[dotted] (3.6, 3.6);
 \draw[tausnow] (3.6, 3.6) -- (4.3, 3.6) node[at start, left] {$\tau_*^{(0.36)}$};
@@
 \draw[tausnow] (1  , 1  ) -- (2.9, 1  ) node[at start, left] {$\tau_*^{(0.1)}$};
-\draw (1.4, -0.4) circle (0.8mm) edge[dotted] (1.4, 1.4);
+\draw (1.4, -0.5) circle (0.8mm) edge[dotted] (1.4, 1.4);
 \draw[tausnow] (1.4, 1.4) -- (2.8, 1.4) node[at start, left] {$\tau_*^{(0.14)}$};
 \draw[tausnow] (2  , 2  ) -- (3.3, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
-\draw[fill] (2.7, -0.4) circle (0.8mm) edge[dotted] (2.7, 2.7);
+\draw[fill] (2.7, -0.5) circle (0.8mm) edge[dotted] (2.7, 2.7);
 \node (box2) at (1,4) {\parbox{13ex}{\small corrective\\ replacement\\ at $\tnow = 0.27$\\ due to system failure}};
@@
 The calculation of $\tausnow$ is described in detail in Section~***.}
+%\begin{tikzpicture}\draw (0,0) circle (0.8mm);\end{tikzpicture}
 \label{fig:timeline}

### 2017-05-11 cbm-rbd-paper.tex
first part of sec 5 rewritten

@@
 
+\newcommand{\tausfun}[1]{\tau_*^{(#1)}}
+
 % ------------ options -------------
@@
 the time granularity according to which maintenance actions can be reasonably triggered***.
-To illustrate, for component with lifetimes measuring in days,
-$\delta$ should be in the order of minutes;
+To illustrate, for components with lifetimes measuring in a few days,
+$\delta$ could be in the order of minutes;
 for components with lifetimes measuring in months,
@@
 that resembles a CBM policy.
-Figure~\ref{fig:timeline} shows two example time lines for the system,
-starting each with a new system (operational cycle) at t=0.
-As described in Section~\ref{intro},
-the health of the system is re-evaluated at
-
-two kinds of triggers
-
-health of system via $\tausnow$, which is described in detail in Section~***
-
-In the left timeline example,
-
-***explain figure, triggers 1, 2, 3***
-
-Consider a set of evaluation time points $\tnow$.
+Our idea is described here first in general terms,
+and then illustrated along two examplary timelines in Section~\ref{sec:policy-example}.
+Afterwards, we introduce the formal definition of the policy in Section~\ref{sec:operationalprocedure}***,
+and give further details on the involved computations in Sections~\ref{sec:costrate} and \ref{sec:optim}.***
+
+We denote by $\tnow$ the moment in time that the system is observed,
+measured from the moment the present operational cycle has started,
+which coincides with starting to use a new system.
 Instead of determining a threshold for a degradation signal like in usual CBM approaches,
-we determine, for each present time $\tnow$,
-the adaptive and dynamic time span $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
-Close to system startup, $\tausnow$ will be large;
-but as components in the system age and some indeed fail over time,
-$\tausnow$ will typically decrease.
-%Let $\tprep$ be the time span needed to prepare maintenance work.
-%Let $\tthresh$ be a threshold time span chosen for practical reasons.
-%used to decide when maintenance is initiated, i.e.,
+we determine, for $\tnow$, the adaptive and dynamic time span $\tausnow$
+which gives the time from $\tnow$ until the next optimal moment to re-evaluate the system.
+%Close to system startup, $\tausnow$ will be large;
+%but as components in the system age and some indeed fail over time,
+%$\tausnow$ will typically decrease.
 A preventive maintenance action is initiated
-as soon as $\tausnow$ decreases below the time span to the next evaluation time.
-%continuing to the the next evaluation point $\tnow$ would carry the risk 
-%a time span chosen to reflect operational practicalities.
-This dynamic and adaptive maintenance policy is described in more detail in Section~\ref{sec:operationalprocedure};
-a flow chart for the policy is given in Figure~\ref{fig:procedure}.
-
-The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
+when $\tnow + \tausnow$ would be earlier than the next planned evaluation time point.
+We describe this dynamic and adaptive maintenance policy in more detail in Section~\ref{sec:operationalprocedure}.
+%a flow chart for the policy is given in Figure~\ref{fig:procedure}.
+
+The near*** optimal time to system re-evaluation $\tausnow$ is determined based on $\Rsysnow(t)$
 by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
-An operational cycle begins with system start-up,
-and ends when either preventive maintenance is carried out,
-or a failure of the system occurs, with subsequent corrective maintenance.
+%An operational cycle begins with system start-up,
+%and ends when either preventive maintenance is carried out,
+%or a failure of the system occurs, with subsequent corrective maintenance.
 This criterion, as detailed in Section~\ref{sec:costrate},
@@
 Section~\ref{sec:optim} then focuses on our choice for the component models and the resulting form for $\Rsysnow(t)$,
-and shows how $\tausnow$ is determined in this situation.
+and shows how $\tausnow$ is numerically determined in this situation.
 %Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
@@
 \caption{Two exemplary timelines for the suggested maintenance policy.
-The horizontal bars depict, for subsequent times $\tnow$,
-the time to the next economically optimal inspection $\tausnow$.
+The horizontal bars depict $\tausnow$,
+the time to the next economically optimal evaluation of the system RLD,
+for subsequent times $\tnow$.
 The times $\tnow$ for which $\tausnow$ is evaluated are
-at regular intervals $\delta, 2\delta, 3\delta,\ldots$ (trigger 1),
+at regular intervals $m \delta, m \in \naturals_0$ (trigger 1),
 and at the time of component failures (trigger 2),
-marked by a circle on the time axis.
-Failures that lead to the whole system failing (trigger 3) are marked by a filled circle.
-The calculation of $\tausnow$ is described in detail in Section~***.}
+which are marked by a circle on the time axis.
+Failures that lead to the whole system failing (trigger 3) are marked by a filled circle.}
+%The calculation of $\tausnow$ is described in detail in Section~***.}
 %\begin{tikzpicture}\draw (0,0) circle (0.8mm);\end{tikzpicture}
@@
 \end{figure}
+
+\subsection{Two exemplary timelines}
+\label{sec:policy-example}
+
+Figure~\ref{fig:timeline} shows two examplary time lines,
+starting each with a new system (operational cycle) at $t=0$.
+The left timeline leads to preventive maintenance,
+the timeline on the right to corrective maintenance.
+
+As described in Section~\ref{intro},
+the health of the system is re-evaluated at three types of triggers.
+Triggers of type (1) are the evenly spaced planned evaluation time points $m\delta$, where $m \in \naturals_0$,
+giving the time granularity at which maintenance actions can be reasonably initiated.***
+%Let $\tthresh$ be a threshold time span chosen for practical reasons.
+%used to decide when maintenance is initiated, i.e.,
+%a time span chosen to reflect operational practicalities.
+The times $m\delta$ are indicated by vertical tick lines on the time axis in Figure~\ref{fig:timeline},
+where $\delta = 0.1$.
+The moments of failure of a component form the other two types of triggers.
+A component failure after which the system still functions is a trigger of type (2),
+depicted as a (non-filled) circle on the time axis.
+A filled circle indicates a trigger of type (3),
+which is a component failure that causes the whole system to fail.
+
+For each trigger of type (1) and (2),
+the system health is evaluated by calculating $\tausnow$,
+the currently optimal time to re-evaluation, %$\tausnow$ is %calculated,
+visualized by the thick horizontal bars in Figure~\ref{fig:timeline}.
+%The details of calculating $\tausnow$ are described in detail in Sections~\ref{sec:costrate} and \ref{sec:optim}.***
+For a type (3) trigger, the system health evaluation just corresponds to acknowledging that the system has failed.
+%/ to the diagnosis/insight*** of system failure.
+%and calculation of $\tausnow$ is 
+For triggers of type (1) and (2),
+the calculated $\tausnow$ is compared to the time to the next planned evaluation time point.
+When $\tausnow$ is shorter than this time,
+preventive maintenance of the system is initiated.
+
+In the timeline on the left of Figure~\ref{fig:timeline},
+$\tausnow$ is re-evaluated at times $\tnow = 0.1, 0.2, 0.24, 0.3, 0.36, 0.4$,
+where $0.24$ and $0.36$ correspond to component failure times.
+Note that the failure at $\tnow = 0.24$ substantially shortens $\tausfun{0.24}$,
+such that $0.24 + \tausfun{0.24} < 0.2 + \tausfun{0.2}$,
+i.e., the optimal moment of re-evaluation has moved backwards in time.
+This illustrates that new insights drawn from a component failure
+(regarding the reliability block diagram as well as the component model)
+may have considerable influence on the system RLD
+and the $\tausnow$ that is derived from it.
+The component failure at $\tnow = 0.36$ leads to a further shortened $\tausfun{0.36}$,
+such that $\tausfun{0.36} < 0.1 = \delta$.
+However, this does not lead to an immediate decision for preventive maintenance,
+since $\tausfun{0.36}$ is compared to the time to the next planned evaluation at $t = 0.4$.
+The decision for preventive maintenance is instead made at $\tnow = 0.4$,
+as only then it is not economical any more to wait for the next planned evaluation at $t = 0.5$.
+
+The timeline on the right of Figure~\ref{fig:timeline} illustrates an operational cycle ending with corrective maintenance.
+Here, the component failure at $\tnow = 0.27$ leads to system failure.
+The size of $\tausfun{0.2}$ indicates that the component failure that happens at $\tnow = 0.27$
+had been deemed very unlikely at time $\tnow = 0.2$.
+but then nevertheless occured at $t = 0.27$.
+
+\subsection{Formal*** / Detailed description of the policy}
+\label{sec:operationalprocedure}
+
+Each operational cycle starts with a system startup.
+At this point in time, the system is in an (as good as) new state,
+i.e., all components in the system are (as good as) new and have not aged.
+An operational cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
+or the system fails, which triggers a corrective maintenance action.
+
+***below two pars towards the end?
+
+We assume that both preventive and corrective maintenance result in an (as good as) new system state by replacing all components,
+such that the system begins a new operational cycle always under the same conditions.
+At first sight, replacing a complete system when only some parts of it are defective may seem strange.
+However, there are many real life examples, including from daily live.
+So called complete clustering \citep{2017:oldekeizer}
+may be optimal in case of a very strong economic dependence between the different parts of a system,
+e.g., due to a very high fixed set-up cost independent of the maintenance activities to be done,
+as is the case of installations/facilities*** used in the generation and distribution of oil and gas.
+Note that often for safety reasons, the latter installations/facilities*** are monitored continuously.
+There may be also technical dependencies between parts of a system that may require combined replacement:
+replacing the cassette of a bike often also requires to replace the chain,
+and the tires of an airplane are required to have the same thickness.
+But also complete systems are replaced because replacing one or more of its parts may take much longer,
+which may result in big production losses.
+Another reason can be that there may be a high probability that when individual parts are replaced,
+other parts will be damaged/have to be damaged***, requiring their replacement as well.
+
+Replacement schemes that do not replace all components during maintenance
+would require to account for the different ages of components in the system
+at the start of a new cycle.
+While this is in principle possible in our approach,
+exploring such selective replacement schemes is out of scope for this paper.
+Optimizing over replacement schemes is, in our view, a higly interesting topic that merits an investigation of its own.
+We will return to this in the conclusion (Section~\ref{sec:outlook}).
 
@@
 
-\subsection{Detailed description of the policy}
-\label{sec:operationalprocedure}
-
-Each operational cycle starts with a system startup.
-At this point in time, the system is in an (as good as) new state,
-i.e., all components in the system are (as good as) new and have not aged.
-An operational cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
-or the system fails, which triggers a corrective maintenance action.
-
-Define a grid of planned evaluation time points as $\{m \delta : m \in \naturals_0\}$,
+Figure~\ref{fig:procedure} depicts the flow chart for the policy,
+indicating the decisions that are repeatedly encountered in a single operational cycle.
+The flow chart also contains the loop back to the start of a new operational cycle.
+
+%***Consider a set of evaluation time points $\tnow$.
+Consider a grid of planned evaluation time points $\{m \delta : m \in \naturals_0\}$,
 %where $m = 0, 1, 2, \ldots$,
@@
 
-Frequent recalculation of $\tausnow$ is feasible
-when computation of the RLD is fast.
-Then, by evaluating the unit cost rate function $\gnow(\tau)$ on a discrete grid,
-$\tausnow$ can be approximated with a simple grid search.
+The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
+of the maintenance interval in an age based policy by trading off the costs of preventive and corrective maintenance
+(see Section~\ref{sec:costrate} below).
+However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
+our policy is adaptive and dynamic like a CBM policy. 
+When computation of the RLD is fast,
+frequent recalculation of $\tausnow$ is feasible,
+%Then, by evaluating the unit cost rate function $\gnow(\tau)$ (see Section~\ref{sec:costrate} below) on a discrete grid,
+%$\tausnow$ can be approximated with a simple grid search.
 %because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
 %and determine $\tausnow$ with a simple grid search.
-Updating $\tausnow$ frequently is useful because,
+%Updating $\tausnow$ frequently is useful because,
+and it is useful because,
 even in absence of failures of system components,
-all components age, and also non-failure adds information to the component models.
+all components age, and also non-failure adds information to the component models,
+reducing uncertainty.
 %Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
@@
 %
-The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
-of the maintenance interval in an age based policy by trading off the costs of preventive and corrective maintenance.
-However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
-our policy is adaptive and dynamic like a CBM policy. 
 %As can happen for an age-based policy, the derived $\gnow(\tau)$ may also be monotonely decreasing.
@@
 In both cases, we decide to maintain the system preventively
-when the optimal time to maintenance is closer to now than the next time we intend to re-evaluate $\tausnow$,
-since otherwise, in waiting to the next evaluation time,
+when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate $\tausnow$,
+since otherwise, in waiting to the next planned evaluation time,
 one would exceed the optimal system failure risk 
-as determined by the trade-off made by $\gnow(\cdot)$.
+as determined by the trade-off made via $\gnow(\cdot)$.
 When $\tausnow$ is instead further in the future than the next planned evaluation time,
-we can safely continue to the next evaluation time,
+we can safely continue to the next planned evaluation time,
 without risking to miss the cost-optimal moment to preventively maintain the system.
@@
 such that $\nkz$ and $\ykz$ for the next operational cycle
-account for the (censored) lifetimes observed during the previous operational cycle.
+account for the (censored) lifetimes observed during the previous operational cycles.
 %We assume that both planned and unplanned maintenance action takes negligible time,
 
-Figure~\ref{fig:procedure} displays the flowchart for the policy,
-indicating the decisions that are repatedly encountered in a single operational cycle.
-The flowchart also contains the loop back to system startup that starts a new operational cycle.
-
-We assume that both preventive and corrective maintenance result in an (as good as) new system state by replacing all components,
-such that the system begins a new operational cycle always under the same conditions.
-Replacement schemes that do not replace all components would require to account for the different ages of components in the system
-at the start of a new cycle.
-While this is in principle possible in our approach,
-exploring such selective replacement schemes is out of scope for this paper,
-since optimizing over replacement schemes is, in our view, a higly interesting topic
-that merits an investigation of its own,
-and we will comment on this in the conclusion (Section~\ref{sec:outlook}).
 %
@@
 we use the one-cycle cost rate as it is the most appropriate for our situation,
-where $\tausnow$ changes continuously.
+where $\tausnow$ changes frequently.
 

### 2017-05-11 cbm-rbd-paper.tex
rest of sec 5 rewritten (now need to check for reviewer comments regarding sec 5)

@@
 
-Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate is 
+Conditional on the realization $\tsysnow$ of $\Tsysnow$, the unit cost rate 
+for planning maintenance at $\tau$ time units after $\tnow$ is 
 \begin{align}
@@
 $\tausnow := \arg\min \gnow(\tau)$
-is the cost-optimal time to maintenance as of $\tnow$,
+is the cost-optimal time to do maintenance as of $\tnow$,
 incorporating all that is known at current time $\tnow$.
@@
 thus is, as of $\tnow$, the lowest cost rate for the current operational cycle
-that we can expected to attain.
+that we can expect to attain.
 %attainable for the span of the remaining lifetime of the system,
@@
 The size of the jump depends on the relevance of the failed component for the current system reliability.
-Common cause failures, i.e., failures of several components at the same time due to a shared root cause,
+
+Note that common cause failures, i.e., failures of several components at the same time due to a shared root cause,
 are currently not accounted for in our model. %, as we assume component failures to be mutually independent
@@
 assuming the failure history $P_2 = 3$, $P_3 = 4$, $C_2 = 6$, $C_3 = 7$, $H = 8$,
-and $c_u = 1$, $c_p = 0.2$.}
+and costs $c_u = 1$, $c_p = 0.2$.}
 \label{fig:tauhist1fig2T}
@@
 
-We have implememted our method in \textsf{R} \citep{R},
+We have implemented our method in \textsf{R} \citep{R},
 using the package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}

### 2017-05-12 answer-to-reviewers.tex
some tweaks reacting to reviewers comments

@@
 and to explain the details of its calculation later.
-We rewrote the entire section as requested, and hope that also this is now more clear.***}
+In rewriting Section~5, we now mention this more explicitely.}
 
@@
 For a practical application, one should indeed update the shape parameter as well,
-but in our view, adding this simple but notationally cumbersome feature would obstruct the goal of this manuscript.***}
+but in our view, adding this conceptually simple but notationally cumbersome feature would obstruct the goal of this manuscript.***}
 
@@
 
-\emph{***depends on the scale of failure times? seconds / minutes? ??? not sure what is meant by the second sentence.}
+\emph{We have completely rewritten Section~5 and now address the role of $\delta$ in more detail there, as well as in the Introduction.
+***not sure what is meant by the second sentence.}
 

### 2017-05-12 cbm-rbd-paper.tex
some tweaks reacting to reviewers comments

@@
 In both cases, we decide to maintain the system preventively
-when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate $\tausnow$,
+when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate the system RLD, %$\tausnow$,
 since otherwise, in waiting to the next planned evaluation time,
 one would exceed the optimal system failure risk 
-as determined by the trade-off made via $\gnow(\cdot)$.
+as determined by the trade-off made via $\gnow(\cdot)$. ***drop $\gnow(\cdot)$ here, like: ...trade-off that results in $\tausnow$.
 When $\tausnow$ is instead further in the future than the next planned evaluation time,

### 2017-05-12 answer-to-reviewers.tex
forgot to save

@@
 
-\emph{***Indeed, after a certain time the parameter $y_k$ (the expected value of the Weibull scale parameter $\lambda_k$)
-will not change by much during the update in Equation (7).
+\emph{***Indeed, due to the weigthed average update in Equation (7),
+it is possible that the parameter $y_k$ (the expected value of the Weibull scale parameter $\lambda_k$)
+will not change by much once it has approached the 'true' value.
 However, the strength parameter $n_k$ will continue to increase,

### 2017-05-12 answer-to-reviewers.tex
further tweaks, and discussions in the conclusion

@@
 Furthermore, the \textsf{R} package \texttt{ReliabilityTheory} allows to automatically calculate the
-survival signature from any given system graph.\\
+survival signature from any given system graph.}
 %no one component can be singled out as the reliability-limiting force.\\
-***add a note on simplicity (to understand what's going on) at example intro in Section~3?***}
+%***add a note on simplicity (to understand what's going on) at example intro in Section~3?***}
 \end{enumerate}
@@
 
-\emph{***This conflicts with our approach that evaluates the RLD and $\tausnow$ also at the exact times of component failures!***\\
-maybe something like
-$\big\{ t_j: (t_j = m\delta, m \in \naturals_0) \cup (t_j = t_{k,i}, k \in \{1,\ldots,K\}, i \in \{1,\ldots, N_k\}) \big\}$ ???
-But this is also quite complex!***}
+\emph{***Our approach evaluates the RLD and $\tausnow$ not only at a regular grid,
+but also at the exact times of component failures.
+The reviewer's suggestion would thus have us describe the set of re-evaluation times as
+$\big\{ t_j: (t_j = m\delta, m \in \naturals_0) \cup (t_j = t_{k,i}, k \in \{1,\ldots,K\}, i \in \{1,\ldots, N_k\}) \big\}$.
+We think this adds unneccessary complexity at the early parts of the manuscript,
+and thus prefer to keep $\tnow$ as a generic evaluation point.}
 
@@
 
-\emph{***unclear which claim exactly he refers to, maybe to
+\emph{***unclear which claim exactly the reviewer refers to, maybe to
 ``Close to system startup, $\tausnow$ will be large;
 but as components in the system age and some indeed fail over time, $\tausnow$ will typically decrease.'' ???
-It will be hard to prove this formally, as $\tausnow$ is a result of an optimization over the re-estimated RLD.
-But informally, this is clear: when a component fails, this is taken up by the RLD calculation,
-such the probability mass of the RLD is moving closer to $\tnow$,
-which leads to $\tausnow$ being closer to $\tnow$ as well.***}
+In the rewrite of Section~5, this sentence was dropped.}
+%(It will be hard to prove this formally, as $\tausnow$ is a result of an optimization over the re-estimated RLD.
+%But informally, this is clear: when a component fails, this is taken up by the RLD calculation,
+%such the probability mass of the RLD is moving closer to $\tnow$,
+%which leads to $\tausnow$ being closer to $\tnow$ as well.)***}
 
@@
 
-\emph{***Hmmm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
-I could change the simulations to execute repair at time $\tnow + \tausnow$,
-but then one needs to check whether there is a component failure (and with it, a system failure)
-between time $\tnow$ and $\tnow + \tausnow$, making the policy flow chart even more complex.
-If we keep it as it is, we need to explain $\delta$ better as being very small such that repair at $\tnow$ or $\tnow + \tausnow$
-do not make a big difference and that without $\delta$, we get a situation like in the paradox of Achilles and the tortoise.}
+\emph{***Our reasoning, now better explained in the Introduction and in the rewritten Section~5,
+is that $\delta$ gives the time granularity according to which maintenance actions can be reasonably triggered,
+and preventive maintenance is initiated only when $\tausnow < \delta$.
+Therefore, initiating maintenance at $\tnow$ or $\tnow + \tausnow$ is practically equivalent.***}
+%Hmmm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
+%I could change the simulations to execute repair at time $\tnow + \tausnow$,
+%but then one needs to check whether there is a component failure (and with it, a system failure)
+%between time $\tnow$ and $\tnow + \tausnow$, making the policy flow chart even more complex.
+%If we keep it as it is, we need to explain $\delta$ better as being very small such that repair at $\tnow$ or $\tnow + \tausnow$
+%do not make a big difference and that without $\delta$, we get a situation like in the paradox of Achilles and the tortoise.}
 
@@
 and to explain the details of its calculation later.
-In rewriting Section~5, we now mention this more explicitely.}
+In the rewritten Section~5, we now mention this more explicitely.}
 

### 2017-05-12 cbm-rbd-paper.tex
further tweaks, and discussions in the conclusion

@@
 %leading to censored observation of certain component lifetimes within the system.
+***Our example system is deliberately kept quite simple for didactical reasons.
+The survival signature allows to analyze much larger systems ***citations***,
+and our approach is able to deal with such systems.***
 
@@
 with conjugate priors to express expert knowledge.
-The resulting policy shows promising results in
+The resulting policy shows promising results for
 different numerical examples and a small simulation study.
@@
 There are several aspects in our modelling that warrant further investigation.
-So far, we assume that component failure times are observed precisely via monitoring.
+In this paper, we assume that component failure times are observed precisely via monitoring.
 However, in many applications, the component status can only be determined
@@
 
-***estimate and update also Weibull shape parameter***
+***Another way to relax the assumption of precise component monitoring
+is to consider unreliable detection of component failures.
+Our approach may be quite sensitive to the non-detection of component failures,
+and one could tackle this by including a probabilistic observation model,
+which assigns probabilities to false positives and false negatives in the component monitoring.***
+
+***We also assume that the component-specific Weibull shape parameters are known,
+and update only the scale parameters.
+We restricted ourselves to this simplistic modelling
+to allow for a clear and straight-forward demonstration of the general approach.
+In a practical application, the shape parameters should be jointly updated together with the scale parameters.
+This could be implemented by adopting the discretized approach by \cite{1969:soland}.***
 
@@
 i.e., simultaneous failures with a shared root cause.
-Common cause failures seriously reduce the system reliability,
-and can lead to sudden system failures.
+Common cause failures can drastically reduce the system reliability
+by leading to sudden system failures.
 To offer a realistic estimation of the optimal time to maintenance $\tausnow$,
@@
 
-In our policy, we assumed that in both preventive and corrective repair
+In our policy, we assumed that in both preventive and corrective replacement
 all components are restored to an as good as new state.
@@
 but would this offer any advantage?
-Furthermore, could it be even optimal to repair a subset of the failed components only?
+Furthermore, could it be even optimal to replace a subset of the failed components only?
 Such selective component replacement schemes
@@
 
-***different cost structures, let repair costs depend on number of failed components?***
-
-***non-detection of component failures***
+***A further simplifying assumption relates to the cost of preventive and corrective replacements,
+which we consider as fixed.
+In many real-life applications, maintenance costs vary over time
+(e.g., increased labour cost due to overtime or night shift premiums),
+and may depend on the number of failed components, or even on the exact system state.
+In our approach, time-dependent cost structures can be easily accounted for,
+by letting $c_p$ and $c_c$ in \eqref{eq:gtau} depend on $\tau$.
+It will be more complex to account for costs that are dependent on the system state,
+but our approach already provides the necessary information
+in form of the posterior predictive distributions derived in Section~\ref{sec:postpred}.***
+%since the calculation of $\Rsysnow(t)$ involves
 

### 2017-05-25 answer-to-reviewers.tex
SDFs comments part 1

@@
 and for such a system, indeed a simpler methodology like the keystone method can very well suffice.
-However, our survival signature based method is also applicable for larger systems ***with hundreds or thousands of components,
-where the keystone method is usually not practical anymore.***\\
-***find surv sign papers with complex systems and add citations***
+However, our survival signature based method is also applicable for much larger systems with complex structures,
+for which the keystone method is not practical anymore,
+see, e.g., \citet[Table~2]{2017:reed}.
 Furthermore, the \textsf{R} package \texttt{ReliabilityTheory} allows to automatically calculate the

### 2017-05-25 cbm-rbd-paper.tex
SDFs comments part 1

@@
 The unit cost rate is recalculated when components fail
-or at the end of every (very short) fixed inter-inspection interval***,
+or at the end of every (very short) fixed inter-monitoring*** interval,
 leading to a dynamic maintenance policy,
@@
 i.e., just before they fail, %but not too early,
-in order to keep their reliability high and operating costs low.
+in order to keep their reliability high and operating costs low,
+using information about the actual condition of the systems or components.
 In this context a trade-off is made between the risk of failure during operation
@@
 
-In this paper, we propose a new kind of inspection-based CBM policy*** (drop inspection-based???***)
+In this paper, we propose a new kind of CBM policy
 for when no such \emph{usual} degradation signal for the system is available,
@@
 because the re-evaluation of the system RLD does not require a physical inspection,
-as we assume to learn of the exact failure times of components online via continuous monitoring.
+as we assume to learn of the exact failure times of components online via (quasi-) continuous monitoring.
 
@@
 the currently used models for component failure times are updated
-to account for the aging of components,
-and the extra lifetime observed for the components.
-The latter information is taken into account via right-censored observations
+to account for the extra lifetime observed for the components.
+This information is taken into account via right-censored observations
 in a Bayesian parameter update step.
@@
 based on minimizing the expected maintenance-related cost per per unit of time for the present operational cycle,
-where an operational cycle starts with a new system, and ends after this system has been replaced by an as good as new system.
+where an operational cycle starts with a new system, and ends after this system has been replaced by a new system.
 
@@
 %the shortest inter-observation period that can be realized from a hardware point of view.
-the shortest inter-evaluation period that can be realized from a hardware point of view*** / 
-the time granularity according to which maintenance actions can be reasonably triggered***.
-To illustrate, for components with lifetimes measuring in a few days,
+the shortest inter-evaluation period that can be realized from a hardware point of view. 
+%the time granularity according to which maintenance actions can be reasonably triggered***.
+To illustrate, for components with lifetimes amounting to a few days,
 $\delta$ could be in the order of minutes;
@@
 However, because $\delta$ is very small when compared to the prior estimates of the lifetime of the components,
-at the time that the next `optimal' observation moment is before the next observation of the status of the still active components,
+at the time that the next `optimal' evaluation moment is before the next planned evaluation moment,
 we usually already have done much better than without updating as described in this paper.
@@
 inherent to using updated information for decisions,
-when these updates can indicate that the former estimates were too optimistic or pessimistic.
+when these updates can indicate that the former estimates were too optimistic or too pessimistic.
 The reason for this is that for some components,
@@
 is uncertain at every moment in time.
-(***As a sidenote,
-this kind of uncertainty about the probabilistic behaviour itself is very often neglected in operations research literature.***)
+As a sidenote,
+this kind of uncertainty about the probabilistic behaviour itself is very often neglected in operations research literature.
 Determining the next `optimal' evaluation moment can thus only indicate whether or not waiting with the replacement
@@
 
-***While we also use a Bayesian approach to provide exact expressions for the RLD,***
+While we also use a Bayesian approach with conjugate priors to provide exact expressions for the RLD,
 one of the main differences between \citet{2013:si-et-al} and our paper
@@
 where there are $N_k$ exchangeable components of type $k$ in the system,
-and the total number of components in the system is $\sum_{k=1}^K N_k = N$.
+and $N$, the total number of components in the system, is given by $\sum_{k=1}^K N_k = N$.
 
@@
 which in turn actuate a braking pad assembly each ($P_1$ -- $P_4$).
-The hand brake mechanism ($H$) directly actuates the brake pad assemblies $P_3$ and $P_4$;
-the vehicle brakes when at least one brake pad assembly is actuated.
+The hand brake mechanism ($H$) directly actuates the brake pad assemblies $P_3$ and $P_4$,
+and the vehicle brakes when at least one brake pad assembly is actuated.
 Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
@@
 %leading to censored observation of certain component lifetimes within the system.
-***Our example system is deliberately kept quite simple for didactical reasons.
-The survival signature allows to analyze much larger systems ***citations***,
-and our approach is able to deal with such systems.***
+Our example system is deliberately kept quite simple for didactical reasons.
+The survival signature allows to analyze much larger systems,
+see, e.g., the examples in \citet{2017:reed},
+and our approach is able to deal with such systems.
 
@@
 In this section, we describe how the system reliability function $\Rsysnow(t)$ at current time $\tnow$ 
-can be calculated for a specific choice of component model.
+can be calculated for a specific component model.
 %Section~\ref{sec:policy} will then show how an adaptive maintenance policy
@@
 our component model allows to include both expert assessments and test data (if available),
-and furthermore can account for component lifetime information from the current operational cycle up to $\tnow$.
+and furthermore can account for component lifetime information from previous operational cycles
+and the current operational cycle up to $\tnow$.
 %***component model: weibull with fixed shape,
@@
 for the Weibull component model as needed for the current system reliability calculation.
-Finally, in Section~\ref{sec:sysreltnow}, we adapt the method from Section~\ref{sec:sysrel} for the adaptive setting,
+Finally, in Section~\ref{sec:sysreltnow}, we adapt the method from Section~\ref{sec:sysrel} to the dynamic setting,
 resulting in a formula for $\Rsysnow(t)$.
@@
 we can use the method from Section~\ref{sec:sysrel}
-to determine the system residual life distribution (RLD) $\Rsysnow(t)$,
+to determine the dynamic system residual life distribution (RLD) $\Rsysnow(t)$,
 giving us the probability that the system functions at times $t > \tnow$,
@@
 and then illustrated along two examplary timelines in Section~\ref{sec:policy-example}.
-Afterwards, we introduce the formal definition of the policy in Section~\ref{sec:operationalprocedure}***,
-and give further details on the involved computations in Sections~\ref{sec:costrate} and \ref{sec:optim}.***
+Afterwards, we give a detailed description of the policy in Section~\ref{sec:operationalprocedure},
+and expand on the involved computations in Sections~\ref{sec:costrate} and \ref{sec:optim}.
 
@@
 
-The near*** optimal time to system re-evaluation $\tausnow$ is determined based on $\Rsysnow(t)$
+The optimal time to system re-evaluation $\tausnow$ is determined based on $\Rsysnow(t)$
 by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
@@
 starting each with a new system (operational cycle) at $t=0$.
-The left timeline leads to preventive maintenance,
+The timeline on the left leads to preventive maintenance,
 the timeline on the right to corrective maintenance.
@@
 the health of the system is re-evaluated at three types of triggers.
-Triggers of type (1) are the evenly spaced planned evaluation time points $m\delta$, where $m \in \naturals_0$,
-giving the time granularity at which maintenance actions can be reasonably initiated.***
+Triggers of type (1) are the evenly spaced planned evaluation time points $m\delta$, where $m \in \naturals_0$.
+%giving the time granularity at which maintenance actions can be reasonably initiated.***
 %Let $\tthresh$ be a threshold time span chosen for practical reasons.

### 2017-05-25 cbm-rbd-paper.tex
SDFs comments part 2

@@
 
+\subsection{Two exemplary timelines}
+\label{sec:policy-example}
+
+Figure~\ref{fig:timeline} shows two examplary time lines,
+starting each with a new system (operational cycle) at $t=0$.
+The timeline on the left leads to preventive maintenance,
+the timeline on the right to corrective maintenance.
+
+As described in Section~\ref{intro},
+the health of the system is re-evaluated at three types of triggers.
+Triggers of type (1) are the evenly spaced planned evaluation time points $m\delta$, where $m \in \naturals_0$.
+%giving the time granularity at which maintenance actions can be reasonably initiated.***
+%Let $\tthresh$ be a threshold time span chosen for practical reasons.
+%used to decide when maintenance is initiated, i.e.,
+%a time span chosen to reflect operational practicalities.
+The times $m\delta$ are indicated by vertical tick lines on the time axis in Figure~\ref{fig:timeline},
+where $\delta = 0.1$.
+The moments of failure of a component form the other two types of triggers.
+A component failure after which the system still functions is a trigger of type (2),
+depicted as a (non-filled) circle on the time axis.
+A filled circle indicates a trigger of type (3),
+which is a component failure that causes the whole system to fail.
+
+For each trigger of type (1) and (2),
+the system health is evaluated by calculating $\tausnow$,
+the currently optimal time to re-evaluation, %$\tausnow$ is %calculated,
+visualized by the thick horizontal bars in Figure~\ref{fig:timeline}.
+%The details of calculating $\tausnow$ are described in detail in Sections~\ref{sec:costrate} and \ref{sec:optim}.***
+For a type (3) trigger, the system health evaluation just corresponds to acknowledging that the system has failed.
+%/ to the diagnosis/insight*** of system failure.
+%and calculation of $\tausnow$ is 
+For triggers of type (1) and (2),
+the calculated $\tausnow$ is compared to the time to the next planned evaluation time point.
+When $\tausnow$ is shorter than this time,
+preventive maintenance of the system is initiated.
+
+In the timeline on the left of Figure~\ref{fig:timeline},
+$\tausnow$ is re-evaluated at times $\tnow = 0.1, 0.2, 0.24, 0.3, 0.36, 0.4$,
+where $0.24$ and $0.36$ correspond to component failure times.
+Note that the failure at $\tnow = 0.24$ substantially shortens $\tausfun{0.24}$,
+such that $0.24 + \tausfun{0.24} < 0.2 + \tausfun{0.2}$,
+i.e., the optimal moment of re-evaluation has moved backwards in time.
+This illustrates that new insights drawn from a component failure
+(regarding the reliability block diagram as well as the component model)
+may have considerable influence on the system RLD
+and the $\tausnow$ that is derived from it.
+The component failure at $\tnow = 0.36$ leads to a further shortened $\tausfun{0.36}$,
+such that $\tausfun{0.36} < 0.1 = \delta$.
+However, this does not lead to an immediate decision for preventive maintenance,
+since $\tausfun{0.36}$ is compared to the time to the next planned evaluation at $t = 0.4$.
+The decision for preventive maintenance is instead made at $\tnow = 0.4$,
+as only then it is not economical any more to wait for the next planned evaluation at $t = 0.5$.
+
 \begin{figure}
@@
 
-\subsection{Two exemplary timelines}
-\label{sec:policy-example}
-
-Figure~\ref{fig:timeline} shows two examplary time lines,
-starting each with a new system (operational cycle) at $t=0$.
-The timeline on the left leads to preventive maintenance,
-the timeline on the right to corrective maintenance.
-
-As described in Section~\ref{intro},
-the health of the system is re-evaluated at three types of triggers.
-Triggers of type (1) are the evenly spaced planned evaluation time points $m\delta$, where $m \in \naturals_0$.
-%giving the time granularity at which maintenance actions can be reasonably initiated.***
-%Let $\tthresh$ be a threshold time span chosen for practical reasons.
-%used to decide when maintenance is initiated, i.e.,
-%a time span chosen to reflect operational practicalities.
-The times $m\delta$ are indicated by vertical tick lines on the time axis in Figure~\ref{fig:timeline},
-where $\delta = 0.1$.
-The moments of failure of a component form the other two types of triggers.
-A component failure after which the system still functions is a trigger of type (2),
-depicted as a (non-filled) circle on the time axis.
-A filled circle indicates a trigger of type (3),
-which is a component failure that causes the whole system to fail.
-
-For each trigger of type (1) and (2),
-the system health is evaluated by calculating $\tausnow$,
-the currently optimal time to re-evaluation, %$\tausnow$ is %calculated,
-visualized by the thick horizontal bars in Figure~\ref{fig:timeline}.
-%The details of calculating $\tausnow$ are described in detail in Sections~\ref{sec:costrate} and \ref{sec:optim}.***
-For a type (3) trigger, the system health evaluation just corresponds to acknowledging that the system has failed.
-%/ to the diagnosis/insight*** of system failure.
-%and calculation of $\tausnow$ is 
-For triggers of type (1) and (2),
-the calculated $\tausnow$ is compared to the time to the next planned evaluation time point.
-When $\tausnow$ is shorter than this time,
-preventive maintenance of the system is initiated.
-
-In the timeline on the left of Figure~\ref{fig:timeline},
-$\tausnow$ is re-evaluated at times $\tnow = 0.1, 0.2, 0.24, 0.3, 0.36, 0.4$,
-where $0.24$ and $0.36$ correspond to component failure times.
-Note that the failure at $\tnow = 0.24$ substantially shortens $\tausfun{0.24}$,
-such that $0.24 + \tausfun{0.24} < 0.2 + \tausfun{0.2}$,
-i.e., the optimal moment of re-evaluation has moved backwards in time.
-This illustrates that new insights drawn from a component failure
-(regarding the reliability block diagram as well as the component model)
-may have considerable influence on the system RLD
-and the $\tausnow$ that is derived from it.
-The component failure at $\tnow = 0.36$ leads to a further shortened $\tausfun{0.36}$,
-such that $\tausfun{0.36} < 0.1 = \delta$.
-However, this does not lead to an immediate decision for preventive maintenance,
-since $\tausfun{0.36}$ is compared to the time to the next planned evaluation at $t = 0.4$.
-The decision for preventive maintenance is instead made at $\tnow = 0.4$,
-as only then it is not economical any more to wait for the next planned evaluation at $t = 0.5$.
-
 The timeline on the right of Figure~\ref{fig:timeline} illustrates an operational cycle ending with corrective maintenance.
@@
 The size of $\tausfun{0.2}$ indicates that the component failure that happens at $\tnow = 0.27$
-had been deemed very unlikely at time $\tnow = 0.2$.
+had been deemed very unlikely at time $\tnow = 0.2$,
 but then nevertheless occured at $t = 0.27$.
 
-\subsection{Formal*** / Detailed description of the policy}
+\subsection{Detailed description of the policy}
 \label{sec:operationalprocedure}
@@
 or the system fails, which triggers a corrective maintenance action.
-
-***below two pars towards the end?
 
@@
 e.g., due to a very high fixed set-up cost independent of the maintenance activities to be done,
-as is the case of installations/facilities*** used in the generation and distribution of oil and gas.
-Note that often for safety reasons, the latter installations/facilities*** are monitored continuously.
+as is the case of installations used in the generation and distribution of oil and gas.
+Note that often for safety reasons, the latter installations are monitored continuously.
 There may be also technical dependencies between parts of a system that may require combined replacement:
@@
 Another reason can be that there may be a high probability that when individual parts are replaced,
-other parts will be damaged/have to be damaged***, requiring their replacement as well.
+other parts will be damaged, requiring their replacement as well.
 
@@
 We will return to this in the conclusion (Section~\ref{sec:outlook}).
+
+Figure~\ref{fig:procedure} depicts the flow chart for the policy,
+indicating the decisions that are repeatedly encountered in a single operational cycle.
+The flow chart also contains the loop back to the start of a new operational cycle.
+
+%***Consider a set of evaluation time points $\tnow$.
+Consider a grid of planned evaluation time points $\{m \delta : m \in \naturals_0\}$,
+%where $m = 0, 1, 2, \ldots$,
+%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
+with $\delta$ a sufficiently small time increment.
+During an operational cycle,
+$\tausnow$ is usually recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
+%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
+However, if a component $i$ of type $k$ fails before the next $\tnow$ on the grid,
+$\tnow$ is set instead to the exact failure time $t_{k,i}$.
+Next, we check whether the system has failed due to this component failure.
+If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
+If the system has not failed, we calculate $\tausnow$ for the current off-grid time $\tnow = t_{k,i}$,
+and move back onto the grid afterwards,
+unless there is another component failure before the next planned evaluation time.
+
+The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
+of the maintenance interval in an age based policy by trading off the costs of preventive and corrective maintenance
+(see Section~\ref{sec:costrate} below).
+However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
+our policy is adaptive and dynamic like a CBM policy. 
+When computation of the RLD is fast,
+frequent recalculation of $\tausnow$ is feasible,
+%Then, by evaluating the unit cost rate function $\gnow(\tau)$ (see Section~\ref{sec:costrate} below) on a discrete grid,
+%$\tausnow$ can be approximated with a simple grid search.
+%because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
+%and determine $\tausnow$ with a simple grid search.
+%Updating $\tausnow$ frequently is useful because,
+and it is useful because,
+even in absence of failures of system components,
+all components age, and also non-failure adds information to the component models,
+reducing uncertainty.
+%Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
+%as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T},
+%which gives a numerical example described in more detail in Section~\ref{sec:examples}.
+%An alternative would be to update $\tausnow$ only when a component fails,
+%but as a (near) real-time update of $\tausnow$ is possible and useful,
+%as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
+%
+%As can happen for an age-based policy, the derived $\gnow(\tau)$ may also be monotonely decreasing.
+%In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
+%This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
+%but also capable of indicating when corrective maintenance is the better option.
+%i.e., capable of choosing the maintenance policy.
+
+Once $\tausnow$ is calculated, it is compared to the time span from the current $\tnow$ to the next planned evaluation time.
+If the current $\tnow$ is a time on the grid, then $\tnow = m \delta$ for some $m \in \naturals_0$.
+The next planned evaluation is then at $(m + 1) \delta$,
+and we compare $\tausnow$ to $\delta$.
+If $\tausnow < \delta$, a preventive maintenance action is triggered, incurring cost $c_p$,
+otherwise we attempt to move to the next planned evaluation point, by setting $m =  (m + 1)$.
+
+If the current $\tnow$ is instead an off-grid time corresponding to failure of component $i$ of type $k$ at time $t_{k,i}$,
+after which the system still functions,
+then the next planned evaluation time is the next time on the grid.
+Let $m$ be such that $m \delta < t_{k,i} < (m + 1) \delta$,
+so the next time on the grid is $(m + 1) \delta$,
+and we compare $\tausnow$ with $(m + 1) \delta - t_{k,i}$.
+If $\tausnow < (m + 1) \delta - t_{k,i}$, a preventive maintenance action is triggered, incurring cost $c_p$,
+otherwise we attempt to move to the next planned evaluation point, which is still $(m + 1) \delta$.
+
+In both cases, we decide to maintain the system preventively
+when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate the system RLD, %$\tausnow$,
+since otherwise, in waiting to the next planned evaluation time,
+one would exceed the optimal system failure risk 
+as determined by the trade-off made via $\gnow(\cdot)$. %***drop $\gnow(\cdot)$ here, like: ...trade-off that results in $\tausnow$.
+When $\tausnow$ is instead further in the future than the next planned evaluation time,
+we can safely continue to the next planned evaluation time,
+without risking to miss the cost-optimal moment to preventively maintain the system.
 
@@
 \draw[pfeil] (tausdel) -| (mincrem) node[at start, above left] {no};
-\draw[very thick] (taudtki) -| (nocoord) node[near start, above] {no} -| (mincrem);
+\draw[pfeil] (taudtki) -| (nocoord) node[near start, above] {no} -- ($(mincrem) + (0,7mm)$); %($(0,1cm)*(nocoord) + (1cm,0)*(mincrem)$); %
 \draw[pfeil] (taudtki) -- (prevmnt) node[midway, above] {yes};
@@
 
-Figure~\ref{fig:procedure} depicts the flow chart for the policy,
-indicating the decisions that are repeatedly encountered in a single operational cycle.
-The flow chart also contains the loop back to the start of a new operational cycle.
-
-%***Consider a set of evaluation time points $\tnow$.
-Consider a grid of planned evaluation time points $\{m \delta : m \in \naturals_0\}$,
-%where $m = 0, 1, 2, \ldots$,
-%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
-with $\delta$ a sufficiently small time increment.
-During an operational cycle,
-$\tausnow$ is usually recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
-%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
-However, if a component fails before the next $\tnow$ on the grid,
-$\tnow$ is set instead to the exact failure time $t_{k,i}$.
-Next, we check whether the system has failed due to this component failure.
-If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
-If the system has not failed, we calculate $\tausnow$ for the current off-grid time $\tnow = t_{k,i}$,
-and move back onto the grid afterwards,
-unless there is another component failure before the next planned evaluation time.
-
-The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
-of the maintenance interval in an age based policy by trading off the costs of preventive and corrective maintenance
-(see Section~\ref{sec:costrate} below).
-However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
-our policy is adaptive and dynamic like a CBM policy. 
-When computation of the RLD is fast,
-frequent recalculation of $\tausnow$ is feasible,
-%Then, by evaluating the unit cost rate function $\gnow(\tau)$ (see Section~\ref{sec:costrate} below) on a discrete grid,
-%$\tausnow$ can be approximated with a simple grid search.
-%because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
-%and determine $\tausnow$ with a simple grid search.
-%Updating $\tausnow$ frequently is useful because,
-and it is useful because,
-even in absence of failures of system components,
-all components age, and also non-failure adds information to the component models,
-reducing uncertainty.
-%Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
-%as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T},
-%which gives a numerical example described in more detail in Section~\ref{sec:examples}.
-%An alternative would be to update $\tausnow$ only when a component fails,
-%but as a (near) real-time update of $\tausnow$ is possible and useful,
-%as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
-%
-%As can happen for an age-based policy, the derived $\gnow(\tau)$ may also be monotonely decreasing.
-%In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
-%This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
-%but also capable of indicating when corrective maintenance is the better option.
-%i.e., capable of choosing the maintenance policy.
-
-Once $\tausnow$ is calculated, it is compared to the time span from the current $\tnow$ to the next planned evaluation time.
-If the current $\tnow$ is a time on the grid, then $\tnow = m \delta$ for some $m \in \naturals_0$.
-The next planned evaluation is then at $(m + 1) \delta$,
-and we compare $\tausnow$ to $\delta$.
-If $\tausnow < \delta$, a preventive maintenance action is triggered, incurring cost $c_p$,
-otherwise we attempt to move to the next planned evaluation point, by setting $m =  (m + 1)$.
-
-If the current $\tnow$ is instead an off-grid time corresponding to a component failure time $t_{k,i}$,
-then the next planned evaluation time is the next time on the grid.
-Let $m$ be such that $m \delta < t_{k,i} < (m + 1) \delta$,
-so the next time on the grid is $(m + 1) \delta$,
-and we compare $\tausnow$ with $(m + 1) \delta - t_{k,i}$.
-If $\tausnow < (m + 1) \delta - t_{k,i}$, a preventive maintenance action is triggered, incurring cost $c_p$,
-otherwise we attempt to move to the next planned evaluation point, which is still $(m + 1) \delta$.
-
-In both cases, we decide to maintain the system preventively
-when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate the system RLD, %$\tausnow$,
-since otherwise, in waiting to the next planned evaluation time,
-one would exceed the optimal system failure risk 
-as determined by the trade-off made via $\gnow(\cdot)$. ***drop $\gnow(\cdot)$ here, like: ...trade-off that results in $\tausnow$.
-When $\tausnow$ is instead further in the future than the next planned evaluation time,
-we can safely continue to the next planned evaluation time,
-without risking to miss the cost-optimal moment to preventively maintain the system.
-
 At the end of each operational cycle, i.e.,
@@
 as the unit cost rate.
-Although a different, renewal theory based way to calculate the unit cost rate is often used
-in CBM literature \citep[e.g.,][]{2013:si-et-al,2011:kim-et-al},
-%As we discussed in the Introduction,
-we use the one-cycle cost rate as it is the most appropriate for our situation,
-where $\tausnow$ changes frequently.
+As discussed in the literature review (Section~\ref{sec:literature}),
+we cannot use the renewal theory based way to calculate the unit cost rate as often encountered
+in CBM literature \citep[e.g.,][]{2013:si-et-al,2011:kim-et-al}.
+%we use the one-cycle cost rate as it is the most appropriate for our situation,
+%where $\tausnow$ changes frequently.
 
@@
 \end{align}
-Note that here, $\tau$ is a time span starting from $\tnow$,
+Note that here $\tau$ is a time span starting from $\tnow$,
 and so is a time on a prospective time scale, where $0$ corresponds to $\tnow$.
 In contrast, $\tnow$ and $\tsysnow$ are times on an absolute time scale,
-where $0$ corresponds to the time of system start-up.
+where $0$ corresponds to the time of a new system start-up.
 Taking the expectation over $\Tsysnow$ in \eqref{eq:gtau} leads to the expected operational cycle cost rate
@@
 with discrete jumps at component failure times.
-The size of the jump depends on the relevance of the failed component for the current system reliability.
+The size of the jump depends on the relevance of the failed component
+for the reliability of the system at the moment that the component failure occurs.
 
@@
 %given the component model parameters.
-Such simulatenous failures will seriously influence the RLD and thus $\tausnow$.
+Such simultaneous failures will seriously influence the RLD and thus $\tausnow$.
 We will return to this in the conclusion (Section~\ref{sec:outlook}).
@@
 using the package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
-to calculate survival signatures.
+to calculate survival signatures
+(code available on request).
 As the parameter update step is closed-form,
-recalculation of $\tausnow$ is a matter of one or two seconds,
+recalculation of $\tausnow$ is a matter of seconds,
 allowing for a near real-time update.

### 2017-05-26 cbm-rbd-paper.tex
SDFs comments part 3

@@
 
-We now explain in more detail the case study used for the previous illustrative figures.
+We now explain in more detail the case study used for the previous illustrative figures
+(Figures~\ref{fig:ghist1fig2T} and \ref{fig:tauhist1fig2T}).
 We use the simplified automotive brake system as introduced in Section~\ref{sec:sysrel},
@@
 %This is because the adaptive algorithm recognizes that system components are more reliable than expected,
-leading to lower expected operational cycle cost rates $\gstarnow$ (right panel).
+leading to higher expected operational cycle cost rates $\gstarnow$ (right panel).
 $\tausnow$ for the policy without parameter update drops below $\delta = 0.1$ at $\tnow = 4$,
@@
 
-Here, both corrective and age-based policies cannot avoid system failures entirely.
-The condition-based policies result in two to three system failures in the $20 \times 5 = 100$ system runs,
-whereas the age-based policies result in nine to ten system failures.
+Here, most condition-based and all age-based policies cannot avoid system failures entirely.
+Both CBM-epu and CBM-npu result in one system failure in the $20 \times 5 = 100$ system runs,
+whereas the two age-based policies each result in ten system failures.
 System runtimes are less variable for the age-based policies
@@
 Again, CBM-cpu performs slightly better than CBM-epu
-as it has the possibility to learn within an operational cycle as well.
-CBM-npu does surprisingly well, considering that it never updates prior component parameters. 
+as it has the possibility to learn within an operational cycle as well,
+managing to avoid system failures entirely. 
+Still, CBM-npu does surprisingly well, considering that it never updates prior component parameters. 
 This confirms the observation from Section~\ref{sec:ex-3}
@@
 
-***Another way to relax the assumption of precise component monitoring
+Another way to relax the assumption of precise component monitoring
 is to consider unreliable detection of component failures.
@@
 and one could tackle this by including a probabilistic observation model,
-which assigns probabilities to false positives and false negatives in the component monitoring.***
-
-***We also assume that the component-specific Weibull shape parameters are known,
+which assigns probabilities to false positives and false negatives in the component monitoring.
+
+We also assume that the component-specific Weibull shape parameters are known,
 and update only the scale parameters.
@@
 In a practical application, the shape parameters should be jointly updated together with the scale parameters.
-This could be implemented by adopting the discretized approach by \cite{1969:soland}.***
+This could be implemented by adopting the discretized approach by \cite{1969:soland}.
 
@@
 
-***A further simplifying assumption relates to the cost of preventive and corrective replacements,
+A further simplifying assumption relates to the cost of preventive and corrective replacements,
 which we consider as fixed.
@@
 but our approach already provides the necessary information
-in form of the posterior predictive distributions derived in Section~\ref{sec:postpred}.***
+in form of the posterior predictive distributions derived in Section~\ref{sec:postpred}.
 %since the calculation of $\Rsysnow(t)$ involves
@@
 This approach is described in \cite{2016:walter-coolen},
-leading to sets of current residual life distributions $\Rsys(t)$.
-Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
+resulting in sets of residual life distributions $\Rsysnow(t)$,
+%Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
+and this would lead to sets of expected operational cycle cost rate functions $\gnow(\tau)$.
 The determination of the (set of) optimal time(s) to maintenance $\tausnow$

### 2017-05-26 answer-to-reviewers.tex
SDFs comments part 4

@@
 
-\emph{The other paper Reviewer 1 mentions here is:}
+\emph{The other paper Reviewer 1 refers to is:}
 
@@
 that our manuscript and the cited paper share the same basic approach, namely
-Weibull component models with conjugate inverse Gamma prior
+Weibull component models with conjugate inverse Gamma priors
 combined with a survival signature approach to calculate the system remaining life distribution (RLD).
@@
 in a similar way as in the cited paper,
-but with notation adapted to the manuscript's objective, i.e., defining a maintenance policy.
+but with notation adapted to the present manuscript's objective, i.e., defining a maintenance policy.
 For readers to be able to understand our approach,
@@
 This is exemplarily shown in the case study in Section~6, with more systematic evidence given in Section~7.
-In Section~6.2, the case of failures happening later than expected, i.e., a pessimistic prior is considered,
+Section~6.2 covers the case of failures happening later than expected, i.e., a pessimistic prior is considered,
 and the last paragraph before Section~6.3 (beginning with ``The effect of the continuous parameter update \ldots'')
 gives a detailed explanation.
-Section~6.3 studies a case with failure times earlier than expected, i.e., with too optimistic prior.
+Section~6.3 studies a case with failure times earlier than expected, i.e., with a too optimistic prior.
 Here, as described in the text, both the approach with and without continuous parameter update
@@
 which may lead to an excess risk of system failure.
-***This is confirmed in the simulation study in Section~7.2, Figure~11 (previously Figure~10),
+This is confirmed in the simulation study in Section~7.2, Figure~11 (previously Figure~10),
 where the continuous update approach (CBM-cpu) can be seen to lead to slightly lower mean cost rates
-than the approach without continuous parameter update (CBM-epu and CBM-npu).\\
-%
-***new simulation scenario to illustrate this!***\\
-%
-***Citing the last sentence of Section~7,
-``[o]verall, it seems that CBM-cpu can play ***exert?*** its adaptive strengths most effectively
+than the approach without continuous parameter update (CBM-epu and CBM-npu).
+Citing the last sentence of Section~7,
+``[o]verall, it seems that CBM-cpu can exert its adaptive strengths most effectively
 when prior assumptions are too pessimistic,
-while also performing well when prior assumptions are correct or too optimistic.''\\
-%
-***impossible to know beforehand if priors too optimistic or too pessimistic***}
-%
+while also performing well when prior assumptions are correct or too optimistic.''
+It is almost alway impossible to know beforehand if priors are too optimistic or too pessimistic.}
+
 \item For the example system, I think we can simply use the key stone method (use H as the key stone) to calculate the system reliability when the components are independent.
@@
 and for such a system, indeed a simpler methodology like the keystone method can very well suffice.
-However, our survival signature based method is also applicable for much larger systems with complex structures,
-for which the keystone method is not practical anymore,
-see, e.g., \citet[Table~2]{2017:reed}.
+However, our survival signature based method is also applicable to much larger systems with complex structures,
+for which the keystone method is not practical.
+We now emphasize this more explicitely,
+and refer to a recent paper on survival signature computations for large and complex systems (Reed 2017).
 Furthermore, the \textsf{R} package \texttt{ReliabilityTheory} allows to automatically calculate the
-survival signature from any given system graph.}
+survival signature from any given system graph,
+thus avoiding manual computations as necessary in the keystone method.}
 %no one component can be singled out as the reliability-limiting force.\\
@@
 
-\emph{***We rewrote Section~5 according to the reviewer's suggestions.***}
+\emph{Yes, we rewrote Section~5 according to the reviewer's suggestions,
+as detailed below in relation to the reviewer's technical and general comments.}
 
@@
 
-\subsection*{Technical comments}
+\subsection*{\emph{Technical comments}}
 
@@
 
-\emph{***Our approach evaluates the RLD and $\tausnow$ not only at a regular grid,
+\emph{Our approach evaluates the RLD and $\tausnow$ not only at a regular grid,
 but also at the exact times of component failures.
 The reviewer's suggestion would thus have us describe the set of re-evaluation times as
-$\big\{ t_j: (t_j = m\delta, m \in \naturals_0) \cup (t_j = t_{k,i}, k \in \{1,\ldots,K\}, i \in \{1,\ldots, N_k\}) \big\}$.
-We think this adds unneccessary complexity at the early parts of the manuscript,
-and thus prefer to keep $\tnow$ as a generic evaluation point.}
+$\big\{ t_j: (t_j = m\delta, m \in \naturals_0) \,\cup\, (t_j = t_{k,i}, k \in \{1,\ldots,K\}, i \in \{1,\ldots, N_k\}) \big\}$.
+We think this adds unnecessary complexity at the early parts of the manuscript,
+and thus prefer to denote $\tnow$ as a generic evaluation point.}
 
@@
 
-\emph{***unclear which claim exactly the reviewer refers to, maybe to
+\emph{We were not sure which claim exactly the reviewer refered to, maybe to
 ``Close to system startup, $\tausnow$ will be large;
-but as components in the system age and some indeed fail over time, $\tausnow$ will typically decrease.'' ???
+but as components in the system age and some indeed fail over time, $\tausnow$ will typically decrease.''
 In the rewrite of Section~5, this sentence was dropped.}
@@
 
-\emph{***Our reasoning, now better explained in the Introduction and in the rewritten Section~5,
-is that $\delta$ gives the time granularity according to which maintenance actions can be reasonably triggered,
+\emph{Our reasoning, now better explained in the Introduction and in the rewritten Section~5,
+is that $\delta$ gives the shortest inter-evaluation time period that can be realized from a hardware point of view,
 and preventive maintenance is initiated only when $\tausnow < \delta$.
-Therefore, initiating maintenance at $\tnow$ or $\tnow + \tausnow$ is practically equivalent.***}
+Therefore, initiating maintenance at $\tnow$ or $\tnow + \tausnow$ is practically equivalent.}
 %Hmmm, yes, currently we have that the system is repaired at $\tnow$ when $\tausnow < \delta$.
@@
 
-\emph{***Yes, we indeed assumed constant cost parameters in our manuscript.
-We now comment on this in the Section~8, where we now state that our model allows
-to let costs depend on time and on system state in the optimization step.
-***Such dependencies will lead to a more variable $\tausnow$***
-}
+\emph{Yes, we indeed assume constant cost parameters in our manuscript.
+We now comment on this in the Conclusion, where we now briefly explain how our model could be extended to allow
+for costs depending on time and on system state.
+Such dependencies will lead to a more variable $\tausnow$.}
 
@@
 
-\emph{***We agree that the simulation study in our submitted manuscript was rather small,
-and thus have extended the simulation to not only to 25 subsequent cycles,
-but also increased the number of repetitions from 20 to 100 for each policy and scenario.
-Furthermore, we added a fourth scenario to better illustrate the advantage of the policy
-using continuous parameter update.***}
+\emph{We agree that the simulation study in our submitted manuscript is rather small,
+but we think it is still sufficiently large to give general impressions on the performance of our method
+and to identify the factors contributing to its performance.}
+%Time restrictions (the first author is no longer employed at TU Eindhoven)
+%unfortunately prevented us from extending the simulation study.}
 
@@
 
-\emph{***We decided to use the simple example also in the simulation study ***to provide clear insights
-that could get lost with a more complex example.***
-Generally, more complex systems are possible, only extending computation times,
-and we comment on the scalability of our approach in Section***.}
+\emph{We decided to use the simple example also in the simulation study to provide clear insights
+that could get lost with a more complex example.
+Generally, more complex systems are possible, only increasing computation times,
+and we now comment on the scalability of our approach when introducing the running example in Section~3.}
 \end{enumerate}
@@
 We also previously denoted our frequent re-evaluation of the system RLD by ``inspections'',
-which was indeed not adequate, and have changed our wording and explanations.***}
+which was indeed not adequate, and we have changed our wording and explanations.}
 
@@
 
-\emph{***Agreed, this is one of the paragraphs that we changed substantially as mentioned in the answer to the previous question,
-and we hope that our argument is now more clear.***}
+\emph{Agreed, this is one of the paragraphs that we changed substantially as mentioned in the answer to the previous question,
+and we hope that our argument is now more clear.}
 %Again, we need to clarify that we do not use a \textbf{usual} degradation signal for the \textbf{system as a whole},
@@
 
-\emph{p.~3: ``where an operational cycle starts with a new system,
-and ends after this system has been replaced by an as good as new system''\\
-Section~5: ``An operational cycle begins with system start-up,
+\emph{We previously wrote on p.~3: ``where an operational cycle starts with a new system,
+and ends after this system has been replaced by an as good as new system'',
+and in Section~5 we wrote: ``An operational cycle begins with system start-up,
 and ends when either preventive maintenance is carried out, or a failure of the system occurs,
-with subsequent corrective maintenance.''\\
-*** I don't quite see the conflict, maybe mention in Sec~5 directly after that sentence that maintenance means replacing the whole system?
-And write on p.~3 ``begins with the start-up of a new system'', or even
-``An operational cycle spans the time between two consecutive system maintenance actions / replacements.
-We thus optimize the unit cost rate calculated over the time since the last system replacement.''
-?***}
+with subsequent corrective maintenance.''
+Since we assume that both preventive and corrective maintenance result in an (as good as) new system state,
+we don't quite see the conflict here.
+In our rewriting of the Introduction and Section~5,
+we now make more clear that in our approach, maintenance means replacing the whole system,
+indicating in Section~5.2 when this is a reasonable assumption.
+Furthermore, in the Introduction, we now write
+``An operational cycle spans the time between two consecutive system maintenance actions.
+We assume that in both preventive and corrective maintenance, the entire system is replaced or brought to an as good as new state,
+and thus optimize the unit cost rate calculated over the time since the last system replacement.''}
 
@@
 We now write ``condition-based maintenance (CBM)'' instead.
-We are sorry that we indeed defined RLD too late, and now define it at the first use on page~2.***}
+We are sorry that we indeed defined RLD too late, and now define it at the first use on page~2.}
 
@@
 
-\emph{*** yes, we should mention this in the introduction.***}
+\emph{Yes, we now mention this early in the Introduction, in a separate paragraph on page~2.}
 
@@
 
-\emph{We had placed Figure~2 (depicting the flowchart for the policy, now Figure~3) directly before Section~5.1 which explains the policy,
-and agree that it should appear during or after Section~5.1 to avoid confusion.}
+\emph{We had placed Figure~2 (depicting the flowchart for the policy, now Figure~3) directly before Section~5.1 which explains the policy.
+We agree that it should appear during or after the detailed description of the policy to avoid confusion,
+and now have placed it within Section~5.2.}
 

### 2017-05-26 cbm-rbd-paper.tex
SDFs comments part 4

@@
 
+To calculate the system RLD, we use the survival signature,
+which allows to deal with different types of components each having an individual failure time model
+(see Section~\ref{sec:sysrel}).
+Here we assume that components of different types fail independently,
+and that failure times of components of the same type are independent given the model parameters.
+
 In our new policy, there are three types of triggers to review the system:
@@
 we calculate the `optimal' next evaluation moment %moment for system replacement***
-based on minimizing the expected maintenance-related cost per per unit of time for the present operational cycle,
-where an operational cycle starts with a new system, and ends after this system has been replaced by a new system.
+based on minimizing the expected maintenance-related cost per unit of time for the present operational cycle.
+An operational cycle spans the time between two consecutive system maintenance actions.
+We assume that in both preventive and corrective maintenance, the entire system is replaced or brought to an as good as new state,
+and thus optimize the unit cost rate calculated over the time since the last system replacement.
 
@@
 %a flow chart for the policy is given in Figure~\ref{fig:procedure}.
-
+%
 The optimal time to system re-evaluation $\tausnow$ is determined based on $\Rsysnow(t)$
@@
 the probability of system failure is at most at some very low pre-determined level.
-
+%
 Section~\ref{sec:optim} then focuses on our choice for the component models and the resulting form for $\Rsysnow(t)$,
@@
 
-Replacement schemes that do not replace all components during maintenance
+Replacing not all components during maintenance
 would require to account for the different ages of components in the system
@@
 Such simultaneous failures will seriously influence the RLD and thus $\tausnow$.
-We will return to this in the conclusion (Section~\ref{sec:outlook}).
+We will return to this in the Conclusion (Section~\ref{sec:outlook}).
 %
@@
 
-Overall, it seems that CBM-cpu can play its adaptive strengths most effectively
+Overall, it seems that CBM-cpu can exert its adaptive strengths most effectively
 when prior assumptions are too pessimistic,

### 2017-05-26 answer-to-reviewers.tex
SDFs comments part 5 and done

@@
 \emph{By using $\naturals_0$ and not $\naturals$ as suggested by Reviewer 2,
-we intended to emphasize that the system RLD is evaluated for the first time directly at system startup time 0.
-***still keep it???***}
+we intended to emphasize that the system RLD is evaluated for the first time directly at system startup time 0,
+and thus prefer to keep using $\naturals_0$.}
 
@@
 
-\emph{***Our intention was to establish the cost rate function $g^{(\tnow)}(\cdot)$ as a generic function first
+\emph{Our intention was to establish the cost rate function $g^{(\tnow)}(\cdot)$ as a generic function first
 and to explain the details of its calculation later.
@@
 
+\smallskip
+
+\emph{In the revision of our manuscript, we have aimed to emphasize the pilot character of our approach,
+which should be seen as a first step towards a completely new class of CBM policies.
+We now discuss these and other restricting assumptions more prominently in the Introduction, Section~5, and in the conclusion (Section~8).}
+
 \begin{enumerate}
@@
 We agree that the assumption of a fixed known shape parameter is a serious limitation of our approach. 
-We added a comment on this in the conclusion,
+We have added a comment on this in the conclusion,
 repeating a comment from the beginning of Section~4, where we wrote:
@@
 For a practical application, one should indeed update the shape parameter as well,
-but in our view, adding this conceptually simple but notationally cumbersome feature would obstruct the goal of this manuscript.***}
+but in our view, adding this conceptually simple but notationally cumbersome feature would obstruct the goal of this manuscript.}
 
@@
 
-\emph{***We have added a short discussion related to the non-detection of component failures in the conclusion.
+\emph{We have added a short discussion related to the non-detection of component failures in the conclusion.
 We were mostly thinking of systems where a failure of a component is immediately eminent,
@@
 is usually reflected in a loss of current (detectable from the control centre),
-but proper health monitoring (going beyond working yes/no) is cumbersome and costly.
-***}
+but proper health monitoring (going beyond working yes/no) is cumbersome and costly.}
 
@@
 
-\emph{***new text by SDF in email 2017-04-05:\\
-{\scriptsize
-At first sight, replacing a complete system when only some parts of it are defective may seem strange.
+\emph{In the rewritten Section~5, we discuss this point now extensively in Section~5.2:
+``At first sight, replacing a complete system when only some parts of it are defective may seem strange.
 However, there are many real life examples, including from daily life.
@@
 may be optimal in case of a very strong economic dependence between the different parts of a system,
-e.g., due to a very high fixed set-up cost independent of the maintenance activities to be done
-as is the case of installations/facilities used in the generation and distribution of oil and gas.
-Note that often for safety reasons, the latter installations/facilities are monitored continuously.
-There also may be technical dependencies between parts of a system that may require combined replacement,
-like in the case of replacing the cassette of a bike often also requiring to replace the chain,
-or the tires of an airplane which are required to have the same thickness.
+e.g., due to a very high fixed set-up cost independent of the maintenance activities to be done,
+as is the case of installations used in the generation and distribution of oil and gas.
+Note that often for safety reasons, the latter installations are monitored continuously.
+There may be also technical dependencies between parts of a system that may require combined replacement:
+replacing the cassette of a bike often also requires to replace the chain,
+and the tires of an airplane are required to have the same thickness.
 But also complete systems are replaced because replacing one or more of its parts may take much longer,
-which may result in large production losses.
+which may result in big production losses.
 Another reason can be that there may be a high probability that when individual parts are replaced,
-other parts will be damaged/have to be damaged, requiring their replacement too.
-}\\
-***2 references to M.Shafiee et al (???)***\\
-***Agreed, this is another important simplifying assumption that we needed to make in this manuscript,
-which should be seen as a first step towards a completely new class of CBM policies.
-We originally mentioned this in the description of the policy but only at the end of Section~5.1,
-and commented on this in the fourth paragraph of the conclusion (Section~8), bottom of p.~25.
-In the introduction and the complete re-write of Section~5, we tried to emphasize the pilot character of our approach,
-mentioning the restricting assumptions more prominently.***}
+other parts will be damaged, requiring their replacement as well.''}
 \end{enumerate}
@@
 
-\emph{***We did mention right in the first paragraph of the discussion of Si et al.~(2013)
+\emph{We did mention right in the first paragraph of the discussion of Si et al.~(2013)
 that they use an empirical Bayesian framework,
-but now also state explicitely that the use of a Bayesian approach is a main reason why we consider this paper relevant for the discussion.}
+but we now also state explicitely that the use of a Bayesian approach is a main reason why we consider this paper relevant for the discussion.}
 
@@
 
-\emph{***??? rewrite???}
+\emph{Agreed. We now give a better definition of CBM, as
+``using information about the actual condition of the systems or components''.}
 
@@
 
-\emph{Agreed, we deleted that notion, and hope to be more clear now here.***}
+\emph{Agreed, we deleted that notion, and hope to be more clear now here.}
 
@@
 \textbf{in combination with the assumed sample model} (here: Weibull).
-Figure~6 (previously Figure~5)*** depicts prior predictive reliability functions for the priors in the case study of Section~6,
+Figure~6 (previously Figure~5) depicts prior predictive reliability functions for the priors in the case study of Section~6,
 as a way to visualize the choice of prior parameters given in Table~2 in the context of the Weibull model.
@@
 under the condition that the sample model is indeed correct.
-(Methods for checking the sample model are discussed, e.g., in
-Bayarri and Berger (2000), ``P values for composite null models'',
-Journal of the American Statistical Association 95(452): 1127–1142.)\\
-***add this reference to the paper?***}
+We now briefly discuss this issue in Section~6.1,
+also giving a reference to methods for checking the correctness of the sampling model.}
 
@@
 
-\emph{We have completely rewritten Section~5 and now address the role of $\delta$ in more detail there, as well as in the Introduction.
-***not sure what is meant by the second sentence.}
+\emph{We have completely rewritten Section~5 and now address the role of $\delta$ in more detail there, as well as in the Introduction.}
 
@@
 
-\emph{***Indeed, due to the weigthed average update in Equation (7),
+\emph{Indeed, due to the weigthed average update in Equation (7),
 it is possible that the parameter $y_k$ (the expected value of the Weibull scale parameter $\lambda_k$)
@@
 
-\emph{***??? In Equation~(15), the unit cost rate $\gnow(\tau)$ is defined as
+\emph{In Equation~(15), the unit cost rate $\gnow(\tau)$ is defined as
 $\gnow(\tau) = \E[g(\tau \mid \Tsysnow)]$,
@@
 \emph{We wrote ``$\gnow(\tau)$ gives the cost rate that we expect to incur [...]'',
-which includes the notion of mean via ``expect'', and we hope this is clear enough.*** (???)}
+which includes the notion of mean via ``expect'', and we hope this is clear enough.}
 \end{enumerate}

### 2017-05-26 cbm-rbd-paper.tex
SDFs comments part 5 and done

@@
 The unit cost rate is recalculated when components fail
-or at the end of every (very short) fixed inter-monitoring*** interval,
+or at the end of every (very short) fixed inter-evaluation interval,
 leading to a dynamic maintenance policy,
@@
 Such simultaneous failures will seriously influence the RLD and thus $\tausnow$.
-We will return to this in the Conclusion (Section~\ref{sec:outlook}).
+We will return to this in the conclusion (Section~\ref{sec:outlook}).
 %
@@
 but weighted averages over Weibull reliability functions according to the prior distribution over the scale parameter $\lambda_k$.
-We see that, e.g., the median prior expected failure times are
+Judging the adequacy of the prior parameter choices thus requires the sampling model to be correct.
+Methods for checking the sampling model are discussed, e.g., in \citet{2000:bayarri-berger}.
+Figure~\ref{fig:compprior1fig1} indicates that, e.g., the median prior expected failure times are
 $2.2$, $4.1$, $6.3$, and $3.1$ for type $C$, $H$, $M$, and $P$ components, respectively.
@@
 we simulated component failure times for five subsequent operational cycles for each simulation repetition.
-We thus can compare policies that carry information gained in one operational cycle to the next operational cycle
+We thus can compare policies that use information gained in previous operational cycles
+%We thus can compare policies that carry information gained in one operational cycle to the next operational cycle
 with policies that do not update component parameters at the end of an operational cycle.
-We also distinguish the condition-based maintenance policies with and without continuous parameter update
+We also distinguish condition-based maintenance policies with and without continuous parameter update
 as in Section~\ref{sec:examples}.
@@
 
-Here, most condition-based and all age-based policies cannot avoid system failures entirely.
+%Here, most condition-based and all age-based policies cannot avoid system failures entirely.
+Here, only CBM-cpu can avoid system failures entirely.
 Both CBM-epu and CBM-npu result in one system failure in the $20 \times 5 = 100$ system runs,
@@
 Extending the model to account for interval-censored failure times
-would allow to derive a condition-based maintenance policy with wider-spaced inspections,
-which could also determine the optimal moment for the next inspection of the system.
+would allow to derive a condition-based maintenance policy with wider-spaced inspections
+by determining the optimal moment for the next inspection of the system.
+%which could also determine the optimal moment for the next inspection of the system.
 %*** extend the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
@@
 This approach is described in \cite{2016:walter-coolen},
-resulting in sets of residual life distributions $\Rsysnow(t)$,
-%Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
-and this would lead to sets of expected operational cycle cost rate functions $\gnow(\tau)$.
+leading to sets of residual life distributions $\Rsysnow(t)$.
+Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
+%and this would lead to sets of expected operational cycle cost rate functions $\gnow(\tau)$.
 The determination of the (set of) optimal time(s) to maintenance $\tausnow$
@@
 (``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'').
-
+%
 Both authors would like to thank Frank Coolen for inspiring discussions

### 2017-05-26 resubmission-source-files/cbm-rbd-paper.tex
typo in abstract, tex source files folder

--- 2017-05-26 cbm-rbd-paper.tex
@@
 based on the status (working, defective) of all components within a system,
-as well as the reliability block diagaram of the system.
-%
+as well as the reliability block diagram of the system.
 By means of the survival signature,
@@
 we obtain a predictive distribution for the system survival time,
-%(also known as RUL, remaining useful life)
 also known as residual life distribution,
@@
 leading to a dynamic maintenance policy,
-since the aging of components and possible failures will change the cost-optimal moment of replacement in the course of time.
+since the ageing of components and possible failures will change the cost-optimal moment of replacement in the course of time.
 Via numerical experiments, some insight into the performance of the policy is given.
@@
 To determine the latter,
-we calculate the `optimal' next evaluation moment %moment for system replacement***
+we calculate the `optimal' next evaluation moment
 based on minimizing the expected maintenance-related cost per unit of time for the present operational cycle.
@@
 else we wait for the next planned evaluation moment.
-The reason behind this decision is that $\delta$ is taken as %usually is 
-%the shortest interval for which re-evaluation of the system RLD will show any difference***
-%the shortest inter-observation period that can be realized from a hardware point of view.
+The reason behind this decision is that $\delta$ is taken as 
 the shortest inter-evaluation period that can be realized from a hardware point of view. 
-%the time granularity according to which maintenance actions can be reasonably triggered***.
 To illustrate, for components with lifetimes amounting to a few days,
@@
 can be efficiently calculated using the survival signature.
-%We will show in Section~\ref{sec:adaptive-sysrel-weibull} how, for a certain choice of component model,
-%this method can be used to find the system reliability function $\Rsysnow(t)$ at current time $\tnow$ for a monitored system,
-%giving us the residual life distribution on which we base our adaptive maintenance policy.
 
@@
 Note that because of the `handbrake shortcut', this system cannot be described as a nesting of series and parallel subsystems.
-%This system is observed until time $\tnow$,
-%leading to censored observation of certain component lifetimes within the system.
 Our example system is deliberately kept quite simple for didactical reasons.
@@
 with four component types $M$, $H$, $C$ and $P$.}
-%Note that this system layout cannot be expressed as a nesting of series and parallel layouts.
-%The corresponding survival signature $\Phi(l_M,l_H,l_C,l_P)$ is given in Table~\ref{tab:brakesys-survsign}.}
 \label{fig:brakesys-layout}
@@
 can be calculated for a specific component model.
-%Section~\ref{sec:policy} will then show how an adaptive maintenance policy
-%can be derived for a monitored system based on such a current system residual life distribution.
 
@@
 and the current operational cycle up to $\tnow$.
-%***component model: weibull with fixed shape,
-%inverse gamma prior on scale parameter,
-%fix priors via expected lifetime and prior strength,
-%test data inclusion
-%with noninformatiove right-censoring
 %
@@
 resulting in a formula for $\Rsysnow(t)$.
-%***output is $\Rsysnow(t)$, the current (at time $\tnow$) system reliability function
-%(residual life distribution, RLD)
-%taking into account the current system state,
-%including the current ages of system components, 
-%and the lifetime histories of all component types,
-%including test data (if available) and expert assessments.
 
@@
 but focus instead on a generalization of the RLD model by using imprecise probability models for the component lifetimes.
-%These sets of priors can be seen as parametric P-boxes,
-%a certain kind of imprecise probability model \citep[see, e.g.,][]{itip}.
-%Such models allow for vague and partial prior specifications,
-%and provide sensitivity to prior-data conflict \cite[\S 2.2.3.3]{diss}.
 
@@
 in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
-%Here, we have added the prior parameters $a_k$ and $b_k$ in notation
-%to indicate that the prior over $\lambda$ depends on their values.
 
@@
 we use the parameters $\nk > 1$ and $\yk > 0$
-%(the upper index ${}\uz$ is used to indicate that these are prior parameters)
 because they are more easy to interpret.
@@
 where $\tautk = \sum_{i=1}^{e_k} (t_{k,i})^\beta + \sum_{i=1}^{c_k} (t^+_{k,i})^\beta$.
-%The upper index ${}\un$ indicates that these are posterior parameters resulting from an update with $n_k$ observations,
-%where we leave out the index $k$ for $n_k$ in the upper index to increase legibility.
 
@@
 \end{align}
-%where we have added the prior parameters $\nkz$ and $\ykz$ in notation
-%to emphasize that the posterior is a synthesis of prior information and data.
 As this posterior can be defined in terms of
@@
 and both types of observations can be used in the update step \eqref{eq:ig-update}.
-%Before we write this out formally in Section~\ref{sec:postpred},
-%we will first present how system reliability functions can be derived based on component models.
-
-%To keep notation simple,
-%we will below denote the parameters of the inverse Gamma distribution by $\nkz$ and $\ykz$,
-%regardless of them expressing expert information alone,
-%or stemming from the combination of expert information and test data.
 
@@
 the component models can be further updated
-using information gained from the current operational cycle as of $\tnow$: %run of the system until $\tnow$:
+using information gained from the current operational cycle as of $\tnow$:
 failure times of failed components,
@@
 We denote the resulting parameter values by $\nknow$ and $\yknow$.
-%(It is of course possible to update $\nkz$ and $\ykz$ directly to $\nknow$ and $\yknow$ if no test data is available.)
-%Furthermore, the fact that the components in the system that still function have reached the age $\tnow$
-%must be used when calculating the posterior predictive distribution.
 
@@
 the grid of prediction values can be very fine.
-%
-%Next, we will describe an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
-%a current residual life distribution,
-%first in general, then for our implementation,
-%where a fine discrete approximation of the RLD is obtained.
 
@@
 
-%***start with $\tausnow$???
 Now we can derive the adaptive and dynamic maintenance policy
@@
 which gives the time from $\tnow$ until the next optimal moment to re-evaluate the system.
-%Close to system startup, $\tausnow$ will be large;
-%but as components in the system age and some indeed fail over time,
-%$\tausnow$ will typically decrease.
 A preventive maintenance action is initiated
@@
 We describe this dynamic and adaptive maintenance policy in more detail in Section~\ref{sec:operationalprocedure}.
-%a flow chart for the policy is given in Figure~\ref{fig:procedure}.
 %
@@
 by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
-%An operational cycle begins with system start-up,
-%and ends when either preventive maintenance is carried out,
-%or a failure of the system occurs, with subsequent corrective maintenance.
 This criterion, as detailed in Section~\ref{sec:costrate},
-%only assumes that $\Rsysnow(t)$ is given,
 only assumes that a RLD is given,
@@
 and shows how $\tausnow$ is numerically determined in this situation.
-%Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
-%and a small simulation study is presented in Section~\ref{sec:sim}.
 
@@
 Triggers of type (1) are the evenly spaced planned evaluation time points $m\delta$, where $m \in \naturals_0$.
-%giving the time granularity at which maintenance actions can be reasonably initiated.***
-%Let $\tthresh$ be a threshold time span chosen for practical reasons.
-%used to decide when maintenance is initiated, i.e.,
-%a time span chosen to reflect operational practicalities.
 The times $m\delta$ are indicated by vertical tick lines on the time axis in Figure~\ref{fig:timeline},
@@
 the system health is evaluated by calculating $\tausnow$,
-the currently optimal time to re-evaluation, %$\tausnow$ is %calculated,
+the currently optimal time to re-evaluation,
 visualized by the thick horizontal bars in Figure~\ref{fig:timeline}.
-%The details of calculating $\tausnow$ are described in detail in Sections~\ref{sec:costrate} and \ref{sec:optim}.***
 For a type (3) trigger, the system health evaluation just corresponds to acknowledging that the system has failed.
-%/ to the diagnosis/insight*** of system failure.
-%and calculation of $\tausnow$ is 
 For triggers of type (1) and (2),
@@
 Failures that lead to the whole system failing (trigger 3) are marked by a filled circle.}
-%The calculation of $\tausnow$ is described in detail in Section~***.}
-%\begin{tikzpicture}\draw (0,0) circle (0.8mm);\end{tikzpicture}
 \label{fig:timeline}
@@
 i.e., all components in the system are (as good as) new and have not aged.
-An operational cycle ends when the system is either maintained preventively, %at time $\tnow + \tausnow$ (on an absolute time scale),
+An operational cycle ends when the system is either maintained preventively, 
 or the system fails, which triggers a corrective maintenance action.
@@
 
-%***Consider a set of evaluation time points $\tnow$.
 Consider a grid of planned evaluation time points $\{m \delta : m \in \naturals_0\}$,
-%where $m = 0, 1, 2, \ldots$,
-%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
 with $\delta$ a sufficiently small time increment.
@@
 $\tausnow$ is usually recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
-%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
 However, if a component $i$ of type $k$ fails before the next $\tnow$ on the grid,
@@
 frequent recalculation of $\tausnow$ is feasible,
-%Then, by evaluating the unit cost rate function $\gnow(\tau)$ (see Section~\ref{sec:costrate} below) on a discrete grid,
-%$\tausnow$ can be approximated with a simple grid search.
-%because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
-%and determine $\tausnow$ with a simple grid search.
-%Updating $\tausnow$ frequently is useful because,
 and it is useful because,
@@
 reducing uncertainty.
-%Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
-%as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T},
-%which gives a numerical example described in more detail in Section~\ref{sec:examples}.
-%An alternative would be to update $\tausnow$ only when a component fails,
-%but as a (near) real-time update of $\tausnow$ is possible and useful,
-%as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
-%
-%As can happen for an age-based policy, the derived $\gnow(\tau)$ may also be monotonely decreasing.
-%In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
-%This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
-%but also capable of indicating when corrective maintenance is the better option.
-%i.e., capable of choosing the maintenance policy.
 
@@
 In both cases, we decide to maintain the system preventively
-when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate the system RLD, %$\tausnow$,
+when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate the system RLD,
 since otherwise, in waiting to the next planned evaluation time,
 one would exceed the optimal system failure risk 
-as determined by the trade-off made via $\gnow(\cdot)$. %***drop $\gnow(\cdot)$ here, like: ...trade-off that results in $\tausnow$.
+as determined by the trade-off made via $\gnow(\cdot)$.
 When $\tausnow$ is instead further in the future than the next planned evaluation time,
@@
 including the loop back to system startup that starts a new cycle as a dashed arrow.}
-%For simplicity of presentation, we exclude the possibility that several component failure times
-%happen between the evaluation times $(m-1) \delta$ and $m \delta$.}
 \label{fig:procedure}
@@
 by updating the parameters $\nk$ and $\yk$ accordingly,
-%using failure and censoring times as of the end of the cycle.
 such that $\nkz$ and $\ykz$ for the next operational cycle
 account for the (censored) lifetimes observed during the previous operational cycles.
-%We assume that both planned and unplanned maintenance action takes negligible time,
-
-%
-%As we use a one-cycle criterion, the time both preventive and corrective maintenance actions require
-%does not matter directly for the determination of $\tausnow$.
-%Longer downtime and other negative effects of corrective maintenance
-%are instead accounted for through the costs parameters $c_p$ and $c_c$ used in the trade-off leading to $\tausnow$,
-%as described next.
 
@@
 in CBM literature \citep[e.g.,][]{2013:si-et-al,2011:kim-et-al}.
-%we use the one-cycle cost rate as it is the most appropriate for our situation,
-%where $\tausnow$ changes frequently.
 
@@
 with support $\{t \in \reals : t > \tnow \}$.
-%In particular, we have $\fsysnow(t) = 0$ for all $t \le \tnow$.
 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{ghist1fig2T}
+%\includegraphics[width=\textwidth]{ghist1fig2T}
+\includegraphics[width=\textwidth]{fig4}
 \caption{System reliability and unit cost rate functions for $\tnow = 0,2,4,6,8$
@@
 Note that for the integral in \eqref{eq:gtnowtau} to exist,
-%$\E[1/\Tsysnow \mid \Tsysnow > \tnow]$ must exist,
 $\E[1/(\Tsysnow - \tnow)]$ must exist,
 which is a condition for $\fsysnow(\tnow + \theta)$ for values of $\theta$ close to $0$ \citep{2006:coolen-schrijner-coolen}.
-%This restriction probably plays a role in the CBM literature's reluctance to adopt the one-cycle criterion.
 For our approach, however, this condition is not relevant,
@@
 incorporating all that is known at current time $\tnow$.
-%The lower index $\tnow$ of $\tausnow$ emphasizes that
-%depends on $\tnow$, and also on the history of the system.
-%illustrates the derivation of $\tausnow$ .
-%Minimizing $\gnow(\tau)$ leads to $\tausnow$,
-%the optimal moment of maintenance on a prospective time scale.
 The minimal expected operational cycle cost rate $\gstarnow := \gnow(\tausnow)$ corresponding to $\tausnow$
@@
 that we can expect to attain.
-%attainable for the span of the remaining lifetime of the system,
-%i.e., for what happens beyond current time $\tnow$.
-%$\gstarnow$ increases over time since 
-%***Also of interest is the total expected cost rate as of $\tnow$, denoted by $\gtotalnow$.
-%This gives the expected unit cost rate calculated over the full time since system start-up,
-%under the assumption that maintenance is scheduled for $\tstarnow := \tnow + \tausnow$.
 $\gstarnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time period.
@@
 Note that common cause failures, i.e., failures of several components at the same time due to a shared root cause,
-are currently not accounted for in our model. %, as we assume component failures to be mutually independent
-%given the component model parameters.
+are currently not accounted for in our model.
 Such simultaneous failures will seriously influence the RLD and thus $\tausnow$.
 We will return to this in the conclusion (Section~\ref{sec:outlook}).
-%
-%Next, we describe how to numerically evaluate \eqref{eq:gtnowtau} and determine $\tausnow$
-%for our choice of component model.
 
 \begin{figure}
-%\centering
-\includegraphics[width=\textwidth]{tauhist1fig2T}
+%\includegraphics[width=\textwidth]{tauhist1fig2T}
+\includegraphics[width=\textwidth]{fig5}
 \caption[t]{$\tausnow$, $\tstarnow = \tnow + \tausnow$ and $\gstarnow = \gnow(\tausnow)$
-%and the total unit cost rate $\gtotalnow$ as functions of $\tnow$
 for the system depicted in Figure~\ref{fig:brakesys-layout},
@@
 covering the time span from $\tnow$ to some horizon time $\tnow + t_h$.
-%(The choice of $t_h$ is discussed in more detail below.)
 We calculate $\gnow(\tau)$ on the same grid,
@@
 where $\fsysnow(t)$ is calculated via differences of $\Rsysnow(t)$.
-%$\gnow(\tau)$ is likewise evaluated on a dense grid,
-%and $\tausnow = \arg\min \gnow(\tau)$ is determined as the minimum over the grid.
 
@@
 but generally should reach far enough into the tail of $\Rsysnow(t)$
-such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
+such that $\gnow(\tau)$ is not cut off before it reaches its minimum.
 Note that according to \eqref{eq:gtnowtau},
@@
 allowing for a near real-time update.
-%
-%***calculations in \textsf{R} can be vectorized and are thus fast.
-%***if min $\gnow(\tau)$ at $\tnow + t_h$, corrective maintenance is optimal: policy switch!
-%***if $\tau_*^{(\tnow)}$ larger than certain horizon, than conclude corrective policy
 
@@
 
-The cost parameters are chosen as $c_c = 1$, $c_p = 0.2$, % in all examples,
+The cost parameters are chosen as $c_c = 1$, $c_p = 0.2$,
 i.e., corrective maintenance is five times more costly than preventive maintenance.
@@
 but corrective maintenance will not be avoided at all cost.
-%Indeed, $c_u / c_p = 5$ means that risking corrective maintenance is worthwile
-%if one can expect to run the system five times longer
-%than the preventive maintenance interval.
 
@@
 \caption{Prior parameters for the four component types as used in the numerical examples.}
-%The corresponding expected failure behaviour is visualized in Figure~\ref{fig:compprior1fig1}.}
 \label{tab:priorparams}
@@
 for the case that an expert's assessment of the component MTTF turns out to be inadequate.
-%things could look different for stronger expert information!
 When $\nkz$ and $\ykz$ also include test data,
@@
 \centering
-\includegraphics[width=\textwidth]{compprior1fig1}
+%\includegraphics[width=\textwidth]{compprior1fig1}
+\includegraphics[width=\textwidth]{fig6}
 \caption{Prior predictive reliability functions corresponding to the values from Table~\ref{tab:priorparams},
-%for the four component types of the system depicted in Figure~\ref{fig:brakesys-layout},
 showing the expected failure behaviour.}
@@
 with small upward jumps at the failures of $P_2$ and $P_3$.
-%so the drops in $\tausnow$ do not entirely outweigh the higher likelihood of system failure
-%due to the failure of these components.
-%\textbf{***show $\Rsysnow(\tausnow)$???}
 At $\tnow = 6$, the expected operational cycle cost rate is $0.033$,
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{tauhist1fig3T}
+%\includegraphics[width=\textwidth]{tauhist1fig3T}
+\includegraphics[width=\textwidth]{fig7}
 \caption{Illustration of the gains due to the parameter update at each $\tnow$,
@@
 and that a failed component changes the system layout.
-%***so dynamic but not adaptive?***
 We see that $\tausnow$ (left panel) is decreasing more quickly in the no update case,
@@
 and maintenance is scheduled too early,
-%$\tausnow$ (left panel) is consistently lower for the non-adaptive algorithm,
-%same with $\tstarnow$ (center panel).
-%This is because the adaptive algorithm recognizes that system components are more reliable than expected,
 leading to higher expected operational cycle cost rates $\gstarnow$ (right panel).
@@
 Overall, prior assumptions are reasonably in line with observed failure behaviour.
-%with a slight tendency to earlier failures.
 Consequently, the difference between the continuous update case and the no update case is small,
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{tauhist2fig3T}
+%\includegraphics[width=\textwidth]{tauhist2fig3T}
+\includegraphics[width=\textwidth]{fig8}
 \caption{Effect of the continuous parameter update for the second failure history ($C_2 = 1$, $C_2 = 3$, $P_2 = 0.5$, $P_3 = 1.5$)
 which is more or less in line with expectations.
-%containing slightly early failures of type $P$ components.
 With observed failure behaviour more or less in line with expectations,
@@
 
-%The third failure history contains very late failures for all component types
-%by assuming $C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$,
-%and following the system until $\tnow = 14$.
-%The late failure times for type $C$ components are especially surprising,
-%with the prior predictive reliability being $0.01$ at time $10$
-%(see top left panel of Figure~\ref{fig:compprior1fig1}).
-%Here, the situation is more extreme than in the first failure history.
-%Figure~\ref{fig:tauhist3fig3} shows that, after a first short dip,
-%$\tausnow$ for the continuous update model steadily increases until the first observed failure at $\tnow = 8$.
-%For the model without update, $\tausnow$ steadily decreases instead,
-%ignoring any information on component behaviour to be gained during the current system run.
-%Assuming $\tthresh = 0.5$, the method without parameter update would recommend to maintain the system preventively at $\tnow = 8.4$,
-%with only $P_2$ having failed by then, and all other components up and running,
-%corresponding to a considerable waste of component lifetime.
-%
-%\begin{figure}
-%\includegraphics[width=\textwidth]{tauhist3fig3}
-%\caption{Effect of the continuous parameter update for the third failure history,
-%containing very late failures for all component types ($C_2 = 10$, $C_3 = 12$, $H = 14$, $P_2 = 8$, $P_3 = 9$).}
-%\label{fig:tauhist3fig3}
-%\end{figure}
-%
 The third failure history contains very early failures
@@
 much higher than for our policy.
-%expected cycle costs are underestimated without update***
 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{tauhist4fig3T}
+%\includegraphics[width=\textwidth]{tauhist4fig3T}
+\includegraphics[width=\textwidth]{fig9}
 \caption{Effect of the continuous parameter update for the third failure history,
@@
 
-%A systematic study based on simulation failure times is subsequently presented in Section~\ref{sec:sim}.
 We conducted a small simulation study to illustrate the performance of our policy
@@
 We thus can compare policies that use information gained in previous operational cycles
-%We thus can compare policies that carry information gained in one operational cycle to the next operational cycle
 with policies that do not update component parameters at the end of an operational cycle.
@@
 We compare these policies by three simple performance measures,
-calculated for each repetition. %, which contains five operational cycles.
+calculated for each repetition. 
 $\esys$ is the number of system failures that occured when applying the policy,
@@
 taken over the five operational cycles per repetition.
-%(I called this 'cycle length' before),
 $\bar{g}$ is the mean realized operational cycle cost rate obtained over the five operational cycles.
@@
 divided by the sum of the five realized operational cycle lengths.
-%This is a weighted average of the realized operational cycle cost rate for each of the five operational cycles,
-%with weights proportional to the corresponding realized operational cycle length.
-%This equals
 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{br1sim1fig5Tt01ac}
+%\includegraphics[width=\textwidth]{br1sim1fig5Tt01ac}
+\includegraphics[width=\textwidth]{fig10}
 \caption{Simulation study with 20 repetitions, where each repetition consists of 5 subsequent operational cycles.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{br1sim2fig5Tt01ac}
+%\includegraphics[width=\textwidth]{br1sim2fig5Tt01ac}
+\includegraphics[width=\textwidth]{fig11}
 \caption{Simulation study with 20 repetitions, where each repetition consists of 5 subsequent operational cycles.
@@
 i.e., $\lambda_k = 0.5 \ykz$ for all $k =$ C, H, M, P.
-%($0.5 \times$ MTTF) than expected.
 The results are depicted in Figure~\ref{fig:br1sim2fig5Tt01}.
 
-%Here, most condition-based and all age-based policies cannot avoid system failures entirely.
 Here, only CBM-cpu can avoid system failures entirely.
@@
 System runtimes are less variable for the age-based policies
-since they do not use the current system structure information, %available information on the component level,
-i.e., which components have failed and which not. %during operational cycles
+since they do not use the current system structure information, 
+i.e., which components have failed and which not.
 System runtimes are more variable for the condition-based policies,
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{br1sim3fig5Tt01ac}
+%\includegraphics[width=\textwidth]{br1sim3fig5Tt01ac}
+\includegraphics[width=\textwidth]{fig12}
 \caption{Simulation study with 20 repetitions, where each repetition consists of 5 subsequent operational cycles.
@@
 while also performing well when prior assumptions are correct or too optimistic.
-%This means that experts may confidently tend towards pessimistic specifications
-%of the component mean time to failures $\yzk$.
-
-% ------------- old overview figures ----------------------------------
-\iffalse
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{br1sim1fig5}
-\includegraphics[width=0.5\textwidth]{br1sim2fig5}
-\includegraphics[width=0.5\textwidth]{br1sim3fig5}
-\includegraphics[width=0.5\textwidth]{br1sim4fig5}
-\caption{***Simulation study with ***prospective costrate criterion***, $\tthresh = 0.5$.
-TL: $\lambda_k =     \ykz$,
-TR: $\lambda_k = 0.5 \ykz$,
-BL: $\lambda_k = 2   \ykz$,
-BR: $\lambda_k = 0.2 \ykz$}
-\label{fig:simprospcostrate05}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{br1sim1fig5T}
-\includegraphics[width=0.5\textwidth]{br1sim2fig5T}
-\includegraphics[width=0.5\textwidth]{br1sim3fig5T}
-\includegraphics[width=0.5\textwidth]{br1sim4fig5T}
-\caption{***Simulation study with ***total costrate criterion***, $\tthresh = 0.5$.
-TL: $\lambda_k =     \ykz$,
-TR: $\lambda_k = 0.5 \ykz$,
-BL: $\lambda_k = 2   \ykz$,
-BR: $\lambda_k = 0.2 \ykz$}
-\label{fig:simtotalcostrate05}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt01}
-\includegraphics[width=0.5\textwidth]{br1sim2fig5Tt02}
-\caption{***Simulation study with ***total costrate criterion***, early failures ($0.5 \times$ MTTF),
-$\tthresh = 0.1$ (left) and $\tthresh = 0.2$ (right).}
-\label{fig:simtotalcostrate0102}
-\end{figure}
-\fi
 
@@
 by determining the optimal moment for the next inspection of the system.
-%which could also determine the optimal moment for the next inspection of the system.
-%*** extend the model for inspection-based CBM (if no repair necessary, find optimal timing of next inspection),
-%we would need to add interval-censored data (failure has happened between last and current inspection)
 
@@
 the system RLD $\Rsys(t)$ needs to account for such failures when they are possible.
-%This needs to be implemented on the level of component models,
-%specifically $P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big)$ 
-%(not a product anymore if common-case failures can affect several component types at once).
 When common cause failures can affect several component types at once,
@@
 However, computational complexity increases with the number of component types,
-%and the conceptual algorithmic advantage of the survival signature vanishes
-%when each component forms its own type
 so it seems most promising to replace batches of components,
 or all components of one type.
-%*** study other replacement schemes, e.g., replacing only failed components:
-%when repaired/replaced components are present in system,
-%then one needs to use actual ages (and not time since system startup) in parameter update,
-%introduces new component type for $\Rsysnow(t)$ calculation but with same posterior parameters as unreplaced component type.
-%Repaired/replaced components require the creation of a separate type in the survival signature decomposition
-%and thus the calculation of separate posterior predictive probabilities
-%$P(C^k_t = l_k \mid \nkz,\ykz,\vectknow)$,
-%which use, however, the same hyperparameter learning (using actual component ages) as the `parent type'.
 
@@
 in form of the posterior predictive distributions derived in Section~\ref{sec:postpred}.
-%since the calculation of $\Rsysnow(t)$ involves
 
@@
 Consequently, we would obtain a set of expected operational cycle cost rate functions $\gnow(\tau)$.
-%and this would lead to sets of expected operational cycle cost rate functions $\gnow(\tau)$.
 The determination of the (set of) optimal time(s) to maintenance $\tausnow$

### 2017-06-13 cbm-rbd-paper.tex
typos, user license for sharing of accepted manuscript

@@
-\documentclass[authoryear]{elsarticle}
+\documentclass[authoryear]{myelsartcl}
 
@@
 i.e.\ that the failure behavior of the system,
-in essence its relibability function, does not change over time,
+in essence its reliability function, does not change over time,
 and that the same policy with the same parameter values is used for a statistically long enough period of time.
@@
 
-There are several aspects in our modelling that warrant further investigation.
+There are several aspects in our modeling that warrant further investigation.
 In this paper, we assume that component failure times are observed precisely via monitoring.
@@
 We think that by combining ideas from \cite{2015:coolen-coolen-maturi} and \cite{Troffaes2014a},
-the proposed policy could be extended to accomodate common cause failures.
+the proposed policy could be extended to accommodate common cause failures.
 
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 
